### 2014-11-18 paper.tex
Add abstract

\documentclass[conference]{IEEEtran}

\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{Robust Energy-Aware Routing with Uncertain Traffic Demands}

\author{\IEEEauthorblockN{Heng Lin}
\IEEEauthorblockA{Tsinghua University}
\and
\IEEEauthorblockN{Mingwei Xu}
\IEEEauthorblockA{Tsinghua University}
\and
\IEEEauthorblockN{Yuan Yang}
\IEEEauthorblockA{Tsinghua University}}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Energy conservation has become a major challenge to the Internet. In existing approaches, a part of line cards are switched into sleep mode for energy conservation, and the routing is configured carefully to balance energy saving and traffic engineering golas, such as the maximum link utilization ratio (MLUR). Typically, traffic demands are used as inputs, and routing is computed accordingly. However, accurate traffic matrices are difficult to obtain and are changing frequently. This makes the approaches difficult to implement. Further, the routing may shift frequently, and is not robust to sudden traffic changes.
In this paper, we propose a different approach that finds one energy-aware routing robust to a set of traffic matrices, in particular, to arbitrary traffic demands. Such a routing without energy consideration is known as the demand-oblivious routing, and is well studied. However, the problem becomes much more challenging when energy conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance ratio with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio, and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve the problem in two phases. REAR select sleeping links based on extended algebraic connectivity, and compute the routing based on a classical demand-oblivious routing algorithm. We evaluate our algorithms on real and synthetic topologies. The simulation results show that REAR can save XX\% of line card power while the performance ratio is less than XX.
\end{abstract}

\IEEEpeerreviewmaketitle

\section{Introduction}
We aim to find the ``robust'' route for all possible traffic matrix, not only consider performance but also energy 
consumption in network.

\section{Motivation}
Suppose two hosts named host A and host B, and there are three links between 
them, respectively, capacity with 2M, 3M and 5M. Now demands come, with 1M from A to B. we regard the capacity 
as the power of the link, and the minimum maximum utilization of network links as a metric of the network performance. 
There are two directions for operating this example. One consider the min power consumption except for the 
utilization, it is obviously that we should close the larger power consuming links, such as the 5M and 3M links, and 
all the traffic go through the 2M link. In this way, the min max utilization of network is 0.5 and the power consuming 
is 2 units (means the power difference come from the link mainly). The other consider the power except for the 
utilization reversely, so we should split the 1M traffic to three parts, 0.2M across 2M link, 0.3M across 3M link and 
0.5M across 5M, consequently with a min max utilization of 0.1, but the power is 10 units however.

Two directions mentioned above both are extremely single-consideration. Previous researchers solve the problem more 
considerable, include ``GreenTE'' and ``a\%-green is engouh''. The former set a threshold of min max utilization, 
close links as many as possible to achive the most power saving. And the latter one set a destination of the power 
saving, calculate optimal route for get the min max utilization. Two work have their restriction, which both need a 
specific traffic matrix that as base of their optimization.

But the need of precise current traffic matrix shound be carefully checked. Although some researcher contribute to this 
area, the real precise traffic matrix still be a challenge. Take a step back, the dynamic of traffic matrix is more 
diffcult even if we obtain the precise current one. Futhermore, ISP will not want to change their route policy 
frequently, as it will result in other route failure possiblly. So our question is that : Is there exist a route both 
satisfy power and utilization requirement for any traffic matrix given?

David Applegate propose a method for obtain a route wihich is ``robust'' to variations in demands for a specific network topology.

\section{Model}
We model the network as a undirected graph $G = (V, E)$, where $V$ is the set of vertices (i.e., routers and end hosts), 
and $E$ is the set of links (either link between routers or router and end-host). In graph $G$, two vertices $u$ and $v$
are called connected if $G$ contains a path from $u$ to $v$. Then We say graph $G$ is connected, if and only if 
every pair of vertices in the graph is connected.

Let $\theta(G) = \{ (V, E - \{ e \}) | e \in E \}$ denote the network set after closing/removing the link $e$ from
$G$. Then, choosing the connected graph from $\theta(G)$ to consist a new set, denoted by 
$\Theta(G) = \{G | G \in \theta(G) \& \& G is connected\}$. We call $\Theta(G)$ as successor of $G$.

A $traffic matrix$ (abbreviation as TM below) is the set of traffic of each Origin-Destination(OD) pair in 
network $G$, and a $routing$ specifies how traffic of each OD pair is routed across the network. Usually, there are 
multiple paths for each OD pair and each path routes a fraction of the traffic. Let $m$ denote the $traffic matrix$, 
which can be represented by a set of trinary group like $(a, b, d_{ab}$, where $a$ and $b$ is the origin and 
destination of pair respectively, $d_{ab}$ is the traffic demand of the OD pair.

Let $r$ denote the $routing$ mentioned above, which is specified by a set of values $f_{ab}(i,j)$ that specifies the 
fraction of demand from $a$ to $b$ that is routed on the link $(i,j)$. So an OD pair contribute to the traffic of 
link $(i,j)$ is $d_{ab}f_{ab}(i,j)$, and all the traffic across link $(i,j)$ can be calculated as :
\begin{equation}
	\sum_{(a,b,d_{ab}\in m)} d_{ab}f_{ab}(i,j)
\end{equation}

Futhermore, we define the utilization of link as traffic acorss the link divide capacity of the link, as ;
\begin{equation}
	u_{ij} = \frac{\sum_{a,b} d_{ab}f_{ab}(i,j)}{cap_{ij}}
\end{equation}
where $cap_{ij}$ si the capacity of the link $(i,j)$.

A common metric for the performance of a given routing with respect to a certain TM is the $maximum link utilization$.
This is the maximum utilization of link over all ones, Formally, the maximum link utilization of a routing $r$ on 
TM $m$ in network $G(V,E)$ is 
\begin{equation}
	U_{r, m, G} = \max_{(i,j)\in E} u_{ij}
\end{equation}

The $optimal routing$ in all the possible route $R$ for network $G$ is a routing which minimize the maximum utilization,
the minimum maximum utilization is called optimal utilization, can be represented by :
\begin{equation}
	OptU_{m, G} = \min_{r\in R} U_{r, m, G}
\end{equation}

The $performance ratio$ of a given routing $r$ on a given TM $m$ and a given network $G$ meaures how far from being 
optimal, it is defined as the maximum link utilization divided by optimal utilization on the $m$ and $G$, as following : 
\begin{equation}
	P(\{ r \},\{ m \}, G) = \frac{U_{r,m,G}}{OptU_{m,G}}
\end{equation}

We now extend the definition of performance ratio of a routing to be with respect to a set of TMs $M$. 
\begin{equation}
	P(\{ r \}, M, G) = \max_{m\in M} P(\{ r \}, \{ m \}, G)
\end{equation}

Obviously, the optimal routing in routing set $R$ for the set of TMs is a routing which minimize the extended 
performance ratio, such as :
\begin{equation}
	P(R, M, G) = \min_{r\in R} P(\{ r \}, M, G)
\end{equation}

I.E. the routing $r$ which arrive at the value of $P(R,M,G)$ is the most ``robust'' routing for the TM set $M$ 
in the network $G$, and if the $M$ range enough, we say that the ``robust'' routing is independent of specific TM.

But definition of ``robust'' above will not work well for next situation. Let us take a cycle network topology $C$ as 
an simple example, in which we should choose one link to close. Before link cutting, the $P(R, M, C)$ is 
approximate to 2, but no matter which link is chosen to close, the cycle network will change to a line network $L$. 
Obviously, the $P(R, M, L)$ will always equal to 1. It means that there is no difference from removing which link,
But the contradiction here is that, the choice for which link should be removed is really different because the 
links are not always the same with each other, such as their capacity.

The reason for the ``fake robust'' is that, the routing in the successor graph (i.e. $L$ in above example) become 
unique, the current routing always be the optimal routing. More generally, we should make a little modification
for the $performance ratio$ as the network self changes.

Let $G$ be the origin network, and the $G^* \in \Theta(G)$ be the successor network from $G$ after closing/removing
some link, we define $performance ratio between different graphs$ as the performance ratio of successor graph divide 
the optimal performance ratio of father graph, like :
\begin{equation}
	P(R^*, \{ m\}, G, G^*) = \min_{r \in R^*} \frac{U_{r,m,G^*}}{OptU_{m,G}}
\end{equation}
where $R^*$ is the routing set on network $G^*$.

And question is that how to meaure a successor network topology is ``robust'' enough for the TM set $M$ when 
pruning is proceeding. We consider the worst situation, namely the successor network topology has its maximum
performance ratio when the TM is $m \in M$, described as following :
\begin{equation}
	P(R^*, M, G, G^*) = \max_{m \in M} P(R^*, \{ m \}, G, G^*)
\end{equation}

Now we can say that, if a successor network arrive the minimum performance ratio, it is the ``robust'' successor 
network graph. Formally, we define the performance ratio as $optimal successor performance ratio$ :
\begin{equation}
	P^{*}(M, G) = \min_{G^* \in \Theta(G)} P(R^*, M, G, G^*)
\end{equation}
where $M$ is the TM set, and $R^*$ is routing set.

If the scope of $M$ is large engouh, the optimal successor network graph is alwo independent from specific TM.

\subsection{Model Example}
We will take an example to explain how to choose the link to close in our experiment.
Three hostes include : A, B, C, Three links are with repectively capacity of 3M, 4M and 2M. For simpleness, we suppose 
there are two TM : ${(A,B,2M), (A,C,1M)}, {(A,B,1M), (A,C,1M)}$.For each traffic matrix, the optimal route is 
obvious, we will trace 2M from A to B across the lower link and trace the 1M from A to C across the upper one 
for the first traffic matrix, whose maximum link utilization is 0.5. we will trace all the traffic acorss the
lower link for the second traffic matrix, whose maximum link utilization is 0.5 as well.

Now for some reason, we will choose one link to shut down for power saving without lose connection of the network. 
There are two choice, remove either the upper link or the lower link. Let us take a little calculation: when 
remove the upper one, we should change all the traffic acorss the lower link, as a result, in the first  
TM the maximum link utilization is 0.75 and the second is 0.5; when close the lower link, we should trace all the 
traffic acorss the upper link, in the first TM the link utilization is 1 and the other is 0.667. 
So according to our theory, the $P^{*}(M, G)$ should be 1.5 and the optimal successor network topology will be
the one which 3M link is closed.

\section{Conclusion}
The conclusion goes here.

\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}

### 2014-11-20 paper.tex
Add algorithm first phase to paper

@@
 \begin{abstract}
-Energy conservation has become a major challenge to the Internet.
-In existing approaches, a part of line cards are switched into sleep mode for energy conservation, and the routing is configured carefully to balance energy saving and traffic engineering golas, such as the maximum link utilization ratio (MLUR).
-Typically, traffic demands are used as inputs, and routing is computed accordingly.
-However, accurate traffic matrices are difficult to obtain and are changing frequently.
-This makes the approaches difficult to implement.
-Further, the routing may shift frequently, and is not robust to sudden traffic changes.
-In this paper, we propose a different approach that finds one energy-aware routing robust to a set of traffic matrices, in particular, to arbitrary traffic demands.
-Such a routing without energy consideration is known as the demand-oblivious routing, and is well studied.
-However, the problem becomes much more challenging when energy conservation is involved.
-To overcome the challenges, we first define a new metric, namely oblivious performance ratio with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when certain energy conservation requirement is satisfied.
-We model the problem of minimizing the performance ratio, and analyze the lower and the upper bounds.
-Then, we propose Robust Energy-Aware Routing (REAR) to solve the problem in two phases.
-REAR select sleeping links based on extended algebraic connectivity, and compute the routing based on a classical demand-oblivious routing algorithm.
-We evaluate our algorithms on real and synthetic topologies.
-The simulation results show that REAR can save XX\% of line card power while the performance ratio is less than XX.
+Energy conservation has become a major challenge to the Internet. In existing approaches, a part of line cards 
+are switched into sleep mode for energy conservation, and the routing is configured carefully to balance energy saving 
+and traffic engineering goals, such as the maximum link utilization ratio (MLUR). Typically, traffic demands are 
+used as inputs, and routing is computed accordingly. However, accurate traffic matrices are difficult to obtain and 
+are changing frequently. This makes the approaches difficult to implement. Further, the routing may shift 
+frequently, and is not robust to sudden traffic changes.
+
+In this paper, we propose a different approach that finds one energy-aware routing robust to a set of traffic 
+matrices, in particular, to arbitrary traffic demands. Such a routing without energy consideration is known as 
+the demand-oblivious routing, and is well studied. However, the problem becomes much more challenging when energy 
+conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance 
+ratio with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when 
+certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio, 
+and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve 
+the problem in two phases. REAR select sleeping links based on extended algebraic connectivity, and compute the 
+routing based on a classical demand-oblivious routing algorithm. We evaluate our algorithms on real and 
+synthetic topologies. The simulation results show that REAR can save XX\% of line card power while the performance 
+ratio is less than XX.
 \end{abstract}
@@
 
+\section{Algorithm}
+In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links 
+should be sleeping from the origin topology based on extended algebraic connectivity, then compute the robust 
+routing by demand-oblivious routing algorithm.
+
+\subsection{First Phase}
+
+\subsubsection{Extend Algebraic Connectivity}
+Network topology is represented by $G = (V, E)$ as mentioned in Model section, where $V$ is the set of vertices
+and $E$ is the set of links. We say $A(G)$ is the adjacency matrix of $G$, which include information for which
+vertices of the graph are adjacent to which other vertices. $A(G)$ is a $N \times N$ matrix, where
+$N = |V|$ and non-diagonal entry $a_{ij}$ is the number of edges from vertex $i$ to vertex $j$, in this paper,
+$a_{ij}$ always be 1 if $(i,j) /in E$ otherwise 0. And we stipulate the diagonal element $a_{ii}$ be 0.
+We say $D(G)$ is the degree matrix of $G$, which is a diagonal matrix and diagonal entry $d_{ii}$ denote 
+the degree of node $i$. It is obvious that there is $d_{ii} == \sum_{j} a_{ij}$.
+We define Laplacian matrix, denoted by $L(G)$ of $G$ as :
+\begin{equation}
+	L(G) = D(G) - A(G)
+\end{equation}
+where $D(G)$ is the degree matrix and $A(G)$ is the adjacency matrix.
+
+In the mathematical field of graph theory, the algebraic connectivity of a graph $G$ is the second-smallest
+eigenvalue of the Laplacian matrix. This eigenvalue is greater than 0 if and only if $G$ is connected, and 
+it measures the connectivity of graph, the greater of which, the more connective of graph.
+
+As far as we know, 
+algebraic connectivity regard every link the same, without considering the capacity of each one, but it is 
+ridiculous in network. It is easy to see, link with greater capacity is more important than the same one
+with lower capacity. So we extend the algebraic connectivity definition by following ways:
+
+1) We change the adjacency matrix from binary-matrix to float-matrix, i.e. if $(i,j) \in E$ we set the $a_{ij}$
+with the capacity of link $l_{ij}$ instead of value 1.
+2) Degree matrix is not ever the denotation for the degree of nodes, but the in-out flows of nodes, we still
+use the equation: $d_{ij} == \sum_{j} a_{ij}$
+3) No modification for Definition of Laplacian matrix
+
+We calculate new extend algebraic connectivity from the new Laplacian matrix, denoted by $\lambda_2(G)$.
+
+Topology always have different algebraic connectivity values for their difference in connectivity property.
+When we remove/sleep one link $l$ from graph $G$, new graph is described as $G^*$, we defined the difference of 
+algebraic connectivity as :
+\begin{equation}
+	\Delta_l = \lambda_2(G) - \lambda_2(G^*)
+\end{equation}
+where $\lambda_2(G)$ and $\lambda_2(G^*)$ is algebraic connectivity of $G$ and $G^*$ respectly.
+
+Clearly, $\Delta_l$ is always greater than 0, because graph will always lose connectivity when link is removed.
+Further more, some link will play a more important role in the connectivity of graph, such as the backbone link 
+of network topology. And we say a link $l$ have more impact on algebraic connectivity if $\Delta_l$ is greater.
+
+\subsection{First Phase Description}
+REAR remove/sleep as many links as possible with not losing much connectivity of graph. Originly,  we should
+calculate impact of all the links and sleep the lowest one on the graph, then repeat calculate and remove
+process until arrive some specific threhold. Obviously, it is NP-Hard, so there is a heuristic algorithm.
+
+For the origin graph, we calculate the impact of every link as $\Delta_{l_i}$ , and then sort these values
+from small to big, output ordered list denoted as $\Gamma$, $\Gamma$ may looks like : 
+\begin{equation}
+	..., l_i, ..., l_j, ...
+\end{equation}
+where $\Delta_{l_i} < \Delta_{l_j}$.
+
+Pay attention we only fetch the link impact once at the begining of algorihtm, and the ordered list $\Gamma$ show 
+the `importantance` of link in the connectivity of the graph. Now we begin selecting which links should be sleep.
+We denote the set of the sleeping links as $S$, and the output of this phase is $G^* = (V, E-S)$. We set 
+$S = \emptyset$, and iterate our selecting process, each iteration we select one link and put it into $S$. 
+In iteration $i$, scan links as the order of $\Gamma$ and choose one which is still not in the $S$, we try to
+remove it from the graph, if some metric of the current graph do not arrive the threhold we put the link into
+$S$ and  begin next iteration, or choose the next link from the $\Gamma$ for try to remove otherwise. Algorithm
+stop until all the links in $\Gamma$ is tried but there is no one to satisfy the threhold.
+
+So before going ahead our algorithm, there is another thing we should done, what is the threhold for the graph.
+It does matter for what we concern most of the graph, in our graph, we choose two threholds, one is connectivity and
+another is power consumption. For considering connectivity , we defined the difference of connectivity between 
+two graphs as:
+\begin{equation}
+	diff_c = \lambda_2(G_{S, l}^o) / \lambda_2(G^o) * 100
+\end{equation}
+where $\lambda_2(G_{S, l}^o)$ is the extend algebraic connectivity of the final graph, when the links set $S$ and 
+link $l$ is removed from the origin graph $G^o$, and the $\lambda_2(G^o)$ is the extend algebraic connectivity of 
+the origin graph.
+
+If we set $diff_c$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
+iteration, the extend algebraic connectivity should never lower than the 90\% of origin. For power consumption
+consideration, we simply take an power model from `Green TE` showed in Table xx, and defined the difference of 
+power consumption between two graphs as:
+\begin{equation}
+	diff_p = \rho(G_{S, l}^o) / \rho(G^o) * 100
+\end{equation}
+where $\rho(G^o)$ is the power consumption of the origin graph, and $\rho(G_{S, l}^o)$ is similar with the 
+definition above.
+
+Experiment shows that...
+
+\subsection{Second Phase}
+When we get the output graph from the first phase based on extend algebraic connectivity, it is time to compute
+the robust routing.
+
 \section{Conclusion}

### 2014-11-20 paper.tex
Add 85 & 95 real result

--- 2014-11-18 paper.tex
@@
 
+\section{Algorithm}
+In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links 
+should be sleeping from the origin topology based on extended algebraic connectivity, then compute the robust 
+routing by demand-oblivious routing algorithm.
+
+\subsection{First Phase}
+
+\subsubsection{Extend Algebraic Connectivity}
+Network topology is represented by $G = (V, E)$ as mentioned in Model section, where $V$ is the set of vertices
+and $E$ is the set of links. We say $A(G)$ is the Adjacency Matrix of graph $G$, that include information for which
+vertices of the graph are adjacent to which other vertices. $A(G)$ is a $N \times N$ matrix, where
+$N = |V|$ and non-diagonal entry $a_{ij}$ equal to the number of edges from vertex $i$ to vertex $j$, in this paper,
+$a_{ij}$ always be 1 if $(i,j) \in E$ otherwise 0. And we stipulate the diagonal element $a_{ii}$ be 0.
+
+We say $D(G)$ is the Degree Matrix of graph $G$, which is a diagonal matrix and diagonal entry $d_{ii}$ denote 
+the degree of node $i$. It is obvious that there is $d_{ii} == \sum_{j} a_{ij}$.
+
+Then we define Laplacian Matrix $L(G)$ of graph $G$ as the difference between Degree Matrix and Adjacency Matrix :
+\begin{equation}
+	L(G) = D(G) - A(G)
+\end{equation}
+where $D(G)$ is the Degree Matrix and $A(G)$ is the Adjacency Matrix.
+
+In the mathematical field of graph theory, the algebraic connectivity of a graph $G$ is the second-smallest
+eigenvalue of the Laplacian Matrix. This eigenvalue is greater than 0 if and only if $G$ is connected, and 
+it measures the connectivity of graph, the greater of which, the more connective of graph.
+
+As far as we know, 
+algebraic connectivity regard every link the same, without considering the capacity of each one, but it is 
+ridiculous in network. It is easy to see, link with greater capacity is more important than the same one
+with lower capacity. So we extend the algebraic connectivity definition by following ways:
+
+\begin{enumerate}
+	\item We change the Adjacency Matrix from binary-matrix to float-matrix, i.e. if $(i,j) \in E$ we set the $a_{ij}$
+with the capacity of link $l_{ij}$ instead of binary value 1.
+	\item Degree Matrix is not ever the denotation for the degree of nodes, but the conbined capacity of all the links
+adjacent to the node, there is still exist the equation: $d_{ij} == \sum_{j} a_{ij}$
+	\item No modification for definition of Laplacian Matrix
+\end{enumerate}
+
+We calculate new extend algebraic connectivity from the new Laplacian matrix, denoted by $\lambda_2(G)$.
+
+Topology always have different extend algebraic connectivity values, it is clear that when one link is added or 
+removed from the graph, the extend algebraic connectivity value changes accordingly. And we say the changed value
+is the impact of this link on the graph. Supposed we sleep link $l$ from graph $G$, new graph is described as $G^*$, 
+we defined the impact of link $l$ as :
+\begin{equation}
+	\Delta_l = \lambda_2(G) - \lambda_2(G^*)
+\end{equation}
+where $\lambda_2(G)$ and $\lambda_2(G^*)$ is extend algebraic connectivity of $G$ and $G^*$ respectly.
+
+Clearly, $\Delta_l$ is always greater than 0, because graph will always lose connectivity when link is removed.
+Further more, some link will play a more important role in the connectivity of graph, such as the backbone link 
+of network topology. And we say a link $l$ affect more if $\Delta_l$ is greater.
+
+\subsection{First Phase Description}
+REAR sleep as many links as possible without losing much connectivity of graph. Originly,  we should
+calculate impact of all the links and sleep the lowest one from the graph, then repeat calculate and remove
+process until arrive some specific threhold. Obviously, it is NP-Hard, following is a heuristic algorithm.
+
+For the origin graph, we calculate the impact of every link as $\Delta_{l_i}$ , and then sort these values
+from small to big, output ordered list denoted as $\Gamma$: 
+\begin{equation}
+	\Gamma = {..., l_i, ..., l_j, ...}
+\end{equation}
+where $\Delta_{l_i} < \Delta_{l_j}$.
+
+Pay attention we only compute the link impact once at the begining of algorihtm, and the ordered list $\Gamma$ show 
+the order of `importantance` among links in the connectivity of the graph.
+
+Now we begin selecting which links should be sleep.
+We denote the set of the sleeping links as $S$, and the output of this phase is final graph $G^* = (V, E-S)$. We set 
+$S = \emptyset$, and repeat our selecting process, each iteration we select one link and put it into $S$. 
+In iteration $i$, algorithm scan links as the order of $\Gamma$ and choose one which is still not in the $S$, we try to
+remove this link from the graph, if some metric of the current graph do not arrive the threhold we put the link into
+$S$ then go next iteration, or choose the next link from the $\Gamma$ for trying to remove otherwise. Algorithm
+stop until all the links in $\Gamma$ is tried but there is no one to satisfy the threhold.
+
+So before going ahead our algorithm, there is another thing we should done, what is the threhold for the graph.
+It does matter for what we concern most of the graph, in our graph, we choose two threholds, one is connectivity and
+another is power consumption. For considering connectivity , we defined the difference of connectivity between 
+two graphs as:
+\begin{equation}
+	diff_c = \lambda_2(G_{S, l}^o) / \lambda_2(G^o) * 100
+\end{equation}
+where $\lambda_2(G_{S, l}^o)$ is the extend algebraic connectivity of the final graph, when the links set $S$ and 
+link $l$ are both removed from the origin graph $G^o$, and the $\lambda_2(G^o)$ is the extend algebraic connectivity of 
+the origin graph.
+
+If we set $diff_c$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
+iteration, the extend algebraic connectivity should never lower than the 90\% of origin one. For power consumption
+consideration, we simply take an power model from `Green TE` showed in Table xx, and defined the difference of 
+power consumption between two graphs as:
+\begin{equation}
+	diff_p = \rho(G_{S, l}^o) / \rho(G^o) * 100
+\end{equation}
+where $\rho(G^o)$ is the power consumption of the origin graph, and $\rho(G_{S, l}^o)$ is similar with the 
+definition above.
+
+Experiment shows that...
+
+\subsection{Second Phase}
+When we get the output graph from the first phase based on extend algebraic connectivity, it is time to compute
+the robust routing.
+
 \section{Conclusion}

### 2014-11-20 paper.tex
Add 85 & 95 real result

@@
 
-\subsection{First Phase}
-
-\subsubsection{Extend Algebraic Connectivity}
+\subsection{Extend Algebraic Connectivity}
 Network topology is represented by $G = (V, E)$ as mentioned in Model section, where $V$ is the set of vertices
@@
 \begin{equation}
-	\Gamma = {..., l_i, ..., l_j, ...}
+	\Gamma = \{..., l_i, ..., l_j, ...\}
 \end{equation}

### 2014-11-20 experiment/src/off_by_power.c
Add power threhold

@@ -1,0 +1,114 @@
+#include "tools.h"
+
+
+//
+//
+// ./off with_weight threshold input_topology output_topology remove_topology
+//
+//
+int main(int argc, char **argv) {
+	// init matrix
+	int nodes_n = 0, links_n = 0;
+	double * matrix = NULL;
+	link_t * links = NULL;
+	bool with_weight = atoi(argv[1]) == 0 ? false : true;
+	init_matrix_with_file(argv[3], &matrix, &links, &nodes_n, &links_n, with_weight);
+
+	// 
+	double * copy_matrix = (double *) malloc(nodes_n * nodes_n * sizeof(double));
+	memcpy(copy_matrix, matrix, nodes_n * nodes_n * sizeof(double));
+	double origin = get_eigenvalue(copy_matrix, nodes_n);
+	free(copy_matrix);
+	
+	double origin_power = get_power(matrix, nodes_n);
+
+	for (int i = 0; i < links_n; i++) {
+		double backup = matrix[links[i].s * nodes_n + links[i].d];
+
+		matrix[links[i].s * nodes_n + links[i].d] = 0;
+		matrix[links[i].d * nodes_n + links[i].s] = 0;
+		matrix[links[i].s * nodes_n + links[i].s] += backup;
+		matrix[links[i].d * nodes_n + links[i].d] += backup;
+		
+		double * copy_matrix = (double *) malloc(nodes_n * nodes_n * sizeof(double));
+		memcpy(copy_matrix, matrix, nodes_n * nodes_n * sizeof(double));
+		double temp_connected_value = get_eigenvalue(copy_matrix, nodes_n);
+		links[i].impact = origin - temp_connected_value;
+		free(copy_matrix);
+
+		matrix[links[i].s * nodes_n + links[i].d] = backup;
+		matrix[links[i].d * nodes_n + links[i].s] = backup;
+		matrix[links[i].s * nodes_n + links[i].s] -= backup;
+		matrix[links[i].d * nodes_n + links[i].d] -= backup;
+	}
+
+	for (int i = 0; i < links_n; i++) {
+		for (int j = i + 1; j < links_n; j++) {
+			if (links[i].impact > links[j].impact) {
+				int s = links[i].s, d = links[i].d;
+				double impact = links[i].impact, c = links[i].c;
+
+				links[i].s = links[j].s;
+				links[i].d = links[j].d;
[…]

### 2014-11-20 experiment/src/power.c

@@ -1,0 +1,36 @@
+#include "tools.h"
+
+double get_power(double *matrix, int nodes_n) {
+	double power_sum = 0;
+	double card[4][2] = {{155.52, 60}, {1244.16, 100}, {2488.32, 140}, {9953.28, 174}};
+	for (int i = 0; i < nodes_n; i++) {
+		for (int j = 0; j < nodes_n; j++) {
+			if (i == j) {
+				continue;
+			}
+
+			double c = matrix[i * nodes_n + j];
+			while (c > 0.0001) {
+				if (c > card[3][0]) {
+					c -= card[3][0];
+					power_sum += card[3][1];
+				} else if (c > card[2][0]) {
+					c -= card[2][0];
+					power_sum += card[2][1];
+				} else if (c > card[1][0]) {
+					c -= card[1][0];
+					power_sum += card[1][1];
+				} else if (c > card[0][0]) {
+					c -= card[0][0];
+					power_sum += card[0][1];
+				} else {
+					power_sum += card[0][1];
+					break;
+				}
+			}
+		}
+	}
+
+	return power_sum;
+}
+

### 2014-11-20 experiment/src/tools.h

@@ -37,3 +37,9 @@ void print_matrix(double *, int);
  */
 double get_eigenvalue(double *, int);
 
+
+/*
+ * Get the power 
+ */
+double get_power(double *, int);
+

### 2014-11-20 experiment/topology/remove_links_from_connected_graph_by_power.sh

@@ -1,0 +1,9 @@
+#for topo in abilene geant 1221 1239 1755 3257 3967 6461; do
+for topo in abilene geant; do
+	for threhold in 80 85 90 95; do
+		../bin/off_by_power 1 ${threhold} \
+			../topology/connected/${topo}-connected-topology \
+			../topology/final/${topo}-final-1-${threhold}-topology-power \
+			../topology/remove/${topo}-remove-1-${threhold}-links-power 
+	done
+done

### 2014-11-20 paper.tex
remove connectivity threhold

@@
 So before going ahead our algorithm, there is another thing we should done, what is the threhold for the graph.
-It does matter for what we concern most of the graph, in our graph, we choose two threholds, one is connectivity and
-another is power consumption. For considering connectivity , we defined the difference of connectivity between 
-two graphs as:
+It does matter for what we concern most of the graph, in our graph, we choose the power consumption. 
+We simple take an power model from `Green TE` showed in Table xx, and defined the difference of power consumption 
+between two graphs as:
 \begin{equation}
-	diff_c = \lambda_2(G_{S, l}^o) / \lambda_2(G^o) * 100
+	diff_p = \rho(G_{S, l}^o) / \rho(G^o) * 100
 \end{equation}
-where $\lambda_2(G_{S, l}^o)$ is the extend algebraic connectivity of the final graph, when the links set $S$ and 
-link $l$ are both removed from the origin graph $G^o$, and the $\lambda_2(G^o)$ is the extend algebraic connectivity of 
+where $\rho(G_{S, l}^o)$ is the power consumption of the final graph, when the links set $S$ and 
+link $l$ are both removed from the origin graph $G^o$, and the $\rho(G^o)$ is the power consumption of 
 the origin graph.
@@
 If we set $diff_c$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
-iteration, the extend algebraic connectivity should never lower than the 90\% of origin one. For power consumption
-consideration, we simply take an power model from `Green TE` showed in Table xx, and defined the difference of 
-power consumption between two graphs as:
-\begin{equation}
-	diff_p = \rho(G_{S, l}^o) / \rho(G^o) * 100
-\end{equation}
-where $\rho(G^o)$ is the power consumption of the origin graph, and $\rho(G_{S, l}^o)$ is similar with the 
-definition above.
+iteration, the power consumption should never lower than the 90\% of origin one. In another words, the output 
+of this phase protect as much connectivity as possible
 

### 2014-11-20 experiment/src/off_by_power.c
change the remove-power implementation

@@ -84,7 +84,7 @@ int main(int argc, char **argv) {
 		double temp_connected_value = get_eigenvalue(copy_matrix, nodes_n);
 		free(copy_matrix);
 
-		if (temp_connected_value <= 0 || temp_power / origin_power < threshold) {
+		if (temp_connected_value <= 0.1 || temp_power / origin_power < threshold) {
 			matrix[links[i].s * nodes_n + links[i].d] = backup;
 			matrix[links[i].d * nodes_n + links[i].s] = backup;
 			matrix[links[i].s * nodes_n + links[i].s] -= backup;

### 2014-11-20 experiment/cplex/real_main.py
change the remove-power implementation

@@ -6,10 +6,10 @@ import adjust_route_in_new_topology as adjust
 # Generate performance 
 
 connected_topology = "../topology/connected/geant-connected-topology"
-final_topology = "../topology/final/geant-final-0-topology"
-remove_links = "../topology/remove/geant-remove-0-links"
+final_topology = "../topology/final/geant-final-1-topology-power"
+remove_links = "../topology/remove/geant-remove-1-links-power"
 demand_file_template = "../demand/real-geant/%d.txt"
-result_file = "result-geant-0"
+result_file = "result-geant-1-80-power"
 begin = 36
 files = 131
 

### 2014-11-20 experiment/cplex/real_main.py
debug for adjust route

@@ -5,6 +5,7 @@ import adjust_route_in_new_topology as adjust
 
 # Generate performance 
 
+'''
 connected_topology = "../topology/connected/geant-connected-topology"
 final_topology = "../topology/final/geant-final-1-topology-power"
 remove_links = "../topology/remove/geant-remove-1-links-power"
@@ -12,15 +13,15 @@ demand_file_template = "../demand/real-geant/%d.txt"
 result_file = "result-geant-1-80-power"
 begin = 36
 files = 131
+'''
 
-'''
 connected_topology = "../topology/connected/abilene-connected-topology"
-final_topology = "../topology/final/abilene-final-0-90-topology"
-remove_links = "../topology/remove/abilene-remove-0-90-links"
+final_topology = "../topology/final/abilene-final-1-90-topology-power"
+remove_links = "../topology/remove/abilene-remove-1-90-links-power"
 demand_file_template = "../demand/real-abilene/XX02/%d.txt"
-result_file = "result-abilene-0-90"
+result_file = "result-abilene-1-90-power"
 files = 288
-'''
+
 
 loop = 20
 diff = 1000
@@ -31,7 +32,7 @@ diff = 1000
 global_routes = common.global_routes(connected_topology)
 
 
-for num in range(begin, files):
+for num in range(files):
     print("Round %d\n" % num)
 
     demand_file = demand_file_template % num

### 2014-11-20 paper.tex
debug for adjust route

@@
 
-In the mathematical field of graph theory, the algebraic connectivity of a graph $G$ is the second-smallest
-eigenvalue of the Laplacian Matrix. This eigenvalue is greater than 0 if and only if $G$ is connected, and 
-it measures the connectivity of graph, the greater of which, the more connective of graph.
+In the mathematical field of graph theory, the number of eigenvalues equal to 0 is the number of connected 
+componements of $G$, so the smallest eigenvalue always be 0. And we call the second smallest one as
+algebraic connectivity, which is greater than 0 if and only if graph $G$ is connected. Further more,  
+it measures the connectivity and stability of graph, the greater of which, the more connective of graph;
+and it is a metric of average distance between any two vertices of graph $G$.
 
@@
 ridiculous in network. It is easy to see, link with greater capacity is more important than the same one
-with lower capacity. So we extend the algebraic connectivity definition by following ways:
+with lower capacity. and in graph theory, algebraic connectivity value monotonically increased when we
+increase the weight of link between vertices. So we extend the algebraic connectivity definition by following ways:
 
@@
 iteration, the power consumption should never lower than the 90\% of origin one. In another words, the output 
-of this phase protect as much connectivity as possible
-
-Experiment shows that...
+of this phase protect as much connectivity as possible. Following is our implementation:
 

### 2014-11-20 experiment/src/off_by_power.c
debug for adjust route

@@ -84,7 +84,7 @@ int main(int argc, char **argv) {
 		double temp_connected_value = get_eigenvalue(copy_matrix, nodes_n);
 		free(copy_matrix);
 
-		if (temp_connected_value <= 0.1 || temp_power / origin_power < threshold) {
+		if (temp_connected_value / origin <= 0.8 || temp_power / origin_power < threshold) {
 			matrix[links[i].s * nodes_n + links[i].d] = backup;
 			matrix[links[i].d * nodes_n + links[i].s] = backup;
 			matrix[links[i].s * nodes_n + links[i].s] -= backup;

### 2014-11-20 paper.tex
debug for adjust route

@@
 ridiculous in network. It is easy to see, link with greater capacity is more important than the same one
-with lower capacity. and in graph theory, algebraic connectivity value monotonically increased when we
-increase the weight of link between vertices. So we extend the algebraic connectivity definition by following ways:
+with lower capacity. and in graph theory So we extend the algebraic connectivity definition by following ways:
 
@@
 iteration, the power consumption should never lower than the 90\% of origin one. In another words, the output 
-of this phase protect as much connectivity as possible. Following is our implementation:
+of this phase protect as much connectivity as possible
+
+Experiment shows that...
 

### 2014-11-20 experiment/cplex/adjust_route_in_new_topology.py

@@ -43,7 +43,7 @@ def adjust_route(topology, remove_file, routes):
                 for j in range(len(routes[s,d][i][0]) - 1):
                     #print("ls, ld : %d %d" % (ls, ld))
                     #print("len : %d, j : %d" % (len(routes[s,d][i][0]), j))
-                    if routes[s,d][i][0][j] == ls and routes[s,d][i][0][j+1] == ld:
+                    if path_replace[ls, ld] != None and routes[s,d][i][0][j] == ls and routes[s,d][i][0][j+1] == ld:
                         weight = 0
                         index = 0
                         for k in range(len(routes[ls,ld])):
@@ -52,5 +52,7 @@ def adjust_route(topology, remove_file, routes):
                                 weight = routes[ls,ld][k][1]
                         routes[s,d][i] = [routes[s,d][i][0][0:j] + path_replace[ls, ld] + routes[s,d][0][j+2:], routes[s,d][i][1]]
                         break
+                    else:
+                        routes[s,d][i] = [g.dfs_path(s, d), routes[s][d][i][1]]
 
     return routes

### 2014-11-20 experiment/cplex/deep_first_search_path.py

@@ -50,7 +50,7 @@ class Graph(object):
         queue[s] = 100000
         parents = {}
         parents[s] = None
-        while True:
+        while len(queue) != 0:
             node = find_max(queue)
             #print("when %d" % node)
             w = queue[node]
@@ -77,6 +77,7 @@ class Graph(object):
                 queue.pop(node)
 
             self.visited[node] = True
+        return None
 		
     def find_path(self, s, v):
         paths = []

### 2014-11-20 experiment/cplex/deep_first_search_path.py
debug for adjust route

@@ -31,7 +31,10 @@ class Graph(object):
                 if q[i] > m:
                     m = q[i]
                     key = i
-            return key
+            if m > 0:
+                return key
+            else:
+                return None
         
         path = []
         def get_path(v, p):
@@ -50,8 +53,11 @@ class Graph(object):
         queue[s] = 100000
         parents = {}
         parents[s] = None
-        while len(queue) != 0:
+        while True:
             node = find_max(queue)
+
+            if node == None:
+                return None
             #print("when %d" % node)
             w = queue[node]
 
@@ -77,7 +83,6 @@ class Graph(object):
                 queue.pop(node)
 
             self.visited[node] = True
-        return None
 		
     def find_path(self, s, v):
         paths = []

### 2014-11-20 experiment/cplex/adjust_route_in_new_topology.py
debug for adjust route

@@ -43,16 +43,19 @@ def adjust_route(topology, remove_file, routes):
                 for j in range(len(routes[s,d][i][0]) - 1):
                     #print("ls, ld : %d %d" % (ls, ld))
                     #print("len : %d, j : %d" % (len(routes[s,d][i][0]), j))
-                    if path_replace[ls, ld] != None and routes[s,d][i][0][j] == ls and routes[s,d][i][0][j+1] == ld:
+                    if routes[s,d][i][0][j] == ls and routes[s,d][i][0][j+1] == ld:
+                        '''
                         weight = 0
                         index = 0
                         for k in range(len(routes[ls,ld])):
                             if routes[ls,ld][k][1]> weight:
                                 index = k
                                 weight = routes[ls,ld][k][1]
-                        routes[s,d][i] = [routes[s,d][i][0][0:j] + path_replace[ls, ld] + routes[s,d][0][j+2:], routes[s,d][i][1]]
+                        '''
+                        if path_replace[ls, ld] != None:
+                            routes[s,d][i] = [routes[s,d][i][0][0:j] + path_replace[ls, ld] + routes[s,d][0][j+2:], routes[s,d][i][1]]
+                        else:
+                            routes[s,d][i] = [g.dfs_path(s, d), routes[s,d][i][1]]
                         break
-                    else:
-                        routes[s,d][i] = [g.dfs_path(s, d), routes[s][d][i][1]]
 
     return routes

### 2014-11-20 experiment/cplex/real_main.py
debug for adjust route

@@ -5,64 +5,70 @@ import adjust_route_in_new_topology as adjust
 
 # Generate performance 
 
-'''
-connected_topology = "../topology/connected/geant-connected-topology"
-final_topology = "../topology/final/geant-final-1-topology-power"
-remove_links = "../topology/remove/geant-remove-1-links-power"
+
+connected_topology_template = "../topology/connected/geant-connected-topology"
+final_topology_template = "../topology/final/geant-final-1-%s-topology-power"
+remove_links_templae = "../topology/remove/geant-remove-1-%s-links-power"
 demand_file_template = "../demand/real-geant/%d.txt"
-result_file = "result-geant-1-80-power"
+result_file_template = "result-geant-1-%s-power"
 begin = 36
 files = 131
-'''
 
+'''
 connected_topology = "../topology/connected/abilene-connected-topology"
 final_topology = "../topology/final/abilene-final-1-90-topology-power"
 remove_links = "../topology/remove/abilene-remove-1-90-links-power"
 demand_file_template = "../demand/real-abilene/XX02/%d.txt"
 result_file = "result-abilene-1-90-power"
 files = 288
+'''
+for alpha in ['80', '85', '90', '95', '100']:
+
+    connected_topology = connected_topology_template % alpha
+    final_topology = final_topology_template % alpha
+    remove_links = remove_links_templae % alpha
+    result_file = result_file_template % alpha
+
+    loop = 20
+    diff = 1000
 
 
-loop = 20
-diff = 1000
+    # Generate the global routes for traffic sets 
+    # Calculate the global maximum utilization for specific traffic matrix sets
+    global_routes = common.global_routes(connected_topology)
 
 
-# Generate the global routes for traffic sets 
-# Calculate the global maximum utilization for specific traffic matrix sets
-global_routes = common.global_routes(connected_topology)
+    for num in range(files):
+        print("Round %d\n" % num)
 
+        demand_file = demand_file_template % num
+        f = open(demand_file, "r")
+        line = f.readline()
+        f.close()
+        if int(line.strip()) == 0:
+            continue
 
-for num in range(files):
-    print("Round %d\n" % num)
+        f = open(result_file,"a")
+        # Calculate the optimal maximum utilization for specific traffic matrix
+        optimal_utilization = optimal.optimal_utilization(connected_topology, demand_file, loop)
+        print('Optimal Utilization is %f\n' % optimal_utilization)
[…]

### 2014-11-21 paper.tex
debug for adjust route
Add algorithm to paper

--- 2014-11-20 paper.tex
@@
 
+\begin{table}[!th]
+\begin{tabular}{ll}
+\hline
+\textbf{Algorithm REAR : Phase One}\\
+\hline
+$\:\:$\textbf{Input:} $G(V, E)$, $threhold$;\\
+$\:\:$\textbf{Output:} $S$ in which links should be switched off;\\
+$\quad\qquad\quad$ $G(V, E-S)$ which is the final network topology;\\
+$\:\:$1:\ \textbf{for} {each link $l$ in $E$}\\
+$\:\:$2:\quad\ $G^* \leftarrow G(V, E-\{l\})$;\\
+$\:\:$3:\quad\ $\Gamma[l] \leftarrow \Delta_l \leftarrow \lambda_2(G) - \lambda_2(G^*)$;\\
+$\:\:$4:\ Resort $\Gamma$ in increasing order based on $\Delta_l$;\\
+$\:\:$5:\ $S \leftarrow \emptyset$, $goon \leftarrow true$;\\
+$\:\:$6:\ \textbf{while} {$goon$}\\
+$\:\:$7:\quad\  $goon \leftarrow false$;\\
+$\:\:$8:\quad\ \textbf{for} {each link $l$ in $\Gamma - S$}\\
+$\:\:$9:\quad\ \quad\ \textbf{if} $G_{S,l}$ is connected and $\rho(G_{S,l})/\rho(G)<threhold$\\
+$\:\:$10:\quad\ \quad\ \quad\ $S \leftarrow S \cup \{l\}$;\\
+$\:\:$11:\quad\ \quad\ \quad\ $goon \leftarrow true$;\\
+$\:\:$12:\quad\ \quad\ \quad\ \textbf{break};\\
+$\:\:$13:\ \textbf{return} $S, G(V, E-S)$;\\
+\hline
+\end{tabular}
+\end{table}
+
 \subsection{Second Phase}

### 2014-11-21 paper.tex
Add phase two description

@@
 
-\subsection{First Phase Description}
+\subsection{Algorithm Phase One}
 REAR sleep as many links as possible without losing much connectivity of graph. Originly,  we should
@@
 
-\subsection{Second Phase}
-When we get the output graph from the first phase based on extend algebraic connectivity, it is time to compute
-the robust routing.
+\subsection{Algorihtm Phase Two}
+Once we get the output network topology from the first phase based on extend algebraic connectivity, it is time to compute
+the robust routing. We first calculate the demand-oblivious rouintg from the origin topology based on algorithm proposed 
+by David pplegate[1]; and adjust routing in details according to the links we switched off in the final topology.
+
+The demand-oblivious routing can be computed by a single LP with $O(mn^2)$ variables and $O(nm^2)$ constraints :
+\begin{table}[!th]
+	\begin{tabular}{ll}
+		$\:\:$\quad\quad\ min $r$ \\
+		$\:\:$\quad\quad\ $f_{ij}(e)$ is a routing \\
+		$\:\:$\quad\quad\ $\forall$ links $l$: $\sum_m cap(m)t(l,m) \le r$ \\
+		$\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ pairs $i \rightarrow j$: \\
+		$\:\:$\quad\quad\quad\quad\ $f_{ij}(l)/cap(l) \le p_l(i,j)$ \\ 
+		$\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $\forall$ edges $e = j \rightarrow k$: \\
+		$\:\:$\quad\quad\quad\quad\ $\pi(l, link-of(e)) + p_l(i,j) - p_l(i,k) \ge 0$ \\
+		$\:\:$\quad\quad\ $\forall$ links $l$, $m$: $\pi(l, m) \ge 0$ \\
+		$\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$: $p_l(i,i) = 0$ \\
+		$\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $j$: $p_l(i,j) \ge 0$ \\
+	\end{tabular}
+\end{table}
+where the $cap(l)$ isthe capacity of link $l$; 
+and $\pi(l,m)$ is the weights for every pair of links $l$, $m$; and the variables $p_l(i,j)$ for each link $l$ 
+and OD pair $i$, $j$ is the length of the shortest path from $i$ to $j$ according to the link weights $\pi(l, m)$.
+
+The routing we get indicate how to arrive destination node from source node for every OD pair in the origin topology.
+What is different is that, the flow can be splited in the routing, i.e. there may be two paths ($path_1$, $path_2$)
+both from source node $s$ to destination node $d$, and the optimal obilious routing trace 70\% traffic on 
+$path_1$ and left on $path_2$. However splitting flow is hard handled, we take a transformation for this case like this:
+when an flow is coming, there is 70\% probability we trace it on $path_1$, otherwise $path_2$.
+
+Because all the routing is based on the origin topology, when switch-off links is done, we must adjust the routing 
+as well. Take pair $(s, d)$ for example, the path in routing maybe like $s \rightarrow i \rightarrow j \rightarrow d$,
+unfortunately link $i \rightarrow j$ is switched off in Phase One of Algorithm. For the final topology is still 
+connected, we must can find another path from $i$ to $j$, such as $i \rightarrow k \rightarrow j$,
+instead of the direct link $i->j$, then we just replace the routhing $s \rightarrow i \rightarrow j \rightarrow d$ with
+$s \rightarrow i \rightarrow \rightarrow k \rightarrow j \rightarrow d$.
+Find the path between two nodes of switch-off link is easy by Dijkstra Algorithm on the final topology.
+
+And this is our implementation:
+\begin{table}[!th]
+\begin{tabular}{ll}
+\hline
+\textbf{Algorithm REAR : Phase Two}\\
+\hline
+$\:\:$\textbf{Input:} $G(V,E)$ which is the origin topology;\\
+$\quad\qquad\quad$ $S$ which is the switch-off links set generated by Phase One;\\
+$\:\:$\textbf{Output:} $Rouing$ Robust Energy-Aware Routing on new topology\\
+$\:\:$1:\ $G^* \leftarrow G(V, E-S)$;\\
+$\:\:$2:\ $Replace \leftarrow \emptyset$;\\
+$\:\:$3:\ \textbf{for} {each link $l$ in $S$}\\
+$\:\:$4:\quad\ $ls \leftarrow node of l$, $ld \leftarrow the other node of l$;\\
+$\:\:$5:\quad\ $Replace[ls, ld] \leftarrow find path form ls to ld on G^*$;\\
+$\:\:$6:\ $Routing \leftarrow run LP in CPLEX, fetch routing by parsing result$;\\
+$\:\:$7:\ \textbf{for} {each r in Routing}\\
+$\:\:$8:\quad\ \textbf{if} $l \in S in r $\\
+$\:\:$9:\quad\ \quad\ $s \leftarrow source of r$, $d \leftarrow destination of r$;\\
+$\:\:$10:\quad\ \quad\ $r \leftarrow r[s, ls] + Replace[ls,ld] + r[ld,d]$;\\
+$\:\:$11:\ \textbf{return} Routing;\\
+\hline
+\end{tabular}
+\end{table}
 
@@
   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
 \end{thebibliography}

### 2014-11-21 experiment/cplex/deep_first_search_path.py

@@ -22,6 +22,7 @@ class Graph(object):
     def nodes(self):
         return self.node_neighbors.keys()
 
+    #dijkstra path
     def dfs_path(self, s, v):
         self.visited = {}
         def find_max(q):

### 2014-11-21 paper.tex
debug for algorithm phase two

--- 2014-11-21 paper.tex
@@
 
-\subsection{Second Phase}
-When we get the output graph from the first phase based on extend algebraic connectivity, it is time to compute
-the robust routing.
+\subsection{Algorihtm Phase Two}
+Once we get the output network topology from the first phase based on extend algebraic connectivity, it is time to compute
+the robust routing. We first calculate the demand-oblivious rouintg from the origin topology based on algorithm proposed 
+by David Applegate[1]; and adjust routing in details according to the links we switched off in the final topology.
+
+The demand-oblivious routing can be computed by a single LP with $O(mn^2)$ variables and $O(nm^2)$ constraints :
+\begin{table}[!th]
+\begin{tabular}{lll}
+    $\:\:$\quad\quad\ min $r$ \\
+    $\:\:$\quad\quad\ $f_{ij}(e)$ is a routing \\
+    $\:\:$\quad\quad\ $\forall$ links $l$: $\sum_m cap(m)t(l,m) \le r$ \\
+    $\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ pairs $i \rightarrow j$: \\
+    $\:\:$\quad\quad\quad\quad\ $f_{ij}(l)/cap(l) \le p_l(i,j)$ \\ 
+    $\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $\forall$ edges $e = j \rightarrow k$: \\
+    $\:\:$\quad\quad\quad\quad\ $\pi(l, link-of(e)) + p_l(i,j) - p_l(i,k) \ge 0$ \\
+    $\:\:$\quad\quad\ $\forall$ links $l$, $m$: $\pi(l, m) \ge 0$ \\
+    $\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$: $p_l(i,i) = 0$ \\
+    $\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $j$: $p_l(i,j) \ge 0$ \\
+\end{tabular}
+\end{table}
+
+where the $cap(l)$ is the capacity of link $l$; 
+and $\pi(l,m)$ is the weights for every pair of links $l$, $m$; and the variables $p_l(i,j)$ for each link $l$ 
+and OD pair $i$, $j$ is the length of the shortest path from $i$ to $j$ according to the link weights $\pi(l, m)$.
+
+The routing we get indicate how to arrive at destination node from source node for every OD pair in the origin topology.
+What is different is that, the flow can be splited in the routing, i.e. there may be two paths ($path_1$, $path_2$)
+both from source node $s$ to destination node $d$, and the optimal obilious routing trace 70\% traffic on 
+$path_1$ and left on $path_2$. However splitting flow is hard handled, we take a transformation for this case like this:
+when an flow is coming, there is 70\% probability we trace it on $path_1$, otherwise $path_2$.
+
+Because all the routing is based on the origin topology, when switch-off links is done, we must adjust the routing 
+as well. Take pair $(s, d)$ for example, the path in routing maybe like $s \rightarrow i \rightarrow j \rightarrow d$,
+unfortunately link $i \rightarrow j$ is switched off in Phase One of Algorithm. For the final topology is still 
+connected, we must can find another path from $i$ to $j$, such as $i \rightarrow k \rightarrow j$,
+then we just replace the routhing $s \rightarrow i \rightarrow j \rightarrow d$ with
+$s \rightarrow i \rightarrow k \rightarrow j \rightarrow d$.
+Find the path between two nodes of switch-off link is easy by Dijkstra Algorithm on the final topology.
+
+And this is our implementation:
+\begin{table}[!th]
+\begin{tabular}{ll}
+\hline
+\textbf{Algorithm REAR : Phase Two}\\
+\hline
+$\:\:$\textbf{Input:} $G(V,E)$ which is the origin topology;\\
+$\quad\quad\ \ \ $ $S$ which is the switch-off links set generated by Phase One;\\
+$\:\:$\textbf{Output:} $Rouing$ Robust Energy-Aware Routing on new topology\\
+$\:\:$1:\ $G^* \leftarrow G(V, E-S)$;\\
+$\:\:$2:\ $Replace \leftarrow \emptyset$;\\
+$\:\:$3:\ \textbf{for} {each link $l$ in $S$}\\
+$\:\:$4:\quad\ $ls \leftarrow$ node of $l$;\\
+$\:\:$5:\quad\ $ld \leftarrow$ the other node of $l$;\\
+$\:\:$6:\quad\ $Replace[ls, ld] \leftarrow$ find path from $ls$ to $ld$ on $G^*$;\\
+$\:\:$7:\ $Routing \leftarrow$ run LP on $G$ by CPLEX, fetch routing through parsing result;\\
+$\:\:$8:\ \textbf{for} {each $r$ in $Routing$}\\
+$\:\:$9:\quad\ \textbf{if} {$l \in S$ in $r$}\\
+$\:\:$10:\quad\quad\ \ $s \leftarrow$ source of $r$;\\
+$\:\:$11:\quad\quad\ \ $d \leftarrow$ destination of $r$;\\
+$\:\:$12:\quad\quad\ $r \leftarrow r[s, ls] + Replace[ls,ld] + r[ld,d]$;\\
+$\:\:$13:\ \textbf{return} Routing;\\
+\hline
+\end{tabular}
+\end{table}
 

### 2014-12-01 experiment/cplex/compare_use_paper.py
Add compare using paper ways

@@ -1,0 +1,93 @@
+from copy import deepcopy
+import parse_xml as xml
+import optimal_route_with_tm as optimal
+import global_route_with_tm_bound as common
+import new_adjust_route_in_new_topology as adjust
+
+# Generate performance 
+
+is_gravity = True
+type_random = "bimodal"
+
+connected_topology_template = "../topology/connected/%s-connected-topology"
+final_topology_template = "../topology/final/%s-final-topology-%d"
+remove_links_template = "../topology/remove/%s-remove-%d-links"
+final_topology_base_template = "../topology/final/%s-final-topology-%d-base"
+remove_links_base_template = "../topology/remove/%s-remove-%d-links-base"
+solution_template = "%s-connected-cplex.xml"
+demand_file_template = "../demand/%s-%s/%d.txt"
+result_file_template = "result-compare-use-paper-%s"
+files = 100
+
+loop = 20
+diff = 1000
+
+remove_links_n = {'abilene':5, 'geant':16}
+
+for t in ['abilene','geant']:
+    result_file = result_file_template % (t)
+    for alpha in range(1, remove_links_n[t]):
+        connected_topology = connected_topology_template % t
+        final_topology = final_topology_template % (t, alpha)
+        remove_links = remove_links_template % (t, alpha)
+        final_topology_base = final_topology_base_template % (t, alpha)
+        remove_links_base = remove_links_base_template % (t, alpha)
+        solution = solution_template % t
+
+        upper = 0
+        if is_gravity:
+            upper = 1.5
+            type_random = "gravity"
+        else:
+            if t == 'abilene':
+                upper = 9424.0
+            elif t == 'geant':
+                upper = 1956.0
+
+        bound = [0, 1.5]
+
+        # Generate the global routes for traffic sets 
+        # Calculate the global maximum utilization for specific traffic matrix sets
+        global_routes = common.global_routes(final_topology, bound, is_gravity)
+        global_routes_base = common.global_routes(final_topology_base, bound, is_gravity)
+
+        max_utilization = 0
+        max_utilization_base = 0
+        for num in range(files):
+            print("Round %d\n" % num)
+
+            demand_file = demand_file_template % (type_random, t, num)
+            f = open(demand_file, "r")
+            line = f.readline()
+            f.close()
+            if int(line.strip()) == 0:
+                continue
+
+            #f = open(result_file,"a")
+            # Calculate the optimal maximum utilization for specific traffic matrix
[…]

### 2014-12-02 experiment/cplex/compare.py
Add png to paper

@@ -17,7 +17,7 @@ remove_links_base_template = "../topology/remove/%s-remove-%d-links-base"
 solution_template = "%s-connected-cplex.xml"
 demand_file_template = "../demand/%s-%s/%d.txt"
 result_file_template = "result-compare-%s"
-files = 100
+files = 50
 
 loop = 20
 diff = 1000

### 2014-12-02 experiment/cplex/algorithms.py
Add png to paper

@@ -114,8 +114,6 @@ def ksp_yen(graph, node_start, node_end, max_k=2):
 # the distances and previous lists are returned.
 #
 def dijkstra(graph, node_start, node_end=None, visited=[]):
-    if node_end == None:
-        print visited
     distances = {}      
     previous = {}       
     Q = priorityDictionary()

### 2014-12-02 experiment/cplex/new_adjust_route_in_new_topology.py

@@ -41,26 +41,6 @@ def adjust_route(topology, remove_file, routes, link_order):
 
         line = f.readline()
     f.close()
-    yen_paths = algorithms.ksp_yen(g, 1, 5, 20)
-    print yen_paths
-
-    gg = DiGraph()
-    f = open(topology)
-    line = f.readline()
-    line = f.readline()
-    while line:
-        s = line.rstrip().split(' ')
-        lls = int(s[0])
-        lld = int(s[1])
-
-        #g.add_nodes([int(s[0]), int(s[1])])
-        gg.add_edge(lls, lld, link_order[lls,lld][1] / link_order[lls,lld][0])
-        gg.add_edge(lld, lls, link_order[lls,lld][1] / link_order[lls,lld][0])
-
-        line = f.readline()
-    f.close()
-    yen_paths = algorithms.ksp_yen(gg, 3, 9, 20)
-    print yen_paths
 
     path_replace = dict()
     for ls,ld in links:
@@ -70,7 +50,7 @@ def adjust_route(topology, remove_file, routes, link_order):
         path_replace[ls,ld] = [[y_path['path'], 0, 0] for y_path in yen_paths]
         #path_replace[ls,ld] = g.find_path_without_weight(ls,ld)
 
-    print path_replace
+    #print path_replace
     #print link_order
     
     def sort_path(paths):
@@ -170,9 +150,9 @@ def adjust_route(topology, remove_file, routes, link_order):
     return routes
 
 if __name__ == '__main__':
-    topology = '../topology/final/abilene-final-topology-3'
+    topology = '../topology/final/abilene-final-topology-2'
     routes = xml.get_route('abilene-connected-cplex.xml')
-    remove_file = '../topology/remove/abilene-remove-3-links'
+    remove_file = '../topology/remove/abilene-remove-2-links'
 
     topology_connect = '../topology/connected/abilene-connected-topology'
     solutions = 'abilene-connected-cplex.xml'

### 2014-12-02 experiment/cplex/new_adjust_route_in_new_topology.py
Add png to paper

@@ -150,12 +150,12 @@ def adjust_route(topology, remove_file, routes, link_order):
     return routes
 
 if __name__ == '__main__':
-    topology = '../topology/final/abilene-final-topology-2'
-    routes = xml.get_route('abilene-connected-cplex.xml')
-    remove_file = '../topology/remove/abilene-remove-2-links'
+    topology = '../topology/final/geant-final-topology-1'
+    routes = xml.get_route('geant-connected-cplex.xml')
+    remove_file = '../topology/remove/geant-remove-1-links'
 
-    topology_connect = '../topology/connected/abilene-connected-topology'
-    solutions = 'abilene-connected-cplex.xml'
+    topology_connect = '../topology/connected/geant-connected-topology'
+    solutions = 'geant-connected-cplex.xml'
     link_order = xml.get_link_order_with_attr(solutions, topology_connect)
 
     adjust_route(topology, remove_file, routes, link_order)

### 2014-12-02 experiment/cplex/pruning_final_topology.py

@@ -37,7 +37,7 @@ for name in files:
         links[d][s] = c
     f.close()
 
-    link_order = xml.get_link_order("../cplex/%s-connected-cplex.sol" % name, topology)
+    link_order = xml.get_link_order("../cplex/%s-connected-cplex.xml" % name, topology)
     remove_links = []
     remove_n = 0
     for l in link_order:

### 2014-12-02 experiment/cplex/algorithms.py
Add png to paper

@@ -24,6 +24,7 @@
 from operator import itemgetter
 from prioritydictionary import priorityDictionary
 from graph import DiGraph
+from copy import deepcopy
 
 
 ## @package YenKSP
@@ -113,9 +114,12 @@ def ksp_yen(graph, node_start, node_end, max_k=2):
 # the distances and previous lists are returned.
 #
 def dijkstra(graph, node_start, node_end=None, visited=[]):
+    if node_end == None:
+        print visited
     distances = {}      
     previous = {}       
     Q = priorityDictionary()
+    visited_copy = deepcopy(visited)
     
     for v in graph:
         
@@ -134,11 +138,11 @@ def dijkstra(graph, node_start, node_end=None, visited=[]):
     Q[node_start] = 0
     
     for v in Q:
-        visited.append(v)
+        visited_copy.append(v)
         if v == node_end: break
 
         for u in graph[v]:
-            if u in visited:
+            if u in visited_copy:
                 continue
             cost_vu = 0
             if distances[v] > graph[v][u]:

### 2014-12-02 experiment/cplex/graph.py

@@ -24,6 +24,7 @@
 import os
 import json
 import random
+from copy import deepcopy
 from graphviz import Graphviz
 
 
@@ -72,7 +73,7 @@ class DiGraph:
         
         self.load()
         
-        self._painter = Graphviz()
+        #self._painter = Graphviz()
         return
 
     ## Gets the edges of a specified node.

### 2014-12-02 experiment/cplex/new_adjust_route_in_new_topology.py

@@ -1,7 +1,7 @@
 import os, random
 from graph import DiGraph
 import algorithms
-from copy import deepcopy
+from copy import deepcopy,copy
 import paper_cplex_input_without_tm as cplex
 import utilization_from_route as utils
 import parse_xml as xml
@@ -25,33 +25,52 @@ def adjust_route(topology, remove_file, routes, link_order):
         links.append((ls,ld))
         line = f.readline()
     f.close()
-    
-    #g = Graph()
+
     g = DiGraph()
     f = open(topology)
     line = f.readline()
     line = f.readline()
     while line:
         s = line.rstrip().split(' ')
-        ls = int(s[0])
-        ld = int(s[1])
+        lls = int(s[0])
+        lld = int(s[1])
 
         #g.add_nodes([int(s[0]), int(s[1])])
-        g.add_edge(ls, ld, link_order[ls,ld][1] / link_order[ls,ld][0])
-        g.add_edge(ld, ls, link_order[ls,ld][1] / link_order[ls,ld][0])
+        g.add_edge(lls, lld, link_order[lls,lld][1] / link_order[lls,lld][0])
+        g.add_edge(lld, lls, link_order[lls,lld][1] / link_order[lls,lld][0])
 
         line = f.readline()
     f.close()
+    yen_paths = algorithms.ksp_yen(g, 1, 5, 20)
+    print yen_paths
 
+    gg = DiGraph()
+    f = open(topology)
+    line = f.readline()
+    line = f.readline()
+    while line:
+        s = line.rstrip().split(' ')
+        lls = int(s[0])
+        lld = int(s[1])
 
+        #g.add_nodes([int(s[0]), int(s[1])])
+        gg.add_edge(lls, lld, link_order[lls,lld][1] / link_order[lls,lld][0])
+        gg.add_edge(lld, lls, link_order[lls,lld][1] / link_order[lls,lld][0])
+
+        line = f.readline()
+    f.close()
+    yen_paths = algorithms.ksp_yen(gg, 3, 9, 20)
+    print yen_paths
 
     path_replace = dict()
     for ls,ld in links:
+        #g._data = deepcopy(graph_data_copy)
         yen_paths = algorithms.ksp_yen(g, ls, ld, 20)
+        #print yen_paths
         path_replace[ls,ld] = [[y_path['path'], 0, 0] for y_path in yen_paths]
         #path_replace[ls,ld] = g.find_path_without_weight(ls,ld)
 
-    #print path_replace
+    print path_replace
     #print link_order
     
[…]

### 2014-12-02 experiment/cplex/compare.py
New adjust way, not between ab, but cd

@@ -51,6 +51,16 @@ for t in ['abilene','geant']:
         global_routes = xml.get_route(solution)
         link_order = xml.get_link_order_with_attr(solution, connected_topology)
 
+        global_routes_copy = deepcopy(global_routes)
+        link_order_copy = deepcopy(link_order)
+        new_global_routes = adjust.adjust_route(final_topology, remove_links, global_routes_copy, link_order_copy)
+        new_global_routes_fixed = adjust.fixed_route(new_global_routes)
+
+        global_routes_base_copy = deepcopy(global_routes)
+        link_order_copy = deepcopy(link_order)
+        new_global_routes_base = adjust.adjust_route(final_topology_base, remove_links_base, global_routes_base_copy, link_order_copy)
+        new_global_routes_fixed = adjust.fixed_route(new_global_routes_base)
+
         max_utilization = 0
         max_utilization_base = 0
         for num in range(files):
@@ -71,19 +81,19 @@ for t in ['abilene','geant']:
 
             #TODO Change Route
             #print("Begin adjust route")
-            global_routes_copy = deepcopy(global_routes)
-            link_order_copy = deepcopy(link_order)
-            new_global_routes = adjust.adjust_route(final_topology, remove_links, global_routes_copy, link_order_copy)
+            #global_routes_copy = deepcopy(global_routes)
+            #link_order_copy = deepcopy(link_order)
+            #new_global_routes = adjust.adjust_route(final_topology, remove_links, global_routes_copy, link_order_copy)
 
             #print("Begin calculate utilization")
-            global_utilization = common.global_utilization(final_topology, new_global_routes, demand_file, loop)
+            global_utilization = common.global_utilization(final_topology, new_global_routes_fixed, demand_file, 1)
             #print('Global Utilization is %f\n' % global_utilization)
             #f.write('%10.4f\t' % global_utilization)
 
-            global_routes_base_copy = deepcopy(global_routes)
-            link_order_copy = deepcopy(link_order)
-            new_global_routes_base = adjust.adjust_route(final_topology_base, remove_links_base, global_routes_base_copy, link_order_copy)
-            global_utilization_base = common.global_utilization(final_topology_base, new_global_routes_base, demand_file, loop)
+            #global_routes_base_copy = deepcopy(global_routes)
+            #link_order_copy = deepcopy(link_order)
+            #new_global_routes_base = adjust.adjust_route(final_topology_base, remove_links_base, global_routes_base_copy, link_order_copy)
[…]

### 2014-12-02 experiment/cplex/new_adjust_route_in_new_topology.py

@@ -8,6 +8,7 @@ import parse_xml as xml
 from deep_first_search_path import *
 
 def adjust_route(topology, remove_file, routes, link_order):
+    # get remove_links
     f = open(remove_file)
     links = []
     line = f.readline()
@@ -26,6 +27,7 @@ def adjust_route(topology, remove_file, routes, link_order):
         line = f.readline()
     f.close()
 
+    # get final topology
     g = DiGraph()
     f = open(topology)
     line = f.readline()
@@ -42,17 +44,6 @@ def adjust_route(topology, remove_file, routes, link_order):
         line = f.readline()
     f.close()
 
-    path_replace = dict()
-    for ls,ld in links:
-        #g._data = deepcopy(graph_data_copy)
-        yen_paths = algorithms.ksp_yen(g, ls, ld, 20)
-        #print yen_paths
-        path_replace[ls,ld] = [[y_path['path'], 0, 0] for y_path in yen_paths]
-        #path_replace[ls,ld] = g.find_path_without_weight(ls,ld)
-
-    #print path_replace
-    #print link_order
-    
     def sort_path(paths):
         for i in range(len(paths)):
             for j in range(i, len(paths)):
@@ -77,85 +68,85 @@ def adjust_route(topology, remove_file, routes, link_order):
             p[1] = cf
             sort_path(paths)
 
-    for (ls,ld) in path_replace:
-        paths = path_replace[ls,ld]
-        calculate_cf(paths, link_order)
-
-    for (ls,ld) in path_replace:
-        paths = path_replace[ls,ld]
-        flows = link_order[ls,ld][1]
-
-        GAP_NUM = 10
-        gap = flows / GAP_NUM
-        used = 0
-        for loop in range(GAP_NUM):
-            #do something
-            for i in range(len(paths[0][0]) - 1):
-                s = paths[0][0][i]
-                d = paths[0][0][i+1]
-
-                if d < s:
-                    tmp = s
-                    s = d
-                    d = tmp
-
-                link_order[s,d][1] += gap
-            paths[0][2] += 0.1
-            calculate_cf(paths, link_order)
-            #print paths
-            #print used
-            used += gap
-
-        path_replace[ls,ld] = paths
-
-    
-    select_path = []
     for ls,ld in links:
         #print(ls,ld)
         for s,d in routes:
-            for i in range(len(routes[s,d])):
-                for j in range(len(routes[s,d][i][0]) - 1):
[…]

### 2014-12-02 experiment/cplex/new_adjust_route_in_new_topology.py
New adjust way, not between ab, but cd

@@ -94,7 +94,8 @@ def adjust_route(topology, remove_file, routes, link_order):
                         break
             if remove_weight != 0:
                 # Find k-shortest-paths between s,d
-                yen_paths = [[yen_path['path'], 0, 0] for yen_path in algorithms.ksp_yen(g, s, d, 20)]
+                tmp_paths = algorithms.ksp_yen(g, s, d, 20)
+                yen_paths = [[yen_path['path'], 0, 0] for yen_path in tmp_paths]
                 
                 # make sure the proportion of every yen_path
                 steps = 10.0

### 2014-12-02 experiment/cplex/compare.py
Debug for node_end 0

@@ -87,7 +87,8 @@ for t in ['abilene','geant']:
             #new_global_routes = adjust.adjust_route(final_topology, remove_links, global_routes_copy, link_order_copy)
 
             #print("Begin calculate utilization")
-            global_utilization = common.global_utilization(final_topology, new_global_routes_fixed, demand_file, 1)
+            new_global_routes_fixed_copy = deepcopy(new_global_routes_fixed)
+            global_utilization = common.global_utilization(final_topology, new_global_routes_fixed_copy, demand_file, 1)
             print global_utilization
             #print('Global Utilization is %f\n' % global_utilization)
             #f.write('%10.4f\t' % global_utilization)
@@ -95,7 +96,8 @@ for t in ['abilene','geant']:
             #global_routes_base_copy = deepcopy(global_routes)
             #link_order_copy = deepcopy(link_order)
             #new_global_routes_base = adjust.adjust_route(final_topology_base, remove_links_base, global_routes_base_copy, link_order_copy)
-            global_utilization_base = common.global_utilization(final_topology_base, new_global_routes_base_fixed, demand_file, 1)
+            new_global_routes_base_fixed_copy = deepcopy(new_global_routes_base_fixed)
+            global_utilization_base = common.global_utilization(final_topology_base, new_global_routes_base_fixed_copy, demand_file, 1)
             print global_utilization_base
 
             if max_utilization_base < (global_utilization_base / optimal_utilization):

### 2014-12-02 experiment/cplex/new_adjust_route_in_new_topology.py
Debug for node_end 0

@@ -142,10 +142,10 @@ def fixed_route(routes):
 
 
 if __name__ == '__main__':
-    topology = '../topology/final/abilene-final-topology-1'
+    topology = '../topology/final/abilene-final-topology-1-base'
     solutions = 'abilene-connected-cplex.xml'
     routes = xml.get_route(solutions)
-    remove_file = '../topology/remove/abilene-remove-1-links'
+    remove_file = '../topology/remove/abilene-remove-1-links-base'
 
     topology_connect = '../topology/connected/abilene-connected-topology'
     link_order = xml.get_link_order_with_attr(solutions, topology_connect)

### 2014-12-04 experiment/demand/generate_gravity_demand.py
modify paper

@@ -2,9 +2,9 @@ import random
 
 topology_template = '../topology/connected/%s-connected-topology'
 demand_template = '../demand/gravity-%s/%d.txt'
-files = 1000
-w = 1.5
-topology_name = ['abilene', 'geant']
+files = 1001
+w = 1
+topology_name = ['abilene']
 
 for t in topology_name:
     topology = topology_template % t
@@ -42,7 +42,7 @@ for t in topology_name:
     random_base = 0.001
     '''
 
-    for n in range(files):
+    for n in range(1000, files):
         demand = demand_template % (t, n)
         f = open(demand, "w")
         f.write("%d\n" % (node_n * node_n - node_n))
@@ -53,6 +53,7 @@ for t in topology_name:
                     continue
 
                 f.write("%d %d %0.3f\n" % (s, d, random.uniform(nodes[s] * nodes[d] / w, nodes[s] * nodes[d] * w)))
+                print "%d %d %0.3f\n" % (s, d, random.uniform(nodes[s] * nodes[d] / w, nodes[s] * nodes[d] * w))
 
         f.close()
 

### 2014-12-04 paper.tex
Add png to paper
modify paper

@@
 \ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
+   \usepackage[pdftex]{graphicx}
   % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
+   \graphicspath{{./png/}}
   % and their extensions so you won't have to specify these with
   % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+   \DeclareGraphicsExtensions{.png}
 \else
@@
 satisfy power and utilization requirement for any traffic matrix given?
+
+\includegraphics[width=10cm]{net5}
 
@@
 
+\section{Samples}
+For showing obilious performance ratio with energy constraint really make a difference in the switching off link 
+process, we will explain it in two simple topologies, cliques and cycles. On the other hand, we also say that
+there will be an upper bound for obilious performance ratio with energy constraint, and get the bound according
+to the topology.
+
+Cycles topology connect all the nodes by a cycle, any node in which has two links joined. Figure 1 show the six
+nodes cycles topology, let nodes named from $A$ to $F$ and links named by its two vertices, such as $l_{ab}$.
+Without loss of generality,
+
 \section{Conclusion}

### 2014-12-04 experiment/cplex/graph.py
debug for fatal error

@@ -71,6 +71,7 @@ class DiGraph:
         if name:
             self._name = name
         
+        self._data = {}
         self.load()
         
         #self._painter = Graphviz()

### 2014-12-04 experiment/cplex/new_adjust_route_in_new_topology.py

@@ -2,6 +2,7 @@ import os, random
 from graph import DiGraph
 import algorithms
 from copy import deepcopy,copy
+import global_route_with_tm_bound as common
 import paper_cplex_input_without_tm as cplex
 import utilization_from_route as utils
 import parse_xml as xml
@@ -71,7 +72,7 @@ def adjust_route(topology, remove_file, routes, link_order):
     for ls,ld in links:
         #print(ls,ld)
         for s,d in routes:
-            route_paths = deepcopy(routes[s,d])
+            route_paths = routes[s,d]
             remove_route = []
             remove_weight = 0
             for path, weight in route_paths:
@@ -190,10 +191,14 @@ def check_route(routes, link_order):
 
 
 if __name__ == '__main__':
-    topology = '../topology/final/abilene-final-topology-3-base'
-    solutions = 'abilene-connected-cplex.xml'
+    topology = '../topology/final/abilene-final-topology-4'
+    topology_base = '../topology/final/abilene-final-topology-4-base'
+    #solutions = 'abilene-connected-cplex.xml'
+    solutions = '1_abilene_cplex.xml'
     routes = xml.get_route(solutions)
-    remove_file = '../topology/remove/abilene-remove-3-links-base'
+    remove_file_base = '../topology/remove/abilene-remove-4-links-base'
+    remove_file = '../topology/remove/abilene-remove-4-links'
+    demand_file = '../demand/gravity-abilene/1000.txt'
     f = open(remove_file)
     removes = []
     line = f.readline()
@@ -215,10 +220,26 @@ if __name__ == '__main__':
 
     topology_connect = '../topology/connected/abilene-connected-topology'
     link_order = xml.get_link_order_with_attr(solutions, topology_connect)
+    
+    min_routes = xml.get_route_with_demand("1_min_abilene_cplex.xml", demand_file)
+    #min_routes = xml.get_route_with_demand("min_cplex_output.xml", demand_file)
+    #print utils.get_utilization_with_probability(topology_connect, min_routes, 1)
+
     #print xml.get_link_order(solutions, topology_connect)
 
     #route = fixed_route(adjust_route(topology, remove_file, routes, link_order))
     check_route_in_detail(routes, link_order, [])
-    route = adjust_route(topology, remove_file, routes, link_order)
+
+    routes_copy = deepcopy(routes)
+    link_order_copy = deepcopy(link_order)
+    route = adjust_route(topology_base, remove_file_base, routes_copy, link_order_copy)
[…]

### 2014-12-04 experiment/cplex/optimal_route_with_tm.py

@@ -29,6 +29,6 @@ def optimal_utilization(topology, demand_file, loop):
 
 if __name__ == '__main__':
     connected_topology = "../topology/connected/abilene-connected-topology"
-    demand_file = "../demand/gravity-abilene/0.txt"
-    min_routes = xml.get_route_with_demand("min_cplex_output.xml", demand_file)
+    demand_file = "../demand/gravity-abilene/1000.txt"
+    min_routes = xml.get_route_with_demand("1_min_abilene_cplex.xml", demand_file)
     print utils.get_utilization_with_probability(connected_topology, min_routes, 1)

### 2015-01-08 paper.tex
add experiment plot and modify paper

@@
 and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve 
-the problem in two phases. REAR select sleeping links based on extended algebraic connectivity, and compute the 
+the problem in two phases. REAR select sleeping links based on extended robust link utilization, and compute the 
 routing based on a classical demand-oblivious routing algorithm. We evaluate our algorithms on real and 
@@
 and $E$ is the set of links (either link between routers or router and end-host). In graph $G$, two vertices $u$ and $v$
-are called connected if $G$ contains a path from $u$ to $v$. Then We say graph $G$ is connected, if and only if 
-every pair of vertices in the graph is connected.
+are called connected if $G$ contains a path between $u$ and $v$. Then We say graph $G$ is connected, if and only if 
+arbitrary pair of vertices in the graph is connected.
 
@@
 $G$. Then, choosing the connected graph from $\theta(G)$ to consist a new set, denoted by 
-$\Theta(G) = \{G | G \in \theta(G) \& \& G is connected\}$. We call $\Theta(G)$ as successor of $G$.
+$\Theta(G) = \{G | G \in \theta(G) \ \& \& \ G\ is\ connected\}$. We call $\Theta(G)$ as successor of $G$.
 
-A $traffic matrix$ (abbreviation as TM below) is the set of traffic of each Origin-Destination(OD) pair in 
+A $traffic\ matrix$ (abbreviation as TM below) is the set of traffic between each Origin-Destination(OD) pair in 
 network $G$, and a $routing$ specifies how traffic of each OD pair is routed across the network. Usually, there are 
-multiple paths for each OD pair and each path routes a fraction of the traffic. Let $m$ denote the $traffic matrix$, 
+multiple paths for each OD pair and each path routes a fraction of the traffic. Let $m$ denote the $traffic\ matrix$, 
 which can be represented by a set of trinary group like $(a, b, d_{ab}$, where $a$ and $b$ is the origin and 
@@
 \end{equation}
-where $cap_{ij}$ si the capacity of the link $(i,j)$.
+where $cap_{ij}$ is the capacity of the link $(i,j)$.
 
-A common metric for the performance of a given routing with respect to a certain TM is the $maximum link utilization$.
+A common metric for the performance of a given routing with respect to a certain TM is the $maximum\ link\ utilization$.
 This is the maximum utilization of link over all ones, Formally, the maximum link utilization of a routing $r$ on 
@@
 
-The $optimal routing$ in all the possible route $R$ for network $G$ is a routing which minimize the maximum utilization,
+The $optimal\ routing$ in all the possible route $R$ for network $G$ is a routing which minimize the maximum utilization,
 the minimum maximum utilization is called optimal utilization, can be represented by :
@@
 
-The $performance ratio$ of a given routing $r$ on a given TM $m$ and a given network $G$ meaures how far from being 
+The $performance\ ratio$ of a given routing $r$ on a given TM $m$ and a given network $G$ meaures how far from being 
 optimal, it is defined as the maximum link utilization divided by optimal utilization on the $m$ and $G$, as following : 
@@
 unique, the current routing always be the optimal routing. More generally, we should make a little modification
-for the $performance ratio$ as the network self changes.
+for the $performance\ ratio$ as the network self changes.
 
 Let $G$ be the origin network, and the $G^* \in \Theta(G)$ be the successor network from $G$ after closing/removing
-some link, we define $performance ratio between different graphs$ as the performance ratio of successor graph divide 
+some link, we define $performance\ ratio\ between\ different\ graphs$ as the performance ratio of successor graph divide 
 the optimal performance ratio of father graph, like :
@@
 Now we can say that, if a successor network arrive the minimum performance ratio, it is the ``robust'' successor 
-network graph. Formally, we define the performance ratio as $optimal successor performance ratio$ :
+network graph. Formally, we define the performance ratio as $optimal\ successor\ performance\ ratio$ :
 \begin{equation}
@@
 Three hostes include : A, B, C, Three links are with repectively capacity of 3M, 4M and 2M. For simpleness, we suppose 
-there are two TM : ${(A,B,2M), (A,C,1M)}, {(A,B,1M), (A,C,1M)}$.For each traffic matrix, the optimal route is 
+there are two TM : ${(A,B,2M), (A,C,1M)}$ and ${(A,B,1M), (A,C,1M)}$. For each traffic matrix, the optimal route is 
 obvious, we will trace 2M from A to B across the lower link and trace the 1M from A to C across the upper one 
@@
 lower link for the second traffic matrix, whose maximum link utilization is 0.5 as well.
+
+\vspace*{0.2in}
+\includegraphics[width=8cm]{3-nodes-example}
+\vspace*{0.2in}
 
@@
 In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links 
-should be sleeping from the origin topology based on extended algebraic connectivity, then compute the robust 
+should be sleeping from the origin topology based on extended robust link utilization, then compute the robust 
 routing by demand-oblivious routing algorithm.

### 2015-01-08 experiment/cplex/parse_xml.py

@@ -251,6 +251,8 @@ def get_link_order_with_attr(solution, topology):
 
     return lo
 
+
+# return the links ordered by capacity/traffic from larger to less
 def get_link_order(solution, topology):
     st_paths = get_route(solution)
 

### 2015-01-08 experiment/cplex/pruning_link_by_link.py

@@ -1,6 +1,10 @@
 import parse_xml as xml
 import global_route_with_tm_bound as cplex
 
+# check the graph represented by links if connected.
+# nodes is the set of visited nodes, stack is the stack of to-be-visited nodes
+# every time pop a node from stack, visit it, 
+# and finally check if all the nodes is visited.
 def is_connected(links, nodes_n):
     stack = [0]
     nodes = set()

### 2015-01-08 experiment/plot/exp1.py

@@ -1,0 +1,25 @@
+import matplotlib.pyplot as plt
+
+result_file_template = "result-compare-abilene"
+
+f = open(result_file_template)
+line = f.readline();
+base = []
+new = []
+x = []
+while line:
+    tokens = line.strip().split()
+    base.append(float(tokens[1]))
+    new.append(float(tokens[2]))
+    x.append(float(tokens[0]))
+
+    line = f.readline()
+
+f.close()
+
+plt.plot(x, base, 'r--')
+plt.plot(x, new, 'b--')
+#plt.axis([0, 6, 0, 20])
+plt.show()
+
+

### 2015-01-08 experiment/plot/exp2.py

@@ -1,0 +1,45 @@
+import matplotlib.pyplot as plt
+
+result_file_template = "middle-compare-abilene"
+count = 1000
+remove = 5
+
+f = open(result_file_template)
+line = f.readline();
+
+base = [([0] * count) for i in range(remove)]
+new = [([0] * count) for i in range(remove)]
+x = [i for i in range(count)]
+while line:
+    tokens = line.strip().split()
+    r = int(tokens[0])
+    n = int(tokens[1])
+    base[r][n] = float(tokens[2])
+    new[r][n] = float(tokens[3])
+
+    line = f.readline()
+
+f.close()
+
+for i in range(remove):
+    for j in range(count):
+        for k in range(j, count):
+            if (base[i][j] > base[i][k]):
+                tmp = base[i][j]
+                base[i][j] = base[i][k]
+                base[i][k] = tmp
+    plt.plot(base[i], x, 'r--')
+#plt.plot(base[4], x, 'r--')
+
+for i in range(remove):
+    for j in range(count):
+        for k in range(j, count):
+            if (new[i][j] > new[i][k]):
+                tmp = new[i][j]
+                new[i][j] = new[i][k]
+                new[i][k] = tmp
+    plt.plot(new[i], x, 'b--')
+#plt.axis([0, 6, 0, 20])
+plt.show()
+
+

### 2015-01-08 experiment/plot/exp2_nosort.py

@@ -1,0 +1,33 @@
+import matplotlib.pyplot as plt
+
+result_file_template = "middle-compare-abilene"
+count = 1000
+remove = 5
+
+f = open(result_file_template)
+line = f.readline();
+
+base = [([0] * count) for i in range(remove)]
+new = [([0] * count) for i in range(remove)]
+x = [i for i in range(count)]
+while line:
+    tokens = line.strip().split()
+    r = int(tokens[0])
+    n = int(tokens[1])
+    base[r][n] = float(tokens[2])
+    new[r][n] = float(tokens[3])
+
+    line = f.readline()
+
+f.close()
+
+for i in range(remove):
+    plt.plot(x, base[i], 'r--')
+
+for i in range(remove):
+    plt.plot(x, new[i], 'b--')
+
+#plt.axis([0, 6, 0, 20])
+plt.show()
+
+

### 2015-01-08 experiment/plot/exp2_sort.py

@@ -1,0 +1,45 @@
+import matplotlib.pyplot as plt
+
+result_file_template = "middle-compare-abilene"
+count = 1000
+remove = 5
+
+f = open(result_file_template)
+line = f.readline();
+
+base = [([0] * count) for i in range(remove)]
+new = [([0] * count) for i in range(remove)]
+x = [i for i in range(count)]
+while line:
+    tokens = line.strip().split()
+    r = int(tokens[0])
+    n = int(tokens[1])
+    base[r][n] = float(tokens[2])
+    new[r][n] = float(tokens[3])
+
+    line = f.readline()
+
+f.close()
+
+for i in range(remove):
+    for j in range(count):
+        for k in range(j, count):
+            if (base[i][j] > base[i][k]):
+                tmp = base[i][j]
+                base[i][j] = base[i][k]
+                base[i][k] = tmp
+    plt.plot(x, base[i], 'r--')
+
+for i in range(remove):
+    for j in range(count):
+        for k in range(j, count):
+            if (new[i][j] > new[i][k]):
+                tmp = new[i][j]
+                new[i][j] = new[i][k]
+                new[i][k] = tmp
+    plt.plot(x, new[i], 'b--')
+
+#plt.axis([0, 6, 0, 20])
+plt.show()
+
+

### 2015-01-12 paper.tex
modify paper

@@
 and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve 
-the problem in two phases. REAR select sleeping links based on extended robust link utilization, and compute the 
-routing based on a classical demand-oblivious routing algorithm. We evaluate our algorithms on real and 
-synthetic topologies. The simulation results show that REAR can save XX\% of line card power while the performance 
-ratio is less than XX.
+the problem in two phases. REAR select sleeping links based on extended robust link utilization or algebraic 
+connectivity, and compute the routing based on a classical demand-oblivious routing algorithm. 
+We evaluate our algorithms on real and synthetic topologies. The simulation results show that REAR can save 
+XX\% of line card power while the performance ratio is less than XX.
 \end{abstract}
@@
 In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links 
-should be sleeping from the origin topology based on extended robust link utilization, then compute the robust 
-routing by demand-oblivious routing algorithm.
+should be sleeping from the origin topology based on extended robust link utilization or algebraic connectivity, 
+then compute the robust routing by demand-oblivious routing algorithm. There are two metrics
+for selecting removed links, our two-phase algorithm is flexible because we can replace the metric with whatever
+metric which will be proposed in the future.
 
-\subsection{Extend Algebraic Connectivity}
+\subsection{Algebraic Connectivity}
 Network topology is represented by $G = (V, E)$ as mentioned in Model section, where $V$ is the set of vertices
@@
 In the mathematical field of graph theory, the number of eigenvalues equal to 0 is the number of connected 
-componements of $G$, so the smallest eigenvalue always be 0. And we call the second smallest one as
+componements of $G$, so the smallest eigenvalue always be 0 in arbitrary graph . And we call the second smallest one as
 algebraic connectivity, which is greater than 0 if and only if graph $G$ is connected. Further more,  
 it measures the connectivity and stability of graph, the greater of which, the more connective of graph;
-and it is a metric of average distance between any two vertices of graph $G$.
+and it is a metric of average distance between any two vertices of graph $G$. We call the algebraic connectivity as
+$\lambda_2(G)$.
 
-As far as we know, 
-algebraic connectivity regard every link the same, without considering the capacity of each one, but it is 
-ridiculous in network. It is easy to see, link with greater capacity is more important than the same one
-with lower capacity. and in graph theory, algebraic connectivity value monotonically increased when we
-increase the weight of link between vertices. So we extend the algebraic connectivity definition by following ways:
-
-\begin{enumerate}
-	\item We change the Adjacency Matrix from binary-matrix to float-matrix, i.e. if $(i,j) \in E$ we set the $a_{ij}$
-with the capacity of link $l_{ij}$ instead of binary value 1.
-	\item Degree Matrix is not ever the denotation for the degree of nodes, but the conbined capacity of all the links
-adjacent to the node, there is still exist the equation: $d_{ij} == \sum_{j} a_{ij}$
-	\item No modification for definition of Laplacian Matrix
-\end{enumerate}
-
-We calculate new extend algebraic connectivity from the new Laplacian matrix, denoted by $\lambda_2(G)$.
-
-Topology always have different extend algebraic connectivity values, it is clear that when one link is added or 
-removed from the graph, the extend algebraic connectivity value changes accordingly. And we say the changed value
+Topology always have different algebraic connectivity values, it is clear that when one link is added or 
+removed from the graph, the algebraic connectivity value changes accordingly. And we say the changed value
 is the impact of this link on the graph. Supposed we sleep link $l$ from graph $G$, new graph is described as $G^*$, 
@@
 \end{equation}
-where $\lambda_2(G)$ and $\lambda_2(G^*)$ is extend algebraic connectivity of $G$ and $G^*$ respectly.
+where $\lambda_2(G)$ and $\lambda_2(G^*)$ is algebraic connectivity of $G$ and $G^*$ respectly.
 
@@
 
+\subsection{Extended Robust Link Utilization}
+The demand-oblivious routing is well studied before, which means that this routing is not always the best one for 
+specific $TM$, but good enough for a range of $TMs$. we mentioned the definition of link utilization above when 
+demand and routing are determined, as demand become oblivious, the definition is also not suitable. So we define
+a notation named $extended\ robust\ link\ utilization$ replace the normal link utilization like :
+\begin{equation}
+	u^e_{ij} = \frac {\sum_{a,b}f_{ab}(i,j)} {cap_{ij}}
+\end{equation}
+
+Proposing this definition for two consideration: firstyly, the more flows across the link, the greater the $u^e_{ij}$ is;
+secondly, the more fraction of traffic in one flow across the link, the greater the $u^e_{ij}$ is. The link with greater
+extended robust link utilization is also more important than others in a sense. Although there is no demand here, we mean
+there is more probability that this link have greater link utilization when specific demand come. Similarly, we define 
+the impact of link $l$ as :
+\begin{equation}
+    \Delta_l = u^e_{l}
+\end{equation}
+
+And there is the same conclusion that a link $l$ affect more if $\Delta_l$ is greater.
+
 \subsection{Algorithm Phase One}
-REAR sleep as many links as possible without losing much connectivity of graph. Originly,  we should
-calculate impact of all the links and sleep the lowest one from the graph, then repeat calculate and remove
+REAR sleep as many links as possible without losing much connectivity or transportation of graph for different metrics. 
+Originly,  we should calculate impact of all the links and sleep the lowest one from the graph, then repeat calculate and remove
 process until arrive some specific threhold. Obviously, it is NP-Hard, following is a heuristic algorithm.
@@
 Pay attention we only compute the link impact once at the begining of algorihtm, and the ordered list $\Gamma$ show 
-the order of `importantance` among links in the connectivity of the graph.
+the order of `importance` among links in the graph.
 
@@
 We denote the set of the sleeping links as $S$, and the output of this phase is final graph $G^* = (V, E-S)$. We set 
-$S = \emptyset$, and repeat our selecting process, each iteration we select one link and put it into $S$. 
-In iteration $i$, algorithm scan links as the order of $\Gamma$ and choose one which is still not in the $S$, we try to
-remove this link from the graph, if some metric of the current graph do not arrive the threhold we put the link into
-$S$ then go next iteration, or choose the next link from the $\Gamma$ for trying to remove otherwise. Algorithm
-stop until all the links in $\Gamma$ is tried but there is no one to satisfy the threhold.
+$S = \emptyset$, and repeat our selecting process, each iteration we select one link, remove it from $\Gamma$ and put it into $S$. 
+In iteration $i$, algorithm scan links as the order in $\Gamma$, we try to
+remove this link from the graph to check if the graph is still connected and the energy conservation have not arrive the threshold.
+If so, we select this one then go next iteration.
+Otherwise choose the next link from $\Gamma$ for trying to remove. Algorithm
+stop until all the links in $\Gamma$ is tried but no one is satisfied with both connectivity and power threhold.
 
-So before going ahead our algorithm, there is another thing we should done, what is the threhold for the graph.
-It does matter for what we concern most of the graph, in our graph, we choose the power consumption. 
+So before going ahead our algorithm, there is another thing we should done, how to measure the power of graph.
 We simple take an power model from `Green TE` showed in Table xx, and defined the difference of power consumption 
@@
 
-If we set $diff_c$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
+If we set $diff_p$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
 iteration, the power consumption should never lower than the 90\% of origin one. In another words, the output 
-of this phase protect as much connectivity as possible. Following is our implementation:
+of this phase protect as much connectivity and transportation as possible. Following is our implementation:
 
@@
 $\:\:$8:\quad\ \textbf{for} {each link $l$ in $\Gamma - S$}\\
-$\:\:$9:\quad\ \quad\ \textbf{if} $G_{S,l}$ is connected and $\rho(G_{S,l})/\rho(G)<threhold$\\
+$\:\:$9:\quad\ \quad\ \textbf{if} $G_{S,l}$ is connected and $\rho(G_{S,l})/\rho(G)>threhold$\\
 $\:\:$10:\quad\ \quad\ \quad\ $S \leftarrow S \cup \{l\}$;\\
@@
 \subsection{Algorihtm Phase Two}
-Once we get the output network topology from the first phase based on extend algebraic connectivity, it is time to compute
-the robust routing. We first calculate the demand-oblivious rouintg from the origin topology based on algorithm proposed 
-by David Applegate[1]; and adjust routing in details according to the links we switched off in the final topology.
+Once we get the output network topology from the first phase based on either metric, it is time to compute
+the robust routing. On one hand, computation process may cost too much time if we directly calculate the robust routing in 
+the final graph; on the other hand, the robust routing based on the final graph may not be the best one.
+There is a heuristic algorithm
+based on the demand-oblivious routing on the origin graph, which should be obtained at first.
+then adjust routing in details according to the links we switched off.
 
-The demand-oblivious routing can be computed by a single LP with $O(mn^2)$ variables and $O(nm^2)$ constraints :
+The demand-oblivious routing can be computed by a single LP with $O(mn^2)$ variables and $O(nm^2)$ constraints[1] :
 \begin{table}[!th]
-\begin{tabular}{lll}
-    $\:\:$\quad\quad\ min $r$ \\
-    $\:\:$\quad\quad\ $f_{ij}(e)$ is a routing \\
-    $\:\:$\quad\quad\ $\forall$ links $l$: $\sum_m cap(m)t(l,m) \le r$ \\
-    $\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ pairs $i \rightarrow j$: \\
-    $\:\:$\quad\quad\quad\quad\ $f_{ij}(l)/cap(l) \le p_l(i,j)$ \\ 
-    $\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $\forall$ edges $e = j \rightarrow k$: \\
-    $\:\:$\quad\quad\quad\quad\ $\pi(l, link-of(e)) + p_l(i,j) - p_l(i,k) \ge 0$ \\
-    $\:\:$\quad\quad\ $\forall$ links $l$, $m$: $\pi(l, m) \ge 0$ \\
-    $\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$: $p_l(i,i) = 0$ \\
-    $\:\:$\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $j$: $p_l(i,j) \ge 0$ \\
+\begin{tabular}{ll}
+$\:\:$\quad\quad\quad\quad\ \textbf{min} $r$ \\
+$\:\:$\quad\quad\quad\quad\ $f_{ij}(e)$ is a routing \\
+$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$: $\sum_m cap(m)t(l,m) \le r$ \\
+$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$, $\forall$ pairs $i \rightarrow j$: \\
+$\:\:$\quad\quad\quad\quad\quad\quad\ $f_{ij}(l)/cap(l) \le p_l(i,j)$ \\ 
+$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $\forall$ edges $e = j \rightarrow k$: \\
+$\:\:$\quad\quad\quad\quad\quad\quad\ $\pi(l, link-of(e)) + p_l(i,j) - p_l(i,k) \ge 0$ \\
+$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$, $m$: $\pi(l, m) \ge 0$ \\
+$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$: $p_l(i,i) = 0$ \\
+$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $j$: $p_l(i,j) \ge 0$ \\
 \end{tabular}
@@
 both from source node $s$ to destination node $d$, and the optimal obilious routing trace 70\% traffic on 
-$path_1$ and left on $path_2$. However splitting flow is hard handled, we take a transformation for this case like this:
-when an flow is coming, there is 70\% probability we trace it on $path_1$, otherwise $path_2$.
+$path_1$ and left on $path_2$. Although splitting flow is hard handled, we take a transformation for the case like that:
+when an flow is coming, there is 70\% probability we trace it on $path_1$, otherwise $path_2$. This is easily implementated 
+in real world.
 
-Because all the routing is based on the origin topology, when switch-off links is done, we must adjust the routing 
-as well. Take pair $(s, d)$ for example, the path in routing maybe like $s \rightarrow i \rightarrow j \rightarrow d$,
-unfortunately link $i \rightarrow j$ is switched off in Phase One of Algorithm. For the final topology is still 
-connected, we must can find another path from $i$ to $j$, such as $i \rightarrow k \rightarrow j$,
-then we just replace the routhing $s \rightarrow i \rightarrow j \rightarrow d$ with
-$s \rightarrow i \rightarrow k \rightarrow j \rightarrow d$.
-Find the path between two nodes of switch-off link is easy by Dijkstra Algorithm on the final topology.
+Because all the routing is based on the origin topology, when some links are switched off, we must adjust the routing 
+as well. Supposed there are some paths between two vertices $s$ and $d$, maybe one link in some paths be removed, 
+and these paths become not reachable any more, we should adjust the traffic in these paths to other paths. Of course,
+we can not put the whole traffic on another path, this will make some links of the path congested, so we should split the traffic 
+to some paths `averagely`, in the sense of extended robust link utilization. Similarly to link utilization, we define the extended
+robust link utilization as the maximum extended robust link utilization of links.
+
+Take pair $(s, d)$ for example, routing includes paths from $s$ to $d$, such as $p_1, p_2, ... , p_n$. While only $p_1$ trace 
+the removed link, and of course it will be unreachable. We split the traffic of $p_1$, and put them on other paths to make 
+the extend robust link utilization of paths almost closely.
 
@@
 $\quad\quad\ \ \ $ $S$ which is the switch-off links set generated by Phase One;\\
-$\:\:$\textbf{Output:} $Rouing$ Robust Energy-Aware Routing on new topology\\
-$\:\:$1:\ $G^* \leftarrow G(V, E-S)$;\\
-$\:\:$2:\ $Replace \leftarrow \emptyset$;\\
-$\:\:$3:\ \textbf{for} {each link $l$ in $S$}\\
-$\:\:$4:\quad\ $ls \leftarrow$ node of $l$;\\
-$\:\:$5:\quad\ $ld \leftarrow$ the other node of $l$;\\
-$\:\:$6:\quad\ $Replace[ls, ld] \leftarrow$ find path from $ls$ to $ld$ on $G^*$;\\
-$\:\:$7:\ $Routing \leftarrow$ run LP on $G$ by CPLEX, fetch routing through parsing result;\\
-$\:\:$8:\ \textbf{for} {each $r$ in $Routing$}\\
-$\:\:$9:\quad\ \textbf{if} {$l \in S$ in $r$}\\
-$\:\:$10:\quad\quad\ \ $s \leftarrow$ source of $r$;\\
-$\:\:$11:\quad\quad\ \ $d \leftarrow$ destination of $r$;\\
-$\:\:$12:\quad\quad\ $r \leftarrow r[s, ls] + Replace[ls,ld] + r[ld,d]$;\\
-$\:\:$13:\ \textbf{return} Routing;\\
+$\quad\quad\ \ \ $ $R$ which is the Robust Routing on origin topology;\\
+$\:\:$\textbf{Output:} $Routing$ Robust Energy-Aware Routing on new topology\\
+$\:\:$\ 1:\ $G^* \leftarrow G(V, E-S)$;\\
+$\:\:$\ 2:\ \textbf{for} {each link $l$ in $S$}\\
+$\:\:$\ 3:\quad\ \textbf{for} {each $s,d,paths$ in $R$}\\
+$\:\:$\ 4:\quad\ \quad\ $traffic \leftarrow$ 0;\\
+$\:\:$\ 5:\quad\ \quad\ \textbf{for} {each $path$ in $paths$}\\
+$\:\:$\ 6:\quad\ \quad\ \quad\ \textbf{if} {$link$ in $path$}\\
+$\:\:$\ 7:\quad\ \quad\ \quad\ \quad\ $traffic \leftarrow$ $traffic$ + $path$.$traffic$; \\
+$\:\:$\ 8:\quad\ \quad\ \quad\ \quad\ $paths$.remove($path$); \\
+$\:\:$\ 9:\quad\ \quad\ $yen\_paths \leftarrow$ yens\_algorithm($G^*$, $s$,$d$);\\
+$\:\:$10:\quad\ \quad\ \textbf{while} {$traffic$ != 0}\\
+$\:\:$11:\quad\ \quad\ \quad\ sort\_paths\_by\_extend\_robust\_link\_utilization($yen\_paths$)\\
+$\:\:$12:\quad\ \quad\ \quad\ $yen\_paths$[0].$traffic$ = $traffic$ / N\\
+$\:\:$13:\quad\ \quad\ \quad\ $traffic$ = $traffic$ - $traffic$ / N\\
+$\:\:$14:\quad\ \quad\ \quad\ $paths$.add($yen\_paths$[0])\\
+$\:\:$15:\quad\ \quad\ $paths$.merge();\\
+$\:\:$16:\ \textbf{return} $R$;\\
 \hline
@@
 
-\section{Samples}
+\section{Samples and Proof}
 For showing obilious performance ratio with energy constraint really make a difference in the switching off link 
@@
 there will be an upper bound for obilious performance ratio with energy constraint, and get the bound according
-to the topology.
+to the topology. For simpleness, we refer
 

### 2015-01-13 paper.tex
complete proof

@@
 satisfy power and utilization requirement for any traffic matrix given?
-
-\includegraphics[width=10cm]{net5}
 
@@
 there will be an upper bound for obilious performance ratio with energy constraint, and get the bound according
-to the topology. For simpleness, we refer
+to the topology. For simpleness, we refer the energy constraint to the quantity of removed links.
 
+\includegraphics[width=4cm]{circle}
+\includegraphics[width=4cm]{clique}
+
+\subsection{Circles}
 Cycles topology connect all the nodes by a cycle, any node in which has two links joined. Figure 1 show the six
-nodes cycles topology, let nodes named from $A$ to $F$ and links named by its two vertices, such as $l_{ab}$.
-Without loss of generality,
+nodes cycles topology, let nodes named from $A$ to $F$ and links named from $a$ to $f$ in the figure.
+Now suppose a traffic in the topology then calculate the optimal routing for it,
+let $D_a$ and $C_a$ be the demand and capacity of the link, without loss of generality, we say the link $d$ is the 
+bottleneck, i.e. with the maximum link utilization. There are two solutions for us, switching off the link $d$,
+or the other link, such as link $f$.
+
+For case one, when we switch off the link $d$, the origin traffic pass the link will be redirected. The worst situation
+is that all the traffic on the link $d$ will be put to the other path : $D \leftarrow C \leftarrow B \leftarrow A \leftarrow 
+F \leftarrow E$. After traffic redirection, the bottleneck link may become the link $e$, according to our definition of
+extended robust link utilization:
+
+\begin{equation}
+    \frac {\frac{D_e + D_d} {C_e}} {\frac {D_d}{C_d}} = (1 + \frac{D_e}{D_d}) \frac{C_d}{C_e}
+\end{equation}
+
+Because the link utilization of link $d$ is the maximum one, we have :
+
+\begin{equation}
+    \frac{D_d}{C_d} > \frac{D_e}{C_e} 
+\end{equation}
+\begin{equation}
+    \frac{D_e * C_d}{C_e * D_d} < 1
+\end{equation}
+
+so we have the extended robust link utilization in case one :
+
+\begin{equation}
+    (1 + \frac{D_e}{D_d}) \frac{C_d}{C_e} < \frac{C_d}{C_e} + 1
+\end{equation}
+
+For case two, similar to case one, all the traffic will be redirected on the other path between $F$ and $A$. There are two 
+sub cases after traffic redirection, the link $D$ is still the bottleneck or the link $E$ become the new bottleneck. In sub 
+case one:
+
+\begin{equation}
+    \frac{\frac{D_d + D_f}{C_d}}{\frac{D_d}{C_d}} = 1 + \frac{D_f}{D_d}
+\end{equation}
+
+Because the link utilization of link $d$ is the maximum one in origin topology, we have as:
+
+\begin{equation}
+    \frac{D_d}{C_d} > \frac{D_f}{C_f} 
+\end{equation}
+\begin{equation}
+    \frac{D_f}{D_d} < \frac{C_d}{C_f} 
+\end{equation}
+
+So we get the extended robust link utilization in this case :
+\begin{equation}
+    (1 + \frac{D_f}{D_d}) < \frac{C_d}{C_f} + 1
+\end{equation}
+
+In sub case two, we get the new extended robust link utilization in link $E$:
+
+\begin{equation}
+    \frac{\frac{D_e + D_d}{C_e}}{\frac{D_d}{C_d}} = \frac{D_e * C_d}{D_d * C_e} * \frac{C_d * D_f}{C_e * D_e}
+\end{equation}
+
+Similarly as mentioned above, we get equations :
+
+\begin{equation}
+    \frac{D_d}{C_d} > \frac{D_e}{C_e} => \frac{D_e * C_d}{C_e * D_d} < 1 
+\end{equation}
+\begin{equation}
+    \frac{D_d}{C_d} > \frac{D_f}{C_f} => \frac{D_f * C_d}{D_d} < C_f
+\end{equation}
+
+So we get the extended robust link utilization:
+
+\begin{equation}
+    \frac{D_e * C_d}{D_d * C_e} + \frac{C_d * D_f}{C_e * D_d} < 1 + \frac{C_f}{C_e}
+\end{equation}
+
+As a result, the upper bound of extended robust link utilization must be :
+
+\begin{equation}
+    Max\{1 + \frac{C_d}{C_e}, 1 + \frac{C_d}{C_f}, 1 + \frac{C_f}{C_e}\}
+\end{equation}
+
+Particularly, if all the links have the same capacity, the upper bound equal to 2 when switch off one link. Otherwise, the 
+upper bound only dependent to the greatest ratio of link capacity.
+
+\subsection{Cliques}
+In clique topology, all the nodes connect to each other, it means that situation become more difficult because the traffic
+can be adjusted to multi paths rather than one path in circle. And we will see that splitting traffic on multi paths is 
+always better than put all the traffic to one, so if we get the upper bound of the worst case, it must be the upper bound
+of other case. Similarly to circle topology, we say the link $a$ is the bottleneck, and we will switch off it or other link
+like $b$.
+
+In case one, after we switch off link $a$, the new bottleneck link must be the affected link, the link contains the origin 
+traffic on link $a$. Otherwise if the link $b$ is the bottleneck, but we adjust the traffic on other links, it means that
+we can do the same thing in the origin topology, and the bottleneck become link $b$ rather than $a$. It is conflict with our
+assumption. So we have the extended robust link utilization as :
+
+\begin{equation}
+    \frac {\frac{D_b + D_a}{C_b}}{\frac{D_a}{C_a}} = (1+\frac{D_b}{D_a}) \frac{C_a}{C_b}
+\end{equation}
+
+Because the link $a$ is the bottleneck link with the maximum link utilization, like what we do above, we can get
+
+\begin{equation}
+    (1+\frac{D_b}{D_a}) \frac{C_a}{C_b} < 1 + \frac{C_a}{C_b}
+\end{equation}
+
+In case two, the bottleneck may still be link $a$ or the new link $c$. If it is link $a$, and no new traffic across it,
+the extended robust link utilization equal to 1 obiliously. Or we adjust the new traffic $D_b$ on it, we can get the
+extended robust link utilization:
+
+\begin{equation}
+    \frac{\frac{D_a + D_b}{C_a}}{\frac{D_a}{C_a}} = 1 + \frac{D_b}{D_a} < 1 + \frac{C_b}{C_a}
+\end{equation}
+
+If the bottleneck become new link $c$, similar to our proof of circle topology, we can get extended robust link utilization:
+\begin{equation}
+    \frac{\frac{D_c + D_b}{C_c}}{\frac{D_a}{C_a}} = \frac{D_c * C_a}{D_a * C_c} + \frac{D_b * C_a}{D_a * C_c} < 1 + \frac{C_b}{C_c}
+\end{equation}
+
+So we obtain the same conclusion as circle topology, the extended robust link utilization must be :
+
+\begin{equation}
+    Max\{1 + \frac{C_a}{C_b}, 1 + \frac{C_b}{C_a}, 1 + \frac{C_b}{C_c}\}
+\end{equation}
+
+\subsection{Other Topology}
+We can also see that, when we switch off different link, it really matters the performance which dependent on not only the 
+demand or traffic, but also the capacity of links. Particularly, the upper bound is just related with the capacity of links.
+And from our proof process, there is no special limitation for specific topology, so we can get the similar conclusion 
+on other topology.
+
+\section{Experiments}
+There is are experiments.
 

### 2015-01-13 experiment/plot/test.py

@@ -1,0 +1,31 @@
+import matplotlib.pyplot as plt
+
+result_file_template = "result-compare-geant"
+
+f = open(result_file_template)
+line = f.readline();
+base = []
+new = []
+x_base = []
+x_new = []
+num = 0
+while line:
+    tokens = line.strip().split()
+    base.append(float(tokens[6]))
+    x_base.append(num)
+
+    if num < 13:
+        new.append(float(tokens[9]))
+        x_new.append(num)
+
+    num = num + 1
+    line = f.readline()
+
+f.close()
+
+plt.plot(x_base, base, 'r--')
+plt.plot(x_new, new, 'b--')
+#plt.axis([0, 6, 0, 20])
+plt.show()
+
+

### 2015-01-13 experiment/cplex/compare.py
rename result

@@ -16,21 +16,21 @@ final_topology_base_template = "../topology/final/%s-final-topology-%d-base"
 remove_links_base_template = "../topology/remove/%s-remove-%d-links-base"
 solution_template = "%s-cplex-%0.1f.xml"
 demand_file_template = "../demand/%s-%s/%0.1f/%d.txt"
-result_file_template = "result-compare-%s"
-middle_file_template = "middle-compare-%s"
+result_file_template = "result-compare-%s-%0.1f"
+middle_file_template = "middle-compare-%s-%0.1f"
 solution_default = "global_opt_cplex_output.sol"
 files = 1000
 
 loop = 1
 w = 1.5
 
-remove_links_n = {'abilene':5, 'geant':13, 'cernet2':4}
+remove_links_n = {'abilene':5, 'geant':16, 'cernet2':4}
 
 for t in ['abilene', 'geant', 'cernet2']:
     connected_topology = connected_topology_template % t
     solution = solution_template % (t, w)
-    result_file = result_file_template % (t)
-    middle_file = middle_file_template % (t)
+    result_file = result_file_template % (t, w)
+    middle_file = middle_file_template % (t, w)
 
     global_routes = xml.get_route(solution)
     link_order = xml.get_link_order_with_attr(solution, connected_topology)

### 2015-01-13 experiment/plot/test.py
add remove 0 links of cernet2

@@ -1,31 +1,0 @@
-import matplotlib.pyplot as plt
-
-result_file_template = "result-compare-geant"
-
-f = open(result_file_template)
-line = f.readline();
-base = []
-new = []
-x_base = []
-x_new = []
-num = 0
-while line:
-    tokens = line.strip().split()
-    base.append(float(tokens[6]))
-    x_base.append(num)
-
-    if num < 13:
-        new.append(float(tokens[9]))
-        x_new.append(num)
-
-    num = num + 1
-    line = f.readline()
-
-f.close()
-
-plt.plot(x_base, base, 'r--')
-plt.plot(x_new, new, 'b--')
-#plt.axis([0, 6, 0, 20])
-plt.show()
-
-

### 2015-01-17 paper.tex
write paper

@@
 We evaluate our algorithms on real and synthetic topologies. The simulation results show that REAR can save 
-XX\% of line card power while the performance ratio is less than XX.
+19\% of line card power while the performance ratio is less than 34\%.
 \end{abstract}
@@
 
+\vspace*{0.2in}
 \includegraphics[width=4cm]{circle}
 \includegraphics[width=4cm]{clique}
+\vspace*{0.2in}
 
@@
 
-\section{Experiments}
-There is are experiments.
+\section{Experiments and Results}
+We implemented our algorithm on real world topology, including Abilene, Geant and Cernet2, and we use Gravity model to generate
+random traffic matrix. Because we take an attribute $w$ to expand the traffic range from $1/w$ to $w$, when the $w$ increased the
+traffic varied in wider range. Particularly, when the $w$ limit extremity, we say the traffic matrix is really random, and our 
+algorithm is irrelevant with traffic.
+
+\vspace*{0.2in}
+\includegraphics[width=4cm]{opr_with_remove_links}
+\includegraphics[width=4cm]{opr_with_power_saving}
+\vspace*{0.2in}
+
+In Figure, we take $w$ as 1.5 and observe that: when we switch off more links, the OPR is increased as well. 
+It is obvious that when the topology
+lose connectivity by removing links, the worst case of robust routing must be far away from the optimal case in origin topology. And
+in Geant and Abilene, even in the origin topology, the OPR value still not be 1. It is reasonable, because our robust routing 
+is used for a range of traffic, however the optimal routing is calculated for the specific traffic matrix. But fortunately, our robust
+routing is only $24\%$ greater than the optimal routing even in its worst case of Geant. And we also see that the curve become 
+cliffy in the end, because when we remove the links the toplogy lose too much connectivity and there alwasy one path between two vertices.
+Obviously, the performance will become worse in the end. Lastly we say that although the OPR relation really different in different 
+topology, but the curve still be similar with each other, they are exponetial curve correspond with their vertices amount.
+
+On the other hand, we may concern how is the OPR varifying when the power saving achived besides the amount of removed links.
+Of course the more we removed the links, the more power we saved, but how to quantify the power of one link is difficult. Green
+TE proposed the simple power model for topology, which can be represented in Table x:
+
+\vspace*{0.2in}
+\includegraphics[width=8cm]{power_model}
+\vspace*{0.2in}
+
+We compute the power saving ratio as the total power of the removed links over the total power of all the links. And we can
+save 19\% power with only 34\% worse than the worst case for all the traffic in Abilene topology. In Geant and Cernet2, 
+the OPR is little higher. Also we can see that two ways for removing links perform almost the same at the begin in Geant,
+and varified at the end. It shows that we may find another better way for removing the links in the future.
+
+For computing the worst case, we generate 1000 traffic matrix for every topoloy and the $w$ with the Gravity Model.
+We show the each result in the Figure x and x when we remove the first 4 links in each topology. In Abilene, the result 
+is more tighter than Geant. Comparsion in two ways, we can see that in Abilene the AC method is worse than the ERLU one,
+and the downmost zone is the same in two ways, because the robust routing is same in the origin topology.
+
+\vspace*{0.2in}
+\includegraphics[width=4cm]{exp2_nosort_abilene}
+\includegraphics[width=4cm]{exp2_nosort_geant}
+\vspace*{0.2in}
+
+\vspace*{0.2in}
+\includegraphics[width=4cm]{exp2_sort_abilene}
+\includegraphics[width=4cm]{exp2_sort_geant}
+\vspace*{0.2in}
+
+From Figure xx and Figure xx, we sort the 1000 TMs by their OPR value, and see that most of the TMs are quite average. 
+It is said that, our metric OPR is always not be achived for most traffic matrix.
+
+We know when we compute the robust routing for specific topology, the $w$ is very important. When the $w$ limit extremely,
+our robust routing is said without knowledge of traffic matrix. Figure xx, show the OPR varified when $w$ changes. The greater
+the $w$ is, the greater the OPR is. It is obvious because when the $w$ is greater, the traffic matrix is random in more wider 
+range, and our OPR is the worst case of all the traffic matrix.
+
+\vspace*{0.2in}
+\includegraphics[width=8cm,height=4cm]{exp3_w}
+\vspace*{0.2in}
 

### 2015-01-17 experiment/plot/exp1_link.py

@@ -1,0 +1,46 @@
+import matplotlib.pyplot as plt
+
+topology_x_range = {'abilene':5, 'geant':12, 'cernet2':4}
+topology_line_type = {'abilene':'o', 'geant':'s', 'cernet2':'^'}
+color_type = {'base':'r--', 'new':'b-'}
+remove_type = {'base':'AC', 'new':'ERLU'}
+result_file_template = "result-compare-%s-1.5"
+
+line_list = []
+label_list = []
+for t in ['abilene', 'geant', 'cernet2']:
+    f = open(result_file_template % t)
+    line = f.readline()
+
+    base = []
+    new = []
+    x = []
+
+    while line:
+        tokens = line.strip().split()
+        base.append(float(tokens[1]))
+        new.append(float(tokens[2]))
+        x.append(float(tokens[0]))
+
+        line = f.readline()
+
+    f.close()
+
+    l1, = plt.plot(x[:topology_x_range[t]], base[:topology_x_range[t]], color_type['base']+topology_line_type[t])
+    l2, = plt.plot(x[:topology_x_range[t]], new[:topology_x_range[t]], color_type['new']+topology_line_type[t])
+
+    label_list.append(t + '-' + remove_type['base'])
+    label_list.append(t + '-' + remove_type['new'])
+    
+    line_list.append(l1)
+    line_list.append(l2)
+
+plt.xlabel('Remove Links')
+plt.ylabel('oblivious performance ratio')
+plt.title('OPR with Power Saving')
+plt.legend(line_list, label_list, loc=2)
+
+plt.show()
+#plt.savefig('exp1.png', bbox_inches='tight')
+
+

### 2015-01-17 experiment/plot/exp1_power.py

@@ -1,0 +1,140 @@
+import matplotlib.pyplot as plt
+
+topology_x_range = {'abilene':5, 'geant':12, 'cernet2':4}
+remove_links = {'abilene':4, 'geant':15, 'cernet2':3}
+topology_line_type = {'abilene':'o', 'geant':'s', 'cernet2':'^'}
+color_type = {'base':'r--', 'new':'b-'}
+remove_type = {'base':'AC', 'new':'ERLU'}
+result_file_template = "result-compare-%s-1.5"
+topology_file_template = "../topology/connected/%s-connected-topology"
+remove_file_template = "../topology/remove/%s-remove-%d-links"
+remove_base_file_template = "../topology/remove/%s-remove-%d-links-base"
+
+
+power_models = {155.0:60, 1240.0:100, 2480.0:140, 9920:174}
+power_model = [60, 100, 140, 174]
+
+
+line_list = []
+label_list = []
+for t in ['abilene', 'geant', 'cernet2']:
+    # compute the total power of topology
+    f = open(topology_file_template % t)
+    line = f.readline()
+    line = f.readline()
+    topo = dict()
+    total = 0
+    while line:
+        tokens = line.strip().split()
+        s = int(tokens[0])
+        d = int(tokens[1])
+        c = float(tokens[2])
+        
+        topo[s,d] = c
+        if c <= 155.0:
+            total = total + power_model[0]
+        elif c <= 1240.0:
+            total = total + power_model[1]
+        elif c <= 2480.0:
+            total = total + power_model[2]
+        elif c <= 9920.0:
+            total = total + power_model[3]
+
+        line = f.readline()
+    f.close()
+    #print total
+
+    # compute the power removed link array
+    removes = dict()
+    power_saving_ratio = [0]
+    saving = 0.0
+    f = open(remove_file_template % (t, remove_links[t]))
+    line = f.readline()
+    num = 1
+    while line:
+        tokens = line.strip().split()
+        s = int(tokens[0])
+        d = int(tokens[1])
+
+        if topo[s,d] <= 155.0:
+            saving = saving + power_model[0]
+        elif topo[s,d] <= 1240.0:
+            saving = saving + power_model[1]
+        elif topo[s,d] <= 2480.0:
+            saving = saving + power_model[2]
+        elif topo[s,d] <= 9920.0:
+            saving = saving + power_model[3]
+        
+        power_saving_ratio.append(saving / total)
[…]

### 2015-01-17 experiment/plot/exp2.py

@@ -1,6 +1,6 @@
 import matplotlib.pyplot as plt
 
-result_file_template = "middle-compare-abilene"
+result_file_template = "middle-compare-abilene-1.5"
 count = 1000
 remove = 5
 

### 2015-01-17 experiment/plot/exp2_nosort.py

@@ -1,6 +1,6 @@
 import matplotlib.pyplot as plt
 
-result_file_template = "middle-compare-abilene"
+result_file_template = "middle-compare-abilene-1.5"
 count = 1000
 remove = 5
 
@@ -13,6 +13,8 @@ x = [i for i in range(count)]
 while line:
     tokens = line.strip().split()
     r = int(tokens[0])
+    if int(r) >= 5:
+        break
     n = int(tokens[1])
     base[r][n] = float(tokens[2])
     new[r][n] = float(tokens[3])
@@ -21,13 +23,21 @@ while line:
 
 f.close()
 
+line1 = None
 for i in range(remove):
-    plt.plot(x, base[i], 'r--')
+    line1, = plt.plot(x, base[i], 'r--')
 
+line2 = None
 for i in range(remove):
-    plt.plot(x, new[i], 'b--')
+    line2, = plt.plot(x, new[i], 'b-')
 
 #plt.axis([0, 6, 0, 20])
-plt.show()
+plt.xlabel('Random Traffic Matrix')
+plt.ylabel('Oblivious Performance Ratio')
+plt.title('OPR with Random TMs')
+plt.legend([line1, line2], ['AC', 'ERLU'], loc=2)
+
+#plt.show()
+plt.savefig('exp2_nosort_abilene.png', bbox_inches='tight')
 
 

### 2015-01-17 experiment/plot/exp2_sort.py

@@ -1,8 +1,8 @@
 import matplotlib.pyplot as plt
 
-result_file_template = "middle-compare-abilene"
+result_file_template = "middle-compare-geant-1.5"
 count = 1000
-remove = 5
+remove = 6
 
 f = open(result_file_template)
 line = f.readline();
@@ -14,6 +14,8 @@ while line:
     tokens = line.strip().split()
     r = int(tokens[0])
     n = int(tokens[1])
+    if int(r) == remove:
+        break
     base[r][n] = float(tokens[2])
     new[r][n] = float(tokens[3])
 
@@ -21,25 +23,33 @@ while line:
 
 f.close()
 
-for i in range(remove):
+line1 = None
+for i in range(2, remove):
     for j in range(count):
         for k in range(j, count):
             if (base[i][j] > base[i][k]):
                 tmp = base[i][j]
                 base[i][j] = base[i][k]
                 base[i][k] = tmp
-    plt.plot(x, base[i], 'r--')
+    line1, = plt.plot(x, base[i], 'r--')
 
-for i in range(remove):
+line2 = None
+for i in range(2, remove):
     for j in range(count):
         for k in range(j, count):
             if (new[i][j] > new[i][k]):
                 tmp = new[i][j]
                 new[i][j] = new[i][k]
                 new[i][k] = tmp
-    plt.plot(x, new[i], 'b--')
+    line2, = plt.plot(x, new[i], 'b-')
 
 #plt.axis([0, 6, 0, 20])
-plt.show()
 
+plt.xlabel('Random Traffic Matrix')
+plt.ylabel('Oblivious Performance Ratio')
+plt.title('OPR with Random TMs')
+plt.legend([line1, line2], ['AC', 'ERLU'], loc=2)
+#plt.show()
+
+plt.savefig('exp2_sort_geant.png', bbox_inches='tight')
 

### 2015-01-17 experiment/plot/exp3_power.py

@@ -1,0 +1,141 @@
+import matplotlib.pyplot as plt
+
+topology_x_range = {'abilene':5, 'geant':12, 'cernet2':4}
+remove_links = {'abilene':4, 'geant':15, 'cernet2':3}
+topology_line_type = {1.5:'o', 2.0:'s'}
+color_type = {'base':'r--', 'new':'b-'}
+remove_type = {'base':'AC', 'new':'ERLU'}
+result_file_template = "result-compare-%s-%0.1f"
+topology_file_template = "../topology/connected/%s-connected-topology"
+remove_file_template = "../topology/remove/%s-remove-%d-links"
+remove_base_file_template = "../topology/remove/%s-remove-%d-links-base"
+
+
+power_models = {155.0:60, 1240.0:100, 2480.0:140, 9920:174}
+power_model = [60, 100, 140, 174]
+
+
+line_list = []
+label_list = []
+for t in ['geant']:
+    # compute the total power of topology
+    f = open(topology_file_template % t)
+    line = f.readline()
+    line = f.readline()
+    topo = dict()
+    total = 0
+    while line:
+        tokens = line.strip().split()
+        s = int(tokens[0])
+        d = int(tokens[1])
+        c = float(tokens[2])
+        
+        topo[s,d] = c
+        if c <= 155.0:
+            total = total + power_model[0]
+        elif c <= 1240.0:
+            total = total + power_model[1]
+        elif c <= 2480.0:
+            total = total + power_model[2]
+        elif c <= 9920.0:
+            total = total + power_model[3]
+
+        line = f.readline()
+    f.close()
+    #print total
+
+    # compute the power removed link array
+    removes = dict()
+    power_saving_ratio = [0]
+    saving = 0.0
+    f = open(remove_file_template % (t, remove_links[t]))
+    line = f.readline()
+    num = 1
+    while line:
+        tokens = line.strip().split()
+        s = int(tokens[0])
+        d = int(tokens[1])
+
+        if topo[s,d] <= 155.0:
+            saving = saving + power_model[0]
+        elif topo[s,d] <= 1240.0:
+            saving = saving + power_model[1]
+        elif topo[s,d] <= 2480.0:
+            saving = saving + power_model[2]
+        elif topo[s,d] <= 9920.0:
+            saving = saving + power_model[3]
+        
+        power_saving_ratio.append(saving / total)
+        removes[num] = [s,d]
+        num = num + 1
+
+        line = f.readline()
[…]

### 2015-01-18 paper.tex
begin modify introduction

@@
 
+\ifCLASSOPTIONcompsoc
+    \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+\else
+    \usepackage[caption=false,font=footnotesize]{subfig}
+\fi
+
 % correct bad hyphenation here
@@
 \author{\IEEEauthorblockN{Heng Lin}
-\IEEEauthorblockA{Tsinghua University}
+\IEEEauthorblockA{Tsinghua University \\ henglin1991@gmail.com}
 \and
 \IEEEauthorblockN{Mingwei Xu}
-\IEEEauthorblockA{Tsinghua University}
+\IEEEauthorblockA{Tsinghua University \\ xmw@cernet.edu.cn}
 \and
 \IEEEauthorblockN{Yuan Yang}
-\IEEEauthorblockA{Tsinghua University}}
+\IEEEauthorblockA{Tsinghua University \\ yyang@csnet1.cs.tsinghua.edu.cn}}
 
@@
 
-\vspace*{0.2in}
+\begin{figure}[!t]
+\centering
+\vspace*{0.1in}
 \includegraphics[width=8cm]{3-nodes-example}
-\vspace*{0.2in}
+\caption{Model Example}
+\label{label}
+\vspace*{0.1in}
+\end{figure}
 
@@
 
-\vspace*{0.2in}
-\includegraphics[width=4cm]{circle}
-\includegraphics[width=4cm]{clique}
-\vspace*{0.2in}
+\begin{figure}[!t]
+\centering
+\vspace*{0.1in}
+\subfloat[Circle]{\includegraphics[width=4cm]{circle}
+\label{subfiga}}
+\hfill
+\subfloat[Clique]{\includegraphics[width=4cm]{clique}
+\label{subfigb}}
+\caption{Circle and Clique topology of 6 nodes}
+\vspace*{0.1in}
+\end{figure}
 
@@
 
-\vspace*{0.2in}
-\includegraphics[width=4cm]{opr_with_remove_links}
-\includegraphics[width=4cm]{opr_with_power_saving}
-\vspace*{0.2in}
+\begin{figure}[!t]
+\centering
+\vspace*{0.1in}
+\subfloat{\includegraphics[width=4cm]{opr_with_remove_links}}
+\subfloat{\includegraphics[width=4cm]{opr_with_power_saving}}
+\caption{OPR with Power Saving}
+\vspace*{0.1in}
+\end{figure}
 
@@
 
-\vspace*{0.2in}
-\includegraphics[width=8cm]{power_model}
-\vspace*{0.2in}
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1}
+\caption{Green TE Power Model}
+\label{power model}
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+\bfseries Line-Card & \bfseries Speed(Mbps) & \bfseries Power(Watts) \\
+\hline
+1-Port OC3 & 155.52 & 60 \\
+\hline
+8-Port OC3 & 1244.16 & 100 \\
+\hline
+1-Port OC48 & 2488.32 & 140 \\
+\hline
+1-Port OC192 & 9953.28 & 174 \\
+\hline
+\end{tabular}
+\end{table}
 
@@
 
-\vspace*{0.2in}
-\includegraphics[width=4cm]{exp2_nosort_abilene}
-\includegraphics[width=4cm]{exp2_nosort_geant}
-\vspace*{0.2in}
+\begin{figure}[!t]
+\centering
+\vspace*{0.1in}
+\subfloat{\includegraphics[width=4cm]{exp2_nosort_abilene}}
+\subfloat{\includegraphics[width=4cm]{exp2_nosort_geant}}
+\caption{Nosort: (a). Abilene (b).Geant}
+\vspace*{0.1in}
+\end{figure}
 
-\vspace*{0.2in}
-\includegraphics[width=4cm]{exp2_sort_abilene}
-\includegraphics[width=4cm]{exp2_sort_geant}
-\vspace*{0.2in}
+\begin{figure}[!t]
+\centering
+\vspace*{0.1in}
+\subfloat{\includegraphics[width=4cm]{exp2_sort_abilene}}
+\subfloat{\includegraphics[width=4cm]{exp2_sort_geant}}
+\caption{Sort: (a). Abilene (b).Geant}
+\vspace*{0.1in}
+\end{figure}
 
@@
 
-\vspace*{0.2in}
+\begin{figure}
+\centering
+\vspace*{0.1in}
 \includegraphics[width=8cm,height=4cm]{exp3_w}
-\vspace*{0.2in}
+\caption{OPR with w relationship}
+\vspace*{0.1in}
+\end{figure}
+
+\section{Related Work}
+related work
 

### 2015-01-18 experiment/plot/exp1.py

@@ -1,25 +1,0 @@
-import matplotlib.pyplot as plt
-
-result_file_template = "result-compare-abilene"
-
-f = open(result_file_template)
-line = f.readline();
-base = []
-new = []
-x = []
-while line:
-    tokens = line.strip().split()
-    base.append(float(tokens[1]))
-    new.append(float(tokens[2]))
-    x.append(float(tokens[0]))
-
-    line = f.readline()
-
-f.close()
-
-plt.plot(x, base, 'r--')
-plt.plot(x, new, 'b--')
-#plt.axis([0, 6, 0, 20])
-plt.show()
-
-

### 2015-01-18 experiment/plot/exp1_link.py

@@ -37,10 +37,9 @@ for t in ['abilene', 'geant', 'cernet2']:
 
 plt.xlabel('Remove Links')
 plt.ylabel('oblivious performance ratio')
-plt.title('OPR with Power Saving')
 plt.legend(line_list, label_list, loc=2)
 
-plt.show()
-#plt.savefig('exp1.png', bbox_inches='tight')
+#plt.show()
+plt.savefig('exp1_link.png', bbox_inches='tight')
 
 

### 2015-01-18 experiment/plot/exp1_power.py

@@ -131,10 +131,9 @@ for t in ['abilene', 'geant', 'cernet2']:
 
 plt.xlabel('Power Saving')
 plt.ylabel('Oblivious Performance Ratio')
-plt.title('OPR with Power Saving')
 plt.legend(line_list, label_list, loc=2)
 
-plt.show()
-#plt.savefig('exp1.png', bbox_inches='tight')
+#plt.show()
+plt.savefig('exp1_power.png', bbox_inches='tight')
 
 

### 2015-01-18 experiment/plot/exp2_nosort.py

@@ -1,6 +1,6 @@
 import matplotlib.pyplot as plt
 
-result_file_template = "middle-compare-abilene-1.5"
+result_file_template = "middle-compare-geant-1.5"
 count = 1000
 remove = 5
 
@@ -34,10 +34,9 @@ for i in range(remove):
 #plt.axis([0, 6, 0, 20])
 plt.xlabel('Random Traffic Matrix')
 plt.ylabel('Oblivious Performance Ratio')
-plt.title('OPR with Random TMs')
 plt.legend([line1, line2], ['AC', 'ERLU'], loc=2)
 
 #plt.show()
-plt.savefig('exp2_nosort_abilene.png', bbox_inches='tight')
+plt.savefig('exp2_nosort_geant.png', bbox_inches='tight')
 
 

### 2015-01-18 experiment/plot/exp2_sort.py

@@ -1,8 +1,8 @@
 import matplotlib.pyplot as plt
 
-result_file_template = "middle-compare-geant-1.5"
+result_file_template = "middle-compare-abilene-1.5"
 count = 1000
-remove = 6
+remove = 5
 
 f = open(result_file_template)
 line = f.readline();
@@ -47,9 +47,8 @@ for i in range(2, remove):
 
 plt.xlabel('Random Traffic Matrix')
 plt.ylabel('Oblivious Performance Ratio')
-plt.title('OPR with Random TMs')
 plt.legend([line1, line2], ['AC', 'ERLU'], loc=2)
 #plt.show()
 
-plt.savefig('exp2_sort_geant.png', bbox_inches='tight')
+plt.savefig('exp2_sort_abilene.png', bbox_inches='tight')
 

### 2015-01-18 experiment/plot/exp3_power.py

@@ -132,10 +132,9 @@ for t in ['geant']:
 
 plt.xlabel('Power Saving')
 plt.ylabel('Oblivious Performance Ratio')
-plt.title('OPR with Power Saving')
 plt.legend(line_list, label_list, loc=2)
 
 #plt.show()
-plt.savefig('exp1.png', bbox_inches='tight')
+plt.savefig('exp3_w.png', bbox_inches='tight')
 
 

### 2015-01-18 paper.tex
begin write introduction

@@
 \documentclass[conference]{IEEEtran}
+
+\usepackage{cite}
 
@@
 In this paper, we propose a different approach that finds one energy-aware routing robust to a set of traffic 
-matrices, in particular, to arbitrary traffic demands. Such a routing without energy consideration is known as 
-the demand-oblivious routing, and is well studied. However, the problem becomes much more challenging when energy 
+matrices, particularly to arbitrary traffic demands. Such a routing without energy consideration is known as 
+the demand-oblivious routing, and is well studied\cite{networking:oblivious}. However, the problem becomes much more challenging when energy 
 conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance 
-ratio with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when 
+ratio (OPR) with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when 
 certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio, 
@@
 \section{Related Work}
-related work
+related work.
 
@@
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+\bibitem{networking:greente}
+M.Zhang, C.Yi, B.Liu and B.Zhang, "GreenTE: Power-Aware Traffic Engineering".
+
+\bibitem{networking:oblivious}
+D.Applegate and E.Cohen, "Making Intra-Domain Routing Robust to Changing and Uncertain Traffic Demands: Understanding Fundamental Tradeoffs".
+
 \end{thebibliography}

### 2015-01-19 paper.tex
draft for introduction

@@
 \documentclass[conference]{IEEEtran}
+
+\makeatletter
+\newcommand{\rmnum}[1]{\romannumeral #1}
+\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
+\makeatother
 
@@
 matrices, particularly to arbitrary traffic demands. Such a routing without energy consideration is known as 
-the demand-oblivious routing, and is well studied\cite{networking:oblivious}. However, the problem becomes much more challenging when energy 
+the demand-oblivious routing, and is well studied. However, the problem becomes much more challenging when energy 
 conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance 
@@
 \section{Introduction}
-We aim to find the ``robust'' route for all possible traffic matrix, not only consider performance but also energy 
-consumption in network.
+Internet was playing a more and more important role in our daily life, as an huge and indispensable communication system
+it also has its considerable share in energy consumption. Devices such as routers and switchs contributed to the most
+consumption because of inefficient energy management solutions, which made the devices always working in full mode 
+regardless of traffic demands. In particular, even there are no traffic in the link between two routers or switches, 
+the line cards related to the link were still working and in previous research line cards are the main energy consuming part of
+routers or switches. So for energy consideration, we should obtain link-level solutions which switched the link (line cards)
+to sleep mode if there is no traffic on it.
 
-\section{Motivation}
-Suppose two hosts named host A and host B, and there are three links between 
-them, respectively, capacity with 2M, 3M and 5M. Now demands come, with 1M from A to B. we regard the capacity 
-as the power of the link, and the minimum maximum utilization of network links as a metric of the network performance. 
-There are two directions for operating this example. One consider the min power consumption except for the 
-utilization, it is obviously that we should close the larger power consuming links, such as the 5M and 3M links, and 
-all the traffic go through the 2M link. In this way, the min max utilization of network is 0.5 and the power consuming 
-is 2 units (means the power difference come from the link mainly). The other consider the power except for the 
-utilization reversely, so we should split the 1M traffic to three parts, 0.2M across 2M link, 0.3M across 3M link and 
-0.5M across 5M, consequently with a min max utilization of 0.1, but the power is 10 units however.
+Usually, We computed routing to stipulate how is the traffic going, aimed to achieved some traffic engineering goals such as 
+the maximum link utilization ratio (MLUR). In details, we used traffic demands and network topology as input for routing 
+computation process, then combined routing and traffic demands to get the traffic on each link, based on which we determind
+which link can be put to sleep. However, measuring and predicting accurate traffic demands are difficult, so did the dynamic
+natrue. Even getting all knowledge about traffic demands, the related routing shift frequently when the traffic demands
+changes. It means that we should change the link (line cards) working mode frequently according to routing, and it is 
+unpractical. So the robust routing is needed, which based on the approximate traffic demands and was robust to sudden traffic changes.
+Such a routing is known as the demand-oblivious routing and is well studied in \cite{networking:oblivious}, which proposed
+the algorithm for computing robust routing with uncertain traffic demands on specific topology.
 
-Two directions mentioned above both are extremely single-consideration. Previous researchers solve the problem more 
-considerable, include ``GreenTE'' and ``a\%-green is engouh''. The former set a threshold of min max utilization, 
-close links as many as possible to achive the most power saving. And the latter one set a destination of the power 
-saving, calculate optimal route for get the min max utilization. Two work have their restriction, which both need a 
-specific traffic matrix that as base of their optimization.
+Unfortunately, there is no metric in such robust routing to measure the importance of links, in another word, we have no 
+ideas to put which link to sleep mode. Furthermore, when some links are switched off and the topology changed actually, but we 
+still have no ideas on how to adjust the routing in final topology. Another challenge is that, to achieve the power saving
+goals we may should switch off not only one link, and it is a classical NP-Hard problem. To overcome the challenges,
+we define a metric namely extended robust link utilization (ERLU) to measure the traffic engineering natrue without real traffic 
+demands, and define oblivious performance ratio (OPR) to reflect the MLUR distance from a routing to the optimal
+when certain energy conservation requirement is satisfied. We use algebraic connectivity \cite{networking:algebraic} and 
+ERLU as criterion to switch off links, and use OPR to adjust routing.
 
-But the need of precise current traffic matrix shound be carefully checked. Although some researcher contribute to this 
-area, the real precise traffic matrix still be a challenge. Take a step back, the dynamic of traffic matrix is more 
-diffcult even if we obtain the precise current one. Futhermore, ISP will not want to change their route policy 
-frequently, as it will result in other route failure possiblly. So our question is that : Is there exist a route both 
-satisfy power and utilization requirement for any traffic matrix given?
+Our main contribution in this paper contains three aspects. Firstly, we model the problem of minimizing the OPR, then
+analyze the lower and the upper bounds. Secondly, we proposed an heuristic algorithm named Robust Energy-Aware Routing (REAR) 
+to solve the problem in two phases, included choosing links to sleep and adjust routing. Thirdly, we implemented our
+algorithm in real topology and arbitrary traffic demands to observe the relationship between power saving and OPR. The
+simulation results show that REAR can save 19\% of line card power while OPR is less than 34\% in some topology. Also 
+we investigate the path stretching problem.
 
-David Applegate propose a method for obtain a route wihich is ``robust'' to variations in demands for a specific network topology.
+The rest of the paper is organized as follows. Section \Rmnum{2} reviews the related work and Section \Rmnum{3}
+define two new metric and model our problem. Following we proposed our algorithm in Section \Rmnum{4}. For understanding
+more clear on our problem, we give two simple samples and prove the bounds in Section \Rmnum{5}. Experiments are discribed
+and result are showed in Section \Rmnum{6}. We discuss issues and future work in Section \Rmnum{7}, then conclude in 
+Section \Rmnum{8}
+
+\section{Related Work}
+related work
 
@@
 
-\section{Related Work}
-related work.
+\section{Future and Issue}
+Future and Issue
 

### 2015-01-23 paper.tex
debug for connected problem

--- 2015-01-18 paper.tex
@@
 and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve 
-the problem in two phases. REAR select sleeping links based on extended robust link utilization or algebraic 
+the problem in two phases. REAR select sleeping links based on extended robust link utilization (ERLU) or algebraic 
 connectivity, and compute the routing based on a classical demand-oblivious routing algorithm. 
@@
 \section{Introduction}
-We aim to find the ``robust'' route for all possible traffic matrix, not only consider performance but also energy 
-consumption in network.
+Internet is playing a more and more important role in our daily life, as an huge and indispensable communication system
+it has considerable share in energy consumption. Network components such as routers and switchs contribute to the prominent
+consumption part on account of inefficient energy management solutions, which makes the devices always working in full mode 
+regardless of traffic demands. In particular, even there are no traffic on the link between two routers or switches, 
+the line cards related to the link are still working. Line cards are the main part of energy consuming in routers or switches 
+which is researched in previous work. For the energy consideration, we should obtain link-level solutions that
+switches the link (line cards) to sleep mode if possible.
 
-\section{Motivation}
-Suppose two hosts named host A and host B, and there are three links between 
-them, respectively, capacity with 2M, 3M and 5M. Now demands come, with 1M from A to B. we regard the capacity 
-as the power of the link, and the minimum maximum utilization of network links as a metric of the network performance. 
-There are two directions for operating this example. One consider the min power consumption except for the 
-utilization, it is obviously that we should close the larger power consuming links, such as the 5M and 3M links, and 
-all the traffic go through the 2M link. In this way, the min max utilization of network is 0.5 and the power consuming 
-is 2 units (means the power difference come from the link mainly). The other consider the power except for the 
-utilization reversely, so we should split the 1M traffic to three parts, 0.2M across 2M link, 0.3M across 3M link and 
-0.5M across 5M, consequently with a min max utilization of 0.1, but the power is 10 units however.
+Usually, We compute routing to stipulate how is the traffic going, to achieve some traffic engineering goals such as 
+the maximum link utilization ratio (MLUR). In details, we use traffic demands and network topology as input for
+computation, then combine routing and traffic demands to get the traffic on each link, based on which we determind
+which link can be put to sleep. However, measuring and predicting accurate traffic demands are difficult, so does its dynamic
+natrue. Although we have obtained all knowledge about traffic demands, the corresponding routing may shift frequently 
+when the traffic demands change. It means that we should change the link (line cards) working mode frequently as well, 
+of course it is unpractical. So we need the routing be robust to sudden traffic changes, and based on the approximate traffic demands.
+Such a routing is known as the demand-oblivious routing and is well studied in \cite{networking:oblivious}, which proposes
+the algorithm for computing robust routing with uncertain traffic demands on specific topology.
 
-Two directions mentioned above both are extremely single-consideration. Previous researchers solve the problem more 
-considerable, include ``GreenTE'' and ``a\%-green is engouh''. The former set a threshold of min max utilization, 
-close links as many as possible to achive the most power saving. And the latter one set a destination of the power 
-saving, calculate optimal route for get the min max utilization. Two work have their restriction, which both need a 
-specific traffic matrix that as base of their optimization.
+Unfortunately, there is no metric in such robust routing to measure the importance of links, in another word, we have no 
+idea to put which link to sleep mode. Furthermore, when some links are switched off and the topology changed actually, but we 
+still have no idea for how to adjust the routing in result topology. Another challenge is that, to achieve the power saving
+goals we may should switch off not only one link, and it is a classical NP-Hard problem. To overcome the challenges,
+we define a metric namely extended robust link utilization (ERLU) to measure the traffic engineering natrue of link without real traffic 
+demands, and define oblivious performance ratio (OPR) to reflect the MLUR distance from a routing to the optimal one
+when certain energy conservation requirement is satisfied. In our algorithm, we use algebraic connectivity \cite{networking:algebraic} and 
+ERLU as criterion to switch off links, and use OPR to adjust routing.
 
-But the need of precise current traffic matrix shound be carefully checked. Although some researcher contribute to this 
-area, the real precise traffic matrix still be a challenge. Take a step back, the dynamic of traffic matrix is more 
-diffcult even if we obtain the precise current one. Futhermore, ISP will not want to change their route policy 
-frequently, as it will result in other route failure possiblly. So our question is that : Is there exist a route both 
-satisfy power and utilization requirement for any traffic matrix given?
+Our main contribution in this paper is three-fold. Firstly, we model the problem of minimizing the OPR, then
+analyze the lower and the upper bounds. Secondly, we propose an heuristic algorithm named Robust Energy-Aware Routing (REAR) 
+to solve the problem in two phases, includes choosing links to sleep and adjusting routing. Thirdly, we implement our
+algorithm on real topology and arbitrary traffic demands to observe the relationship between energy conservation and OPR. The
+simulation results show that REAR can save 19\% power of line cards while OPR is less than 34\% in some topology. Also 
+we investigate the path stretching problem.
 
-David Applegate propose a method for obtain a route wihich is ``robust'' to variations in demands for a specific network topology.
+The rest of the paper is organized as follows. Section \Rmnum{2} reviews the related work and Section \Rmnum{3}
+defines two metric and models our problem. Following we propose our algorithm in Section \Rmnum{4}. For clearer understanding
+on our problem, we give two simple samples and prove the bounds in Section \Rmnum{5}. Experiments are discribed
+and result are showed in Section \Rmnum{6}. We discuss issues and future work in Section \Rmnum{7}, then conclude our wok in 
+Section \Rmnum{8}
+
+\section{Related Work}
+related work
 
 \section{Model}
-We model the network as a undirected graph $G = (V, E)$, where $V$ is the set of vertices (i.e., routers and end hosts), 
-and $E$ is the set of links (either link between routers or router and end-host). In graph $G$, two vertices $u$ and $v$
+The network is modeled as a undirected graph $G = (V, E)$, where $V$ is the set of vertices (i.e., routers, switches 
+and end hosts), and $E$ is the set of links. In graph $G$, two vertices $u$ and $v$
 are called connected if $G$ contains a path between $u$ and $v$. Then We say graph $G$ is connected, if and only if 
@@
 
-Let $\theta(G) = \{ (V, E - \{ e \}) | e \in E \}$ denote the network set after closing/removing the link $e$ from
-$G$. Then, choosing the connected graph from $\theta(G)$ to consist a new set, denoted by 
-$\Theta(G) = \{G | G \in \theta(G) \ \& \& \ G\ is\ connected\}$. We call $\Theta(G)$ as successor of $G$.
+Let $\theta(G) = \{ (V, E - \{ e \}) | e \in E \}$ denote the network set after removing the link $e$ from
+$G$. Then, choosing the connected graph from $\theta(G)$ to consist of a new set, denoted by 
+$\Theta(G) = \{G | G \in \theta(G) \ \&\& \ G\ is\ connected\}$. We call $\Theta(G)$ as successor of $G$.
 
-A $traffic\ matrix$ (abbreviation as TM below) is the set of traffic between each Origin-Destination(OD) pair in 
-network $G$, and a $routing$ specifies how traffic of each OD pair is routed across the network. Usually, there are 
-multiple paths for each OD pair and each path routes a fraction of the traffic. Let $m$ denote the $traffic\ matrix$, 
-which can be represented by a set of trinary group like $(a, b, d_{ab}$, where $a$ and $b$ is the origin and 
-destination of pair respectively, $d_{ab}$ is the traffic demand of the OD pair.
+A traffic matrix (abbreviation as TM below) is the set of traffic demands between each Origin-Destination(OD) pair in 
+network $G$, and the $routing$ specifies how traffic of each OD pair is routed across the network. Usually, there are 
+multiple paths for each OD pair and each path routes a fraction of the traffic.
+TM can be represented by a set of trinary group like $(a, b, d_{ab})$, where $a$ and $b$ is the origin and 
+destination node respectively, $d_{ab}$ is the traffic demand between the OD pair.
 
@@
 \begin{equation}
-	\sum_{(a,b,d_{ab}\in m)} d_{ab}f_{ab}(i,j)
+	\sum_{(a,b,d_{ab})\in TM} d_{ab}f_{ab}(i,j)
 \end{equation}
 
-Futhermore, we define the utilization of link as traffic acorss the link divide capacity of the link, as ;
+Futhermore, we define the utilization of link as traffic acorss the link divide the capacity of link, as ;
 \begin{equation}
@@
 
-A common metric for the performance of a given routing with respect to a certain TM is the $maximum\ link\ utilization$.
-This is the maximum utilization of link over all ones, Formally, the maximum link utilization of a routing $r$ on 
+A common metric of the performance for a given routing respect to a certain TM is the maximum link utilization ratio (MLUR).
+This is the maximum one of all links, Formally, the maximum link utilization ratio of a routing $r$ on 
 TM $m$ in network $G(V,E)$ is 
@@
 
-The $optimal\ routing$ in all the possible route $R$ for network $G$ is a routing which minimize the maximum utilization,
-the minimum maximum utilization is called optimal utilization, can be represented by :
+The optimal routing in all possible routes $R$ for network $G$ is a routing which minimize the MLUR,
+the minimum maximum link utilization ratio is called optimal utilization, can be represented by :
 \begin{equation}
@@
 
-The $performance\ ratio$ of a given routing $r$ on a given TM $m$ and a given network $G$ meaures how far from being 
-optimal, it is defined as the maximum link utilization divided by optimal utilization on the $m$ and $G$, as following : 
+The performance ratio of a given routing $r$ on a given TM $m$ and a given network $G$ meaures how far from the routing to
+the optimal one, it is defined as the MLUR divided by optimal utilization, as following : 
 \begin{equation}
@@
 
-We now extend the definition of performance ratio of a routing to be with respect to a set of TMs $M$. 
+We now extend the definition of performance ratio of a routing, from the specific TM $m$ to TM set $M$. 
 \begin{equation}
@@
 
-Obviously, the optimal routing in routing set $R$ for the set of TMs is a routing which minimize the extended 
-performance ratio, such as :
+Obviously, the optimal routing in routing set $R$ is the routing which minimize the extended performance ratio, such as :
 \begin{equation}
@@
 unique, the current routing always be the optimal routing. More generally, we should make a little modification
-for the $performance\ ratio$ as the network self changes.
+for the performance ratio when the network self changes.
 
-Let $G$ be the origin network, and the $G^* \in \Theta(G)$ be the successor network from $G$ after closing/removing
-some link, we define $performance\ ratio\ between\ different\ graphs$ as the performance ratio of successor graph divide 
-the optimal performance ratio of father graph, like :
+Let $G$ be the origin network, and the $G^* \in \Theta(G)$ be the successor network from $G$ after removing
+some links, we define extended performance ratio between different graphs as the MLUR of successor graph divide 
+the optimal utilization of origin graph, and get the minimum value of all routings, like :
 \begin{equation}
@@
 Now we can say that, if a successor network arrive the minimum performance ratio, it is the ``robust'' successor 
-network graph. Formally, we define the performance ratio as $optimal\ successor\ performance\ ratio$ :
+network graph. Formally, we define the performance ratio as optimal successor performance ratio :
 \begin{equation}
@@
 
-If the scope of $M$ is large engouh, the optimal successor network graph is alwo independent from specific TM.
+If the scope of $M$ is large engouh, the optimal successor network graph is also independent from specific TM.
 
 \subsection{Model Example}
-We will take an example to explain how to choose the link to close in our experiment.
-Three hostes include : A, B, C, Three links are with repectively capacity of 3M, 4M and 2M. For simpleness, we suppose 
+We will take an example to explain how to choose the link to close in our algorithm.
+Three hostes include : A, B, C, three links are with repectively capacity of 3M, 4M and 2M. For simpleness, we suppose 
 there are two TM : ${(A,B,2M), (A,C,1M)}$ and ${(A,B,1M), (A,C,1M)}$. For each traffic matrix, the optimal route is 
@@
 In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links 
-should be sleeping from the origin topology based on extended robust link utilization or algebraic connectivity, 
+should be put to sleep from the origin topology based on extended robust link utilization or algebraic connectivity, 
 then compute the robust routing by demand-oblivious routing algorithm. There are two metrics
 for selecting removed links, our two-phase algorithm is flexible because we can replace the metric with whatever
-metric which will be proposed in the future.
+metric.
 
@@
 algebraic connectivity, which is greater than 0 if and only if graph $G$ is connected. Further more,  
-it measures the connectivity and stability of graph, the greater of which, the more connective of graph;
+it measures the connectivity and stability of graph, the greater of the value, the more connective of graph;
 and it is a metric of average distance between any two vertices of graph $G$. We call the algebraic connectivity as
@@
 \subsection{Extended Robust Link Utilization}
-The demand-oblivious routing is well studied before, which means that this routing is not always the best one for 
-specific $TM$, but good enough for a range of $TMs$. we mentioned the definition of link utilization above when 
+The demand-oblivious routing is not always the best one for 
+specific $TM$, but good enough for a range of $TM$. we mentioned the definition of link utilization above when 
 demand and routing are determined, as demand become oblivious, the definition is also not suitable. So we define
-a notation named $extended\ robust\ link\ utilization$ replace the normal link utilization like :
+a notation named extended robust link utilization (ERLU) replace the normal link utilization like :
 \begin{equation}
@@
 
-Proposing this definition for two consideration: firstyly, the more flows across the link, the greater the $u^e_{ij}$ is;
-secondly, the more fraction of traffic in one flow across the link, the greater the $u^e_{ij}$ is. The link with greater
-extended robust link utilization is also more important than others in a sense. Although there is no demand here, we mean
+Proposing this definition for two consideration: firstly, the more flows across the link, the greater the $u^e_{ij}$ is;
+secondly, the more fraction of one flow across the link, the greater the $u^e_{ij}$ is. The link with greater
+ERLU is also more important than others in a sense. Although there is no demand here, we mean
 there is more probability that this link have greater link utilization when specific demand come. Similarly, we define 
@@
 Pay attention we only compute the link impact once at the begining of algorihtm, and the ordered list $\Gamma$ show 
-the order of `importance` among links in the graph.
+the order of `importance' among links in the graph.
 
@@
 So before going ahead our algorithm, there is another thing we should done, how to measure the power of graph.
-We simple take an power model from `Green TE` showed in Table xx, and defined the difference of power consumption 
+We simple take an power model from \cite{networking:greente} showed in Table \Rmnum{1}, and defined the difference of power consumption 
 between two graphs as:
 \begin{equation}
-	diff_p = \rho(G_{S, l}^o) / \rho(G^o) * 100
+	diff_p = \frac{\rho(G_{S, l}^o)} {\rho(G^o)} * 100
 \end{equation}
@@
 
+\begin{figure*}[!t]
+\centering
+\vspace*{0.1in}
+\subfloat{\includegraphics[width=6cm]{exp2_sort_cernet2}}
+\subfloat{\includegraphics[width=6cm]{exp2_sort_abilene}}
+\subfloat{\includegraphics[width=6cm]{exp2_sort_geant}}
+\caption{Sort: (a). Abilene (b).Geant}
+\vspace*{0.1in}
+\end{figure*}
+
 \section{Experiments and Results}
@@
 
-\begin{figure}[!t]
-\centering
-\vspace*{0.1in}
-\subfloat{\includegraphics[width=4cm]{exp2_nosort_abilene}}
-\subfloat{\includegraphics[width=4cm]{exp2_nosort_geant}}
-\caption{Nosort: (a). Abilene (b).Geant}
-\vspace*{0.1in}
-\end{figure}
-
-\begin{figure}[!t]
-\centering
-\vspace*{0.1in}
-\subfloat{\includegraphics[width=4cm]{exp2_sort_abilene}}
-\subfloat{\includegraphics[width=4cm]{exp2_sort_geant}}
-\caption{Sort: (a). Abilene (b).Geant}
-\vspace*{0.1in}
-\end{figure}
-
 From Figure xx and Figure xx, we sort the 1000 TMs by their OPR value, and see that most of the TMs are quite average. 

### 2015-01-23 experiment/cplex/deep_first_search_path.py

@@ -148,7 +148,11 @@ class Graph(object):
                 min_weight = 0
                 for i in range(len(path) - 1):
                     for n in self.node_neighbors[path[i]]:
-                        if (n[0] == path[i+1] and min_weight > n[1]) or (n[0] == path[i+1] and min_weight == 0):
+                        if i == 0 and path[i+1] == n[0]:
+                            min_weight = n[1]
+                            continue
+
+                        if (n[0] == path[i+1] and min_weight > n[1]):
                             min_weight = n[1]
                 
                 for i in range(len(path) - 1):

### 2015-01-23 experiment/cplex/exp_path.py

@@ -1,0 +1,221 @@
+import matplotlib.pyplot as plt
+from copy import deepcopy
+from prioritydictionary import priorityDictionary
+from graph import DiGraph
+import parse_xml as xml
+import optimal_route_with_tm as optimal
+import global_route_with_tm_bound as common
+import new_adjust_route_in_new_topology as adjust
+
+# Generate performance 
+
+is_gravity = True
+type_random = "bimodal"
+
+connected_topology_template = "../topology/connected/%s-connected-topology"
+final_topology_template = "../topology/final/%s-final-topology-%d"
+remove_links_template = "../topology/remove/%s-remove-%d-links"
+final_topology_base_template = "../topology/final/%s-final-topology-%d-base"
+remove_links_base_template = "../topology/remove/%s-remove-%d-links-base"
+solution_template = "%s-cplex-%0.1f.xml"
+demand_file_template = "../demand/%s-%s/%0.1f/%d.txt"
+result_file_template = "result-compare-%s-%0.1f"
+middle_file_template = "middle-compare-%s-%0.1f"
+solution_default = "global_opt_cplex_output.sol"
+files = 1000
+
+loop = 1
+w = 1.5
+
+remove_links_n = {'abilene':5, 'geant':16, 'cernet2':4}
+
+def dijkstra(g, length_graph, node_start):
+    distances = {}
+    Q = priorityDictionary()
+    visited  = []
+
+    for v in g:
+        distances[v] = g.INFINITY
+        Q[v] = g.INFINITY
+
+    distances[node_start] = 0
+    Q[node_start] = 0
+
+    for v in Q:
+        visited.append(v)
+        if len(visited) == length_graph:
+            break
+
+        for u in g[v]:
+            if u in visited:
+                continue
+            
+            cost_vu = distances[v] + g[v][u]
+            
+            if cost_vu < distances[u]:
+                distances[u] = cost_vu
+                Q[u] = cost_vu
+    return distances
+
+#for t in ['abilene', 'geant', 'cernet2']:
+for t in ['abilene', 'geant', 'cernet2']:
+    connected_topology = connected_topology_template % t
+    solution = solution_template % (t, w)
+    result_file = result_file_template % (t, w)
+    middle_file = middle_file_template % (t, w)
+
+
+    global_routes = xml.get_route(solution)
+    link_order = xml.get_link_order_with_attr(solution, connected_topology)
+    path_len_routes = dict()
[…]

### 2015-01-23 experiment/cplex/len_path.py

@@ -1,0 +1,50 @@
+import matplotlib.pyplot as plt
+
+topology_x_range = {'abilene':5, 'geant':12, 'cernet2':4}
+topology_line_type = {'abilene':'o', 'geant':'s', 'cernet2':'^'}
+color_type = {'base':'r--', 'new':'b-'}
+remove_type = {'base':'AC', 'new':'ERLU'}
+result_file_template = "path_stretch_%s.txt"
+
+line_list = []
+label_list = []
+for t in ['abilene', 'geant', 'cernet2']:
+    f = open(result_file_template % t)
+    line = f.readline()
+
+    m_mine = []
+    a_mine = []
+    m_base = []
+    a_base = []
+    x = []
+
+    while line:
+        tokens = line.strip().split(', ')
+        m_mine.append(float(tokens[1]))
+        a_mine.append(float(tokens[2]))
+        m_base.append(float(tokens[3]))
+        a_base.append(float(tokens[4]))
+
+        x.append(float(tokens[0]))
+
+        line = f.readline()
+
+    f.close()
+
+    l1, = plt.plot(x[:topology_x_range[t]], m_mine[:topology_x_range[t]], color_type['new']+topology_line_type[t])
+    l2, = plt.plot(x[:topology_x_range[t]], m_base[:topology_x_range[t]], color_type['base']+topology_line_type[t])
+    l1, = plt.plot(x[:topology_x_range[t]], a_mine[:topology_x_range[t]], color_type['new']+topology_line_type[t])
+    l2, = plt.plot(x[:topology_x_range[t]], a_base[:topology_x_range[t]], color_type['base']+topology_line_type[t])
+
+    label_list.append(t + '-' + remove_type['base'])
+    label_list.append(t + '-' + remove_type['new'])
+    
+    line_list.append(l1)
+    line_list.append(l2)
+
+#plt.legend(line_list, label_list, loc=2)
+
+plt.show()
+#plt.savefig('exp1_link.png', bbox_inches='tight')
+
+

### 2015-01-23 experiment/cplex/new_adjust_route_in_new_topology.py

@@ -73,6 +73,7 @@ def adjust_route(topology, remove_file, routes, link_order):
         #print(ls,ld)
         for s,d in routes:
             route_paths = routes[s,d]
+
             remove_route = []
             remove_weight = 0
             for path, weight in route_paths:
@@ -192,7 +193,7 @@ def check_route(routes, link_order):
 
 if __name__ == '__main__':
     #topology = '../topology/final/geant-final-topology-12-base'
-    topology_base = '../topology/final/geant-final-topology-12-base'
+    topology_base = '../topology/final/geant-final-topology-15-base'
     #solutions = 'abilene-connected-cplex.xml'
     solutions = 'geant-connected-cplex.xml'
     routes = xml.get_route(solutions)

### 2015-01-23 experiment/plot/exp2_sort.py

@@ -1,8 +1,8 @@
 import matplotlib.pyplot as plt
 
-result_file_template = "middle-compare-abilene-1.5"
+result_file_template = "middle-compare-cernet2-1.5"
 count = 1000
-remove = 5
+remove = 4
 
 f = open(result_file_template)
 line = f.readline();
@@ -48,7 +48,7 @@ for i in range(2, remove):
 plt.xlabel('Random Traffic Matrix')
 plt.ylabel('Oblivious Performance Ratio')
 plt.legend([line1, line2], ['AC', 'ERLU'], loc=2)
-#plt.show()
 
-plt.savefig('exp2_sort_abilene.png', bbox_inches='tight')
+#plt.show()
+plt.savefig('exp2_sort_cernet2.png', bbox_inches='tight')
 

### 2015-01-23 experiment/src/off_by_connectivity.c

@@ -70,6 +70,7 @@ int main(int argc, char **argv) {
 	int remove_link_n = 0;
 	FILE *remove = fopen(argv[5], "w");
 	for (int i = 0; i < links_n; i++) {
+        printf("%d\n", i);
 		double backup = matrix[links[i].s * nodes_n + links[i].d];
 
 		matrix[links[i].s * nodes_n + links[i].d] = 0;

### 2015-01-23 experiment/src/test_connectivity.c

@@ -1,0 +1,26 @@
+#include "tools.h"
+
+
+//
+//
+// ./off with_weight threshold input_topology output_topology remove_topology
+//
+//
+int main(int argc, char **argv) {
+	// init matrix
+	int nodes_n = 0, links_n = 0;
+	double * matrix = NULL;
+	link_t * links = NULL;
+    bool with_weight = true;
+	init_matrix_with_file(argv[1], &matrix, &links, &nodes_n, &links_n, with_weight);
+    
+    if (check_connectivity(matrix, nodes_n)) {
+        printf("connected\n");
+    } else {
+        printf("disconnected\n");
+    }
+
+	free(matrix);
+	return 0;
+}
+

### 2015-01-23 experiment/src/utils.c

@@ -62,18 +62,39 @@ void print_matrix(double * const matrix, int nodes_n) {
 	}
 }
 
+int get_unvisited(int * visited, int nodes_n) {
+    for (int i = 0; i < nodes_n; i++) {
+        if (visited[i] == 1) {
+            return i;
+        }
+    }
+    return -1;
+}
+
 bool check_connectivity(double * const matrix, int nodes_n) {
-	for (int i = 0; i < nodes_n; i++) {
-		bool connectivity = false;
+    int * visited = (int *) malloc(nodes_n * sizeof(int));
+    for (int i = 0; i < nodes_n; i++) {
+        visited[i] = 0;
+    }
+    visited[0] = 1;
+    
+    int unvisited = get_unvisited(visited, nodes_n);
+    while(unvisited != -1) {
+        visited[unvisited] = -1;
 		for (int j = 0; j < nodes_n; j++) {
-			if (i != j && matrix[i * nodes_n + j] < 0) {
-				connectivity = true;
-				break;
+			if (unvisited != j && matrix[unvisited * nodes_n + j] < 0) {
+				if (visited[j] == 0)
+                    visited[j] = 1;
 			}
 		}
-		if (!connectivity) {
-			return connectivity;
-		}
+
+        unvisited = get_unvisited(visited, nodes_n);
 	}
+
+    for (int i = 0; i < nodes_n; i++) {
+        if (visited[i] != -1) {
+            return false;
+        }
+    }
 	return true;
 }

### 2015-01-23 experiment/topology/remove_links_from_connected_graph_by_connectivity.sh

@@ -8,3 +8,13 @@ for topo in cernet2; do
 			../topology/remove/${topo}-remove-${remove_n}-links-base 
 	done
 done
+
+for topo in geant; do
+	#for with_weigth in 0 1; do
+	for remove_n in {1..15}; do
+		../bin/off_by_connectivity 0 ${remove_n}\
+			../topology/connected/${topo}-connected-topology \
+			../topology/final/${topo}-final-topology-${remove_n}-base \
+			../topology/remove/${topo}-remove-${remove_n}-links-base 
+	done
+done

### 2015-01-26 paper.tex
done with introduction by yy

@@
 \section{Introduction}
-Internet is playing a more and more important role in our daily life, as an huge and indispensable communication system
-it has considerable share in energy consumption. Network components such as routers and switchs contribute to the prominent
-consumption part on account of inefficient energy management solutions, which makes the devices always working in full mode 
-regardless of traffic demands. In particular, even there are no traffic on the link between two routers or switches, 
-the line cards related to the link are still working. Line cards are the main part of energy consuming in routers or switches 
-which is researched in previous work. For the energy consideration, we should obtain link-level solutions that
-switches the link (line cards) to sleep mode if possible.
 
-Usually, We compute routing to stipulate how is the traffic going, to achieve some traffic engineering goals such as 
-the maximum link utilization ratio (MLUR). In details, we use traffic demands and network topology as input for
-computation, then combine routing and traffic demands to get the traffic on each link, based on which we determind
-which link can be put to sleep. However, measuring and predicting accurate traffic demands are difficult, so does its dynamic
-natrue. Although we have obtained all knowledge about traffic demands, the corresponding routing may shift frequently 
-when the traffic demands change. It means that we should change the link (line cards) working mode frequently as well, 
-of course it is unpractical. So we need the routing be robust to sudden traffic changes, and based on the approximate traffic demands.
-Such a routing is known as the demand-oblivious routing and is well studied in \cite{networking:oblivious}, which proposes
-the algorithm for computing robust routing with uncertain traffic demands on specific topology.
+Energy conservation has become a global concern nowadays.
+The Internet is one of the major energy consumers, and its rapid growth makes the green Internet a hot research topic.
+In the Internet backbone, energy is mainly drawn by routers and switches.
+Such devices consume almost full power even if the traffic load is small.
+Thus, an effective method to save energy in the Internet is to aggregate traffic into part of the routers when the traffic load is small, and switch the under-utilized components (routers or line cards) into off/sleep mode.
+Such a method is known as the energy efficient routing.
 
-Unfortunately, there is no metric in such robust routing to measure the importance of links, in another word, we have no 
-idea to put which link to sleep mode. Furthermore, when some links are switched off and the topology changed actually, but we 
-still have no idea for how to adjust the routing in result topology. Another challenge is that, to achieve the power saving
-goals we may should switch off not only one link, and it is a classical NP-Hard problem. To overcome the challenges,
-we define a metric namely extended robust link utilization (ERLU) to measure the traffic engineering natrue of link without real traffic 
-demands, and define oblivious performance ratio (OPR) to reflect the MLUR distance from a routing to the optimal one
-when certain energy conservation requirement is satisfied. In our algorithm, we use algebraic connectivity \cite{networking:algebraic} and 
-ERLU as criterion to switch off links, and use OPR to adjust routing.
+An important issue for energy efficient routing is to avoid network congestion after the traffic is aggregated.
+Many approaches have been proposed in existing works.
+Most approaches compute the routing based on real-time traffic matrices or link loads, to achieve a good load balancing and avoid congestion.
+However, such approaches come at a cost of obtaining real-time traffic data.
+Furthermore, the routing may shift frequently with the traffic changes, and a sudden traffic change may still induce congestions.
+To this end, we need to study the robustness of energy efficient routing.
 
-Our main contribution in this paper is three-fold. Firstly, we model the problem of minimizing the OPR, then
-analyze the lower and the upper bounds. Secondly, we propose an heuristic algorithm named Robust Energy-Aware Routing (REAR) 
-to solve the problem in two phases, includes choosing links to sleep and adjusting routing. Thirdly, we implement our
-algorithm on real topology and arbitrary traffic demands to observe the relationship between energy conservation and OPR. The
-simulation results show that REAR can save 19\% power of line cards while OPR is less than 34\% in some topology. Also 
-we investigate the path stretching problem.
+Specifically, we study the energy efficient routing when traffic matrices cannot be obtained or predicted precisely, i.e., with uncertain traffic demands.
+To achieve robustness, we need to find a routing, which can perform near optimally under a range of traffic matrices.
+The key technique that makes this possible is the advanced \emph{demand-oblivious routing}.
+A seminal work \cite{networking:oblivious} find that, the distance between the maximum link utilization ratio (MLUR) of a demand-oblivious routing and the MLUR of the optimal routing is bounded.
+Thus, no matter how the traffic demand changes, the demand-oblivious routing can guarantee certain performance.
+We note that this conclusion is in a network without off/sleep components, and we need to consider the situation when energy conservation is required.
 
-The rest of the paper is organized as follows. Section \Rmnum{2} reviews the related work and Section \Rmnum{3}
-defines two metric and models our problem. Following we propose our algorithm in Section \Rmnum{4}. For clearer understanding
-on our problem, we give two simple samples and prove the bounds in Section \Rmnum{5}. Experiments are discribed
-and result are showed in Section \Rmnum{6}. We discuss issues and future work in Section \Rmnum{7}, then conclude our wok in 
-Section \Rmnum{8}
+However, existing demand-oblivious routing algorithms cannot be directly applied to energy efficient routing.
+There are several challenges.
+First, we need to define a metric that can effectively measure the distance between a robust energy efficient routing and the optimal routing, because the existing metric for demand-oblivious routing fails in the situation when some components are switched into off/sleep mode.
+Second, we need to analyze whether the metric can be bounded, just like for demand-oblivious routing.
+If there exists no bound, then it is not feasible to find a robust energy efficient routing.
+Third, we need practical algorithms to compute the robust energy efficient routing.
+Specifically, we need to determine: 1) which routers or line cards should be switched into off/sleep node; and 2) in which path to forward the traffic.
+
+In this paper, we overcome the aforementioned challenges.
+First, we define a new metric, namely the Oblivious Performance Ratio with Energy constraint (OPRE).
+The OPRE reflects the MLUR distance from a routing to the optimal one when certain energy conservation requirement is satisfied.
+We model the problem of minimizing the OPRE.
+Second, we prove that there exists a robust energy efficient routing with the minimum OPRE, which has an upper bound given a network.
+Then, we propose Robust Energy-Aware Routing (REAR) scheme, which uses heuristic algorithms to solve the problem.
+We develop algorithm XXX, which chooses off/sleep line cards in a way that the OPRE can be minimized potentially.
+We then develop algorithm XXX to compute the routing in the remaining topology, by extending existing optimal demand-oblivious routing algorithm.
+We evaluate our algorithms by simulations on real topologies and synthetic traffic demands with random fluctuations.
+The results show that REAR can achieve an OPRE of 1.34 while 19\% of line card power is saved.
+
+The rest of the paper is organized as follows.
+Section \Rmnum{2} shows the related work.
+Section \Rmnum{3} presents metric OPRE and formally models the problem.
+We presents the bounds on OPRE in Section \Rmnum{4}, and propose our algorithms in Section \Rmnum{5}.
+Section \Rmnum{6} shows our simulation setup and results, and Section \Rmnum{7} concludes our work.
 
@@
 So before going ahead our algorithm, there is another thing we should done, how to measure the power of graph.
-We simple take an power model from \cite{networking:greente} showed in Table \Rmnum{1}, and defined the difference of power consumption 
+We simple take an power model from \cite{networking:greente} showed in Table \Rmnum{2}, and defined the difference of power consumption 
 between two graphs as:
@@
 \section{Experiments and Results}
-We implemented our algorithm on real world topology, including Abilene, Geant and Cernet2, and we use Gravity model to generate
-random traffic matrix. Because we take an attribute $w$ to expand the traffic range from $1/w$ to $w$, when the $w$ increased the
-traffic varied in wider range. Particularly, when the $w$ limit extremity, we say the traffic matrix is really random, and our 
+We simulated our algorithm on real world topology, including Abilene, Geant and Cernet2, whose number of nodes and links are listed in Table \Rmnum{1}.
+Then we generate 1000 random traffic matrix with Gravity Model \cite{networking:gravity}, which assume that the traffic demand between nodes is proportional
+to their combined capacity of connecting links. To extrapolate a complete TM, we take an attribute $w$ to scale the traffic range from $1/w$ to $w$
+base on the basic traffic demand. Particularly, when the $w$ limit extremity, we say the traffic matrix is really arbitrary, and our 
 algorithm is irrelevant with traffic.
+
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1}
+\caption{Topologies}
+\label{three topologies}
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+\bfseries Topology & \bfseries Nodes & \bfseries Links & \bfseries Links can be Removed \\
+\hline
+Abilene & 12 & 15 & 4 \\
+\hline
+Geant & 23 & 37 & 15 \\
+\hline
+Cernet2 & 20 & 22 & 3 \\
+\hline
+\end{tabular}
+\end{table}
 
@@
 
-In Figure, we take $w$ as 1.5 and observe that: when we switch off more links, the OPR is increased as well. 
-It is obvious that when the topology
-lose connectivity by removing links, the worst case of robust routing must be far away from the optimal case in origin topology. And
-in Geant and Abilene, even in the origin topology, the OPR value still not be 1. It is reasonable, because our robust routing 
-is used for a range of traffic, however the optimal routing is calculated for the specific traffic matrix. But fortunately, our robust
-routing is only $24\%$ greater than the optimal routing even in its worst case of Geant. And we also see that the curve become 
-cliffy in the end, because when we remove the links the toplogy lose too much connectivity and there alwasy one path between two vertices.
-Obviously, the performance will become worse in the end. Lastly we say that although the OPR relation really different in different 
-topology, but the curve still be similar with each other, they are exponetial curve correspond with their vertices amount.
+\subsection{OPR versus Power Saving}
+In Figure 4(a), we see that the value of OPR is at least 1 even in the origin topology, particularly in Geant the value is 1.24,
+it means the robust routing always not be the optimal for all TMs even no links removed from topology. It is reasonable because
+our robust routing is used for a range of traffic rather than a specific TM.
 
-On the other hand, we may concern how is the OPR varifying when the power saving achived besides the amount of removed links.
-Of course the more we removed the links, the more power we saved, but how to quantify the power of one link is difficult. Green
-TE proposed the simple power model for topology, which can be represented in Table x:
+When we switch off links, the topology lose connectivity and some routing paths will be failed, traffic on those paths will be 
+adjusted to others, which result in the value of OPR increased. We take margin as 1.5 and observe this phenomena from Figure 4(a).
+And all the curves can split in two phases according to the growth speed of OPR, for example in Abilene, the OPR rise geantly 
+before 4 links are removed, and rise rapidly since then. It is revelatory for implementing our algorithm in real life, controlling
+the number of removed links less than the turning point is more efficient. The another reason for avoiding removeing too much links
+is that the robust routing will be less `robust', because there is only one path between two vertices in the minimum connected topology.
+
+On the other hand, we concern more about how is the OPR varifying when achived specific power saving target. Obviously, the more 
+links we removed, the more power we saved, but how to quantify the power of one link is difficult. Green TE \cite{networking:greente} 
+proposed a simple power model, which can be represented in Table \Rmnum{2}. In which, the total energy of topology is dominant by
 
@@
 
+\bibitem{networking:gravity}
+M.Roughan, A.Greenberg, C.Kalmanek, M.Rumsewicz, J.Yates, and Y.Zhang.
+Experience in measuring backbone traffic variability: models, metrics, measurements, and meaning.
+InProceedings of the 2nd Internet Measurement Workshop.
+ACM, 2002
 \end{thebibliography}

### 2015-01-26 experiment/cplex/compare.py

@@ -71,9 +71,7 @@ for t in ['abilene', 'geant', 'cernet2']:
 
         max_utilization = 0
         max_utilization_base = 0
-        f_optimal = None
-        if alpha != 0:
-            f_optimal = open(optimal_file, "r")
+        f_optimal = open(optimal_file, "r")
 
         for num in range(files):
             print("Round %d" % num)
@@ -88,17 +86,11 @@ for t in ['abilene', 'geant', 'cernet2']:
             #f = open(result_file,"a")
             # Calculate the optimal maximum utilization for specific traffic matrix
             optimal_utilization = 0
-            if alpha == 0:
-                f_tmp = open(optimal_file, "a")
-                optimal_utilization = optimal.optimal_utilization(connected_topology, demand_file, loop)
-                f_tmp.write("%d %f\n" % (num, optimal_utilization))
-                f_tmp.close()
+            optimal_line = f_optimal.readline().strip().split(' ')
+            if int(optimal_line[0]) != num:
+                print 'wrong'
             else:
-                optimal_line = f_optimal.readline().strip().split(' ')
-                if int(optimal_line[0]) != num:
-                    print 'wrong'
-                else:
-                    optimal_utilization = float(optimal_line[1])
+                optimal_utilization = float(optimal_line[1])
 
             print optimal_utilization
             #print('Optimal Utilization is %f\n' % optimal_utilization)
@@ -136,8 +128,7 @@ for t in ['abilene', 'geant', 'cernet2']:
                 max_utilization = global_utilization / optimal_utilization
 
         
-        if alpha != 0:
-            f_optimal.close()
+        f_optimal.close()
         f = open(result_file, 'a')
         print("%d %.4f %.4f\n" % (alpha, max_utilization_base, max_utilization))
         f.write("%d %.4f %.4f\n" % (alpha, max_utilization_base, max_utilization))

### 2015-01-26 experiment/cplex/exp_path.py

@@ -99,7 +99,6 @@ for t in ['abilene', 'geant', 'cernet2']:
                 path_len += (len(path) - 1) * weight
             path_len_routes[(alpha, s, d)] = path_len
 
-        print new_global_routes_fixed[17,18]
 
         #print path_len_routes
 

### 2015-01-26 paper.tex
change remove links ways

@@
 conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance 
-ratio (OPR) with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when 
+ratio (OPRE) with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when 
 certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio, 
@@
 We simulated our algorithm on real world topology, including Abilene, Geant and Cernet2, whose number of nodes and links are listed in Table \Rmnum{1}.
-Then we generate 1000 random traffic matrix with Gravity Model \cite{networking:gravity}, which assume that the traffic demand between nodes is proportional
+Then we generate random traffic matrix with Gravity Model \cite{networking:gravity}, which assume that the traffic demand between nodes is proportional
 to their combined capacity of connecting links. To extrapolate a complete TM, we take an attribute $w$ to scale the traffic range from $1/w$ to $w$
@@
 \subfloat{\includegraphics[width=4cm]{opr_with_power_saving}}
-\caption{OPR with Power Saving}
+\caption{OPRE with Power Saving}
 \vspace*{0.1in}
@@
 
-\subsection{OPR versus Power Saving}
-In Figure 4(a), we see that the value of OPR is at least 1 even in the origin topology, particularly in Geant the value is 1.24,
+\subsection{OPRE versus Power Saving}
+In Figure 4 (a), we see that the value of OPRE is at least 1 even in the origin topology, particularly in Geant the value is 1.24,
 it means the robust routing always not be the optimal for all TMs even no links removed from topology. It is reasonable because
@@
 When we switch off links, the topology lose connectivity and some routing paths will be failed, traffic on those paths will be 
-adjusted to others, which result in the value of OPR increased. We take margin as 1.5 and observe this phenomena from Figure 4(a).
-And all the curves can split in two phases according to the growth speed of OPR, for example in Abilene, the OPR rise geantly 
+adjusted to others, which result in the value of OPRE increased. We take margin as 1.5 and observe this phenomena from Figure 4 (a).
+And all the curves can split in two phases according to the growth speed of OPRE, for example in Abilene, the OPRE rise geantly 
 before 4 links are removed, and rise rapidly since then. It is revelatory for implementing our algorithm in real life, controlling
-the number of removed links less than the turning point is more efficient. The another reason for avoiding removeing too much links
-is that the robust routing will be less `robust', because there is only one path between two vertices in the minimum connected topology.
+the number of removed links less than the turning point is more efficient. The another reason for avoiding removing too much links
+is that the robust routing will be less `robust' or induce network congestions easily, because there is only one path between two
+vertices in the minimum connected topology.
 
-On the other hand, we concern more about how is the OPR varifying when achived specific power saving target. Obviously, the more 
+On the other hand, we concern more about how is the OPRE varifying when achived specific power saving target. Obviously, the more 
 links we removed, the more power we saved, but how to quantify the power of one link is difficult. Green TE \cite{networking:greente} 
-proposed a simple power model, which can be represented in Table \Rmnum{2}. In which, the total energy of topology is dominant by
+proposed a simple power model, which can be represented in Table \Rmnum{2}. In which, the total energy of topology is dominant by line
+cards of routers or switches, when saying switch off the links we mean put down the according line cards.
 
@@
 
-We compute the power saving ratio as the total power of the removed links over the total power of all the links. And we can
-save 19\% power with only 34\% worse than the worst case for all the traffic in Abilene topology. In Geant and Cernet2, 
-the OPR is little higher. Also we can see that two ways for removing links perform almost the same at the begin in Geant,
-and varified at the end. It shows that we may find another better way for removing the links in the future.
+We compute the power saving ratio as the total power of the removed links over the total power of all the links. 
+In Figure 4 (b), it shows we can save 19\% energy only with an OPRE of 1.34 in Abilene topology, and in Geant and Cernet2, 
+the OPRE is little higher. We also can see that two ways for removing links perform differently in different topologies,
+or perform differently in different phases of the same topology. For example, ERLU is better than AC in Abilene and AC is
+better in Cernet2, particularly in Geant, ERLU peform better at begining time.
 
@@
 
-From Figure xx and Figure xx, we sort the 1000 TMs by their OPR value, and see that most of the TMs are quite average. 
-It is said that, our metric OPR is always not be achived for most traffic matrix.
+From Figure xx and Figure xx, we sort the 1000 TMs by their OPRE value, and see that most of the TMs are quite average. 
+It is said that, our metric OPRE is always not be achived for most traffic matrix.
 
 We know when we compute the robust routing for specific topology, the $w$ is very important. When the $w$ limit extremely,
-our robust routing is said without knowledge of traffic matrix. Figure xx, show the OPR varified when $w$ changes. The greater
-the $w$ is, the greater the OPR is. It is obvious because when the $w$ is greater, the traffic matrix is random in more wider 
-range, and our OPR is the worst case of all the traffic matrix.
+our robust routing is said without knowledge of traffic matrix. Figure xx, show the OPRE varified when $w$ changes. The greater
+the $w$ is, the greater the OPRE is. It is obvious because when the $w$ is greater, the traffic matrix is random in more wider 
+range, and our OPRE is the worst case of all the traffic matrix.
 
@@
 \includegraphics[width=8cm,height=4cm]{exp3_w}
-\caption{OPR with w relationship}
+\caption{OPRE with w relationship}
 \vspace*{0.1in}

### 2015-01-26 experiment/cplex/pruning_link_by_link.py

@@ -22,7 +22,7 @@ def is_connected(links, nodes_n):
         return False
 
 #files = ['abilene', 'geant']
-files = ['cernet2']
+files = ['abilene', 'geant', 'cernet2']
 for name in files:
     topology = "../topology/connected/%s-connected-topology" % name
     f = open(topology, "r")
@@ -43,7 +43,7 @@ for name in files:
         links[d][s] = c
     f.close()
 
-    w = 1.5
+    w = 2.0
     temporary_topology = topology
     remove_links = []
     remove_n = 0
@@ -66,7 +66,7 @@ for name in files:
                 remove_links.append(l)
                 remove_n += 1
         
-                temporary_topology = "../topology/final/%s-final-topology-%d" % (name, remove_n)
+                temporary_topology = "../topology/final/%s-final-topology-%d-%0.1f" % (name, remove_n, w)
                 f = open(temporary_topology, "w")
                 f.write('%d %d\n' % (nodes_n, links_n-remove_n))
 
@@ -76,7 +76,7 @@ for name in files:
                             f.write('%d %d %.2f\n' % (s, d, links[s][d]))
                 f.close()
 
-                f = open("../topology/remove/%s-remove-%d-links" % (name, remove_n), "w")
+                f = open("../topology/remove/%s-remove-%d-links-%0.1f" % (name, remove_n, w), "w")
                 for l in remove_links:
                     f.write('%d %d\n' % (l[0], l[1]))
                 f.close()

### 2015-01-26 experiment/cplex/pruning_link_by_link.py
change remove links ways

@@ -48,8 +48,7 @@ for name in files:
     remove_links = []
     remove_n = 0
     while True:
-        cplex.generate_sol(temporary_topology, [0, w], True)  
-        link_order = xml.get_link_order("global_opt_cplex_output.sol", temporary_topology)
+        link_order = xml.get_link_order("%s-cplex-%0.1f.xml" % (name, w), temporary_topology)
 
         have_remove = False
         for l in link_order:

### 2015-01-28 paper.tex
update Jan 28th

@@
   % every instance of \includegraphics
-   \DeclareGraphicsExtensions{.png}
+   \DeclareGraphicsExtensions{.pdf,.png}
 \else
@@
 \hyphenation{op-tical net-works semi-conduc-tor}
+\newcommand{\ignore}[1]{{}}
 
@@
 conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance
-ratio (OPRE) with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when 
+ratio (OPR) with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when
 certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio,
@@
 Third, we need practical algorithms to compute the robust energy efficient routing.
-Specifically, we need to determine: 1) which routers or line cards should be switched into off/sleep node; and 2) in which path to forward the traffic.
+Specifically, we need to determine: 1) which routers or line cards should be switched into off/sleep mode, to achieve energy efficiency; and 2) in which path to forward the traffic for robustness, while the path does not traverse the off/sleep components.
 
 In this paper, we overcome the aforementioned challenges.
-First, we define a new metric, namely the Oblivious Performance Ratio with Energy constraint (OPRE).
+First, we define a new metric, namely the oblivious performance ratio with energy constraint (OPRE).
 The OPRE reflects the MLUR distance from a routing to the optimal one when certain energy conservation requirement is satisfied.
@@
 
+\ignore{
+Usually, We compute routing to stipulate how is the traffic going, to achieve some traffic engineering goals such as
+the maximum link utilization ratio (MLUR). In details, we use traffic demands and network topology as input for
+computation, then combine routing and traffic demands to get the traffic on each link, based on which we determind
+which link can be put to sleep. However, measuring and predicting accurate traffic demands are difficult, so does its dynamic
+natrue. Although we have obtained all knowledge about traffic demands, the corresponding routing may shift frequently
+when the traffic demands change. It means that we should change the link (line cards) working mode frequently as well,
+of course it is unpractical. So we need the routing be robust to sudden traffic changes, and based on the approximate traffic demands.
+Such a routing is known as the demand-oblivious routing and is well studied in \cite{networking:oblivious}, which proposes
+the algorithm for computing robust routing with uncertain traffic demands on specific topology.
+
+Unfortunately, there is no metric in such robust routing to measure the importance of links, in another word, we have no
+idea to put which link to sleep mode. Furthermore, when some links are switched off and the topology changed actually, but we
+still have no idea for how to adjust the routing in result topology. Another challenge is that, to achieve the power saving
+goals we may should switch off not only one link, and it is a classical NP-Hard problem. To overcome the challenges,
+we define a metric namely extended robust link utilization (ERLU) to measure the traffic engineering natrue of link without real traffic
+demands, and define oblivious performance ratio (OPR) to reflect the MLUR distance from a routing to the optimal one
+when certain energy conservation requirement is satisfied. In our algorithm, we use algebraic connectivity \cite{networking:algebraic} and
+ERLU as criterion to switch off links, and use OPR to adjust routing.
+
+Our main contribution in this paper is three-fold. Firstly, we model the problem of minimizing the OPR, then
+analyze the lower and the upper bounds. Secondly, we propose an heuristic algorithm named Robust Energy-Aware Routing (REAR)
+to solve the problem in two phases, includes choosing links to sleep and adjusting routing. Thirdly, we implement our
+algorithm on real topology and arbitrary traffic demands to observe the relationship between energy conservation and OPR. The
+simulation results show that REAR can save 19\% power of line cards while OPR is less than 34\% in some topology. Also
+we investigate the path stretching problem.
+
+The rest of the paper is organized as follows. Section \Rmnum{2} reviews the related work and Section \Rmnum{3}
+defines two metric and models our problem. Following we propose our algorithm in Section \Rmnum{4}. For clearer understanding
+on our problem, we give two simple samples and prove the bounds in Section \Rmnum{5}. Experiments are discribed
+and result are showed in Section \Rmnum{6}. We discuss issues and future work in Section \Rmnum{7}, then conclude our wok in
+Section \Rmnum{8}}
+
 \section{Related Work}
@@
 
-\section{Model}
-The network is modeled as a undirected graph $G = (V, E)$, where $V$ is the set of vertices (i.e., routers, switches 
-and end hosts), and $E$ is the set of links. In graph $G$, two vertices $u$ and $v$
-are called connected if $G$ contains a path between $u$ and $v$. Then We say graph $G$ is connected, if and only if 
-arbitrary pair of vertices in the graph is connected.
+\section{Problem Statement}
 
-Let $\theta(G) = \{ (V, E - \{ e \}) | e \in E \}$ denote the network set after removing the link $e$ from
-$G$. Then, choosing the connected graph from $\theta(G)$ to consist of a new set, denoted by 
-$\Theta(G) = \{G | G \in \theta(G) \ \&\& \ G\ is\ connected\}$. We call $\Theta(G)$ as successor of $G$.
+\subsection{Background of Demand-Oblivious Routing}
 
-A traffic matrix (abbreviation as TM below) is the set of traffic demands between each Origin-Destination(OD) pair in 
-network $G$, and the $routing$ specifies how traffic of each OD pair is routed across the network. Usually, there are 
-multiple paths for each OD pair and each path routes a fraction of the traffic.
-TM can be represented by a set of trinary group like $(a, b, d_{ab})$, where $a$ and $b$ is the origin and 
-destination node respectively, $d_{ab}$ is the traffic demand between the OD pair.
+As mentioned above, demand-oblivious routing aims at finding one routing that performs near optimally under a range of traffic demands.
+In traffic engineering, a typical metric to evaluate routing performance is the maximum link utilization ratio (MLUR).
+Clearly, the MLUR is corresponded with a specified traffic matrix (TM).
+Demand-oblivious routing defines oblivious performance ratio (OPR) to evaluate the routing performance without the knowledge of TM.
+We briefly present the background.
 
-Let $r$ denote the $routing$ mentioned above, which is specified by a set of values $f_{ab}(i,j)$ that specifies the 
-fraction of demand from $a$ to $b$ that is routed on the link $(i,j)$. So an OD pair contribute to the traffic of 
-link $(i,j)$ is $d_{ab}f_{ab}(i,j)$, and all the traffic across link $(i,j)$ can be calculated as :
+Given a TM, the distance between a routing to the optimal one is defined as the ratio between their MLURs.
+Formally, a network is modeled as undirected graph $G(V, E)$, where $V$ is the set of vertices (nodes), and $E$ is the set of edges (links).
+Let $cap_{ij}$ denote the capacity of the link $(i, j) \in E$.
+Let $d_{ab}$ denote the traffic demand from origin node $a$ and destination node $b$, and $m$ denote the TM that contains $d_{ab}$ for all $a, b \in V$.
+Let $f_{ab}(i,j)$ be the fraction of $d_{ab}$ that is routed on link $(i, j)$ $(0 \leq f_{ab}(i,j) \leq 1)$.
+Routing $r$ is specified by $f_{ab}(i,j)$ for all $a, b \in V$ and $(i, j) \in E$, and we will formally define routing consistency later in Section III.C.
+Let $U_{r, m, G}$ be the MLUR of routing $r$ under TM $m$.
+We have
 \begin{equation}
-	\sum_{(a,b,d_{ab})\in TM} d_{ab}f_{ab}(i,j)
+	U_{r, m, G} = \max_{(i,j)\in E} \frac{\sum_{a,b} d_{ab}f_{ab}(i,j)}{cap_{ij}}.
+\end{equation}
+Let $P(\{ r \},\{ m \}, G)$ be the \emph{performance ratio} of routing $r$ under TM $m$, which reflects how far from the routing to the optimal one, and is defined as
+\begin{equation}
+	P(\{ r \},\{ m \}, G) = \frac{U_{r,m,G}}{\min_{r'} U_{r', m, G}}.
 \end{equation}
 
-Futhermore, we define the utilization of link as traffic acorss the link divide the capacity of link, as ;
+The \emph{oblivious performance ratio} (OPR) for routing $r$ is defined by extending TM $m$ to a set of TMs $M$, where $M$ can be the set of any TMs. We have
 \begin{equation}
-	u_{ij} = \frac{\sum_{a,b} d_{ab}f_{ab}(i,j)}{cap_{ij}}
+	P(\{ r \}, M, G) = \max_{m\in M} P(\{ r \}, \{ m \}, G).
 \end{equation}
-where $cap_{ij}$ is the capacity of the link $(i,j)$.
+The target of demand-oblivious routing is to find routing $r$ that minimizes OPR $P(\{ r \}, M, G)$.
+Such a ``robust'' routing is independent of a specific TM, but can perform near optimally.
+A seminal work \cite{networking:oblivious} uses linear programming to find the routing that minimizes the OPR, and finds that the optimal solution exists, which means that the OPR is bounded.
 
-A common metric of the performance for a given routing respect to a certain TM is the maximum link utilization ratio (MLUR).
-This is the maximum one of all links, Formally, the maximum link utilization ratio of a routing $r$ on 
-TM $m$ in network $G(V,E)$ is 
+\subsection{Oblivious Performance Ratio with Energy Constraint}
+
+With energy constraint, a network may have to switch part of line cards into off/sleep mode to save the total energy consumption.
+This changes the network topology and makes metric OPR fail to evaluate the robustness of a routing.
+We use an example to show this.
+Assume that $G$ is a cycle with $n$ unit capacity links.
+Then, the minimal OPR of $G$ is $2-2/n$ \cite{networking:oblivious}.
+Now we pruning one link from $G$ to save energy, and the topology changes to $G^*$.
+Because there is only one routing feasible in $G^*$, OPR $P(\{ r \}, M, G^*)$ equals 1.
+Since 1 is less than $2-2/n$ for $n > 2$, it means that the routing after pruning one link is more robust than before.
+However, it is false because there are less links and the network is more likely to be congested.
+
+The intrinsic reason for such a ``fake robust'' is that the topology is not changing when performance ratio is computed in Eq.
+(2).
+To address this issue, we extend the definition of OPR.
+Formally, let $G^*$ be a sub-graph of $G$ that satisfies the energy constraint (We will formally give the model in Section III.C).
+The extended performance ratio is defined as
 \begin{equation}
-	U_{r, m, G} = \max_{(i,j)\in E} u_{ij}
+	P(\{ r \},\{ m \}, G, G^*) = \frac{U_{r,m,G^*}}{\min_{r'} U_{r', m, G}}.
 \end{equation}
+Let $P^*(\{ r \}, M, G)$ be the \emph{oblivious performance ratio with energy constraint} (OPRE) for routing $r$.
+We define $P^*(\{ r \}, M, G)$ by extending $m$ to $M$, and finding $G^*$ that satisfies the energy constraint and has the minimum performance ratio.
+We have
+\begin{equation}
+	P^*(\{ r \}, M, G) = \min_{G^*} \max_{m\in M} P(\{ r \}, \{ m \}, G, G^*)
+\end{equation}
+Note that when there is no energy constraint, $G$ is the sub-graph that has the minimum performance ratio, and Eq. (5) naturally reduces to Eq. (3).
 
-The optimal routing in all possible routes $R$ for network $G$ is a routing which minimize the MLUR,
-the minimum maximum link utilization ratio is called optimal utilization, can be represented by :
-\begin{equation}
-	OptU_{m, G} = \min_{r\in R} U_{r, m, G}
-\end{equation}
-
-The performance ratio of a given routing $r$ on a given TM $m$ and a given network $G$ meaures how far from the routing to
-the optimal one, it is defined as the MLUR divided by optimal utilization, as following : 
-\begin{equation}
-	P(\{ r \},\{ m \}, G) = \frac{U_{r,m,G}}{OptU_{m,G}}
-\end{equation}
-
-We now extend the definition of performance ratio of a routing, from the specific TM $m$ to TM set $M$. 
-\begin{equation}
-	P(\{ r \}, M, G) = \max_{m\in M} P(\{ r \}, \{ m \}, G)
-\end{equation}
-
-Obviously, the optimal routing in routing set $R$ is the routing which minimize the extended performance ratio, such as :
-\begin{equation}
-	P(R, M, G) = \min_{r\in R} P(\{ r \}, M, G)
-\end{equation}
-
-I.E. the routing $r$ which arrive at the value of $P(R,M,G)$ is the most ``robust'' routing for the TM set $M$ 
-in the network $G$, and if the $M$ range enough, we say that the ``robust'' routing is independent of specific TM.
-
-But definition of ``robust'' above will not work well for next situation. Let us take a cycle network topology $C$ as 
-an simple example, in which we should choose one link to close. Before link cutting, the $P(R, M, C)$ is 
-approximate to 2, but no matter which link is chosen to close, the cycle network will change to a line network $L$. 
-Obviously, the $P(R, M, L)$ will always equal to 1. It means that there is no difference from removing which link,
-But the contradiction here is that, the choice for which link should be removed is really different because the 
-links are not always the same with each other, such as their capacity.
-
-The reason for the ``fake robust'' is that, the routing in the successor graph (i.e. $L$ in above example) become 
-unique, the current routing always be the optimal routing. More generally, we should make a little modification
-for the performance ratio when the network self changes.
-
-Let $G$ be the origin network, and the $G^* \in \Theta(G)$ be the successor network from $G$ after removing
-some links, we define extended performance ratio between different graphs as the MLUR of successor graph divide 
-the optimal utilization of origin graph, and get the minimum value of all routings, like :
-\begin{equation}
-	P(R^*, \{ m\}, G, G^*) = \min_{r \in R^*} \frac{U_{r,m,G^*}}{OptU_{m,G}}
-\end{equation}
-where $R^*$ is the routing set on network $G^*$.
-
-And question is that how to meaure a successor network topology is ``robust'' enough for the TM set $M$ when 
-pruning is proceeding. We consider the worst situation, namely the successor network topology has its maximum
-performance ratio when the TM is $m \in M$, described as following :
-\begin{equation}
-	P(R^*, M, G, G^*) = \max_{m \in M} P(R^*, \{ m \}, G, G^*)
-\end{equation}
-
-Now we can say that, if a successor network arrive the minimum performance ratio, it is the ``robust'' successor 
-network graph. Formally, we define the performance ratio as optimal successor performance ratio :
-\begin{equation}
-	P^{*}(M, G) = \min_{G^* \in \Theta(G)} P(R^*, M, G, G^*)
-\end{equation}
-where $M$ is the TM set, and $R^*$ is routing set.
-
-If the scope of $M$ is large engouh, the optimal successor network graph is also independent from specific TM.
+\subsection{Problem Formulation}
 
@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
 \centering
 \vspace*{0.1in}
-\subfloat{\includegraphics[width=4cm]{opr_with_remove_links}}
-\subfloat{\includegraphics[width=4cm]{opr_with_power_saving}}
+\subfloat{\includegraphics[width=6cm]{opr_with_power_abilene}}
+\subfloat{\includegraphics[width=6cm]{opr_with_power_geant}}
+\subfloat{\includegraphics[width=6cm]{opr_with_power_cernet2}}
 \caption{OPRE with Power Saving}
 \vspace*{0.1in}
-\end{figure}
+\end{figure*}
+
+\begin{figure*}[!t]
+\centering
+\vspace*{0.1in}
+\subfloat{\includegraphics[width=6cm]{exp4_path_geant}}
+\subfloat{\includegraphics[width=6cm]{exp4_path_abilene}}
+\subfloat{\includegraphics[width=6cm]{exp4_path_cernet2}}
+\caption{Sort: (a). Abilene (b).Geant}
+\vspace*{0.1in}
+\end{figure*}
 
@@
 
-For computing the worst case, we generate 1000 traffic matrix for every topoloy and the $w$ with the Gravity Model.
-We show the each result in the Figure x and x when we remove the first 4 links in each topology. In Abilene, the result 
-is more tighter than Geant. Comparsion in two ways, we can see that in Abilene the AC method is worse than the ERLU one,
-and the downmost zone is the same in two ways, because the robust routing is same in the origin topology.
+\subsection{OPRE versus TMs}
+To simulate the worst case, we generate 1000 traffic matrices for every topoloy with margin attribute $w$. Figure 5 shows
+the OPRE distribution in the process of experiment. For avoiding mess result from too many lines, we just show the first 
+three lines and the base line, which shows the distribution when no links is removed, i.e. seven lines in each figure.
 
-From Figure xx and Figure xx, we sort the 1000 TMs by their OPRE value, and see that most of the TMs are quite average. 
-It is said that, our metric OPRE is always not be achived for most traffic matrix.
+In Figure 3 (a), we can only observe five lines because there are two overlapping lines, which means that when removing 
+links the worst case for the robust routing does not change. Maybe the random traffic matrices is not bad enough, or the 
+removed link really do not affect the MLUR. And from Figure 3, we see that the OPRE is not always be achived for most
+traffic matrices, the common value is much less than OPRE.
 
-We know when we compute the robust routing for specific topology, the $w$ is very important. When the $w$ limit extremely,
-our robust routing is said without knowledge of traffic matrix. Figure xx, show the OPRE varified when $w$ changes. The greater
-the $w$ is, the greater the OPRE is. It is obvious because when the $w$ is greater, the traffic matrix is random in more wider 
-range, and our OPRE is the worst case of all the traffic matrix.
+Comparing two ways in first phase of REAR algorithm, in Abilene and Geant ERLU is always better than AC, furthermore in
+some time, although more links are removed from topology the result of ERLU is still better. For most TMs, after switching 
+off three links the OPRE is 1.2 and 1.6 respectively in Abilene and Geant. However, the ERLU is less optimal than ERLU in 
+Cernet2, when we investigate the Cernet2 topology and find the crucial reason is the link between vertex Hangzhou and 
+vertex Xiamen, which is least important in the meaning of algebraic connectivity rather ERLU.
+
+\subsection{OPRE versus Margin}
+We take the margin $w$ as one of the input for computing robust routing, and margin identify a range of TMs the routing is 
+robust for. Once the $w$ limit extremely, our robust routing is said without knowledge of traffic matrix. Figure 5 shows the 
+OPRE increased as $w$ increased. It is obvious because when the $w$ is greater, the traffic matrix is random in more wider
+range, and our OPRE may achieve worse case with more probability.
+
+And we find when the margin increases from 1.5 to 2.0, the OPER increases much less, particularly in the begining of removing,
+the difference almost can not be observed. It is a good phenomena for us, the variation of margin, i.e. the range of traffic
+matrices affect little on the OPRE when the energy conservation is limited within 12\% in Geant.
+
+\subsection{Path Stretching}
+Path stretching must be careful concerned in routing problem. Suppose two vertices connect directly each other in the origin topology,
+if we remove the connected link then they can connect by another path which is composed by multi links. However we argue path stretching
+between these situation may be unjust, because path stretching result from the difference of topologies rather than routing selection.
+So we obtain the shortest path by Dijkstra Algorithm in the final topology, and compare it with robust routings generated by 
+our REAR algorithm. Futher, we show the difference between two ways of removing link, and see the tendency when margin increased.
+
+In Figure 5, we see every line ends with path stretching ratio of 1, because topology become a tree structure when lose too much links,
+every path between vertices come to be unique, namely each path is the shortest path. Another conclusion is that, even in the origin 
+topology, our robust routing is 17\% longer than the shortest one, it is beacuse our algorithm not only consider the MLUR but also 
+the robust performance. However the Dijkstra just take the path length as metric.
+
+We can observe that, ERLU is always shorter than AC, althoungh in Geant, the worst case is 36\% than the shortest path when margin 
+equal to 1.5. And in the first removed links, the path stretching ratio is near 20\%.
 
@@
 \end{figure}
-
-\section{Future and Issue}
-Future and Issue
 

### 2015-01-28 experiment/cplex/compare.py

@@ -12,8 +12,8 @@ type_random = "bimodal"
 connected_topology_template = "../topology/connected/%s-connected-topology"
 final_topology_template = "../topology/final/%s-final-topology-%d"
 remove_links_template = "../topology/remove/%s-remove-%d-links"
-final_topology_base_template = "../topology/final/%s-final-topology-%d-base"
-remove_links_base_template = "../topology/remove/%s-remove-%d-links-base"
+final_topology_base_template = "../topology/final/%s-final-topology-%d-power"
+remove_links_base_template = "../topology/remove/%s-remove-%d-links-power"
 solution_template = "%s-cplex-%0.1f.xml"
 demand_file_template = "../demand/%s-%s/%0.1f/%d.txt"
 result_file_template = "result-compare-%s-%0.1f"
@@ -23,7 +23,7 @@ solution_default = "global_opt_cplex_output.sol"
 files = 1000
 
 loop = 1
-w = 1.5
+w = 2.5
 
 remove_links_n = {'abilene':5, 'geant':16, 'cernet2':4}
 

### 2015-01-28 experiment/cplex/exp_path.py

@@ -15,8 +15,8 @@ type_random = "bimodal"
 connected_topology_template = "../topology/connected/%s-connected-topology"
 final_topology_template = "../topology/final/%s-final-topology-%d"
 remove_links_template = "../topology/remove/%s-remove-%d-links"
-final_topology_base_template = "../topology/final/%s-final-topology-%d-base"
-remove_links_base_template = "../topology/remove/%s-remove-%d-links-base"
+final_topology_base_template = "../topology/final/%s-final-topology-%d-power"
+remove_links_base_template = "../topology/remove/%s-remove-%d-links-power"
 solution_template = "%s-cplex-%0.1f.xml"
 demand_file_template = "../demand/%s-%s/%0.1f/%d.txt"
 result_file_template = "result-compare-%s-%0.1f"
@@ -25,7 +25,6 @@ solution_default = "global_opt_cplex_output.sol"
 files = 1000
 
 loop = 1
-w = 1.5
 
 remove_links_n = {'abilene':5, 'geant':16, 'cernet2':4}
 
@@ -57,164 +56,142 @@ def dijkstra(g, length_graph, node_start):
                 Q[u] = cost_vu
     return distances
 
-#for t in ['abilene', 'geant', 'cernet2']:
-for t in ['abilene', 'geant', 'cernet2']:
-    connected_topology = connected_topology_template % t
-    solution = solution_template % (t, w)
-    result_file = result_file_template % (t, w)
-    middle_file = middle_file_template % (t, w)
+for w in [1.5, 2.0, 2.5, 3.0, 3.5, 4.0]:
+    for t in ['abilene', 'geant', 'cernet2']:
+        connected_topology = connected_topology_template % t
+        solution = solution_template % (t, w)
+        result_file = result_file_template % (t, w)
+        middle_file = middle_file_template % (t, w)
 
 
-    global_routes = xml.get_route(solution)
-    link_order = xml.get_link_order_with_attr(solution, connected_topology)
-    path_len_routes = dict()
-    path_len_routes_base = dict()
-    path_len_shortest = dict()
-    path_len_shortest_base = dict()
-    for alpha in range(0, remove_links_n[t]):
-        final_topology = final_topology_template % (t, alpha)
-        remove_links = remove_links_template % (t, alpha)
-        final_topology_base = final_topology_base_template % (t, alpha)
-        remove_links_base = remove_links_base_template % (t, alpha)
+        global_routes = xml.get_route(solution)
[…]

### 2015-01-28 experiment/cplex/len_path.py

@@ -1,50 +1,55 @@
 import matplotlib.pyplot as plt
 
-topology_x_range = {'abilene':5, 'geant':12, 'cernet2':4}
+topology_x_range = {'abilene':5, 'geant':16, 'cernet2':4}
 topology_line_type = {'abilene':'o', 'geant':'s', 'cernet2':'^'}
 color_type = {'base':'r--', 'new':'b-'}
 remove_type = {'base':'AC', 'new':'ERLU'}
-result_file_template = "path_stretch_%s.txt"
+result_file_template = "path_stretch_%s_%0.1f.txt"
 
 line_list = []
 label_list = []
-for t in ['abilene', 'geant', 'cernet2']:
-    f = open(result_file_template % t)
-    line = f.readline()
-
-    m_mine = []
-    a_mine = []
-    m_base = []
-    a_base = []
-    x = []
-
-    while line:
-        tokens = line.strip().split(', ')
-        m_mine.append(float(tokens[1]))
-        a_mine.append(float(tokens[2]))
-        m_base.append(float(tokens[3]))
-        a_base.append(float(tokens[4]))
-
-        x.append(float(tokens[0]))
-
+#for t in ['geant']:
+#for t in ['abilene']:
+for t in ['cernet2']:
+    for w in [1.5, 2.0]:
+        f = open(result_file_template % (t, w))
         line = f.readline()
 
-    f.close()
+        m_mine = []
+        a_mine = []
+        m_base = []
+        a_base = []
+        x = []
 
-    l1, = plt.plot(x[:topology_x_range[t]], m_mine[:topology_x_range[t]], color_type['new']+topology_line_type[t])
-    l2, = plt.plot(x[:topology_x_range[t]], m_base[:topology_x_range[t]], color_type['base']+topology_line_type[t])
-    l1, = plt.plot(x[:topology_x_range[t]], a_mine[:topology_x_range[t]], color_type['new']+topology_line_type[t])
-    l2, = plt.plot(x[:topology_x_range[t]], a_base[:topology_x_range[t]], color_type['base']+topology_line_type[t])
+        while line:
+            tokens = line.strip().split(', ')
+            m_mine.append(float(tokens[1]))
+            a_mine.append(float(tokens[2]))
+            m_base.append(float(tokens[3]))
+            a_base.append(float(tokens[4]))
 
-    label_list.append(t + '-' + remove_type['base'])
-    label_list.append(t + '-' + remove_type['new'])
-    
[…]

### 2015-01-28 experiment/cplex/pruning_link_by_link.py

@@ -43,7 +43,7 @@ for name in files:
         links[d][s] = c
     f.close()
 
-    w = 2.0
+    w = 4.0
     temporary_topology = topology
     remove_links = []
     remove_n = 0

### 2015-01-28 experiment/cplex/pruning_link_by_power.py

@@ -1,0 +1,110 @@
+import parse_xml as xml
+import global_route_with_tm_bound as cplex
+
+# check the graph represented by links if connected.
+# nodes is the set of visited nodes, stack is the stack of to-be-visited nodes
+# every time pop a node from stack, visit it, 
+# and finally check if all the nodes is visited.
+def is_connected(links, nodes_n):
+    stack = [0]
+    nodes = set()
+    
+    while len(stack) > 0:
+        from_node = stack.pop()
+        nodes.add(from_node)
+        for to_node in range(nodes_n):
+            if links[from_node][to_node] != 0 and to_node not in nodes:
+                stack.append(to_node)
+
+    if len(nodes) == nodes_n:
+        return True
+    else:
+        return False
+
+
+
+#files = ['abilene', 'geant']
+power_models = {155.0:60, 1240.0:100, 2480.0:140, 9920:174}
+power_model = [60, 100, 140, 174]
+
+files = ['abilene', 'cernet2', 'geant']
+for name in files:
+    topology = "../topology/connected/%s-connected-topology" % name
+    f = open(topology, "r")
+    
+    line = f.readline().strip()
+    nodes_n = int(line.split(' ')[0])
+    links_n = int(line.split(' ')[1])
+
+    links = [[0 for i in range(nodes_n)] for j in range(nodes_n)]
+    powers = []
+    for line in f:
+        tokens = line.strip().split(' ')
+
+        s = int(tokens[0])
+        d = int(tokens[1])
+        c = float(tokens[2])
+
+        total = 0
+        if c <= 155.0:
+            total = power_model[0]
+        elif c <= 1240.0:
+            total = power_model[1]
+        elif c <= 2480.0:
+            total = power_model[2]
+        elif c <= 9920.0:
+            total = power_model[3]
+
+        powers.append((s,d,total))
+
+        links[s][d] = c
+        links[d][s] = c
+    f.close()
+
+    for i in range(0, len(powers) - 1):
+        for j in range(i+1, len(powers)):
+            si, di, pi = powers[i]
+            sj, dj, pj = powers[j]
+            
+            if pi < pj:
+                powers[i] = (sj, dj, pj)
+                powers[j] = (si, di, pi)
+
+
+    temporary_topology = topology
+    remove_links = []
+    remove_n = 0
+    while True:
+        for ls,ld,lp in powers:
+
+            temp_c = links[ls][ld]
+            links[ls][ld] = 0
+            links[ld][ls] = 0
+
+            if not is_connected(links, nodes_n):
[…]

### 2015-01-28 experiment/plot/exp1_link.py

@@ -1,6 +1,6 @@
 import matplotlib.pyplot as plt
 
-topology_x_range = {'abilene':5, 'geant':12, 'cernet2':4}
+topology_x_range = {'abilene':5, 'geant':10, 'cernet2':4}
 topology_line_type = {'abilene':'o', 'geant':'s', 'cernet2':'^'}
 color_type = {'base':'r--', 'new':'b-'}
 remove_type = {'base':'AC', 'new':'ERLU'}
@@ -8,7 +8,8 @@ result_file_template = "result-compare-%s-1.5"
 
 line_list = []
 label_list = []
-for t in ['abilene', 'geant', 'cernet2']:
+#for t in ['abilene', 'geant', 'cernet2']:
+for t in ['geant']:
     f = open(result_file_template % t)
     line = f.readline()
 
@@ -39,7 +40,7 @@ plt.xlabel('Remove Links')
 plt.ylabel('oblivious performance ratio')
 plt.legend(line_list, label_list, loc=2)
 
-#plt.show()
-plt.savefig('exp1_link.png', bbox_inches='tight')
+plt.show()
+#plt.savefig('exp1_link.png', bbox_inches='tight')
 
 

### 2015-01-28 experiment/plot/exp1_power.py

@@ -1,14 +1,20 @@
+from matplotlib.backends.backend_pdf import PdfPages
 import matplotlib.pyplot as plt
+import matplotlib.ticker as tic
 
-topology_x_range = {'abilene':5, 'geant':12, 'cernet2':4}
+fig1, ax1 = plt.subplots()
+
+topology_x_range = {'abilene':5, 'geant':13, 'cernet2':4}
 remove_links = {'abilene':4, 'geant':15, 'cernet2':3}
-topology_line_type = {'abilene':'o', 'geant':'s', 'cernet2':'^'}
-color_type = {'base':'r--', 'new':'b-'}
-remove_type = {'base':'AC', 'new':'ERLU'}
-result_file_template = "result-compare-%s-1.5"
+w_line_type = {'1.5':'o', '2.0':'s', '2.5':'^'}
+color_type = {'base':'r-', 'new':'b-'}
+remove_type = {'base':'TMP', 'new':'ERLU'}
+result_file_template = "result-compare-%s-%s"
 topology_file_template = "../topology/connected/%s-connected-topology"
 remove_file_template = "../topology/remove/%s-remove-%d-links"
-remove_base_file_template = "../topology/remove/%s-remove-%d-links-base"
+remove_base_file_template = "../topology/remove/%s-remove-%d-links-power"
+
+y_lim = {'abilene':9, 'geant':200, 'cernet2':4}
 
 
 power_models = {155.0:60, 1240.0:100, 2480.0:140, 9920:174}
@@ -17,7 +23,9 @@ power_model = [60, 100, 140, 174]
 
 line_list = []
 label_list = []
-for t in ['abilene', 'geant', 'cernet2']:
+#for t in ['abilene', 'geant', 'cernet2']:
+t = 'geant'
+for w in ['1.5', '2.0']:
     # compute the total power of topology
     f = open(topology_file_template % t)
     line = f.readline()
@@ -103,7 +111,7 @@ for t in ['abilene', 'geant', 'cernet2']:
     print power_base_saving_ratio
 
 
-    f = open(result_file_template % t)
+    f = open(result_file_template % (t, w))
     line = f.readline()
 
     base = []
@@ -120,20 +128,29 @@ for t in ['abilene', 'geant', 'cernet2']:
 
     f.close()
 
[…]

### 2015-01-28 experiment/plot/exp2_sort.py

@@ -1,6 +1,10 @@
+from matplotlib.backends.backend_pdf import PdfPages
 import matplotlib.pyplot as plt
 
-result_file_template = "middle-compare-cernet2-1.5"
+fig1, ax1 = plt.subplots()
+
+t = 'abilene'
+result_file_template = "middle-compare-%s-1.5" % t
 count = 1000
 remove = 4
 
@@ -24,7 +28,7 @@ while line:
 f.close()
 
 line1 = None
-for i in range(2, remove):
+for i in range(0, remove):
     for j in range(count):
         for k in range(j, count):
             if (base[i][j] > base[i][k]):
@@ -34,7 +38,7 @@ for i in range(2, remove):
     line1, = plt.plot(x, base[i], 'r--')
 
 line2 = None
-for i in range(2, remove):
+for i in range(0, remove):
     for j in range(count):
         for k in range(j, count):
             if (new[i][j] > new[i][k]):
@@ -47,8 +51,12 @@ for i in range(2, remove):
 
 plt.xlabel('Random Traffic Matrix')
 plt.ylabel('Oblivious Performance Ratio')
-plt.legend([line1, line2], ['AC', 'ERLU'], loc=2)
+plt.legend([line1, line2], ['TMP', 'ERLU'], loc=2)
 
-#plt.show()
-plt.savefig('exp2_sort_cernet2.png', bbox_inches='tight')
+pp = PdfPages('exp2_sort_%s.pdf' % t)
+pp.savefig(fig1)
+pp.close()
+
+plt.show()
+#plt.savefig('exp2_sort_cernet2.png', bbox_inches='tight')
 

### 2015-01-29 paper.tex
update figure

@@
 \usepackage{cite}
+\usepackage{amsmath}
 
@@
 \subsection{Problem Formulation}
+We formulate our problem as following:
+
+\begin{equation}
+Minimize \max_{m \in M} \frac{U_{r,m,G^*}} {min_{r'} U_{r', m, G}}
+\end{equation}
+
+\begin{equation}
+    G^* = (V,E^*), E^* \subset E
+\end{equation}
+
+\begin{equation}
+    \begin{split}
+    \forall (\epsilon, \gamma) \in \{ (E, r'), (E^*, r)\} \\
+    \sum_{(i,j) \in \epsilon}f_{ab}(i,j)O_{(i,j)}^i - \sum_{(i,j) \in \epsilon}f_{ab}(i,j)I_{(i,j)}^i = \\
+    \left\{
+        \begin{array}{c}
+        1, i = b \\
+        -1, i = a \\
+        0, i \neq a,b \\
+        \end{array}
+    \right.
+    , \ \ \ \ a,b,i \in V, a \neq b, f_{ab}(i,j) \in \gamma
+    \end{split}
+\end{equation}
+
+\begin{equation}
+    \sum_{l \in E^*} p(l) / \sum_{l \in E} p(l) < 1 - \theta
+\end{equation}
+
+Eq. (6) is our target, which minimize the value of OPRE defined in \Rmnum{3}.B. Eq. (7) say $G^*$ be a sub-graph of $G$, which means remove/sleep
+some links from $G$, and keep vertices the same. Eq. (8) ensures the graph is connected and define the routing. In details, $O_{(i,j)}^i$ equal to
+1 if $i$ is the tail node of link $(i,j)$, and $I_(i,j)^i$ equal to 1 if $i$ is the head node of link $(i,j)$, this equation states the flow 
+conservation constraints. In the other hand, $f_{ab}(i,j)$ is specified by routing $\gamma$, if the graph is not connected it will be unavailable
+for some origin and destination pair. And from Eq. (8) we know that routing $r$ is corresponded with $G^*$, and $r'$ with $G$. We calculate the 
+power constraints in Eq. (9), it ensure that we can save more than $\theta$ energy consumption. The function $p$ which maps link to power consumption
+is proposed in \cite{networking:greente}.
 
@@
 We will take an example to explain how to choose the link to close in our algorithm.
-Three hostes include : A, B, C, three links are with repectively capacity of 3M, 4M and 2M. For simpleness, we suppose
-there are two TM : ${(A,B,2M), (A,C,1M)}$ and ${(A,B,1M), (A,C,1M)}$. For each traffic matrix, the optimal route is
-obvious, we will trace 2M from A to B across the lower link and trace the 1M from A to C across the upper one
+Three hostes include : a, b, c, three links are with repectively capacity of 3M, 4M and 2M. For simpleness, we suppose
+there are two TM : ${(a,b,2M), (a,c,1M)}$ and ${(a,b,1M), (a,c,1M)}$. For each traffic matrix, the optimal route is
+obvious, we will trace 2M from a to b across the lower link and trace the 1M from a to c across the upper one
 for the first traffic matrix, whose maximum link utilization is 0.5. we will trace all the traffic acorss the
@@
 \includegraphics[width=8cm]{3-nodes-example}
-\caption{Model Example}
+\caption{Model Example, TM \Rmnum{1} : (a, b, 2M), (a, c, 1M); TM \Rmnum{2} : (a, b, 1M), (a, c, 1M).}
 \label{label}
@@
 \vspace*{0.1in}
-\subfloat{\includegraphics[width=6cm]{exp2_sort_cernet2}}
+\subfloat{\includegraphics[width=6cm]{opr_with_power_abilene}}
+\subfloat{\includegraphics[width=6cm]{opr_with_power_geant}}
+\subfloat{\includegraphics[width=6cm]{opr_with_power_cernet2}}
+\caption{OPRE versus Power Saving: (1). Abilene, (b). Geant, (c). Cernet2}
+\vspace*{0.1in}
+\end{figure*}
+
+\begin{figure*}[!t]
+\centering
+\vspace*{0.1in}
 \subfloat{\includegraphics[width=6cm]{exp2_sort_abilene}}
 \subfloat{\includegraphics[width=6cm]{exp2_sort_geant}}
-\caption{Sort: (a). Abilene (b).Geant}
+\subfloat{\includegraphics[width=6cm]{exp2_sort_cernet2}}
+\caption{OPRE versus TMs: (a). Abilene, (b). Geant, (c). Cernet2}
 \vspace*{0.1in}
@@
 Then we generate random traffic matrix with Gravity Model \cite{networking:gravity}, which assume that the traffic demand between nodes is proportional
-to their combined capacity of connecting links. To extrapolate a complete TM, we take an attribute $w$ to scale the traffic range from $1/w$ to $w$
+to their combined capacity of connecting links. To extrapolate a complete TM, we take an attribute margin $w$ to scale the traffic range from $1/w$ to $w$
 base on the basic traffic demand. Particularly, when the $w$ limit extremity, we say the traffic matrix is really arbitrary, and our 
@@
 \vspace*{0.1in}
-\subfloat{\includegraphics[width=6cm]{opr_with_power_abilene}}
-\subfloat{\includegraphics[width=6cm]{opr_with_power_geant}}
-\subfloat{\includegraphics[width=6cm]{opr_with_power_cernet2}}
-\caption{OPRE with Power Saving}
-\vspace*{0.1in}
-\end{figure*}
-
-\begin{figure*}[!t]
-\centering
-\vspace*{0.1in}
+\subfloat{\includegraphics[width=6cm]{exp4_path_abilene}}
 \subfloat{\includegraphics[width=6cm]{exp4_path_geant}}
-\subfloat{\includegraphics[width=6cm]{exp4_path_abilene}}
 \subfloat{\includegraphics[width=6cm]{exp4_path_cernet2}}
-\caption{Sort: (a). Abilene (b).Geant}
+\caption{Path Stretching: (a). Abilene, (b). Geant, (c). Cernet2}
 \vspace*{0.1in}
@@
 \subsection{OPRE versus Power Saving}
-In Figure 4 (a), we see that the value of OPRE is at least 1 even in the origin topology, particularly in Geant the value is 1.24,
-it means the robust routing always not be the optimal for all TMs even no links removed from topology. It is reasonable because
-our robust routing is used for a range of traffic rather than a specific TM.
+In Figure 3, we see that the value of OPRE is at least 1 for all topologies even no links removed, particularly in Geant the value is 1.24,
+it means the robust routing always not be the optimal for all TMs. It is reasonable because our robust routing is used for a range of traffic 
+rather than a specific TM.
 
 When we switch off links, the topology lose connectivity and some routing paths will be failed, traffic on those paths will be 
-adjusted to others, which result in the value of OPRE increased. We take margin as 1.5 and observe this phenomena from Figure 4 (a).
-And all the curves can split in two phases according to the growth speed of OPRE, for example in Abilene, the OPRE rise geantly 
-before 4 links are removed, and rise rapidly since then. It is revelatory for implementing our algorithm in real life, controlling
-the number of removed links less than the turning point is more efficient. The another reason for avoiding removing too much links
-is that the robust routing will be less `robust' or induce network congestions easily, because there is only one path between two
-vertices in the minimum connected topology.
+adjusted to others, which result in the value of OPRE increased. We take margin from 1.5 to 3.5 and observe this phenomena from Figure.
+Pay attention that we scale the y-axis as logarithm for comparing TMP and ERLU in one figure. Intuitively, we can see ERLU is always
+better than TMP whatever margin or power saving target is, because ERLU consider much more than TMP, such as capacity and robust traffic 
+flows. Another information from Figure 4 is that, we should carefully set the value of power saving for avoiding removing too much
+links, which result in the OPRE increases rapidly, induce network congestions easily and make the robust routing be less `robust'.
 
-On the other hand, we concern more about how is the OPRE varifying when achived specific power saving target. Obviously, the more 
-links we removed, the more power we saved, but how to quantify the power of one link is difficult. Green TE \cite{networking:greente} 
-proposed a simple power model, which can be represented in Table \Rmnum{2}. In which, the total energy of topology is dominant by line
-cards of routers or switches, when saying switch off the links we mean put down the according line cards.
+we concern more about how is the OPRE varifying when achived specific power saving target. Obviously, the more links we removed, 
+the more power we saved, but how to quantify the power of one link is difficult. Green TE proposed a simple power model \cite{networking:greente}, 
+which can be represented in Table \Rmnum{2}. In which, the total energy of topology is dominant by line cards of routers or switches, 
+when saying switch off the links we mean put down the according line cards.
 
@@
 We compute the power saving ratio as the total power of the removed links over the total power of all the links. 
-In Figure 4 (b), it shows we can save 19\% energy only with an OPRE of 1.34 in Abilene topology, and in Geant and Cernet2, 
-the OPRE is little higher. We also can see that two ways for removing links perform differently in different topologies,
-or perform differently in different phases of the same topology. For example, ERLU is better than AC in Abilene and AC is
-better in Cernet2, particularly in Geant, ERLU peform better at begining time.
+In Figure 3 (a), it shows we can save 19\% energy only with an OPRE of 1.30 in Abilene topology, and in Geant and Cernet2, 
+the OPRE is little higher. Curves present some scalariform, it means that in some range of power saving, the OPRE rise slowly,
+and in the end of range, the energy conservation is efficient.
+
+\subsection{OPRE versus Margin}
+We take the margin $w$ as one of the input for computing robust routing, and margin identify a range of TMs the routing is 
+robust for. Once the $w$ limit extremely, our robust routing is said without knowledge of traffic matrix. Figure 3 shows the 
+OPRE increases little as $w$ increases, particularly in Geant, the difference almost can not be observed. It is obvious because
+when the $w$ is greater, the traffic matrix is random in more wider range, and our OPRE may achieve worse case with more probability.
 
 \subsection{OPRE versus TMs}
-To simulate the worst case, we generate 1000 traffic matrices for every topoloy with margin attribute $w$. Figure 5 shows
+To simulate the worst case, we generate 1000 traffic matrices for every topoloy with margin attribute $w$. Figure 4 shows
 the OPRE distribution in the process of experiment. For avoiding mess result from too many lines, we just show the first 
@@
 
-In Figure 3 (a), we can only observe five lines because there are two overlapping lines, which means that when removing 
+In Figure 4 (a), we can only observe five lines because there are two overlapping lines, which means that when removing 
 links the worst case for the robust routing does not change. Maybe the random traffic matrices is not bad enough, or the 
-removed link really do not affect the MLUR. And from Figure 3, we see that the OPRE is not always be achived for most
+removed link really do not affect the MLUR. And from Figure 4, we see that the OPRE is not always be achived for most
 traffic matrices, the common value is much less than OPRE.
 
-Comparing two ways in first phase of REAR algorithm, in Abilene and Geant ERLU is always better than AC, furthermore in
-some time, although more links are removed from topology the result of ERLU is still better. For most TMs, after switching 
-off three links the OPRE is 1.2 and 1.6 respectively in Abilene and Geant. However, the ERLU is less optimal than ERLU in 
-Cernet2, when we investigate the Cernet2 topology and find the crucial reason is the link between vertex Hangzhou and 
-vertex Xiamen, which is least important in the meaning of algebraic connectivity rather ERLU.
-
-\subsection{OPRE versus Margin}
-We take the margin $w$ as one of the input for computing robust routing, and margin identify a range of TMs the routing is 
-robust for. Once the $w$ limit extremely, our robust routing is said without knowledge of traffic matrix. Figure 5 shows the 
-OPRE increased as $w$ increased. It is obvious because when the $w$ is greater, the traffic matrix is random in more wider
-range, and our OPRE may achieve worse case with more probability.
-
-And we find when the margin increases from 1.5 to 2.0, the OPER increases much less, particularly in the begining of removing,
-the difference almost can not be observed. It is a good phenomena for us, the variation of margin, i.e. the range of traffic
-matrices affect little on the OPRE when the energy conservation is limited within 12\% in Geant.
+Comparing TMP and ERLU, the conclusion is similar to Figure 3, the latter is always better than the former. Even in some 
+time, ERLU obtains more power saving but with a lower OPRE.
 
@@
 
-We can observe that, ERLU is always shorter than AC, althoungh in Geant, the worst case is 36\% than the shortest path when margin 
+We can observe that, ERLU is always shorter than TMP, althoungh in Geant, the worst case is 36\% than the shortest path when margin 
 equal to 1.5. And in the first removed links, the path stretching ratio is near 20\%.
-
-\begin{figure}
-\centering
-\vspace*{0.1in}
-\includegraphics[width=8cm,height=4cm]{exp3_w}
-\caption{OPRE with w relationship}
-\vspace*{0.1in}
-\end{figure}
 

### 2015-01-29 experiment/cplex/compare.py

@@ -23,7 +23,7 @@ solution_default = "global_opt_cplex_output.sol"
 files = 1000
 
 loop = 1
-w = 2.5
+w = 4.0
 
 remove_links_n = {'abilene':5, 'geant':16, 'cernet2':4}
 

### 2015-01-29 experiment/cplex/len_path.py

@@ -1,17 +1,20 @@
+from matplotlib.backends.backend_pdf import PdfPages
 import matplotlib.pyplot as plt
 
+fig1, ax1 = plt.subplots()
+
 topology_x_range = {'abilene':5, 'geant':16, 'cernet2':4}
-topology_line_type = {'abilene':'o', 'geant':'s', 'cernet2':'^'}
+topology_line_type = {'1.5':'o', '2.5':'s', '3.5':'^'}
 color_type = {'base':'r--', 'new':'b-'}
-remove_type = {'base':'AC', 'new':'ERLU'}
-result_file_template = "path_stretch_%s_%0.1f.txt"
+remove_type = {'base':'TMP', 'new':'ERLU'}
+result_file_template = "path_stretch_%s_%s.txt"
 
 line_list = []
 label_list = []
 #for t in ['geant']:
 #for t in ['abilene']:
-for t in ['cernet2']:
-    for w in [1.5, 2.0]:
+for t in ['geant']:
+    for w in ['1.5', '2.5', '3.5']:
         f = open(result_file_template % (t, w))
         line = f.readline()
 
@@ -36,20 +39,23 @@ for t in ['cernet2']:
 
         #l1, = plt.plot(x[:topology_x_range[t]], m_mine[:topology_x_range[t]], color_type['new']+topology_line_type[t])
         #l2, = plt.plot(x[:topology_x_range[t]], m_base[:topology_x_range[t]], color_type['base']+topology_line_type[t])
-        l1, = plt.plot(x[:topology_x_range[t]], a_mine[:topology_x_range[t]], color_type['new']+topology_line_type[t])
-        l2, = plt.plot(x[:topology_x_range[t]], a_base[:topology_x_range[t]], color_type['base']+topology_line_type[t])
+        l1, = plt.plot(x[:topology_x_range[t]], a_mine[:topology_x_range[t]], color_type['new']+topology_line_type[w])
+        l2, = plt.plot(x[:topology_x_range[t]], a_base[:topology_x_range[t]], color_type['base']+topology_line_type[w])
 
-        label_list.append(t + '-' + remove_type['base'])
-        label_list.append(t + '-' + remove_type['new'])
+        label_list.append(w + '-' + remove_type['base'])
+        label_list.append(w + '-' + remove_type['new'])
         
         line_list.append(l1)
         line_list.append(l2)
 
[…]

### 2015-01-29 experiment/plot/exp1_power.py

@@ -6,7 +6,7 @@ fig1, ax1 = plt.subplots()
 
 topology_x_range = {'abilene':5, 'geant':13, 'cernet2':4}
 remove_links = {'abilene':4, 'geant':15, 'cernet2':3}
-w_line_type = {'1.5':'o', '2.0':'s', '2.5':'^'}
+w_line_type = {'1.5':'o', '2.5':'s', '3.5':'^'}
 color_type = {'base':'r-', 'new':'b-'}
 remove_type = {'base':'TMP', 'new':'ERLU'}
 result_file_template = "result-compare-%s-%s"
@@ -25,7 +25,7 @@ line_list = []
 label_list = []
 #for t in ['abilene', 'geant', 'cernet2']:
 t = 'geant'
-for w in ['1.5', '2.0']:
+for w in ['1.5', '2.5', '3.5']:
     # compute the total power of topology
     f = open(topology_file_template % t)
     line = f.readline()
@@ -73,7 +73,7 @@ for w in ['1.5', '2.0']:
         elif topo[s,d] <= 9920.0:
             saving = saving + power_model[3]
         
-        power_saving_ratio.append(saving / total)
+        power_saving_ratio.append(saving / total * 100)
         removes[num] = [s,d]
         num = num + 1
 
@@ -102,7 +102,7 @@ for w in ['1.5', '2.0']:
         elif topo[s,d] <= 9920.0:
             saving = saving + power_model[3]
         
-        power_base_saving_ratio.append(saving / total)
+        power_base_saving_ratio.append(saving / total * 100)
         removes_base[num] = [s,d]
         num = num + 1
 
@@ -128,8 +128,8 @@ for w in ['1.5', '2.0']:
 
     f.close()
 
-    l1, = ax1.plot(power_saving_ratio[:topology_x_range[t]], base[:topology_x_range[t]], color_type['base']+w_line_type[w])
-    l2, = ax1.plot(power_base_saving_ratio[:topology_x_range[t]], new[:topology_x_range[t]], color_type['new']+w_line_type[w])
+    l1, = ax1.plot(power_base_saving_ratio[:topology_x_range[t]], base[:topology_x_range[t]], color_type['base']+w_line_type[w])
+    l2, = ax1.plot(power_saving_ratio[:topology_x_range[t]], new[:topology_x_range[t]], color_type['new']+w_line_type[w])
 
[…]

### 2015-01-29 experiment/plot/exp2_sort.py

@@ -3,7 +3,7 @@ import matplotlib.pyplot as plt
 
 fig1, ax1 = plt.subplots()
 
-t = 'abilene'
+t = 'cernet2'
 result_file_template = "middle-compare-%s-1.5" % t
 count = 1000
 remove = 4
@@ -13,7 +13,7 @@ line = f.readline();
 
 base = [([0] * count) for i in range(remove)]
 new = [([0] * count) for i in range(remove)]
-x = [i for i in range(count)]
+x = [i/10 for i in range(count)]
 while line:
     tokens = line.strip().split()
     r = int(tokens[0])
@@ -49,8 +49,8 @@ for i in range(0, remove):
 
 #plt.axis([0, 6, 0, 20])
 
-plt.xlabel('Random Traffic Matrix')
-plt.ylabel('Oblivious Performance Ratio')
+plt.xlabel('Random Traffic Matrix (%)', fontsize=22)
+plt.ylabel('Oblivious Performance Ratio', fontsize=22)
 plt.legend([line1, line2], ['TMP', 'ERLU'], loc=2)
 
 pp = PdfPages('exp2_sort_%s.pdf' % t)

### 2015-01-29 experiment/plot/exp3_w.py

@@ -1,8 +1,11 @@
+from matplotlib.backends.backend_pdf import PdfPages
 import matplotlib.pyplot as plt
+
+fig1, ax1 = plt.subplots()
 
 topology_x_range = {'abilene':5, 'geant':12, 'cernet2':4}
 remove_links = {'abilene':4, 'geant':15, 'cernet2':3}
-topology_line_type = {1.5:'o', 2.0:'s'}
+topology_line_type = {1.5:'o', 2.0:'s', 2.5:'^', 3.0:'o', 3.5:'s', 4.0:'^'}
 color_type = {'base':'r--', 'new':'b-'}
 remove_type = {'base':'AC', 'new':'ERLU'}
 result_file_template = "result-compare-%s-%0.1f"
@@ -103,7 +106,7 @@ for t in ['geant']:
     print power_base_saving_ratio
 
 
-    for w in [1.5, 2.0]:
+    for w in [1.5, 2.0, 2.5, 3.0, 3.5, 4.0]:
         f = open(result_file_template % (t, w))
         line = f.readline()
 
@@ -121,20 +124,23 @@ for t in ['geant']:
 
         f.close()
 
-        l1, = plt.plot(power_saving_ratio[:topology_x_range[t]], base[:topology_x_range[t]], color_type['base']+topology_line_type[w])
+        #l1, = plt.plot(power_saving_ratio[:topology_x_range[t]], base[:topology_x_range[t]], color_type['base']+topology_line_type[w])
         l2, = plt.plot(power_base_saving_ratio[:topology_x_range[t]], new[:topology_x_range[t]], color_type['new']+topology_line_type[w])
 
-        label_list.append(t + '-' + remove_type['base'] + '-%0.1f' % w)  
+        #label_list.append(t + '-' + remove_type['base'] + '-%0.1f' % w)  
         label_list.append(t + '-' + remove_type['new'] + '-%0.1f' % w)
         
-        line_list.append(l1)
+        #line_list.append(l1)
         line_list.append(l2)
 
 plt.xlabel('Power Saving')
 plt.ylabel('Oblivious Performance Ratio')
 plt.legend(line_list, label_list, loc=2)
 
-#plt.show()
-plt.savefig('exp3_w.png', bbox_inches='tight')
+pp = PdfPages('exp3_w.pdf')
+pp.savefig(fig1)
+pp.close()
+
+plt.show()
 
 

### 2015-01-29 paper.tex
modify algorithm and proof

@@
 \usepackage{amsmath}
+\usepackage{amsthm}
+
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}[theorem]{Lemma}
 
@@
 
-\begin{equation}
-Minimize \max_{m \in M} \frac{U_{r,m,G^*}} {min_{r'} U_{r', m, G}}
-\end{equation}
+\begin{center}
+Minimize \quad $P^*(\{r\},M,G)$
+\end{center}
 
-\begin{equation}
-    G^* = (V,E^*), E^* \subset E
-\end{equation}
+\begin{center}
+s.t. (1),\ (4)
+\end{center}
+
+\begin{center}
+    $\forall a,b,i \in V$: \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad 
+    \vspace{-0.3in}
+\end{center}
 
@@
     \begin{split}
-    \forall (\epsilon, \gamma) \in \{ (E, r'), (E^*, r)\} \\
-    \sum_{(i,j) \in \epsilon}f_{ab}(i,j)O_{(i,j)}^i - \sum_{(i,j) \in \epsilon}f_{ab}(i,j)I_{(i,j)}^i = \\
+    \sum_{j, s.t.(i,j) \in E}\hspace{-0.2in}f'_{ab}(i,j) - \hspace{-0.2in}\sum_{j, s.t.(j,i) \in E}\hspace{-0.2in}f'_{ab}(j,i) = 
     \left\{
         \begin{array}{c}
-        1, i = b \\
-        -1, i = a \\
-        0, i \neq a,b \\
+        \ \ 1, \ i = b \\
+        -1, \ i = a \\
+        \ \ \ \ \ 0, \ i \neq a,b \\
         \end{array}
     \right.
-    , \ \ \ \ a,b,i \in V, a \neq b, f_{ab}(i,j) \in \gamma
+    \end{split}
+\end{equation}
+
+\begin{center}
+    \vspace{0.1in}
+    $\forall a,b,i \in V$: \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad
+    \vspace{-0.3in}
+\end{center}
+
+\begin{equation}
+    \begin{split}
+    \sum_{j, s.t.(i,j) \in E^*}\hspace{-0.2in}f_{ab}(i,j) - \hspace{-0.3in}\sum_{j, s.t.(j,i) \in E^*}\hspace{-0.2in}f_{ab}(j,i) = 
+    \left\{
+        \begin{array}{c}
+        \ \ 1, \ i = b \\
+        -1, \ i = a \\
+        \ \ \ \ \ 0, \ i \neq a,b \\
+        \end{array}
+    \right.
     \end{split}
@@
     \sum_{l \in E^*} p(l) / \sum_{l \in E} p(l) < 1 - \theta
+\end{equation}
+
+\begin{equation}
+    0 \leq f_{ab}(i,j),f'_{ab}(i,j) \leq 1
 \end{equation}
@@
 In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links 
-should be put to sleep from the origin topology based on extended robust link utilization or algebraic connectivity, 
-then compute the robust routing by demand-oblivious routing algorithm. There are two metrics
-for selecting removed links, our two-phase algorithm is flexible because we can replace the metric with whatever
-metric.
-
-\subsection{Algebraic Connectivity}
-Network topology is represented by $G = (V, E)$ as mentioned in Model section, where $V$ is the set of vertices
-and $E$ is the set of links. We say $A(G)$ is the Adjacency Matrix of graph $G$, that include information for which
-vertices of the graph are adjacent to which other vertices. $A(G)$ is a $N \times N$ matrix, where
-$N = |V|$ and non-diagonal entry $a_{ij}$ equal to the number of edges from vertex $i$ to vertex $j$, in this paper,
-$a_{ij}$ always be 1 if $(i,j) \in E$ otherwise 0. And we stipulate the diagonal element $a_{ii}$ be 0.
-
-We say $D(G)$ is the Degree Matrix of graph $G$, which is a diagonal matrix and diagonal entry $d_{ii}$ denote 
-the degree of node $i$. It is obvious that there is $d_{ii} == \sum_{j} a_{ij}$.
-
-Then we define Laplacian Matrix $L(G)$ of graph $G$ as the difference between Degree Matrix and Adjacency Matrix :
-\begin{equation}
-	L(G) = D(G) - A(G)
-\end{equation}
-where $D(G)$ is the Degree Matrix and $A(G)$ is the Adjacency Matrix.
-
-In the mathematical field of graph theory, the number of eigenvalues equal to 0 is the number of connected 
-componements of $G$, so the smallest eigenvalue always be 0 in arbitrary graph . And we call the second smallest one as
-algebraic connectivity, which is greater than 0 if and only if graph $G$ is connected. Further more,  
-it measures the connectivity and stability of graph, the greater of the value, the more connective of graph;
-and it is a metric of average distance between any two vertices of graph $G$. We call the algebraic connectivity as
-$\lambda_2(G)$.
-
-Topology always have different algebraic connectivity values, it is clear that when one link is added or 
-removed from the graph, the algebraic connectivity value changes accordingly. And we say the changed value
-is the impact of this link on the graph. Supposed we sleep link $l$ from graph $G$, new graph is described as $G^*$, 
-we defined the impact of link $l$ as :
-\begin{equation}
-	\Delta_l = \lambda_2(G) - \lambda_2(G^*)
-\end{equation}
-where $\lambda_2(G)$ and $\lambda_2(G^*)$ is algebraic connectivity of $G$ and $G^*$ respectly.
-
-Clearly, $\Delta_l$ is always greater than 0, because graph will always lose connectivity when link is removed.
-Further more, some link will play a more important role in the connectivity of graph, such as the backbone link 
-of network topology. And we say a link $l$ affect more if $\Delta_l$ is greater.
+should be put to sleep from the origin topology based on extended robust link utilization (ERLU), 
+then compute the robust routing based on demand-oblivious routing algorithm.
 
 \subsection{Extended Robust Link Utilization}
-The demand-oblivious routing is not always the best one for 
-specific $TM$, but good enough for a range of $TM$. we mentioned the definition of link utilization above when 
-demand and routing are determined, as demand become oblivious, the definition is also not suitable. So we define
-a notation named extended robust link utilization (ERLU) replace the normal link utilization like :
+The demand-oblivious routing is not always the best one for specific $TM$, but good enough for a range of $TM$. 
+we mentioned the definition of link utilization above when demand and routing are determined, as demand become 
+oblivious, the definition is also not suitable. So we define a notation named extended robust link utilization (ERLU) 
+replace the normal link utilization like :
+
 \begin{equation}
@@
 ERLU is also more important than others in a sense. Although there is no demand here, we mean
-there is more probability that this link have greater link utilization when specific demand come. Similarly, we define 
-the impact of link $l$ as :
-\begin{equation}
-    \Delta_l = u^e_{l}
-\end{equation}
-
-And there is the same conclusion that a link $l$ affect more if $\Delta_l$ is greater.
+there is more probability that this link have greater link utilization when specific demand come.
 
 \subsection{Algorithm Phase One}
-REAR sleep as many links as possible without losing much connectivity or transportation of graph for different metrics. 
-Originly,  we should calculate impact of all the links and sleep the lowest one from the graph, then repeat calculate and remove
+REAR sleep as many links as possible without losing connectivity of graph. 
+Originly,  we should calculate ERLU of all the links and sleep the lowest one from the graph, then repeat calculate and remove
 process until arrive some specific threhold. Obviously, it is NP-Hard, following is a heuristic algorithm.
 
-For the origin graph, we calculate the impact of every link as $\Delta_{l_i}$ , and then sort these values
+For the origin graph, we calculate the ERLU of every link, and then sort these values
 from small to big, output ordered list denoted as $\Gamma$: 
@@
 \end{equation}
-where $\Delta_{l_i} < \Delta_{l_j}$.
+where $u^e_{l_i} < u^e_{l_j}$.
 
-Pay attention we only compute the link impact once at the begining of algorihtm, and the ordered list $\Gamma$ show 
+Pay attention we only compute the ERLU once at the begining of algorihtm, and the ordered list $\Gamma$ show 
 the order of `importance' among links in the graph.
 
-Now we begin selecting which links should be sleep.
+Now we begin selecting which link should be sleep.
 We denote the set of the sleeping links as $S$, and the output of this phase is final graph $G^* = (V, E-S)$. We set 
@@
 remove this link from the graph to check if the graph is still connected and the energy conservation have not arrive the threshold.
-If so, we select this one then go next iteration.
+If so, we select it then go next iteration.
 Otherwise choose the next link from $\Gamma$ for trying to remove. Algorithm
@@
 
-So before going ahead our algorithm, there is another thing we should done, how to measure the power of graph.
+But before going ahead our algorithm, there is another thing we should care, how to measure the power of graph.
 We simple take an power model from \cite{networking:greente} showed in Table \Rmnum{2}, and defined the difference of power consumption 
@@
 \begin{equation}
-	diff_p = \frac{\rho(G_{S, l}^o)} {\rho(G^o)} * 100
+	diff_p = 1 - \theta = \frac{\rho(G_{S, l}^o)} {\rho(G^o)} * 100
 \end{equation}
@@
 If we set $diff_p$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
-iteration, the power consumption should never lower than the 90\% of origin one. In another words, the output 
-of this phase protect as much connectivity and transportation as possible. Following is our implementation:
+iteration, the power consumption should never lower than the 90\% of origin one. Following is our implementation:
 
@@
 $\:\:$1:\ \textbf{for} {each link $l$ in $E$}\\
-$\:\:$2:\quad\ $G^* \leftarrow G(V, E-\{l\})$;\\
-$\:\:$3:\quad\ $\Gamma[l] \leftarrow \Delta_l \leftarrow \lambda_2(G) - \lambda_2(G^*)$;\\
-$\:\:$4:\ Resort $\Gamma$ in increasing order based on $\Delta_l$;\\
-$\:\:$5:\ $S \leftarrow \emptyset$, $goon \leftarrow true$;\\
-$\:\:$6:\ \textbf{while} {$goon$}\\
-$\:\:$7:\quad\  $goon \leftarrow false$;\\
-$\:\:$8:\quad\ \textbf{for} {each link $l$ in $\Gamma - S$}\\
-$\:\:$9:\quad\ \quad\ \textbf{if} $G_{S,l}$ is connected and $\rho(G_{S,l})/\rho(G)>threhold$\\
-$\:\:$10:\quad\ \quad\ \quad\ $S \leftarrow S \cup \{l\}$;\\
-$\:\:$11:\quad\ \quad\ \quad\ $goon \leftarrow true$;\\
-$\:\:$12:\quad\ \quad\ \quad\ \textbf{break};\\
-$\:\:$13:\ \textbf{return} $S, G(V, E-S)$;\\
+$\:\:$2:\quad\ $\Gamma[l] \leftarrow u^e_l$;\\
+$\:\:$3:\ Resort $\Gamma$ in increasing order based on $u^e_l$;\\
+$\:\:$4:\ $S \leftarrow \emptyset$, $goon \leftarrow true$;\\
+$\:\:$5:\ \textbf{while} {$goon$}\\
+$\:\:$6:\quad\  $goon \leftarrow false$;\\
+$\:\:$7:\quad\ \textbf{for} {each link $l$ in $\Gamma - S$}\\
+$\:\:$8:\quad\ \quad\ \textbf{if} $G_{S,l}$ is connected and $\rho(G_{S,l})/\rho(G)>threhold$\\
+$\:\:$9:\quad\ \quad\ \quad\ $S \leftarrow S \cup \{l\}$;\\
+$\:\:$10:\quad\ \quad\ \quad\ $goon \leftarrow true$;\\
+$\:\:$11:\quad\ \quad\ \quad\ \textbf{break};\\
+$\:\:$12:\ \textbf{return} $S, G(V, E-S)$;\\
 \hline
@@
 \subsection{Algorihtm Phase Two}
-Once we get the output network topology from the first phase based on either metric, it is time to compute
+Once we get the output network topology from the first phase, it is time to compute
 the robust routing. On one hand, computation process may cost too much time if we directly calculate the robust routing in 
@@
 \section{Samples and Proof}
-For showing obilious performance ratio with energy constraint really make a difference in the switching off link 
-process, we will explain it in two simple topologies, cliques and cycles. On the other hand, we also say that
-there will be an upper bound for obilious performance ratio with energy constraint, and get the bound according
-to the topology. For simpleness, we refer the energy constraint to the quantity of removed links.
+For explaining OPRE clearly, we will show it in two simple topologies, Cliques and Cycles. With a specific power saving 
+threshold, some links will be removed from the topology then robust routing will be computed. Taking two extreme examples from 
+origin topology, one with no links removed, i.e the topology itself, and the other with no more link can be removed, i.e. 
+spanning tree of the topology. And the corresponding thresholds are 0 and maximum value can be achieved. We prove the upper 
+bound of OPRE for cycles and cliques in these two situations, and we say when taking a threshold between 0 and maximum value,
+the corresponding OPRE is also bounded.
 
@@
 
-\subsection{Circles}
-Cycles topology connect all the nodes by a cycle, any node in which has two links joined. Figure 1 show the six
-nodes cycles topology, let nodes named from $A$ to $F$ and links named from $a$ to $f$ in the figure.
-Now suppose a traffic in the topology then calculate the optimal routing for it,
-let $D_a$ and $C_a$ be the demand and capacity of the link, without loss of generality, we say the link $d$ is the 
-bottleneck, i.e. with the maximum link utilization. There are two solutions for us, switching off the link $d$,
-or the other link, such as link $f$.
+\begin{lemma}
+The upper bound of OPR for $C_n$ (the cycle on n vertices) and $K_n$ (the complete graph on n vertices) is 2-2/n.
+\end{lemma}
 
-For case one, when we switch off the link $d$, the origin traffic pass the link will be redirected. The worst situation
+Lemma 1 is proved in \cite{networking:oblivious} and it assumes all the links the same. We extend this lemma on $C_n$ and
+$K_n$ with different capacity of links. In the latter proof, we use the extended $C_n$ and $K_n$ definition without specified.
+
+\begin{theorem}
+The upper bound of OPRE for spanning tree of $C_n$ is 1+$Max_{cap}$/$Min_{cap}$.
+\end{theorem}
+
+\begin{proof}
+Cycles topology connect all the nodes by a cycle, any node in which has two links joined. Figure 2.(a) show the six
+nodes cycles topology, let nodes named from $A$ to $F$ and links named from $a$ to $f$. Now suppose a traffic in the 
+topology then calculate the optimal routing for it, let $D_a$ and $C_a$ be the demand and capacity of the link $a$, 
+without loss of generality, we say the link $d$ is the bottleneck, namely link with MLUR.
+
+The spanning tree of $C_n$ is generated by removing one link from origin topology. There are two ways to generate 
+the spanning tree, remove the link $d$ or remove the other link such as $f$.
+
+For case \Rmnum{1}, when we switch off the link $d$, the origin traffic pass the link will be redirected. The worst situation
 is that all the traffic on the link $d$ will be put to the other path : $D \leftarrow C \leftarrow B \leftarrow A \leftarrow 
-F \leftarrow E$. After traffic redirection, the bottleneck link may become the link $e$, according to our definition of
-extended robust link utilization:
+F \leftarrow E$. After traffic redirection, the bottleneck link may become the link $e$, we have OPRE in this routing situation:
 
@@
 
-so we have the extended robust link utilization in case one :
+so we have OPRE in case \Rmnum{1} :
 
@@
 
-For case two, similar to case one, all the traffic will be redirected on the other path between $F$ and $A$. There are two 
-sub cases after traffic redirection, the link $D$ is still the bottleneck or the link $E$ become the new bottleneck. In sub 
-case one:
+For case \Rmnum{2}, similar to case \Rmnum{1}, all the traffic will be redirected on the other path between $F$ and $A$. There are two 
+sub cases after traffic redirection, the link $D$ is still the bottleneck or the link $E$ become the new bottleneck. In case \Rmnum{2}.\Rmnum{1},
+we have OPRE:
 
@@
 
-Because the link utilization of link $d$ is the maximum one in origin topology, we have as:
+Because the link utilization of link $d$ is the maximum one in origin topology, we have:
 
@@
 
-So we get the extended robust link utilization in this case :
+So we get OPRE in case \Rmnum{2}.\Rmnum{1}:
 \begin{equation}
@@
 
-In sub case two, we get the new extended robust link utilization in link $E$:
+In case \Rmnum{2}.\Rmnum{2}, we get OPRE:
 
@@
 
-So we get the extended robust link utilization:
+So we obtain OPRE:
 
@@
 \begin{equation}
-    Max\{1 + \frac{C_d}{C_e}, 1 + \frac{C_d}{C_f}, 1 + \frac{C_f}{C_e}\}
+    Max\{1 + \frac{C_d}{C_e}, 1 + \frac{C_d}{C_f}, 1 + \frac{C_f}{C_e}\} < 1 + \frac{Max_{cap}}{Min_{cap}}
 \end{equation}
 
-Particularly, if all the links have the same capacity, the upper bound equal to 2 when switch off one link. Otherwise, the 
+Particularly, if all the links have the same capacity, the upper bound equal to 2 for the spanning tree. Otherwise, the 
 upper bound only dependent to the greatest ratio of link capacity.
 
-\subsection{Cliques}
-In clique topology, all the nodes connect to each other, it means that situation become more difficult because the traffic
-can be adjusted to multi paths rather than one path in circle. And we will see that splitting traffic on multi paths is 
-always better than put all the traffic to one, so if we get the upper bound of the worst case, it must be the upper bound
-of other case. Similarly to circle topology, we say the link $a$ is the bottleneck, and we will switch off it or other link
-like $b$.
+\end{proof}
 
-In case one, after we switch off link $a$, the new bottleneck link must be the affected link, the link contains the origin 
+\begin{theorem}
+The upper bound of OPRE for $C_n$ is 1+${Max_{cap}}$/${Min_{cap}}$.
+\end{theorem}
+
+\begin{proof}
+The robust routing which will not trace demand on one link must be less optimal than the routing can trace demand on any link,
+and obviously the former routing is one of the routing on the spanning tree of $C_n$. So the bound of Theorem 2 is also the 
+bound of Theorem 3.
+
+Particularly, If the links of $C_n$ have the same capacity, OPRE will reduce to OPR. According to Lemma 1, we have the inequality:
+
+\begin{equation}
+OPRE = OPR < 2 - \frac{2}{n} < 1 + \frac{Max_{cap}}{Min_{cap}} = 2
+\end{equation}
+
+\end{proof}
+
+\begin{theorem}
+The upper bound of OPRE for $K_n$ is 1+${Max_{cap}}$/${Min_{cap}}$.
+\end{theorem}
+
+\begin{proof}
+Similar to the proof of Theorem 3, we say the robust routing which will not trace demand on one link must be less optimal than
+the real optimal robust routing. And it is one routing of topology which remove one link from origin topology $K_n$. Without
+loss of generality, we say the link $a$ is the bottleneck, and we will switch off it or other link like $b$, then consider
+the OPRE when adjust the demand to other link.
+
+In case \Rmnum{1}, after we switch off link $a$, the new bottleneck link must be the affected link, the link contains the origin 
 traffic on link $a$. Otherwise if the link $b$ is the bottleneck, but we adjust the traffic on other links, it means that
 we can do the same thing in the origin topology, and the bottleneck become link $b$ rather than $a$. It is conflict with our
-assumption. So we have the extended robust link utilization as :
+assumption. So we have the OPRE as :
 
@@
 
-In case two, the bottleneck may still be link $a$ or the new link $c$. If it is link $a$, and no new traffic across it,
-the extended robust link utilization equal to 1 obiliously. Or we adjust the new traffic $D_b$ on it, we can get the
-extended robust link utilization:
+In case \Rmnum{2}, the bottleneck may still be link $a$ or the new link $c$. If it is link $a$, and no new traffic across it,
+the OPRE equal to 1 obiliously. Or we adjust the new traffic $D_b$ on it, we can get the OPRE:
 
@@
 
-If the bottleneck become new link $c$, similar to our proof of circle topology, we can get extended robust link utilization:
+If the bottleneck become new link $c$, similar to our proof of circle topology, we can get OPRE:
 \begin{equation}
@@
 
-So we obtain the same conclusion as circle topology, the extended robust link utilization must be :
+So we obtain the same conclusion as circle topology, the OPRE must be :
 
 \begin{equation}
-    Max\{1 + \frac{C_a}{C_b}, 1 + \frac{C_b}{C_a}, 1 + \frac{C_b}{C_c}\}
+    Max\{1 + \frac{C_a}{C_b}, 1 + \frac{C_b}{C_a}, 1 + \frac{C_b}{C_c}\} = 1 + \frac{Max_{cap}}{Min_{cap}}
 \end{equation}
 
-\subsection{Other Topology}
-We can also see that, when we switch off different link, it really matters the performance which dependent on not only the 
-demand or traffic, but also the capacity of links. Particularly, the upper bound is just related with the capacity of links.
-And from our proof process, there is no special limitation for specific topology, so we can get the similar conclusion 
-on other topology.
+When the links of $K_n$ is the same, Theorem 4 will reduce to Lemma 1. The upper bound is bounded.
+\end{proof}
+
+\begin{theorem}
+The upper bound of OPRE for spanning tree of $K_n$ is $\frac{n^2}{2} Max_{cap}/Min_{cap}$.
+\end{theorem}
+
+\begin{proof}
+Every link in the spanning tree will split the graph to two parts, the flow between two parts must need across this link,
+Without loss of generality, let $l_{da}$ be the link with maximum link utilization. And let $l_{be}$ be the bottleneck link 
+in the optimal routing for origin topology. So we have OPRE:
+
+\begin{equation}
+    \frac{\frac{\sum_{i,j \in V} D_{ij}}{C_{da}}}{\frac{D_{be}}{C_{be}}} = \sum_{i,j \in V} \frac{D_{ij}}{D_{be}} \frac{C_{be}}{C_{da}} 
+\end{equation}
+
+Because the $l_{be}$ is the bottleneck link, we have:
+
+\begin{equation}
+    \frac{D_{ij}}{C_{ij}} < \frac{D_{be}}{C_{be}}
+\end{equation}
+
+\begin{equation}
+    \frac{D_{ij}}{D_{be}} < \frac{C_{ij}}{C_{be}}
+\end{equation}
+
+So we have OPRE:
+
+\begin{equation}
+    \sum_{i,j \in V} \frac{D_{ij}}{D_{be}} \frac{C_{be}}{C_{da}} < \sum_{i,j \in V} \frac{C_{ij}}{C_{be}}
+\end{equation}
+
+And we know that, the flow between two parts of topology must less than $\frac{n^2}{2}$, so OPRE must lower than:
+
+\begin{equation}
+    \sum_{i,j \in V} \frac{C_{ij}}{C_{be}} < \frac{n^2}{2} \frac{Max_{cap}}{Min_{cap}}
+\end{equation}
+
+\end{proof}
 
@@
 adjusted to others, which result in the value of OPRE increased. We take margin from 1.5 to 3.5 and observe this phenomena from Figure.
-Pay attention that we scale the y-axis as logarithm for comparing TMP and ERLU in one figure. Intuitively, we can see ERLU is always
-better than TMP whatever margin or power saving target is, because ERLU consider much more than TMP, such as capacity and robust traffic 
+Pay attention that we scale the y-axis as logarithm for comparing DMP and ERLU in one figure. Intuitively, we can see ERLU is always
+better than DMP whatever margin or power saving target is, because ERLU consider much more than DMP, such as capacity and robust traffic 
 flows. Another information from Figure 4 is that, we should carefully set the value of power saving for avoiding removing too much
@@
 
-Comparing TMP and ERLU, the conclusion is similar to Figure 3, the latter is always better than the former. Even in some 
+Comparing DMP and ERLU, the conclusion is similar to Figure 3, the latter is always better than the former. Even in some 
 time, ERLU obtains more power saving but with a lower OPRE.
@@
 
-We can observe that, ERLU is always shorter than TMP, althoungh in Geant, the worst case is 36\% than the shortest path when margin 
+We can observe that, ERLU is always shorter than DMP, althoungh in Geant, the worst case is 36\% than the shortest path when margin 
 equal to 1.5. And in the first removed links, the path stretching ratio is near 20\%.
@@
 ACM, 2002
+
+\bibitem{networking:dmp}
+A.P. Bianzino, L. Chiaraviglio, M. Mellia, Distributed algorithms for green IP networks, in: IEEE INFOCOM Workshop on Green Networking and Smart Grid, 2012
+
 \end{thebibliography}

### 2015-01-29 experiment/cplex/len_path.py

@@ -6,7 +6,7 @@ fig1, ax1 = plt.subplots()
 topology_x_range = {'abilene':5, 'geant':16, 'cernet2':4}
 topology_line_type = {'1.5':'o', '2.5':'s', '3.5':'^'}
 color_type = {'base':'r--', 'new':'b-'}
-remove_type = {'base':'TMP', 'new':'ERLU'}
+remove_type = {'base':'DMP', 'new':'ERLU'}
 result_file_template = "path_stretch_%s_%s.txt"
 
 line_list = []
@@ -39,8 +39,8 @@ for t in ['geant']:
 
         #l1, = plt.plot(x[:topology_x_range[t]], m_mine[:topology_x_range[t]], color_type['new']+topology_line_type[t])
         #l2, = plt.plot(x[:topology_x_range[t]], m_base[:topology_x_range[t]], color_type['base']+topology_line_type[t])
-        l1, = plt.plot(x[:topology_x_range[t]], a_mine[:topology_x_range[t]], color_type['new']+topology_line_type[w])
-        l2, = plt.plot(x[:topology_x_range[t]], a_base[:topology_x_range[t]], color_type['base']+topology_line_type[w])
+        l1, = plt.plot(x[:topology_x_range[t]], a_mine[:topology_x_range[t]], color_type['new']+topology_line_type[w], ms=8)
+        l2, = plt.plot(x[:topology_x_range[t]], a_base[:topology_x_range[t]], color_type['base']+topology_line_type[w], ms=8)
 
         label_list.append(w + '-' + remove_type['base'])
         label_list.append(w + '-' + remove_type['new'])
@@ -56,6 +56,6 @@ for t in ['geant']:
     pp.savefig(fig1)
     pp.close()
 
-    plt.show()
+    #plt.show()
 
 

### 2015-01-29 experiment/plot/exp1_power.py

@@ -7,8 +7,8 @@ fig1, ax1 = plt.subplots()
 topology_x_range = {'abilene':5, 'geant':13, 'cernet2':4}
 remove_links = {'abilene':4, 'geant':15, 'cernet2':3}
 w_line_type = {'1.5':'o', '2.5':'s', '3.5':'^'}
-color_type = {'base':'r-', 'new':'b-'}
-remove_type = {'base':'TMP', 'new':'ERLU'}
+color_type = {'base':'r--', 'new':'b-'}
+remove_type = {'base':'DMP', 'new':'ERLU'}
 result_file_template = "result-compare-%s-%s"
 topology_file_template = "../topology/connected/%s-connected-topology"
 remove_file_template = "../topology/remove/%s-remove-%d-links"
@@ -24,7 +24,7 @@ power_model = [60, 100, 140, 174]
 line_list = []
 label_list = []
 #for t in ['abilene', 'geant', 'cernet2']:
-t = 'geant'
+t = 'cernet2'
 for w in ['1.5', '2.5', '3.5']:
     # compute the total power of topology
     f = open(topology_file_template % t)
@@ -128,8 +128,8 @@ for w in ['1.5', '2.5', '3.5']:
 
     f.close()
 
-    l1, = ax1.plot(power_base_saving_ratio[:topology_x_range[t]], base[:topology_x_range[t]], color_type['base']+w_line_type[w])
-    l2, = ax1.plot(power_saving_ratio[:topology_x_range[t]], new[:topology_x_range[t]], color_type['new']+w_line_type[w])
+    l1, = ax1.plot(power_base_saving_ratio[:topology_x_range[t]], base[:topology_x_range[t]], color_type['base']+w_line_type[w], ms=8)
+    l2, = ax1.plot(power_saving_ratio[:topology_x_range[t]], new[:topology_x_range[t]], color_type['new']+w_line_type[w], ms=8)
 
     label_list.append(remove_type['base'] + '-' + w)
     label_list.append(remove_type['new'] + '-' + w)
@@ -150,7 +150,7 @@ pp = PdfPages('opr_with_power_%s.pdf' % t)
 pp.savefig(fig1)
 pp.close()
 
-plt.show()
+#plt.show()
 #plt.savefig('opr_with_power_%s.png' % t, bbox_inches='tight')
 
 

### 2015-01-29 experiment/plot/exp2_sort.py

@@ -35,7 +35,7 @@ for i in range(0, remove):
                 tmp = base[i][j]
                 base[i][j] = base[i][k]
                 base[i][k] = tmp
-    line1, = plt.plot(x, base[i], 'r--')
+    line1, = plt.plot(x, base[i], 'r--', ms=8)
 
 line2 = None
 for i in range(0, remove):
@@ -45,18 +45,18 @@ for i in range(0, remove):
                 tmp = new[i][j]
                 new[i][j] = new[i][k]
                 new[i][k] = tmp
-    line2, = plt.plot(x, new[i], 'b-')
+    line2, = plt.plot(x, new[i], 'b-', ms=8)
 
 #plt.axis([0, 6, 0, 20])
 
 plt.xlabel('Random Traffic Matrix (%)', fontsize=22)
 plt.ylabel('Oblivious Performance Ratio', fontsize=22)
-plt.legend([line1, line2], ['TMP', 'ERLU'], loc=2)
+plt.legend([line1, line2], ['DMP', 'ERLU'], loc=2)
 
 pp = PdfPages('exp2_sort_%s.pdf' % t)
 pp.savefig(fig1)
 pp.close()
 
-plt.show()
+#plt.show()
 #plt.savefig('exp2_sort_cernet2.png', bbox_inches='tight')
 

### 2015-02-01 dot/circle.tex
left related work and conclusion

\documentclass{standalone}
\usepackage[x11names, rgb]{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{snakes,arrows,shapes}
\usepackage{amsmath}
%
%

%

%

\begin{document}
\pagestyle{empty}
%
%
%

% Start of code
% \begin{tikzpicture}[anchor=mid,>=latex',line join=bevel,]
\begin{tikzpicture}[>=latex',line join=bevel,]
  \pgfsetlinewidth{1bp}
%%
\pgfsetcolor{black}
  % Edge: N1 -- N2
  \draw [] (60.347bp,37.149bp) .. controls (50.961bp,53.406bp) and (36.496bp,78.46bp)  .. (27.139bp,94.667bp);
  % Edge: N2 -- N3
  \draw [] (27.219bp,126.46bp) .. controls (36.605bp,142.72bp) and (51.07bp,167.77bp)  .. (60.427bp,183.98bp);
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (29.785bp,158.27bp) node {$l_{cd}$};
  % Edge: N4 -- N5
  \draw [] (181.92bp,183.84bp) .. controls (191.3bp,167.59bp) and (205.77bp,142.53bp)  .. (215.13bp,126.33bp);
  \draw (208.18bp,165.72bp) node {$l_{ef}$};
  % Edge: N0 -- N1
  \draw [] (154.26bp,21.181bp) .. controls (135.49bp,21.181bp) and (106.56bp,21.181bp)  .. (87.845bp,21.181bp);
  \draw (125.43bp,7.5bp) node {$l_{ab}$};
  % Edge: N5 -- N0
  \draw [] (215.05bp,94.528bp) .. controls (205.66bp,78.271bp) and (191.19bp,53.217bp)  .. (181.84bp,37.01bp);
  % Edge: N3 -- N4
  \draw [] (88.004bp,199.81bp) .. controls (106.78bp,199.81bp) and (135.71bp,199.81bp)  .. (154.42bp,199.81bp);
  % Node: N0
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (173.0bp,21.0bp) ellipse (18.0bp and 18.0bp);
  \draw (172.7bp,21.181bp) node {$a$};
\end{scope}
  % Node: N1
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (70.0bp,21.0bp) ellipse (18.0bp and 18.0bp);
  \draw (69.566bp,21.181bp) node {$b$};
\end{scope}
  % Node: N2
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (18.0bp,110.0bp) ellipse (18.0bp and 18.0bp);
  \draw (18.0bp,110.5bp) node {$c$};
\end{scope}
  % Node: N3
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (70.0bp,200.0bp) ellipse (18.0bp and 18.0bp);
  \draw (69.566bp,199.81bp) node {$d$};
\end{scope}
  % Node: N4
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (173.0bp,200.0bp) ellipse (18.0bp and 18.0bp);
  \draw (172.7bp,199.81bp) node {$e$};
\end{scope}
  % Node: N5
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (224.0bp,110.0bp) ellipse (18.0bp and 18.0bp);
  \draw (224.26bp,110.5bp) node {$f$};
\end{scope}
%
\end{tikzpicture}
% End of code

%
\end{document}
%

### 2015-02-01 dot/clique.tex
left related work and conclusion

--- 2015-02-01 dot/circle.tex
@@
 \pgfsetcolor{black}
+  % Edge: N1 -- N5
+  \draw [] (208.58bp,101.44bp) .. controls (178.93bp,84.322bp) and (114.97bp,47.397bp)  .. (85.292bp,30.26bp);
+  % Edge: N0 -- N5
+  \draw [] (154.26bp,21.181bp) .. controls (135.49bp,21.181bp) and (106.56bp,21.181bp)  .. (87.845bp,21.181bp);
+  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
+  \pgfsetstrokecolor{strokecol}
+  \draw (125.43bp,7.5bp) node {$l_{ab}$};
+  % Edge: N0 -- N4
+  \draw [] (172.7bp,39.292bp) .. controls (172.7bp,73.529bp) and (172.7bp,147.38bp)  .. (172.7bp,181.65bp);
+  % Edge: N4 -- N5
+  \draw [] (163.55bp,183.96bp) .. controls (143.98bp,150.06bp) and (98.251bp,70.864bp)  .. (78.698bp,36.998bp);
+  % Edge: N4 -- N1
+  \draw [] (181.92bp,183.84bp) .. controls (191.3bp,167.59bp) and (205.77bp,142.53bp)  .. (215.13bp,126.33bp);
+  \draw (208.18bp,165.72bp) node {$l_{ef}$};
+  % Edge: N0 -- N3
+  \draw [] (163.55bp,37.033bp) .. controls (143.98bp,70.931bp) and (98.251bp,150.13bp)  .. (78.698bp,183.99bp);
+  % Edge: N0 -- N2
+  \draw [] (157.01bp,30.236bp) .. controls (127.36bp,47.355bp) and (63.408bp,84.28bp)  .. (33.726bp,101.42bp);
+  % Edge: N2 -- N4
+  \draw [] (33.685bp,119.55bp) .. controls (63.335bp,136.67bp) and (127.29bp,173.59bp)  .. (156.97bp,190.73bp);
   % Edge: N1 -- N2
-  \draw [] (60.347bp,37.149bp) .. controls (50.961bp,53.406bp) and (36.496bp,78.46bp)  .. (27.139bp,94.667bp);
+  \draw [] (205.96bp,110.5bp) .. controls (166.82bp,110.5bp) and (75.369bp,110.5bp)  .. (36.264bp,110.5bp);
+  % Edge: N1 -- N3
+  \draw [] (208.58bp,119.55bp) .. controls (178.93bp,136.67bp) and (114.97bp,173.59bp)  .. (85.292bp,190.73bp);
   % Edge: N2 -- N3
   \draw [] (27.219bp,126.46bp) .. controls (36.605bp,142.72bp) and (51.07bp,167.77bp)  .. (60.427bp,183.98bp);
-  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
-  \pgfsetstrokecolor{strokecol}
   \draw (29.785bp,158.27bp) node {$l_{cd}$};
-  % Edge: N4 -- N5
-  \draw [] (181.92bp,183.84bp) .. controls (191.3bp,167.59bp) and (205.77bp,142.53bp)  .. (215.13bp,126.33bp);
-  \draw (208.18bp,165.72bp) node {$l_{ef}$};
-  % Edge: N0 -- N1
-  \draw [] (154.26bp,21.181bp) .. controls (135.49bp,21.181bp) and (106.56bp,21.181bp)  .. (87.845bp,21.181bp);
-  \draw (125.43bp,7.5bp) node {$l_{ab}$};
-  % Edge: N5 -- N0
-  \draw [] (215.05bp,94.528bp) .. controls (205.66bp,78.271bp) and (191.19bp,53.217bp)  .. (181.84bp,37.01bp);
   % Edge: N3 -- N4
   \draw [] (88.004bp,199.81bp) .. controls (106.78bp,199.81bp) and (135.71bp,199.81bp)  .. (154.42bp,199.81bp);
+  % Edge: N1 -- N0
+  \draw [] (215.05bp,94.528bp) .. controls (205.66bp,78.271bp) and (191.19bp,53.217bp)  .. (181.84bp,37.01bp);
+  % Edge: N2 -- N5
+  \draw [] (27.219bp,94.528bp) .. controls (36.605bp,78.271bp) and (51.07bp,53.217bp)  .. (60.427bp,37.01bp);
+  % Edge: N3 -- N5
+  \draw [] (69.566bp,181.7bp) .. controls (69.566bp,147.46bp) and (69.566bp,73.614bp)  .. (69.566bp,39.34bp);
   % Node: N0
@@
   \pgfsetstrokecolor{strokecol}
-  \draw (70.0bp,21.0bp) ellipse (18.0bp and 18.0bp);
-  \draw (69.566bp,21.181bp) node {$b$};
+  \draw (224.0bp,110.0bp) ellipse (18.0bp and 18.0bp);
+  \draw (224.26bp,110.5bp) node {$f$};
 \end{scope}
@@
   \pgfsetstrokecolor{strokecol}
-  \draw (224.0bp,110.0bp) ellipse (18.0bp and 18.0bp);
-  \draw (224.26bp,110.5bp) node {$f$};
+  \draw (70.0bp,21.0bp) ellipse (18.0bp and 18.0bp);
+  \draw (69.566bp,21.181bp) node {$b$};
 \end{scope}

### 2015-02-01 dot/sample.tex
left related work and conclusion

--- 2015-02-01 dot/circle.tex
@@
 \pgfsetcolor{black}
-  % Edge: N1 -- N2
-  \draw [] (60.347bp,37.149bp) .. controls (50.961bp,53.406bp) and (36.496bp,78.46bp)  .. (27.139bp,94.667bp);
-  % Edge: N2 -- N3
-  \draw [] (27.219bp,126.46bp) .. controls (36.605bp,142.72bp) and (51.07bp,167.77bp)  .. (60.427bp,183.98bp);
+  % Edge: N0 -- N1
+  \draw [] (35.352bp,28.256bp) .. controls (55.506bp,30.438bp) and (88.555bp,30.437bp)  .. (108.69bp,28.252bp);
   \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
   \pgfsetstrokecolor{strokecol}
-  \draw (29.785bp,158.27bp) node {$l_{cd}$};
-  % Edge: N4 -- N5
-  \draw [] (181.92bp,183.84bp) .. controls (191.3bp,167.59bp) and (205.77bp,142.53bp)  .. (215.13bp,126.33bp);
-  \draw (208.18bp,165.72bp) node {$l_{ef}$};
+  \draw (70.102bp,38.783bp) node {$l_1: 3Mbps$};
   % Edge: N0 -- N1
-  \draw [] (154.26bp,21.181bp) .. controls (135.49bp,21.181bp) and (106.56bp,21.181bp)  .. (87.845bp,21.181bp);
-  \draw (125.43bp,7.5bp) node {$l_{ab}$};
-  % Edge: N5 -- N0
-  \draw [] (215.05bp,94.528bp) .. controls (205.66bp,78.271bp) and (191.19bp,53.217bp)  .. (181.84bp,37.01bp);
-  % Edge: N3 -- N4
-  \draw [] (88.004bp,199.81bp) .. controls (106.78bp,199.81bp) and (135.71bp,199.81bp)  .. (154.42bp,199.81bp);
+  \draw [] (35.352bp,18.027bp) .. controls (55.506bp,15.845bp) and (88.555bp,15.846bp)  .. (108.69bp,18.031bp);
+  \draw (70.102bp,7.5bp) node {$l_2: 4Mbps$};
   % Node: N0
@@
   \pgfsetstrokecolor{strokecol}
-  \draw (173.0bp,21.0bp) ellipse (18.0bp and 18.0bp);
-  \draw (172.7bp,21.181bp) node {$a$};
+  \draw (18.0bp,23.0bp) ellipse (18.0bp and 18.0bp);
+  \draw (18.0bp,23.141bp) node {$a$};
 \end{scope}
@@
   \pgfsetstrokecolor{strokecol}
-  \draw (70.0bp,21.0bp) ellipse (18.0bp and 18.0bp);
-  \draw (69.566bp,21.181bp) node {$b$};
-\end{scope}
-  % Node: N2
-\begin{scope}
-  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
-  \pgfsetstrokecolor{strokecol}
-  \draw (18.0bp,110.0bp) ellipse (18.0bp and 18.0bp);
-  \draw (18.0bp,110.5bp) node {$c$};
-\end{scope}
-  % Node: N3
-\begin{scope}
-  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
-  \pgfsetstrokecolor{strokecol}
-  \draw (70.0bp,200.0bp) ellipse (18.0bp and 18.0bp);
-  \draw (69.566bp,199.81bp) node {$d$};
-\end{scope}
-  % Node: N4
-\begin{scope}
-  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
-  \pgfsetstrokecolor{strokecol}
-  \draw (173.0bp,200.0bp) ellipse (18.0bp and 18.0bp);
-  \draw (172.7bp,199.81bp) node {$e$};
-\end{scope}
-  % Node: N5
-\begin{scope}
-  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
-  \pgfsetstrokecolor{strokecol}
-  \draw (224.0bp,110.0bp) ellipse (18.0bp and 18.0bp);
-  \draw (224.26bp,110.5bp) node {$f$};
+  \draw (126.0bp,23.0bp) ellipse (18.0bp and 18.0bp);
+  \draw (126.0bp,23.141bp) node {$b$};
 \end{scope}

### 2015-02-01 paper_linheng_4.tex
left related work and conclusion

--- 2015-01-29 paper.tex
@@
 Let $d_{ab}$ denote the traffic demand from origin node $a$ and destination node $b$, and $m$ denote the TM that contains $d_{ab}$ for all $a, b \in V$.
-Let $f_{ab}(i,j)$ be the fraction of $d_{ab}$ that is routed on link $(i, j)$ $(0 \leq f_{ab}(i,j) \leq 1)$.
-Routing $r$ is specified by $f_{ab}(i,j)$ for all $a, b \in V$ and $(i, j) \in E$, and we will formally define routing consistency later in Section III.C.
+Let $f^r_{ab}(i,j)$ be the fraction of $d_{ab}$ that is routed on link $(i, j)$ $(0 \leq f^r_{ab}(i,j) \leq 1)$, using routing $r$.
+Routing $r$ is specified by $f^r_{ab}(i,j)$ for all $a, b \in V$ and $(i, j) \in E$, and we will formally define routing consistency later in Section III.C.
 Let $U_{r, m, G}$ be the MLUR of routing $r$ under TM $m$.
@@
 \begin{equation}
-	U_{r, m, G} = \max_{(i,j)\in E} \frac{\sum_{a,b} d_{ab}f_{ab}(i,j)}{cap_{ij}}.
+	U_{r, m, G} = \max_{(i,j)\in E} \frac{\sum_{a,b} d_{ab}f^r_{ab}(i,j)}{cap_{ij}}.
 \end{equation}
@@
 \begin{equation}
-	P(\{ r \},\{ m \}, G) = \frac{U_{r,m,G}}{\min_{r'} U_{r', m, G}}.
+	P(r,\{ m \}, G) = \frac{U_{r,m,G}}{\min_{r'} U_{r', m, G}}.
 \end{equation}
 
-The \emph{oblivious performance ratio} (OPR) for routing $r$ is defined by extending TM $m$ to a set of TMs $M$, where $M$ can be the set of any TMs. We have
+The \emph{oblivious performance ratio} (OPR) for routing $r$ is defined by extending TM $m$ to a set of TMs $M$, where $M$ can be the set of all TMs. We have
 \begin{equation}
-	P(\{ r \}, M, G) = \max_{m\in M} P(\{ r \}, \{ m \}, G).
+	P(r, M, G) = \max_{m\in M} P(r, \{ m \}, G).
 \end{equation}
@@
 To address this issue, we extend the definition of OPR.
-Formally, let $G^*$ be a sub-graph of $G$ that satisfies the energy constraint (We will formally give the model in Section III.C).
+Formally, let $G^*$ be a sub-graph of $G$ that satisfies the energy constraint (We will formally define the energy constraint in Section III.C, i.e., Eq.
+(8)).
+Note that in this case, a path cannot traverse a off/sleeping link, so routing $r$ is limited by $G^*$ (Eq.
+(7) in Section III.C).
 The extended performance ratio is defined as
 \begin{equation}
-	P(\{ r \},\{ m \}, G, G^*) = \frac{U_{r,m,G^*}}{\min_{r'} U_{r', m, G}}.
+	P(r, \{ m \}, G, G^*) = \frac{U_{r,m,G^*}}{\min_{r'} U_{r', m, G}}.
 \end{equation}
-Let $P^*(\{ r \}, M, G)$ be the \emph{oblivious performance ratio with energy constraint} (OPRE) for routing $r$.
-We define $P^*(\{ r \}, M, G)$ by extending $m$ to $M$, and finding $G^*$ that satisfies the energy constraint and has the minimum performance ratio.
-We have
+Let $P^*(r, M, G, G^*)$ be the \emph{oblivious performance ratio with energy constraint} (OPRE) for routing $r$. We define $P^*(r, M, G, G^*)$ by extending $m$ to $M$. Similar to Eq. (3), we have
 \begin{equation}
-	P^*(\{ r \}, M, G) = \min_{G^*} \max_{m\in M} P(\{ r \}, \{ m \}, G, G^*)
+	P^*(r, M, G, G^*) = \max_{m\in M} P(r, \{ m \}, G, G^*).
 \end{equation}
-Note that when there is no energy constraint, $G$ is the sub-graph that has the minimum performance ratio, and Eq. (5) naturally reduces to Eq. (3).
+Note that $G^*$ is used to achieve certain energy conservation target.
+For an energy conservation target, there may exist a set of different $G^*$, which result in different OPRE.
+We will show an example below.
+When there is no energy constraint, $G^*$ equals $G$, and Eq.
+(5) naturally reduces to Eq.
+(3).
+
+\subsection{Example}
+
+We show an example of our new metric OPRE.
+The network is shown in Fig.
+1, where two nodes $a, b$ are connected by two links $l_1$ and $l_2$.{\footnote{When there are parallel links, we can add a virtual node in each parallel link to keep $G(V,E)$ as a simple graph.}} The capacities of the links are 3 Mbps and 4 Mbps, respectively.
+To forward a traffic demand of $d_{ab}$, the optimal routing is to put $\frac{3}{7}d_{ab}$ on link $l_1$ and $\frac{4}{7}d_{ab}$ on link $l_2$, which results in the MLUR of $\frac{1}{7}d_{ab}$.
+This routing is also the optimal demand-oblivious routing, because the routing is optimal no matter how $d_{ab}$ changes.
+Thus, the OPR equals 1.
+
+\begin{figure}[!t]
+\centering
+\vspace*{0.1in}
+\includegraphics[width=6cm]{3-nodes-example}
+\caption{Model Example. There is traffic demand $d_{ab}$ from $a$ to $b$.}
+\label{label}
+\vspace*{0.1in}
+\end{figure}
+
+Now, assume that links $l_1$ and $l_2$ consume the same power, and one link has to be switched off/sleep to save energy.
+Let us check the OPRE after pruning $l_1$ and $l_2$, respectively.
+If $l_1$ is pruned, $d_{ab}$ is put on link $l_2$, and the MLUR is $\frac{1}{4}d_{ab}$, so the OPRE is $\frac{1}{4}d_{ab}/\frac{1}{7}d_{ab} = 7/4 = 1.75$.
+If $l_2$ is pruned, $d_{ab}$ traverses link $l_1$, resulting in the MLUR of $\frac{1}{3}d_{ab}$, so the OPRE is $\frac{1}{3}d_{ab}/\frac{1}{7}d_{ab} = 7/3 = 2.33$.
+The results tell us that pruning link $l_1$ is more robust than pruning link $l_2$.
+This is consistent with the intuition that link $l_2$ has a larger capacity and is stronger against congestion.
 
 \subsection{Problem Formulation}
-We formulate our problem as following:
+
+Now we formally model the problem.
+Our objective is to minimize OPRE $P^*(r, M, G, G^*)$, where $M$ and $G$ are inputs, and routing $r$ and sub-graph $G^*$ are decision variables.
+The Min-OPRE problem is as follows.
 
 \begin{center}
-Minimize \quad $P^*(\{r\},M,G)$
+Minimize \quad $P^*(r, M, G, G^*)$
 \end{center}
@@
 \begin{center}
-s.t. (1),\ (4)
+s.t. (1),\ (4),\ (5)
 \end{center}
@@
     \begin{split}
-    \sum_{j, s.t.(i,j) \in E}\hspace{-0.2in}f'_{ab}(i,j) - \hspace{-0.2in}\sum_{j, s.t.(j,i) \in E}\hspace{-0.2in}f'_{ab}(j,i) = 
+    \sum_{j, s.t.(i,j) \in E}\hspace{-0.2in}f^{r'}_{ab}(i,j) - \hspace{-0.2in}\sum_{j, s.t.(j,i) \in E}\hspace{-0.2in}f^{r'}_{ab}(j,i) =
     \left\{
         \begin{array}{c}
-        \ \ 1, \ i = b \\
-        -1, \ i = a \\
+        \ \ 1, \ i = a \\
+        -1, \ i = b \\
         \ \ \ \ \ 0, \ i \neq a,b \\
@@
     \begin{split}
-    \sum_{j, s.t.(i,j) \in E^*}\hspace{-0.2in}f_{ab}(i,j) - \hspace{-0.3in}\sum_{j, s.t.(j,i) \in E^*}\hspace{-0.2in}f_{ab}(j,i) = 
+    \sum_{j, s.t.(i,j) \in E^*}\hspace{-0.2in}f^r_{ab}(i,j) - \hspace{-0.3in}\sum_{j, s.t.(j,i) \in E^*}\hspace{-0.2in}f^r_{ab}(j,i) =
     \left\{
         \begin{array}{c}
-        \ \ 1, \ i = b \\
-        -1, \ i = a \\
+        \ \ 1, \ i = a \\
+        -1, \ i = b \\
         \ \ \ \ \ 0, \ i \neq a,b \\
@@
 
+\begin{center}
+    \vspace{0.1in}
+    $\forall a,b \in V$, $\forall i,j \in E$: \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad 
+    \vspace{-0.15in}
+\end{center}
+
 \begin{equation}
-    \sum_{l \in E^*} p(l) / \sum_{l \in E} p(l) < 1 - \theta
+    0 \leq f^r_{ab}(i,j),f^{r'}_{ab}(i,j) \leq 1
 \end{equation}
@@
 \begin{equation}
-    0 \leq f_{ab}(i,j),f'_{ab}(i,j) \leq 1
+    \sum_{l \in E^*} p(l) / \sum_{l \in E} p(l) \leq 1 - \theta
 \end{equation}
 
-Eq. (6) is our target, which minimize the value of OPRE defined in \Rmnum{3}.B. Eq. (7) say $G^*$ be a sub-graph of $G$, which means remove/sleep
-some links from $G$, and keep vertices the same. Eq. (8) ensures the graph is connected and define the routing. In details, $O_{(i,j)}^i$ equal to
-1 if $i$ is the tail node of link $(i,j)$, and $I_(i,j)^i$ equal to 1 if $i$ is the head node of link $(i,j)$, this equation states the flow 
-conservation constraints. In the other hand, $f_{ab}(i,j)$ is specified by routing $\gamma$, if the graph is not connected it will be unavailable
-for some origin and destination pair. And from Eq. (8) we know that routing $r$ is corresponded with $G^*$, and $r'$ with $G$. We calculate the 
-power constraints in Eq. (9), it ensure that we can save more than $\theta$ energy consumption. The function $p$ which maps link to power consumption
-is proposed in \cite{networking:greente}.
+Constraints (1), (4), and (5) follow our definition of the OPRE.
+Eq.
+(6) means that the optimal routing $r'$ in $G$ must be a valid routing, i.e.
+with routing consistency.
+Specifically, for the source/destination node, all traffic must be routed/received; and for an intermediate node, the traffic flowing out must equal the traffic flowing in.
+Similarly, Eq.
+(7) means that the robust routing $r$ in $G^*$ must be a valid routing.
+Ineq.
+(8) means that the range of $f^r_{ab}(i,j)$ and $f^{r'}_{ab}(i,j)$ is from 0 to 1.
+Ineq.
+(9) means that the power consumption of links in $G^*$ must be less than a given threshold.
+In Ineq.
+(9), $\theta$ denotes the power saving ratio we must achieve by using $G^*$.
+Here, we use $p(l)$ to denote the power consumption of link $l$, which is mainly drawn by the line cards at the two ends of the link.
+Note that $p(l)$ is independent of the traffic volume, and this assumption is based on the fact that in current stage, the power of a line card changes little with the traffic volume \cite{networking:hopbyhop}.
 
-\subsection{Model Example}
-We will take an example to explain how to choose the link to close in our algorithm.
-Three hostes include : a, b, c, three links are with repectively capacity of 3M, 4M and 2M. For simpleness, we suppose
-there are two TM : ${(a,b,2M), (a,c,1M)}$ and ${(a,b,1M), (a,c,1M)}$. For each traffic matrix, the optimal route is
-obvious, we will trace 2M from a to b across the lower link and trace the 1M from a to c across the upper one
-for the first traffic matrix, whose maximum link utilization is 0.5. we will trace all the traffic acorss the
-lower link for the second traffic matrix, whose maximum link utilization is 0.5 as well.
+Note that if $G^* = G$ satisfy the energy constraint Ineq.
+(9) and $M$ is the set of all TMs, the Min-OPRE problem reduces to the demand-oblivious routing problem, and can be transformed into a linear program and solved in polynomial time \cite{networking:oblivious}.
+However, we must find the optimal $G^*$ to achieve the required power saving ratio in other cases, and Min-OPRE is an MILP and is NP-hard in general.
 
-\begin{figure}[!t]
-\centering
-\vspace*{0.1in}
-\includegraphics[width=8cm]{3-nodes-example}
-\caption{Model Example, TM \Rmnum{1} : (a, b, 2M), (a, c, 1M); TM \Rmnum{2} : (a, b, 1M), (a, c, 1M).}
-\label{label}
-\vspace*{0.1in}
-\end{figure}
+Also note that we put the power saving in the constraint of our problem, instead of the objective function.
+In such a way, we can balance the trade off between energy conservation and the OPRE, by setting different values of power saving ratio $\theta$.
+We can even achieve the maximum power saving ratio by a binary search on $\theta$.
 
-Now for some reason, we will choose one link to shut down for power saving without lose connection of the network.
-There are two choice, remove either the upper link or the lower link. Let us take a little calculation: when
-remove the upper one, we should change all the traffic acorss the lower link, as a result, in the first
-TM the maximum link utilization is 0.75 and the second is 0.5; when close the lower link, we should trace all the
-traffic acorss the upper link, in the first TM the link utilization is 1 and the other is 0.667.
-So according to our theory, the $P^{*}(M, G)$ should be 1.5 and the optimal successor network topology will be
-the one which 3M link is closed.
+\section{Upper Bounds of the Minimum OPRE}
 
-\section{Algorithm}
+In this section, we analyze the upper bounds of the minimum OPRE.
+We are interested in two extreme types of networks, i.e., cycles and cliques, because general networks can be seen as intermediate cases between them.
+We will present the upper bounds with small and large values of $\theta$.
+We find that, though the minimum OPR of cycles and cliques is similar and bounded by 2 \cite{networking:oblivious}, the minimum OPRE is much more different and has a larger upper bound with a larger $\theta$.
+These theoretical results tell us that the robust energy efficient routing exists, and tell us how close a robust routing can get to the optimal routing.
+
+\begin{lemma}
+$\min P^*(r, M, G, G^*) \geq \min P^*(r, M, G)$ if $G^* \subseteq G$, where the equation holds if $G^* = G$.
+\end{lemma}
+\begin{proof}
+We assume exist a $G^*$, s.t. min $P^*(r,M,G,G^*)$ $<$ min $P^*(r, M, G)$. Becuase $G^*$ is the subset of $G$, we directly
+use the robust routing of $G^*$ to $G$, then $P^*(r, M, G)$ will equal to $P^*(r,M,G,G^*)$, and arise contradiction.
+Particularly, when $G^* = G$, $G^*$ is the subset of $G$, and $G$ is the subset of $G^*$, so there is both 
+min $P^*(r,M,G,G^*)$ $\geq$ min $P^*(r, M, G)$ and $P^*(r, M ,G)$ $\geq$ $P^*(r, M, G, G^*)$, so they are equal to each other 
+when $G^*$ = $G$. This ends our proof.
+\end{proof}
+
+\begin{theorem}
+The minimum OPRE of $C_n$ (the cycle on $n$ vertices with unit capacity links) and $K_n$ (the complete graph on $n$ vertices with unit capacity links) is $2-2/n$ if $\theta = 0$.
+\end{theorem}
+\begin{proof}
+According to Lemma 1, the minimum OPRE of $C_n$ is the minimum OPR, i.e., $\min P^*(r, M, C_n)$, when $\theta = 0$.
+Similarly, the minimum OPRE of $K_n$ is $\min P^*(r, M, K_n)$ when $\theta = 0$.
+On the other hand, we know from \cite{networking:oblivious} that the minimum OPR of $C_n$ is $2-2/n$, and the minimum OPR of $K_n$ is also $2-2/n$.
+This ends our proof.
+\end{proof}
+
+Theorem 2 shows the minimum OPRE when $\theta = 0$ and all link capacities are the same. In a more general case when there are different link capacities, we have
+
+\begin{theorem}
+The upper bound of the minimum OPRE for a cycle on $n$ nodes is $1 + \frac{\max cap_{ij}}{\min cap_{ij}}$ if $\theta = 0$.
+\end{theorem}
+\begin{proof}
+See Appendix A.
+\end{proof}
+
+\begin{theorem}
+The upper bound of the minimum OPRE for a complete graph on $n$ nodes is $1 + \frac{\max cap_{ij}}{\min cap_{ij}}$ if $\theta = 0$.
+\end{theorem}
+\begin{proof}
+See Appendix A.
+\end{proof}
+
+Theorem 3 and Theorem 4 tell us that the minimum OPRE is related to the link capacity difference in the network.
+The above results are for $\theta = 0$.
+Now let us see the results for a large $\theta$.
+Since there is not much difference between the power consumptions for links with different capacities \cite{}, we consider the spanning trees of a graph, which can achieve a near-optimal $\theta$.
+We have
+\begin{theorem}
+Let $G^*$ be a spanning tree of a cycle on $n$ nodes, and then the upper bound of the OPRE is $1 + \frac{\max cap_{ij}}{\min cap_{ij}}$.
+\end{theorem}
+\begin{proof}
+See Appendix B.
+\end{proof}
+\begin{theorem}
+Let $G^*$ be a spanning tree of a complete graph on $n$ nodes, and then the upper bound of the OPRE is $\frac{n^2}{2} \frac{\max cap_{ij}}{\min cap_{ij}}$.
+\end{theorem}
+\begin{proof}
+See Appendix C.
+\end{proof}
+
+Theorem 5 and Theorem 6 present a large gap between the OPRE upper bounds in the two types of networks, because when $G^*$ is a spanning tree, more links are pruned in the complete graph.
+This implies that in order to achieve more energy conservation, the OPRE may become larger quickly, and the routing becomes less robust, in the worst case.
+However, we can still develop effective algorithms to achieve a small OPRE and save energy in general cases, i.e., in real-world networks which have much less link densities than a complete graph.
+
+\section{Robust Energy-Aware Routing Algorithms}
+
 In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links
@@
 
-\section{Samples and Proof}
-For explaining OPRE clearly, we will show it in two simple topologies, Cliques and Cycles. With a specific power saving 
-threshold, some links will be removed from the topology then robust routing will be computed. Taking two extreme examples from 
-origin topology, one with no links removed, i.e the topology itself, and the other with no more link can be removed, i.e. 
-spanning tree of the topology. And the corresponding thresholds are 0 and maximum value can be achieved. We prove the upper 
-bound of OPRE for cycles and cliques in these two situations, and we say when taking a threshold between 0 and maximum value,
-the corresponding OPRE is also bounded.
-
-\begin{figure}[!t]
-\centering
-\vspace*{0.1in}
-\subfloat[Circle]{\includegraphics[width=4cm]{circle}
-\label{subfiga}}
-\hfill
-\subfloat[Clique]{\includegraphics[width=4cm]{clique}
-\label{subfigb}}
-\caption{Circle and Clique topology of 6 nodes}
-\vspace*{0.1in}
-\end{figure}
-
-\begin{lemma}
-The upper bound of OPR for $C_n$ (the cycle on n vertices) and $K_n$ (the complete graph on n vertices) is 2-2/n.
-\end{lemma}
-
-Lemma 1 is proved in \cite{networking:oblivious} and it assumes all the links the same. We extend this lemma on $C_n$ and
-$K_n$ with different capacity of links. In the latter proof, we use the extended $C_n$ and $K_n$ definition without specified.
-
-\begin{theorem}
-The upper bound of OPRE for spanning tree of $C_n$ is 1+$Max_{cap}$/$Min_{cap}$.
-\end{theorem}
-
-\begin{proof}
-Cycles topology connect all the nodes by a cycle, any node in which has two links joined. Figure 2.(a) show the six
-nodes cycles topology, let nodes named from $A$ to $F$ and links named from $a$ to $f$. Now suppose a traffic in the 
-topology then calculate the optimal routing for it, let $D_a$ and $C_a$ be the demand and capacity of the link $a$, 
-without loss of generality, we say the link $d$ is the bottleneck, namely link with MLUR.
-
-The spanning tree of $C_n$ is generated by removing one link from origin topology. There are two ways to generate 
-the spanning tree, remove the link $d$ or remove the other link such as $f$.
-
-For case \Rmnum{1}, when we switch off the link $d$, the origin traffic pass the link will be redirected. The worst situation
-is that all the traffic on the link $d$ will be put to the other path : $D \leftarrow C \leftarrow B \leftarrow A \leftarrow 
-F \leftarrow E$. After traffic redirection, the bottleneck link may become the link $e$, we have OPRE in this routing situation:
-
-\begin{equation}
-    \frac {\frac{D_e + D_d} {C_e}} {\frac {D_d}{C_d}} = (1 + \frac{D_e}{D_d}) \frac{C_d}{C_e}
-\end{equation}
-
-Because the link utilization of link $d$ is the maximum one, we have :
-
-\begin{equation}
-    \frac{D_d}{C_d} > \frac{D_e}{C_e} 
-\end{equation}
-\begin{equation}
-    \frac{D_e * C_d}{C_e * D_d} < 1
-\end{equation}
-
-so we have OPRE in case \Rmnum{1} :
-
-\begin{equation}
-    (1 + \frac{D_e}{D_d}) \frac{C_d}{C_e} < \frac{C_d}{C_e} + 1
-\end{equation}
-
-For case \Rmnum{2}, similar to case \Rmnum{1}, all the traffic will be redirected on the other path between $F$ and $A$. There are two 
-sub cases after traffic redirection, the link $D$ is still the bottleneck or the link $E$ become the new bottleneck. In case \Rmnum{2}.\Rmnum{1},
-we have OPRE:
-
-\begin{equation}
-    \frac{\frac{D_d + D_f}{C_d}}{\frac{D_d}{C_d}} = 1 + \frac{D_f}{D_d}
-\end{equation}
-
-Because the link utilization of link $d$ is the maximum one in origin topology, we have:
-
-\begin{equation}
-    \frac{D_d}{C_d} > \frac{D_f}{C_f} 
-\end{equation}
-\begin{equation}
-    \frac{D_f}{D_d} < \frac{C_d}{C_f} 
-\end{equation}
-
-So we get OPRE in case \Rmnum{2}.\Rmnum{1}:
-\begin{equation}
-    (1 + \frac{D_f}{D_d}) < \frac{C_d}{C_f} + 1
-\end{equation}
-
-In case \Rmnum{2}.\Rmnum{2}, we get OPRE:
-
-\begin{equation}
-    \frac{\frac{D_e + D_d}{C_e}}{\frac{D_d}{C_d}} = \frac{D_e * C_d}{D_d * C_e} * \frac{C_d * D_f}{C_e * D_e}
-\end{equation}
-
-Similarly as mentioned above, we get equations :
-
-\begin{equation}
-    \frac{D_d}{C_d} > \frac{D_e}{C_e} => \frac{D_e * C_d}{C_e * D_d} < 1 
-\end{equation}
-\begin{equation}
-    \frac{D_d}{C_d} > \frac{D_f}{C_f} => \frac{D_f * C_d}{D_d} < C_f
-\end{equation}
-
-So we obtain OPRE:
-
-\begin{equation}
-    \frac{D_e * C_d}{D_d * C_e} + \frac{C_d * D_f}{C_e * D_d} < 1 + \frac{C_f}{C_e}
-\end{equation}
-
-As a result, the upper bound of extended robust link utilization must be :
-
-\begin{equation}
-    Max\{1 + \frac{C_d}{C_e}, 1 + \frac{C_d}{C_f}, 1 + \frac{C_f}{C_e}\} < 1 + \frac{Max_{cap}}{Min_{cap}}
-\end{equation}
-
-Particularly, if all the links have the same capacity, the upper bound equal to 2 for the spanning tree. Otherwise, the 
-upper bound only dependent to the greatest ratio of link capacity.
-
-\end{proof}
-
-\begin{theorem}
-The upper bound of OPRE for $C_n$ is 1+${Max_{cap}}$/${Min_{cap}}$.
-\end{theorem}
-
-\begin{proof}
-The robust routing which will not trace demand on one link must be less optimal than the routing can trace demand on any link,
-and obviously the former routing is one of the routing on the spanning tree of $C_n$. So the bound of Theorem 2 is also the 
-bound of Theorem 3.
-
-Particularly, If the links of $C_n$ have the same capacity, OPRE will reduce to OPR. According to Lemma 1, we have the inequality:
-
-\begin{equation}
-OPRE = OPR < 2 - \frac{2}{n} < 1 + \frac{Max_{cap}}{Min_{cap}} = 2
-\end{equation}
-
-\end{proof}
-
-\begin{theorem}
-The upper bound of OPRE for $K_n$ is 1+${Max_{cap}}$/${Min_{cap}}$.
-\end{theorem}
-
-\begin{proof}
-Similar to the proof of Theorem 3, we say the robust routing which will not trace demand on one link must be less optimal than
-the real optimal robust routing. And it is one routing of topology which remove one link from origin topology $K_n$. Without
-loss of generality, we say the link $a$ is the bottleneck, and we will switch off it or other link like $b$, then consider
-the OPRE when adjust the demand to other link.
-
-In case \Rmnum{1}, after we switch off link $a$, the new bottleneck link must be the affected link, the link contains the origin 
-traffic on link $a$. Otherwise if the link $b$ is the bottleneck, but we adjust the traffic on other links, it means that
-we can do the same thing in the origin topology, and the bottleneck become link $b$ rather than $a$. It is conflict with our
-assumption. So we have the OPRE as :
-
-\begin{equation}
-    \frac {\frac{D_b + D_a}{C_b}}{\frac{D_a}{C_a}} = (1+\frac{D_b}{D_a}) \frac{C_a}{C_b}
-\end{equation}
-
-Because the link $a$ is the bottleneck link with the maximum link utilization, like what we do above, we can get
-
-\begin{equation}
-    (1+\frac{D_b}{D_a}) \frac{C_a}{C_b} < 1 + \frac{C_a}{C_b}
-\end{equation}
-
-In case \Rmnum{2}, the bottleneck may still be link $a$ or the new link $c$. If it is link $a$, and no new traffic across it,
-the OPRE equal to 1 obiliously. Or we adjust the new traffic $D_b$ on it, we can get the OPRE:
-
-\begin{equation}
-    \frac{\frac{D_a + D_b}{C_a}}{\frac{D_a}{C_a}} = 1 + \frac{D_b}{D_a} < 1 + \frac{C_b}{C_a}
-\end{equation}
-
-If the bottleneck become new link $c$, similar to our proof of circle topology, we can get OPRE:
-\begin{equation}
-    \frac{\frac{D_c + D_b}{C_c}}{\frac{D_a}{C_a}} = \frac{D_c * C_a}{D_a * C_c} + \frac{D_b * C_a}{D_a * C_c} < 1 + \frac{C_b}{C_c}
-\end{equation}
-
-So we obtain the same conclusion as circle topology, the OPRE must be :
-
-\begin{equation}
-    Max\{1 + \frac{C_a}{C_b}, 1 + \frac{C_b}{C_a}, 1 + \frac{C_b}{C_c}\} = 1 + \frac{Max_{cap}}{Min_{cap}}
-\end{equation}
-
-When the links of $K_n$ is the same, Theorem 4 will reduce to Lemma 1. The upper bound is bounded.
-\end{proof}
-
-\begin{theorem}
-The upper bound of OPRE for spanning tree of $K_n$ is $\frac{n^2}{2} Max_{cap}/Min_{cap}$.
-\end{theorem}
-
-\begin{proof}
-Every link in the spanning tree will split the graph to two parts, the flow between two parts must need across this link,
-Without loss of generality, let $l_{da}$ be the link with maximum link utilization. And let $l_{be}$ be the bottleneck link 
-in the optimal routing for origin topology. So we have OPRE:
-
-\begin{equation}
-    \frac{\frac{\sum_{i,j \in V} D_{ij}}{C_{da}}}{\frac{D_{be}}{C_{be}}} = \sum_{i,j \in V} \frac{D_{ij}}{D_{be}} \frac{C_{be}}{C_{da}} 
-\end{equation}
-
-Because the $l_{be}$ is the bottleneck link, we have:
-
-\begin{equation}
-    \frac{D_{ij}}{C_{ij}} < \frac{D_{be}}{C_{be}}
-\end{equation}
-
-\begin{equation}
-    \frac{D_{ij}}{D_{be}} < \frac{C_{ij}}{C_{be}}
-\end{equation}
-
-So we have OPRE:
-
-\begin{equation}
-    \sum_{i,j \in V} \frac{D_{ij}}{D_{be}} \frac{C_{be}}{C_{da}} < \sum_{i,j \in V} \frac{C_{ij}}{C_{be}}
-\end{equation}
-
-And we know that, the flow between two parts of topology must less than $\frac{n^2}{2}$, so OPRE must lower than:
-
-\begin{equation}
-    \sum_{i,j \in V} \frac{C_{ij}}{C_{be}} < \frac{n^2}{2} \frac{Max_{cap}}{Min_{cap}}
-\end{equation}
-
-\end{proof}
-
 \begin{figure*}[!t]
@@
 
+\bibitem{networking:hopbyhop}
+C. Hou, F. Zhang, A. F. Anta, L. Wang, and Z. Liu. “A Hopby-hop Energy Efficient Distributed Routing Scheme,” in Proc. of Greenmetrics Workshop, 2013.
+
 \end{thebibliography}
+
+\appendices
+
+\section{}
+\begin{proof}
+Fig. (5) shows the 6-nodes cycle and clique topologies. We label three links $l_{ab}$, $l_{cd}$ and $l_{ef}$
+for our proof, let $cap_{ab}$, $cap_{cd}$ and $cap_{ef}$ be their link capacities. Now a arbitrary traffic
+comes, we compute the optimal routing and forward the demand on the topologies, let $dem_{ab}$, $dem_{cd}$
+and $dem_{ef}$ be the traffic on each link. Without loss of generality, we say the link $l_{ab}$ is the 
+bottleneck, namely the link with MLUR.
+
+Now let's consider the robust routing. When the routing changes, the traffic on each link also changes.
+We image a simple situation, just forward the traffic from one link to another path base on the optimal
+routing, and the link utilization of links on the path will increase, and accordingly the link 
+utilization of former link will reduce to 0. Obviously, the routing must have a worse performance than 
+the optimal robust routing, so its upper bound also is the bound of minimum OPRE.
+
+\begin{figure}[!t]
+\centering
+\vspace*{0.1in}
+\subfloat[Circle]{\includegraphics[width=4cm]{circle}
+\label{subfiga}}
+\hfill
+\subfloat[Clique]{\includegraphics[width=4cm]{clique}
+\label{subfigb}}
+\caption{Circle and Clique topology of 6 nodes}
+\vspace*{0.1in}
+\end{figure}
+
+For Case \Rmnum{1}.\Rmnum{1}, the adjusted link may be $l_{cd}$, the new bottleneck still be $l_{ab}$. 
+The traffic on $l_{ab}$ is increased by the origin traffic on link $l_{cd}$, So we compute OPRE by:
+
+\begin{equation}
+\frac {\frac{dem_{ab} + dem_{cd}}{cap_{ab}}} {\frac{dem_{ab}}{cap_{ab}}} = 1 + \frac{dem_{cd}}{dem_{ab}}
+\end{equation}
+
+Because the old bottleneck is $l_{ab}$, so we have inequation:
+
+\begin{equation}
+\frac {dem_{cd}} {cap_{cd}} < \frac {dem_{ab}} {cap_{ab}}
+\end{equation}
+
+From Ineq. (14) we get:
+
+\begin{equation}
+\frac {dem_{cd}} {dem_{ab}} < \frac {cap_{cd}} {cap_{ab}}
+\end{equation}
+
+So we have OPRE in Case \Rmnum{1}.\Rmnum{1} combined by Eq. (13) and Ineq. (15):
+
+\begin{equation}
+1 + \frac {dem_{cd}} {dem_{ab}} < 1 + \frac {cap_{cd}} {cap_{ab}}
+\end{equation}
+
+For Case \Rmnum{1}.\Rmnum{2}, the adjusted link also be $l_{cd}$, but the new bottleneck may be $l_{ef}$.
+Computing the OPRE similar as above:
+
+\begin{equation}
+\frac {\frac{dem_{ef} + dem_{cd}}{cap_{ef}}} {\frac{dem_{ab}}{cap_{ab}}} = 
+\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac {dem_{cd} * cap_{ab}}{dem_{ab} * cap_{ef}}
+\end{equation}
+
+Because the old bottleneck is $l_{ab}$, so we have Ineq. (14) and :
+
+\begin{equation}
+\frac {dem_{ef}} {cap_{ef}} < \frac {dem_{ab}} {cap_{ab}}
+\end{equation}
+
+So we get inequation from Ineq. (18):
+
+\begin{equation}
+\frac {dem_{ef} * cap_{ab}} {dem_{ab} * cap_{ef}} < 1
+\end{equation}
+
+Also from Ineq. (14) we have :
+
+\begin{equation}
+\frac {dem_{cd} * cap_{ab}} {dem_{ab}} < cap_{cd}
+\end{equation}
+
+Combine Eq. (17), Ineq. (19) and Ineq. (20), we have OPRE in Case \Rmnum{1}.\Rmnum{2}:
+
+\begin{equation}
+\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac {dem_{cd} * cap_{ab}}{dem_{ab} * cap_{ef}} 
+< 1 + \frac {cap_{cd}}{cap_{ef}}
+\end{equation}
+
+For Case \Rmnum{2}.\Rmnum{1}, the adjusted link may be $l_{ab}$, namely the old bottleneck link, the new bottleneck
+maybe $l_{ef}$. Computing the OPRE similar as above:
+
+\begin{equation}
+\frac {\frac{dem_{ef} + dem_{ab}}{cap_{ef}}} {\frac{dem_{ab}}{cap_{ab}}} = 
+\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac{cap_{ab}}{cap_{ef}} 
+\end{equation}
+
+Becuase the old bottleneck has the maximum link utilization, so combine Ineq. (19) and Eq.(22) we obtain OPRE in Case 
+\Rmnum{2}.\Rmnum{1}:
+
+\begin{equation}
+\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac{cap_{ab}}{cap_{ef}} < 1 + \frac{cap_{ab}}{cap_{ef}}
+\end{equation}
+
+To sum up, we have inequation from Ineq. (16), Ineq. (21) and Ineq. (23):
+
+\begin{equation}
+1 + \max \{\frac{cap_{cd}}{cap_{ab}}, \frac{cap_{cd}}{cap_{ef}}, \frac{cap_{ab}}{cap_{ef}} \} < 1 + \frac{\max_{l \in E} cap_{l}}{\min_{l \in E} cap_{l}}
+\end{equation}
+
+\end{proof}
+
+\section{}
+\begin{proof}
+The spanning tree of circle is the topology which lose one link. In Appendix. A, when we consider the robust routing, we adjust the traffic 
+on one link to another path, it is similar that we switch off the link and forward the traffic to some other path. The complete proof is 
+almost the same with Appendix. A.
+\end{proof}
+
+\section{}
+\begin{proof}
+Every link in the spanning tree will split the graph to two components, the flow between them must need trace this link.
+we say the bottleneck link is $l_{ab}$ for optimal routing on the origin topology, and let $l_{ef}$ be the bottleneck link for 
+the robust routing on the spanning tree. Other symbols are consistent with Appendix. A. So we have OPRE:
+
+\begin{equation}
+    \frac{\frac{\sum_{(i,j) \in E} dem_{ij}}{cap_{ef}}}{\frac{dem_{ab}}{cap_{ab}}} = \frac{cap_{ab}}{cap_{ef}} \sum_{(i,j) \in E} \frac{dem_{ij}}{dem_{ab}}
+\end{equation}
+
+Because the $l_{ab}$ is the bottleneck link, we have:
+
+\begin{equation}
+    \frac{dem_{ij}}{cap_{ij}} < \frac{dem_{ab}}{cap_{ab}}, \forall (i,j) \in E
+\end{equation}
+
+\begin{equation}
+    \frac{dem_{ij} * cap_{ab}}{dem_{ab}} < cap_{ij}, \forall (i,j) \in E
+\end{equation}
+
+So we have OPRE:
+
+\begin{equation}
+    \frac{cap_{ab}}{cap_{ef}} \sum_{(i,j) \in E} \frac{dem_{ij}}{dem_{ab}} < \sum_{(i,j) \in E} \frac{cap_{ij}}{cap_{ef}}
+\end{equation}
+
+And we know that, the amount of $l_{ij}$ between two parts must less than $\frac{n^2}{2}$, so OPRE must lower than:
+
+\begin{equation}
+    \sum_{(i,j) \in E} \frac{cap_{ij}}{cap_{ef}} < \frac{n^2}{2} \frac{\max_{l \in E} cap_l}{\min_{l \in E} cap_l}
+\end{equation}
+
+\end{proof}
 

### 2015-02-01 experiment/cplex/len_path.py

@@ -11,9 +11,7 @@ result_file_template = "path_stretch_%s_%s.txt"
 
 line_list = []
 label_list = []
-#for t in ['geant']:
-#for t in ['abilene']:
-for t in ['geant']:
+for t in ['abilene']:
     for w in ['1.5', '2.5', '3.5']:
         f = open(result_file_template % (t, w))
         line = f.readline()
@@ -39,8 +37,8 @@ for t in ['geant']:
 
         #l1, = plt.plot(x[:topology_x_range[t]], m_mine[:topology_x_range[t]], color_type['new']+topology_line_type[t])
         #l2, = plt.plot(x[:topology_x_range[t]], m_base[:topology_x_range[t]], color_type['base']+topology_line_type[t])
-        l1, = plt.plot(x[:topology_x_range[t]], a_mine[:topology_x_range[t]], color_type['new']+topology_line_type[w], ms=8)
-        l2, = plt.plot(x[:topology_x_range[t]], a_base[:topology_x_range[t]], color_type['base']+topology_line_type[w], ms=8)
+        l1, = plt.plot(x[:topology_x_range[t]], a_mine[:topology_x_range[t]], color_type['new']+topology_line_type[w], ms=10)
+        l2, = plt.plot(x[:topology_x_range[t]], a_base[:topology_x_range[t]], color_type['base']+topology_line_type[w], ms=10)
 
         label_list.append(w + '-' + remove_type['base'])
         label_list.append(w + '-' + remove_type['new'])

### 2015-02-01 experiment/plot/exp1_power.py

@@ -1,4 +1,5 @@
 from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib.ticker import FormatStrFormatter
 import matplotlib.pyplot as plt
 import matplotlib.ticker as tic
 
@@ -24,7 +25,7 @@ power_model = [60, 100, 140, 174]
 line_list = []
 label_list = []
 #for t in ['abilene', 'geant', 'cernet2']:
-t = 'cernet2'
+t = 'abilene'
 for w in ['1.5', '2.5', '3.5']:
     # compute the total power of topology
     f = open(topology_file_template % t)
@@ -128,8 +129,8 @@ for w in ['1.5', '2.5', '3.5']:
 
     f.close()
 
-    l1, = ax1.plot(power_base_saving_ratio[:topology_x_range[t]], base[:topology_x_range[t]], color_type['base']+w_line_type[w], ms=8)
-    l2, = ax1.plot(power_saving_ratio[:topology_x_range[t]], new[:topology_x_range[t]], color_type['new']+w_line_type[w], ms=8)
+    l1, = ax1.plot(power_base_saving_ratio[:topology_x_range[t]], base[:topology_x_range[t]], color_type['base']+w_line_type[w], ms=10)
+    l2, = ax1.plot(power_saving_ratio[:topology_x_range[t]], new[:topology_x_range[t]], color_type['new']+w_line_type[w], ms=10)
 
     label_list.append(remove_type['base'] + '-' + w)
     label_list.append(remove_type['new'] + '-' + w)
@@ -138,19 +139,20 @@ for w in ['1.5', '2.5', '3.5']:
     line_list.append(l2)
 
 plt.xlabel('Power Saving Ratio (%)', fontsize=22)
-plt.ylabel('Oblivious Performance Ratio', fontsize=22)
+plt.ylabel('OPRE', fontsize=22)
 #plt.legend([l1, l2], ['TMP, w=1.5, 2.0, 2.5...', 'ERLU, w=1.5, 2.0, 2.5...'], loc=2)
 plt.legend(line_list, label_list, loc=2)
 
 ax1.set_yscale('log')
 ax1.set_ylim([1,y_lim[t]])
 ax1.get_yaxis().set_major_formatter(tic.ScalarFormatter())
+ax1.yaxis.set_minor_formatter(FormatStrFormatter("%0.1f"))
 
 pp = PdfPages('opr_with_power_%s.pdf' % t)
[…]

### 2015-02-01 experiment/plot/exp2_sort.py

@@ -35,7 +35,7 @@ for i in range(0, remove):
                 tmp = base[i][j]
                 base[i][j] = base[i][k]
                 base[i][k] = tmp
-    line1, = plt.plot(x, base[i], 'r--', ms=8)
+    line1, = plt.plot(base[i], x, 'r--', ms=8)
 
 line2 = None
 for i in range(0, remove):
@@ -45,18 +45,18 @@ for i in range(0, remove):
                 tmp = new[i][j]
                 new[i][j] = new[i][k]
                 new[i][k] = tmp
-    line2, = plt.plot(x, new[i], 'b-', ms=8)
+    line2, = plt.plot(new[i], x, 'b-', ms=8)
 
 #plt.axis([0, 6, 0, 20])
 
-plt.xlabel('Random Traffic Matrix (%)', fontsize=22)
-plt.ylabel('Oblivious Performance Ratio', fontsize=22)
-plt.legend([line1, line2], ['DMP', 'ERLU'], loc=2)
+plt.ylabel('CDF (%)', fontsize=22)
+plt.xlabel('OPRE', fontsize=22)
+plt.legend([line1, line2], ['DMP', 'ERLU'], loc=4)
 
 pp = PdfPages('exp2_sort_%s.pdf' % t)
 pp.savefig(fig1)
 pp.close()
 
-#plt.show()
+plt.show()
 #plt.savefig('exp2_sort_cernet2.png', bbox_inches='tight')
 

### 2015-02-04 paper_linheng_5.tex
add related work and ref

--- 2015-02-01 paper_linheng_4.tex
@@
 conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance
-ratio (OPR) with energy constraint, which reflects the MLUR distance from a routing to the optimal routing when
+ratio with energy constraint (OPRE), which reflects the MLUR distance from a routing to the optimal routing when
 certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio,
 and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve
-the problem in two phases. REAR select sleeping links based on extended robust link utilization (ERLU) or algebraic
-connectivity, and compute the routing based on a classical demand-oblivious routing algorithm.
+the problem in two phases. REAR select sleeping links based on extended robust link utilization (ERLU)
+and compute the routing based on a classical demand-oblivious routing algorithm.
 We evaluate our algorithms on real and synthetic topologies. The simulation results show that REAR can save
@@
 \section{Introduction}
+\label{introduction}
 
@@
 Thus, no matter how the traffic demand changes, the demand-oblivious routing can guarantee certain performance.
-We note that this conclusion is in a network without off/sleep components, and we need to consider the situation when energy conservation is required.
+We note that this conclusion is in a network without sleeping components, and we need to consider the situation when energy conservation is required.
 
@@
 Third, we need practical algorithms to compute the robust energy efficient routing.
-Specifically, we need to determine: 1) which routers or line cards should be switched into off/sleep mode, to achieve energy efficiency; and 2) in which path to forward the traffic for robustness, while the path does not traverse the off/sleep components.
+Specifically, we need to determine: 1) which routers or line cards should be switched into off/sleep mode, to achieve energy efficiency; and 2) in which path to forward the traffic for robustness, while the path does not traverse the sleeping components.
 
@@
 Then, we propose Robust Energy-Aware Routing (REAR) scheme, which uses heuristic algorithms to solve the problem.
-We develop algorithm XXX, which chooses off/sleep line cards in a way that the OPRE can be minimized potentially.
-We then develop algorithm XXX to compute the routing in the remaining topology, by extending existing optimal demand-oblivious routing algorithm.
+We develop algorithm RLP, which chooses sleeping line cards in a way that the OPRE can be minimized potentially.
+We then develop algorithm RRA to compute the routing in the remaining topology, by extending existing optimal demand-oblivious routing algorithm.
 We evaluate our algorithms by simulations on real topologies and synthetic traffic demands with random fluctuations.
@@
 The rest of the paper is organized as follows.
-Section \Rmnum{2} shows the related work.
-Section \Rmnum{3} presents metric OPRE and formally models the problem.
-We presents the bounds on OPRE in Section \Rmnum{4}, and propose our algorithms in Section \Rmnum{5}.
-Section \Rmnum{6} shows our simulation setup and results, and Section \Rmnum{7} concludes our work.
-
-\ignore{
-Usually, We compute routing to stipulate how is the traffic going, to achieve some traffic engineering goals such as
-the maximum link utilization ratio (MLUR). In details, we use traffic demands and network topology as input for
-computation, then combine routing and traffic demands to get the traffic on each link, based on which we determind
-which link can be put to sleep. However, measuring and predicting accurate traffic demands are difficult, so does its dynamic
-natrue. Although we have obtained all knowledge about traffic demands, the corresponding routing may shift frequently
-when the traffic demands change. It means that we should change the link (line cards) working mode frequently as well,
-of course it is unpractical. So we need the routing be robust to sudden traffic changes, and based on the approximate traffic demands.
-Such a routing is known as the demand-oblivious routing and is well studied in \cite{networking:oblivious}, which proposes
-the algorithm for computing robust routing with uncertain traffic demands on specific topology.
-
-Unfortunately, there is no metric in such robust routing to measure the importance of links, in another word, we have no
-idea to put which link to sleep mode. Furthermore, when some links are switched off and the topology changed actually, but we
-still have no idea for how to adjust the routing in result topology. Another challenge is that, to achieve the power saving
-goals we may should switch off not only one link, and it is a classical NP-Hard problem. To overcome the challenges,
-we define a metric namely extended robust link utilization (ERLU) to measure the traffic engineering natrue of link without real traffic
-demands, and define oblivious performance ratio (OPR) to reflect the MLUR distance from a routing to the optimal one
-when certain energy conservation requirement is satisfied. In our algorithm, we use algebraic connectivity \cite{networking:algebraic} and
-ERLU as criterion to switch off links, and use OPR to adjust routing.
-
-Our main contribution in this paper is three-fold. Firstly, we model the problem of minimizing the OPR, then
-analyze the lower and the upper bounds. Secondly, we propose an heuristic algorithm named Robust Energy-Aware Routing (REAR)
-to solve the problem in two phases, includes choosing links to sleep and adjusting routing. Thirdly, we implement our
-algorithm on real topology and arbitrary traffic demands to observe the relationship between energy conservation and OPR. The
-simulation results show that REAR can save 19\% power of line cards while OPR is less than 34\% in some topology. Also
-we investigate the path stretching problem.
-
-The rest of the paper is organized as follows. Section \Rmnum{2} reviews the related work and Section \Rmnum{3}
-defines two metric and models our problem. Following we propose our algorithm in Section \Rmnum{4}. For clearer understanding
-on our problem, we give two simple samples and prove the bounds in Section \Rmnum{5}. Experiments are discribed
-and result are showed in Section \Rmnum{6}. We discuss issues and future work in Section \Rmnum{7}, then conclude our wok in
-Section \Rmnum{8}}
+Section \ref{related_work} shows the related work.
+Section \ref{problem_statement} presents metric OPRE and formally models the problem.
+We presents the bounds on OPRE in Section \ref{upper_bounds_of_the_minimum_opre}, and propose our algorithms in Section \ref{robust_energy_aware_routing_algorithms}.
+Section \ref{performance_evaluation} shows our simulation setup and results, and Section \ref{conclusion} concludes our work.
 
 \section{Related Work}
-related work
+\label{related_work}
+Green routing is studied because we can not use as much of a resource as we need \cite{networking:designing}, such as line cards always work in full mode even with 
+low traffic fraction. So there are many studies to save energy consumption by put some links in sleep mode, for example GreenTE \cite{networking:greente} is 
+proposed for maximuming the sleeping links while $E^2$-MCRA \cite{networking:active} is proposed for minimizing the active links and nodes by a depth-first search approach.
+Besides these centralized algorithms, EAR \cite{networking:car} and GRiDA \cite{networking:grida} are proposed for distributed deployment, both of them are compatible 
+with OSPF sharing additional information between nodes. For addressing the problem of routing convergence when traffic changes frequently, GreenFRR 
+\cite{networking:greenfrr} is proposed by leveraging the technique of fast rerouting.
+
+Network may suffer from bad performance because of both frequent traffic demand and routing changes. There are studies to estimate traffic matrices in the context
+of Internet traffic, such as LP approach \cite{networking:lp}, Bayesian Infereence techniques \cite{networking:bayesian} and Time-Varying Network Tomography
+\cite{networking:time}. All the estimatation for traffic matrices result in the changes of routing, \cite{networking:minimize} proposed an oblivious routing algorithm with a polylog 
+competitive ratio with respect to congestion and \cite{networking:polynomial} give a polynomial time algorithm based on applying the Ellipsoid algorithm to an exponential-size LP model.
+To be practical for large networks, the oblivious-demand routing based on polynomial-size LP formulation is investigated in \cite{networking:oblivious}.
+
+In this paper, we proposed robust energy-aware routing based on the oblivious-demand \cite{networking:oblivious}, which is both green for the energy consumption by pruning
+some links based on ERLU, and also robust for uncertain traffic demands. It is more practical than existing green routing algorihtm because it almost do not need changes when 
+real traffic varifies.
 
 \section{Problem Statement}
+\label{problem_statement}
 
@@
 We have
+
 \begin{equation}
+\label{equation_U_rmG}
 	U_{r, m, G} = \max_{(i,j)\in E} \frac{\sum_{a,b} d_{ab}f^r_{ab}(i,j)}{cap_{ij}}.
 \end{equation}
+
 Let $P(\{ r \},\{ m \}, G)$ be the \emph{performance ratio} of routing $r$ under TM $m$, which reflects how far from the routing to the optimal one, and is defined as
 \begin{equation}
+\label{equation_P_rmG}
 	P(r,\{ m \}, G) = \frac{U_{r,m,G}}{\min_{r'} U_{r', m, G}}.
@@
 \begin{equation}
+\label{equation_P_rMG}
 	P(r, M, G) = \max_{m\in M} P(r, \{ m \}, G).
@@
 The intrinsic reason for such a ``fake robust'' is that the topology is not changing when performance ratio is computed in Eq.
-(2).
+(\ref{equation_P_rmG}).
 To address this issue, we extend the definition of OPR.
 Formally, let $G^*$ be a sub-graph of $G$ that satisfies the energy constraint (We will formally define the energy constraint in Section III.C, i.e., Eq.
-(8)).
-Note that in this case, a path cannot traverse a off/sleeping link, so routing $r$ is limited by $G^*$ (Eq.
-(7) in Section III.C).
+(\ref{inequation_power_threshold})).
+Note that in this case, a path cannot traverse a sleeping link, so routing $r$ is limited by $G^*$ (Eq.
+(\ref{equation_flow_for_routing}) in Section III.C).
 The extended performance ratio is defined as
 \begin{equation}
+\label{equation_P_rmGG}
 	P(r, \{ m \}, G, G^*) = \frac{U_{r,m,G^*}}{\min_{r'} U_{r', m, G}}.
 \end{equation}
-Let $P^*(r, M, G, G^*)$ be the \emph{oblivious performance ratio with energy constraint} (OPRE) for routing $r$. We define $P^*(r, M, G, G^*)$ by extending $m$ to $M$. Similar to Eq. (3), we have
+Let $P^*(r, M, G, G^*)$ be the \emph{oblivious performance ratio with energy constraint} (OPRE) for routing $r$.
+We define $P^*(r, M, G, G^*)$ by extending $m$ to $M$.
+Similar to Eq.
+(\ref{equation_P_rMG}), we have
 \begin{equation}
+\label{equation_P_rMGG}
 	P^*(r, M, G, G^*) = \max_{m\in M} P(r, \{ m \}, G, G^*).
@@
 When there is no energy constraint, $G^*$ equals $G$, and Eq.
-(5) naturally reduces to Eq.
-(3).
+(\ref{equation_P_rMGG}) naturally reduces to Eq.
+(\ref{equation_P_rMG}).
 
@@
 The network is shown in Fig.
-1, where two nodes $a, b$ are connected by two links $l_1$ and $l_2$.{\footnote{When there are parallel links, we can add a virtual node in each parallel link to keep $G(V,E)$ as a simple graph.}} The capacities of the links are 3 Mbps and 4 Mbps, respectively.
+\ref{figure_an_example_of_opre}, where two nodes $a, b$ are connected by two links $l_1$ and $l_2$.{\footnote{When there are parallel links, we can add a virtual node in each parallel link to keep $G(V,E)$ as a simple graph.}} The capacities of the links are 3 Mbps and 4 Mbps, respectively.
 To forward a traffic demand of $d_{ab}$, the optimal routing is to put $\frac{3}{7}d_{ab}$ on link $l_1$ and $\frac{4}{7}d_{ab}$ on link $l_2$, which results in the MLUR of $\frac{1}{7}d_{ab}$.
@@
 \centering
-\vspace*{0.1in}
-\includegraphics[width=6cm]{3-nodes-example}
-\caption{Model Example. There is traffic demand $d_{ab}$ from $a$ to $b$.}
-\label{label}
-\vspace*{0.1in}
+\includegraphics[width=1.3in]{3-nodes-example}
+\vspace{-0.15in}
+\caption{An example of the OPRE, where the traffic demand is $d_{ab}$.}
+\label{figure_an_example_of_opre}
 \end{figure}
@@
 \begin{equation}
+\label{equation_flow_for_routing_second}
     \begin{split}
@@
 \begin{equation}
+\label{equation_flow_for_routing}
     \begin{split}
@@
 \begin{equation}
+\label{inequation_traffic_fraction}
     0 \leq f^r_{ab}(i,j),f^{r'}_{ab}(i,j) \leq 1
@@
 \begin{equation}
+\label{inequation_power_threshold}
     \sum_{l \in E^*} p(l) / \sum_{l \in E} p(l) \leq 1 - \theta
@@
 
-Constraints (1), (4), and (5) follow our definition of the OPRE.
+Constraints (\ref{equation_U_rmG}), (\ref{equation_P_rmGG}), and (\ref{equation_P_rMGG}) follow our definition of the OPRE.
 Eq.
-(6) means that the optimal routing $r'$ in $G$ must be a valid routing, i.e.
+(\ref{equation_flow_for_routing_second}) means that the optimal routing $r'$ in $G$ must be a valid routing, i.e.
 with routing consistency.
@@
 Similarly, Eq.
-(7) means that the robust routing $r$ in $G^*$ must be a valid routing.
+(\ref{equation_flow_for_routing}) means that the robust routing $r$ in $G^*$ must be a valid routing.
 Ineq.
-(8) means that the range of $f^r_{ab}(i,j)$ and $f^{r'}_{ab}(i,j)$ is from 0 to 1.
+(\ref{inequation_traffic_fraction}) means that the range of $f^r_{ab}(i,j)$ and $f^{r'}_{ab}(i,j)$ is from 0 to 1.
 Ineq.
-(9) means that the power consumption of links in $G^*$ must be less than a given threshold.
+(\ref{inequation_power_threshold}) means that the power consumption of links in $G^*$ must be less than a given threshold.
 In Ineq.
-(9), $\theta$ denotes the power saving ratio we must achieve by using $G^*$.
+(\ref{inequation_power_threshold}), $\theta$ denotes the power saving ratio we must achieve by using $G^*$.
 Here, we use $p(l)$ to denote the power consumption of link $l$, which is mainly drawn by the line cards at the two ends of the link.
@@
 Note that if $G^* = G$ satisfy the energy constraint Ineq.
-(9) and $M$ is the set of all TMs, the Min-OPRE problem reduces to the demand-oblivious routing problem, and can be transformed into a linear program and solved in polynomial time \cite{networking:oblivious}.
+(\ref{inequation_power_threshold}) and $M$ is the set of all TMs, the Min-OPRE problem reduces to the demand-oblivious routing problem, and can be transformed into a linear program and solved in polynomial time \cite{networking:oblivious}.
 However, we must find the optimal $G^*$ to achieve the required power saving ratio in other cases, and Min-OPRE is an MILP and is NP-hard in general.
@@
 \section{Upper Bounds of the Minimum OPRE}
+\label{upper_bounds_of_the_minimum_opre}
 
@@
 
-Theorem 2 shows the minimum OPRE when $\theta = 0$ and all link capacities are the same. In a more general case when there are different link capacities, we have
+Theorem 2 shows the minimum OPRE when $\theta$ equals 0 and all link capacities are the same. In a more general case when there are different link capacities, we have
 
 \begin{theorem}
-The upper bound of the minimum OPRE for a cycle on $n$ nodes is $1 + \frac{\max cap_{ij}}{\min cap_{ij}}$ if $\theta = 0$.
+The upper bound of the minimum OPRE for a cycle/complete graph on $n$ nodes is $1 + \frac{\max cap_{ij}}{\min cap_{ij}}$ if $\theta = 0$.
 \end{theorem}
@@
 
-\begin{theorem}
-The upper bound of the minimum OPRE for a complete graph on $n$ nodes is $1 + \frac{\max cap_{ij}}{\min cap_{ij}}$ if $\theta = 0$.
-\end{theorem}
-\begin{proof}
-See Appendix A.
-\end{proof}
-
-Theorem 3 and Theorem 4 tell us that the minimum OPRE is related to the link capacity difference in the network.
+Theorem 3 tells us that the minimum OPRE is related to the link capacity difference in the network.
 The above results are for $\theta = 0$.
 Now let us see the results for a large $\theta$.
-Since there is not much difference between the power consumptions for links with different capacities \cite{}, we consider the spanning trees of a graph, which can achieve a near-optimal $\theta$.
+Since there is not much difference between the power consumptions for links with different capacities \cite{networking:hopbyhop}, we consider the spanning trees of a graph, which can achieve a near-optimal $\theta$.
 We have
@@
 
-Theorem 5 and Theorem 6 present a large gap between the OPRE upper bounds in the two types of networks, because when $G^*$ is a spanning tree, more links are pruned in the complete graph.
+Theorem 4 and Theorem 5 present a large gap between the OPRE upper bounds in the two types of networks, because when $G^*$ is a spanning tree, more links are pruned in the complete graph.
 This implies that in order to achieve more energy conservation, the OPRE may become larger quickly, and the routing becomes less robust, in the worst case.
@@
 \section{Robust Energy-Aware Routing Algorithms}
+\label{robust_energy_aware_routing_algorithms}
 
-In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links
-should be put to sleep from the origin topology based on extended robust link utilization (ERLU),
-then compute the robust routing based on demand-oblivious routing algorithm.
+In this section, we present our REAR approach to solve the Min-OPRE problem.
+We first develop the robust link pruning (RLP) algorithm.
+RLP selects sleeping links that we will prune from the topology, to achieve the required power saving ratio and potentially reduce the OPRE.
+Then, we develop the robust routing adjustment (RRA) algorithm.
+RRA adjusts the demand-oblivious routing that has the minimum OPR, to detour the traffic around the sleeping links.
 
-\subsection{Extended Robust Link Utilization}
-The demand-oblivious routing is not always the best one for specific $TM$, but good enough for a range of $TM$.
-we mentioned the definition of link utilization above when demand and routing are determined, as demand become
-oblivious, the definition is also not suitable. So we define a notation named extended robust link utilization (ERLU)
-replace the normal link utilization like :
+\subsection{Algorithm RLP}
 
+Several heuristics have been proposed to select sleeping links without the knowledge of a specific TM, with various considerations \cite{}\cite{}\cite{}.
+However, we need a algorithm that can potentially minimize the OPRE.
+To this end, we first find the demand-oblivious routing that minimizes the OPR, using the linear programming approach in \cite{networking:oblivious}.
+Bases on the routing, we define the extended robust link utilization (ERLU), to evaluate the contribution of a link to the OPRE.
+
+Intuitively, a link is less preferred to be pruned if there are more flows traversing the link.
+Though we are not aware of the TM, the traffic volume is likely to fluctuate largely if there are many flows.
+This means that if we prune this link, these flows have to be carried by other links in the network, and the OPRE may increase largely.
+On the other hand, a link is less preferred to be pruned if the link has a less capacity.
+This is because in the optimal demand-oblivious routing where the OPR is minimized, such a link is not likely to be heavy-loaded, and we should keep the link to maintain the robustness.
+Formally, let $r_0$ be the optimal demand-oblivious routing, and $u^e_{ij}$ be the ERLU of link $(i, j)$, we have
 \begin{equation}
-	u^e_{ij} = \frac {\sum_{a,b}f_{ab}(i,j)} {cap_{ij}}
+\label{equation_u_eijr}
+	u^e_{ij}(r_0) = \frac {\sum_{a,b}f^{r_0}_{ab}(i,j)} {cap_{ij}}
 \end{equation}
 
-Proposing this definition for two consideration: firstly, the more flows across the link, the greater the $u^e_{ij}$ is;
-secondly, the more fraction of one flow across the link, the greater the $u^e_{ij}$ is. The link with greater
-ERLU is also more important than others in a sense. Although there is no demand here, we mean
-there is more probability that this link have greater link utilization when specific demand come.
-
-\subsection{Algorithm Phase One}
-REAR sleep as many links as possible without losing connectivity of graph.
-Originly,  we should calculate ERLU of all the links and sleep the lowest one from the graph, then repeat calculate and remove
-process until arrive some specific threhold. Obviously, it is NP-Hard, following is a heuristic algorithm.
-
-For the origin graph, we calculate the ERLU of every link, and then sort these values
-from small to big, output ordered list denoted as $\Gamma$:
-\begin{equation}
-	\Gamma = \{..., l_i, ..., l_j, ...\}
-\end{equation}
-where $u^e_{l_i} < u^e_{l_j}$.
-
-Pay attention we only compute the ERLU once at the begining of algorihtm, and the ordered list $\Gamma$ show
-the order of `importance' among links in the graph.
-
-Now we begin selecting which link should be sleep.
-We denote the set of the sleeping links as $S$, and the output of this phase is final graph $G^* = (V, E-S)$. We set
-$S = \emptyset$, and repeat our selecting process, each iteration we select one link, remove it from $\Gamma$ and put it into $S$.
-In iteration $i$, algorithm scan links as the order in $\Gamma$, we try to
-remove this link from the graph to check if the graph is still connected and the energy conservation have not arrive the threshold.
-If so, we select it then go next iteration.
-Otherwise choose the next link from $\Gamma$ for trying to remove. Algorithm
-stop until all the links in $\Gamma$ is tried but no one is satisfied with both connectivity and power threhold.
-
-But before going ahead our algorithm, there is another thing we should care, how to measure the power of graph.
-We simple take an power model from \cite{networking:greente} showed in Table \Rmnum{2}, and defined the difference of power consumption
-between two graphs as:
-\begin{equation}
-	diff_p = 1 - \theta = \frac{\rho(G_{S, l}^o)} {\rho(G^o)} * 100
-\end{equation}
-where $\rho(G_{S, l}^o)$ is the power consumption of the final graph, when the links set $S$ and
-link $l$ are both removed from the origin graph $G^o$, and the $\rho(G^o)$ is the power consumption of
-the origin graph.
-
-If we set $diff_p$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in
-iteration, the power consumption should never lower than the 90\% of origin one. Following is our implementation:
+With the ERLU, we iteratively select the link with the smallest ERLU as the sleeping link.
+If the topology after pruning the selected link is not connected, we pass the link and continue to search.
+We stop the process once we have sufficient sleeping links to achieve the required power saving ratio.
+We develop the RLP algorithm.
 
@@
 \hline
-\textbf{Algorithm REAR : Phase One}\\
+\textbf{Algorithm RLP()}\\
 \hline
-$\:\:$\textbf{Input:} $G(V, E)$, $threhold$;\\
-$\:\:$\textbf{Output:} $S$ in which links should be switched off;\\
-$\quad\qquad\quad$ $G(V, E-S)$ which is the final network topology;\\
-$\:\:$1:\ \textbf{for} {each link $l$ in $E$}\\
-$\:\:$2:\quad\ $\Gamma[l] \leftarrow u^e_l$;\\
-$\:\:$3:\ Resort $\Gamma$ in increasing order based on $u^e_l$;\\
-$\:\:$4:\ $S \leftarrow \emptyset$, $goon \leftarrow true$;\\
+$\:\:$\textbf{Input:} $G(V, E)$, $\theta$;\\
+$\:\:$\textbf{Output:} the set of sleeping links $S$;\\
+$\:\:$1:\ $r_0 \leftarrow$ the optimal demand-oblivious routing \cite{networking:oblivious} on $G$;\\
+$\:\:$2:\ \textbf{for} each link $l$ in E\\
+$\:\:$3:\quad\ compute ERLU $u^e_l(r_0)$, using Eq. (\ref{equation_u_eijr});\\
+$\:\:$4:\ $S \leftarrow \emptyset$; $goon \leftarrow \textrm{true}$;\\
 $\:\:$5:\ \textbf{while} {$goon$}\\
-$\:\:$6:\quad\  $goon \leftarrow false$;\\
-$\:\:$7:\quad\ \textbf{for} {each link $l$ in $\Gamma - S$}\\
-$\:\:$8:\quad\ \quad\ \textbf{if} $G_{S,l}$ is connected and $\rho(G_{S,l})/\rho(G)>threhold$\\
-$\:\:$9:\quad\ \quad\ \quad\ $S \leftarrow S \cup \{l\}$;\\
-$\:\:$10:\quad\ \quad\ \quad\ $goon \leftarrow true$;\\
-$\:\:$11:\quad\ \quad\ \quad\ \textbf{break};\\
-$\:\:$12:\ \textbf{return} $S, G(V, E-S)$;\\
+$\:\:$6:\quad\ $goon \leftarrow \textrm{false}$;\\
+$\:\:$7:\quad\ \textbf{for} {each link $l$ in $E-S$ with increasing order based on $u^e_l(r_0)$}\\
+$\:\:$8:\quad\ \quad\ $G^* \leftarrow (V, E^* = E-S-\{l\})$;\\
+$\:\:$9:\quad\ \quad\ \textbf{if} {$G^*$ is connected and $\sum_{l' \in E^*} p(l') / \sum_{l' \in E} p(l') > 1 - \theta$}\\
+$\:\:$10:\quad\ \quad\ \quad\ $S \leftarrow S \cup \{l\}$;\\
+$\:\:$11:\quad\ \quad\ \quad\ $goon \leftarrow \textrm{true}$;\\
+$\:\:$12:\quad\ \quad\ \quad\ \textbf{break};\\
+$\:\:$13:\ \textbf{return} $S$;\\
 \hline
@@
 
-\subsection{Algorihtm Phase Two}
-Once we get the output network topology from the first phase, it is time to compute
-the robust routing. On one hand, computation process may cost too much time if we directly calculate the robust routing in
-the final graph; on the other hand, the robust routing based on the final graph may not be the best one.
-There is a heuristic algorithm
-based on the demand-oblivious routing on the origin graph, which should be obtained at first.
-then adjust routing in details according to the links we switched off.
+The inputs of RLP include graph $G(V, E)$ and required power saving ratio $\theta$, and the output is the sleeping link set $S$.
+The ERLU of each link is computed in Steps 1 to 3.
+$S$ is initialized to be empty (Step 4).
+In each iteration of the outer loop (Steps 5 to 12), a feasible sleeping link is selected (Steps 7 to 12).
+If a feasible sleeping link is found and the power saving ratio is not achieved yet (Step 9), the selected link is added into set $S$ (Step 10), binary variable $goon$ will be true (Step 11), and the process continues (Step 12).
+Or else, binary variable $goon$ will remain false (Step 6), and the algorithm ends.
+The computation complexity of the RLP algorithm is $O(LP + |E||V|^2 + (|E|-|V|)|V||E|\log|E|)$ in the worst case, where $O(LP)$ is for solving the linear programming in \cite{networking:oblivious}, $O(|E||V|^2)$ is for computing the ERLU, $O(|E|-|V|)$ is the maximum number of sleeping links, and $O(|V||E|\log|E|)$ is for the connectivity check and the sleeping link search.
 
-The demand-oblivious routing can be computed by a single LP with $O(mn^2)$ variables and $O(nm^2)$ constraints[1] :
+\subsection{Algorithm RRA}
+
+After pruning the links, we get graph $G^*$ (if exists) that satisfies the energy conservation requirement.
+Now we should compute the robust routing that minimizes the OPRE.
+Note that we cannot simply apply the algorithm in \cite{networking:oblivious} on $G^*$, because the algorithm minimizes OPR but not OPRE.
+We observe that the optimal demand-oblivious routing $r_0$ minimizes the OPR in $G$, and minimizes OPRE when $G^* = G$ according to Theorem 2.
+Thus, to obtain a robust routing in $G^*$, we take a heuristic that adjusts routing $r_0$ to detour the traffic around the sleeping links in $G^*$.
+
+Note that there may be multiple paths in $r_0$ between a source-destination pair.
+We first decompose the paths by a standard procedure given in \cite{}.
+Formally, let $p^h_{ab}$ denote the $h$-th path between nodes $a$ and $b$, and $t^h_{ab}$ be the fraction of the traffic that is routed on $p^h_{ab}$.
+For each $p^h_{ab}$ that traverses a sleeping link, we must find some detour paths to absorb $t^h_{ab}$.
+Such detour paths should not increase the OPRE too much.
+Recall that ERLU $u^e_{ij}(r)$ reflects the link utilization ratio without the knowledge of the TM, under routing $r$.
+Thus, we prefer a path whose maximum $u^e_{ij}(r)$ is small.
+On the other hand, the detour paths should not be too long, in order to limit the path stretch.
+To this end, we use YEN's algorithm \cite{networking:yens} to compute the $k$-th shortest path in graph $G^*$.
+We develop Algorithm RRA.
+
 \begin{table}[!th]
 \begin{tabular}{ll}
-$\:\:$\quad\quad\quad\quad\ \textbf{min} $r$ \\
-$\:\:$\quad\quad\quad\quad\ $f_{ij}(e)$ is a routing \\
-$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$: $\sum_m cap(m)t(l,m) \le r$ \\
-$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$, $\forall$ pairs $i \rightarrow j$: \\
-$\:\:$\quad\quad\quad\quad\quad\quad\ $f_{ij}(l)/cap(l) \le p_l(i,j)$ \\
-$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $\forall$ edges $e = j \rightarrow k$: \\
-$\:\:$\quad\quad\quad\quad\quad\quad\ $\pi(l, link-of(e)) + p_l(i,j) - p_l(i,k) \ge 0$ \\
-$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$, $m$: $\pi(l, m) \ge 0$ \\
-$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$: $p_l(i,i) = 0$ \\
-$\:\:$\quad\quad\quad\quad\ $\forall$ links $l$, $\forall$ nodes $i$, $j$: $p_l(i,j) \ge 0$ \\
+\hline
+\textbf{Algorithm RRA()}\\
+\hline
+$\:\:$\textbf{Input:} $G(V,E)$, sleeping link set $S$,\\
+$\quad\quad\ \ \ $ optimal demand-oblivious routing $r_0$, $N$;\\
+$\:\:$\textbf{Output:} robust energy-aware routing $r$;\\
+$\:\:$\ 1:\ $G^* \leftarrow G(V, E-S)$; $r \leftarrow r_0$;\\
+$\:\:$\ 2:\ \textbf{for} {each link $l$ in $S$}\\
+$\:\:$\ 3:\quad\ \textbf{for} {each $s, d \in V$}\\
+$\:\:$\ 4:\quad\ \quad\ $t \leftarrow f^r_{sd}(l)$;\\
+$\:\:$\ 5:\quad\ \quad\ $paths \leftarrow$ the extracted paths for $s, d$;\\
+$\:\:$\ 6:\quad\ \quad\ \textbf{for} {each path $p^h_{sd} \in paths$}\\
+$\:\:$\ 7:\quad\ \quad\ \quad\ \textbf{if} {$l \in path$}\\
+$\:\:$\ 8:\quad\ \quad\ \quad\ \quad\ $paths$.remove($p^h_{sd}$); \\
+$\:\:$\ 9:\quad\ \quad\ $yen\_paths \leftarrow$ yens\_algorithm($G^*$, $s$, $d$);\\
+$\:\:$10:\quad\ \quad\ \textbf{for} {$counter = 1$ to $N$}\\
+$\:\:$11:\quad\ \quad\ \quad\ compute $u^e_{ij}(r)$;\\
+$\:\:$12:\quad\ \quad\ \quad\ $p \leftarrow$ the path in $yen\_paths$ with the min. $\max_{ij} u^e_{ij}(r)$;\\
+$\:\:$13:\quad\ \quad\ \quad\ $p.fraction = t / N$;\\
+$\:\:$14:\quad\ \quad\ \quad\ $paths$.add($p$);\\
+$\:\:$15:\quad\ \quad\ $r \leftarrow paths$.merge();\\
+$\:\:$16:\ \textbf{return} $r$;\\
+\hline
 \end{tabular}
@@
 
-where the $cap(l)$ is the capacity of link $l$;
-and $\pi(l,m)$ is the weights for every pair of links $l$, $m$; and the variables $p_l(i,j)$ for each link $l$
-and OD pair $i$, $j$ is the length of the shortest path from $i$ to $j$ according to the link weights $\pi(l, m)$.
-
-The routing we get indicate how to arrive at destination node from source node for every OD pair in the origin topology.
-What is different is that, the flow can be splited in the routing, i.e. there may be two paths ($path_1$, $path_2$)
-both from source node $s$ to destination node $d$, and the optimal obilious routing trace 70\% traffic on
-$path_1$ and left on $path_2$. Although splitting flow is hard handled, we take a transformation for the case like that:
-when an flow is coming, there is 70\% probability we trace it on $path_1$, otherwise $path_2$. This is easily implementated
-in real world.
-
-Because all the routing is based on the origin topology, when some links are switched off, we must adjust the routing
-as well. Supposed there are some paths between two vertices $s$ and $d$, maybe one link in some paths be removed,
-and these paths become not reachable any more, we should adjust the traffic in these paths to other paths. Of course,
-we can not put the whole traffic on another path, this will make some links of the path congested, so we should split the traffic
-to some paths `averagely`, in the sense of extended robust link utilization. Similarly to link utilization, we define the extended
-robust link utilization as the maximum extended robust link utilization of links.
-
-Take pair $(s, d)$ for example, routing includes paths from $s$ to $d$, such as $p_1, p_2, ... , p_n$. While only $p_1$ trace
-the removed link, and of course it will be unreachable. We split the traffic of $p_1$, and put them on other paths to make
-the extend robust link utilization of paths almost closely.
-
-And this is our implementation:
-\begin{table}[!th]
-\begin{tabular}{ll}
-\hline
-\textbf{Algorithm REAR : Phase Two}\\
-\hline
-$\:\:$\textbf{Input:} $G(V,E)$ which is the origin topology;\\
-$\quad\quad\ \ \ $ $S$ which is the switch-off links set generated by Phase One;\\
-$\quad\quad\ \ \ $ $R$ which is the Robust Routing on origin topology;\\
-$\:\:$\textbf{Output:} $Routing$ Robust Energy-Aware Routing on new topology\\
-$\:\:$\ 1:\ $G^* \leftarrow G(V, E-S)$;\\
-$\:\:$\ 2:\ \textbf{for} {each link $l$ in $S$}\\
-$\:\:$\ 3:\quad\ \textbf{for} {each $s,d,paths$ in $R$}\\
-$\:\:$\ 4:\quad\ \quad\ $traffic \leftarrow$ 0;\\
-$\:\:$\ 5:\quad\ \quad\ \textbf{for} {each $path$ in $paths$}\\
-$\:\:$\ 6:\quad\ \quad\ \quad\ \textbf{if} {$link$ in $path$}\\
-$\:\:$\ 7:\quad\ \quad\ \quad\ \quad\ $traffic \leftarrow$ $traffic$ + $path$.$traffic$; \\
-$\:\:$\ 8:\quad\ \quad\ \quad\ \quad\ $paths$.remove($path$); \\
-$\:\:$\ 9:\quad\ \quad\ $yen\_paths \leftarrow$ yens\_algorithm($G^*$, $s$,$d$);\\
-$\:\:$10:\quad\ \quad\ \textbf{while} {$traffic$ != 0}\\
-$\:\:$11:\quad\ \quad\ \quad\ sort\_paths\_by\_extend\_robust\_link\_utilization($yen\_paths$)\\
-$\:\:$12:\quad\ \quad\ \quad\ $yen\_paths$[0].$traffic$ = $traffic$ / N\\
-$\:\:$13:\quad\ \quad\ \quad\ $traffic$ = $traffic$ - $traffic$ / N\\
-$\:\:$14:\quad\ \quad\ \quad\ $paths$.add($yen\_paths$[0])\\
-$\:\:$15:\quad\ \quad\ $paths$.merge();\\
-$\:\:$16:\ \textbf{return} $R$;\\
-\hline
-\end{tabular}
-\end{table}
+The inputs of RRA include graph $G(V,E)$, sleeping link set $S$, optimal demand-oblivious routing $r_0$ in $G$, and $N$ which will be used latter.
+The output is the robust energy efficient routing $r$.
+$G^*$ and $r$ are initialized in Step 1.
+The main loop from Step 2 to Step 14 finds the detour paths for each sleeping link in $S$, and for each source-destination pair.
+The traffic fraction that should be detoured is denoted by $t$ (Step 4), and the original paths are extracted and removed from routing $r$ (Steps 5 to 8).
+Then, the $k$-th shortest paths are computed in Step 9.
+The traffic fraction of $t$ is detoured by $N$ times evenly (Steps 10 to 14), and the detour path with the minimum value of the ERLU is selected (Steps 11 and 12).
+In Step 15, the duplicate paths are merges and new routing $r$ that does not traverse link $l$ is obtained.
+The computation complexity of the RRA algorithm is
+$O((|E|-|V|)|V|^2(|R||E| + K|V|(|E| + |V|\log|V|) + N(|E||V|^2 + K|E|) + |R||E|))$ in the worst case, where $O(|E|-|V|)$ is the maximum number of sleeping links, $O(|V|^2)$ is the maximum
+number of OD pairs, $O(|R||E|)$ is for computing detoured traffic and remove failed paths where $O(|R|)$ is the number of input routings, $O(K|V|(|E| + |V|\log|V|))$ is for solving the 
+yens algorithm where $K$ is the number of shortest paths, $O(N(|E||V|^2 + K|E|))$ is for detouring traffic fraction by $N$ times, and $O(|R||E|)$ is for merging routings.
 
@@
 \subfloat{\includegraphics[width=6cm]{opr_with_power_cernet2}}
-\caption{OPRE versus Power Saving: (1). Abilene, (b). Geant, (c). Cernet2}
+\caption{OPRE versus TMs: (a). Abilene, (b). Geant, (c). Cernet2}
+\label{figure_opr_with_power}
 \vspace*{0.1in}
@@
 \subfloat{\includegraphics[width=6cm]{exp2_sort_cernet2}}
-\caption{OPRE versus TMs: (a). Abilene, (b). Geant, (c). Cernet2}
+\caption{OPRE versus Power Saving: (a). Abilene with 4 links removed (b). Geant with 6 links removed (c). Cernet2 with 2 links removed}
+\label{figure_exp2_sort}
 \vspace*{0.1in}
@@
 
-\section{Experiments and Results}
-We simulated our algorithm on real world topology, including Abilene, Geant and Cernet2, whose number of nodes and links are listed in Table \Rmnum{1}.
-Then we generate random traffic matrix with Gravity Model \cite{networking:gravity}, which assume that the traffic demand between nodes is proportional
-to their combined capacity of connecting links. To extrapolate a complete TM, we take an attribute margin $w$ to scale the traffic range from $1/w$ to $w$
-base on the basic traffic demand. Particularly, when the $w$ limit extremity, we say the traffic matrix is really arbitrary, and our
-algorithm is irrelevant with traffic.
+\section{Performance Evaluation}
+\label{performance_evaluation}
 
-\begin{table}[!t]
+We evaluate the REAR approach by simulations on three real-world network topologies, including Abilene \cite{networking:abilene}, Geant \cite{networking:geant}, and CERNET2 \cite{networking:cernet2}.
+The numbers of nodes and links of the topologies are listed in Table \ref{table_topology}.
+The traffic matrices we used in our simulations are generated as follows.
+We first generate a baseline traffic matrix using the gravity model \cite{networking:gravity}, where the baseline traffic demand $d_{ab}$ is proportional to their total capacity.
+Then, the traffic demand is generated randomly in the range from $d_{ab}/\omega$ to $d_{ab}\omega$, where $\omega \geq 1$ is a margin factor used to control the fluctuation range of the traffic.
+We generate 1000 random TMs for each topology with each $\omega$.
+The power consumption of different line cards is set as constant in the simulations, as shown in Table \ref{table_line_card_power_consumption}, following \cite{networking:greente}.
+
+\begin{table}[h]
+\label{table_topology}
 \renewcommand{\arraystretch}{1}
@@
 
-\begin{figure*}[!t]
-\centering
-\vspace*{0.1in}
-\subfloat{\includegraphics[width=6cm]{exp4_path_abilene}}
-\subfloat{\includegraphics[width=6cm]{exp4_path_geant}}
-\subfloat{\includegraphics[width=6cm]{exp4_path_cernet2}}
-\caption{Path Stretching: (a). Abilene, (b). Geant, (c). Cernet2}
-\vspace*{0.1in}
-\end{figure*}
+For comparison, we simulate a recent energy efficient routing approach, namely DMP \cite{networking:dmp}, which also does not use the TMs as inputs.
+DMP always selects the most power-hungry links to switch into off/sleep mode, and can achieve a large power saving ratio, but does not consider routing robustness.
+We evaluate the OPRE and its distribution, the power saving ratio, and the path stretch of the approaches.
 
-\subsection{OPRE versus Power Saving}
-In Figure 3, we see that the value of OPRE is at least 1 for all topologies even no links removed, particularly in Geant the value is 1.24,
-it means the robust routing always not be the optimal for all TMs. It is reasonable because our robust routing is used for a range of traffic
-rather than a specific TM.
-
-When we switch off links, the topology lose connectivity and some routing paths will be failed, traffic on those paths will be
-adjusted to others, which result in the value of OPRE increased. We take margin from 1.5 to 3.5 and observe this phenomena from Figure.
-Pay attention that we scale the y-axis as logarithm for comparing DMP and ERLU in one figure. Intuitively, we can see ERLU is always
-better than DMP whatever margin or power saving target is, because ERLU consider much more than DMP, such as capacity and robust traffic
-flows. Another information from Figure 4 is that, we should carefully set the value of power saving for avoiding removing too much
-links, which result in the OPRE increases rapidly, induce network congestions easily and make the robust routing be less `robust'.
-
-we concern more about how is the OPRE varifying when achived specific power saving target. Obviously, the more links we removed,
-the more power we saved, but how to quantify the power of one link is difficult. Green TE proposed a simple power model \cite{networking:greente},
-which can be represented in Table \Rmnum{2}. In which, the total energy of topology is dominant by line cards of routers or switches,
-when saying switch off the links we mean put down the according line cards.
-
-\begin{table}[!t]
+\begin{table}[h]
+\label{table_line_card_power_consumption}
 \renewcommand{\arraystretch}{1}
-\caption{Green TE Power Model}
+\caption{Line Card Power Consumption}
 \label{power model}
@@
 
-We compute the power saving ratio as the total power of the removed links over the total power of all the links.
-In Figure 3 (a), it shows we can save 19\% energy only with an OPRE of 1.30 in Abilene topology, and in Geant and Cernet2,
-the OPRE is little higher. Curves present some scalariform, it means that in some range of power saving, the OPRE rise slowly,
-and in the end of range, the energy conservation is efficient.
+\begin{figure*}[!t]
+\centering
+\vspace*{0.1in}
+\subfloat{\includegraphics[width=6cm]{exp4_path_abilene}}
+\subfloat{\includegraphics[width=6cm]{exp4_path_geant}}
+\subfloat{\includegraphics[width=6cm]{exp4_path_cernet2}}
+\caption{Path Stretching: (a). Abilene, (b). Geant, (c). Cernet2}
+\label{figure_exp4_path}
+\vspace*{0.1in}
+\end{figure*}
+
+\subsection{OPRE versus Power Saving}
+Fig. \ref{figure_opr_with_power} (a) shows the OPRE as a function of power saving ratio $\theta$, in the Abilene topology. We see that the OPRE increases when more power is saved.
+This is not surprising because the routing becomes less robust when more links are switched into off/sleep mode. Our REAR has an OPRE ranging from 
+1.06 to 2.32, which is much less than the results of DMP. This is because REAR takes routing robustness into consideration when it prunes 
+links and computes routing. For instance, when $\omega = 3.5$ and 25\% power is saved, the OPRE of REAR is 2.32, while the OPRE of DMP is 5.09. 
+This implies that REAR is more robust against traffic uncertainty. We also see that a larger $\omega$ results in a larger OPRE, because 
+the traffic volume fluctuates in a wider range. For instance, when $\omega$ increases from 1.5 to 3.5, the OPRE of REAR increases about 
+0.17, while the OPRE of DMP increases about 0.53.
+
+Similar results are showed in Fig. \ref{figure_opr_with_power} (b) and (c), namely in Geant and Cernet2 topology. In Geant, we see that OPRE sacle with a wider range both
+in DMP and REAR, it is because Geant is much larger than other topologies, when removing too much links, the network will suffer from more 
+serious congestion. In Cernet2, Although REAR is better than DMP, the difference is marginal when achieved a large $\theta$. It can be explained
+by the density of links, REAR obtains a better performance in dense topology because it will have more choices.
 
 \subsection{OPRE versus Margin}
-We take the margin $w$ as one of the input for computing robust routing, and margin identify a range of TMs the routing is
-robust for. Once the $w$ limit extremely, our robust routing is said without knowledge of traffic matrix. Figure 3 shows the
-OPRE increases little as $w$ increases, particularly in Geant, the difference almost can not be observed. It is obvious because
-when the $w$ is greater, the traffic matrix is random in more wider range, and our OPRE may achieve worse case with more probability.
+Fig. \ref{figure_exp2_sort} (a) shows the amount of TMs as a cumulative distribution function (CDF) of OPRE, when remove 4 links in Abilene topology. We see that the curves of
+DMP are right of REAR, means REAR always have lower OPRE whatever TMs is. It is consistent with Fig. \ref{figure_opr_with_power} (a). We also observe that our REAR has
+more concentrated curves, means REAR have the almost same performance when TM changes, it is because REAR remove the less `important' link from 
+topology and the left topology is more robust for TMs than DMP. For instance, REAR ranges from 1.74 to 2.32 while DMP range from 2.97 to 5.09 
+when $\omega = 3.5$. Also we can see that curve become smooth when $\omega$ increases, it is because the TMs range from wider scope, and the OPRE
+may achieved wider scope too. However we see that whatever $\omega$ is, the center of the curve are almost the same postion. It is because 
+we only change the margin $\omega$ rather than the base TM, so the medial value will not changes apparently.
 
-\subsection{OPRE versus TMs}
-To simulate the worst case, we generate 1000 traffic matrices for every topoloy with margin attribute $w$. Figure 4 shows
-the OPRE distribution in the process of experiment. For avoiding mess result from too many lines, we just show the first
-three lines and the base line, which shows the distribution when no links is removed, i.e. seven lines in each figure.
-
-In Figure 4 (a), we can only observe five lines because there are two overlapping lines, which means that when removing
-links the worst case for the robust routing does not change. Maybe the random traffic matrices is not bad enough, or the
-removed link really do not affect the MLUR. And from Figure 4, we see that the OPRE is not always be achived for most
-traffic matrices, the common value is much less than OPRE.
-
-Comparing DMP and ERLU, the conclusion is similar to Figure 3, the latter is always better than the former. Even in some
-time, ERLU obtains more power saving but with a lower OPRE.
+Fig. \ref{figure_exp2_sort} (b) shows the amount of TMs as a CDF of OPRE when remove 6 links in Geant, and Fig. \ref{figure_exp2_sort} (c) shows the situation when remove 2 links in Cernet2.
+Similar results are showed in them, however both the centers of REAR curve in Fig. \ref{figure_exp2_sort} (b) and DMP in Fig. \ref{figure_exp2_sort} (c) are not at the same postion 
+when $\omega$ changes. The reasons are two-folds, firstly the curves is drawn by sampling from origin data so the center of curve may not the real 
+center. On the other hand, we calculate the distance of centers over the scope of OPRE, respectively 0.9\% for REAR in Geant and 0.1\% for DMP in Cernet2,
+so it is obvious that from sight of the scope of OPRE, the center of curves are the same `postion'.
 
 \subsection{Path Stretching}
-Path stretching must be careful concerned in routing problem. Suppose two vertices connect directly each other in the origin topology,
-if we remove the connected link then they can connect by another path which is composed by multi links. However we argue path stretching
-between these situation may be unjust, because path stretching result from the difference of topologies rather than routing selection.
-So we obtain the shortest path by Dijkstra Algorithm in the final topology, and compare it with robust routings generated by
-our REAR algorithm. Futher, we show the difference between two ways of removing link, and see the tendency when margin increased.
+Fig. \ref{figure_exp4_path} (a) shows the path stretching ratio (PSR) as a function of the number of removed links in Abilene topology. We see that PSR will 
+equal to 1 when maximum number of links are removed. It is because when the topology reduces to a spanning tree, the routing between two 
+vertices become unique, namely each path is the shortest path. Our REAR has an worst PSR value of 1.30, better than 1.36 in DMP, when 
+remove 1 link and $\omega = 3.5$. We observe that when remove more than 1 link, the DMP is even better than REAR sometimes. This is 
+because both REAR and DMP implement our RRP algorihtm for adjusting routing, and in RRP we always choose the routing path from k-shortest 
+paths for the traffic on the removed link, which make the PSR little as possible. We also see that a larger $\omega$ results in a 
+larger PSR, and reduces to 1 as explained above, because the demand-oblivious routing is computed based on $\omega$, when $\omega$ increases
+the routing will find much more paths for avoiding sudden traffic demand, which makes the PSR increases. For example, when $\omega$ increases
+from 1.5 to 3.5, the PSR of REAR increases about 0.08, while the PSR of DMP increasess about 0.14.
 
-In Figure 5, we see every line ends with path stretching ratio of 1, because topology become a tree structure when lose too much links,
-every path between vertices come to be unique, namely each path is the shortest path. Another conclusion is that, even in the origin
-topology, our robust routing is 17\% longer than the shortest one, it is beacuse our algorithm not only consider the MLUR but also
-the robust performance. However the Dijkstra just take the path length as metric.
-
-We can observe that, ERLU is always shorter than DMP, althoungh in Geant, the worst case is 36\% than the shortest path when margin
-equal to 1.5. And in the first removed links, the path stretching ratio is near 20\%.
+Fig. \ref{figure_exp4_path} (b) and Fig. \ref{figure_exp4_path} (c) show the similar results in Geant and Cernet2, while our REAR is always better than DMP. For instance, REAR
+have the worst PSR of 1.35 and DMP is 1.54 when $\omega = 1.5$ in Geant, REAR have the worst PSR of 1.20 and DMP is 1.27 when $\omega = 3.5$
 
 \section{Conclusion}
+\label{conclusion}
 The conclusion goes here.
@@
 
+\bibitem{networking:designing}
+J. Carter and K. Rajamani, ``Designing Energy-Efficient Servers and Data Centers," Computer, 2010.
+
+\bibitem{networking:active}
+S. Avallone, G. Ventre. ``Energy efficient online routing of flows with additive constraints." Computer Networks, 2012.
+
 \bibitem{networking:greente}
-M.Zhang, C.Yi, B.Liu and B.Zhang, "GreenTE: Power-Aware Traffic Engineering".
+M. Zhang, C. Yi, B. Liu, et al. ``GreenTE: Power-Aware Traffic Engineering," in Proc. of IEEE ICNP, October 2010.
+
+\bibitem{networking:car}
+A. Cianfrani, V. Eramo, M. Listanti, and M. Polverini, ``An OSPF enhancement for energy saving in IP networks," in IEEE INFOCOM Workshop on Green Communications and Networking, April 2011.
+
+\bibitem{networking:grida}
+A. P. Bianzino, L. Chiaraviglio, M. Mellia, et al. ``GRiDA: GReen Distributed Algorithm for energy-efficient IP backbone networks," Computer Networks, 2012.
+
+\bibitem{networking:greenfrr}
+Y. Yang, M. Xu, Q. Li. ``Towards fast rerouting-based energy efficient routing," Computer Networks, 2014.
 
 \bibitem{networking:oblivious}
-D.Applegate and E.Cohen, "Making Intra-Domain Routing Robust to Changing and Uncertain Traffic Demands: Understanding Fundamental Tradeoffs".
+D.
+Applegate and E.
+Cohen, ``Making Intra-Domain Routing Robust to Changing and Uncertain Traffic Demands: Understanding Fundamental Tradeoffs," in Proceedings of ACM SIGCOMM ’03, Karlsruhe, Germany, August 2003.
+
+\bibitem{networking:lp}
+O. Goldschmidt. ``ISP Backbone Traffic Inference Methods to Support Traffic Engineering," In Internet Statistics and Metrics Analysis (ISMA) Workshop, San Diego, CA, December 2000.
+
+\bibitem{networking:bayesian}
+C. Tebaldi and M. West. ``Bayesian Inference of Network Traffic Using Link Count Data," J. of the American Statistical Association, June 1998.
+
+\bibitem{networking:time}
+J. Cao, D. Davis, S. Vander Weil, and B. Yu. ``Time-Varying Network Tomography," J. of the American Statistical Association, 2000.
+
+\bibitem{networking:minimize}
+Harald R\"{a}cke. ``Minimizing congestion in general networks," In Proceedings of the 43rd IEEE Symposium on Foundations of Computer Science (FOCS), 2002. Co-Winner of Best Paper Award.
+
+\bibitem{networking:polynomial}
+Y. Azar, E. Cohen, A. Fiat, H. Kaplan, and H. R ̈acke. ``Optimal oblivious routing in polynomial time," In Proceedings of the 35th ACM Symposium on the Theory of Computing, 2003.
 
@@
 M.Roughan, A.Greenberg, C.Kalmanek, M.Rumsewicz, J.Yates, and Y.Zhang.
-Experience in measuring backbone traffic variability: models, metrics, measurements, and meaning.
-InProceedings of the 2nd Internet Measurement Workshop.
+``Experience in measuring backbone traffic variability: models, metrics, measurements, and meaning," InProceedings of the 2nd Internet Measurement Workshop.
 ACM, 2002
@@
 \bibitem{networking:dmp}
-A.P. Bianzino, L. Chiaraviglio, M. Mellia, Distributed algorithms for green IP networks, in: IEEE INFOCOM Workshop on Green Networking and Smart Grid, 2012
+A.P. Bianzino, L. Chiaraviglio, M. Mellia, ``Distributed algorithms for green IP networks," in: IEEE INFOCOM Workshop on Green Networking and Smart Grid, 2012
 
 \bibitem{networking:hopbyhop}
-C. Hou, F. Zhang, A. F. Anta, L. Wang, and Z. Liu. “A Hopby-hop Energy Efficient Distributed Routing Scheme,” in Proc. of Greenmetrics Workshop, 2013.
+C. Hou, F. Zhang, A. F. Anta, L. Wang, and Z. Liu. ``A Hopby-hop Energy Efficient Distributed Routing Scheme," in Proc. of Greenmetrics Workshop, 2013.
+
+\bibitem{networking:yens}
+Yen, Jin Y. ``Finding the k Shortest Loopless Paths in a Network," Management Science 17 (11), 1971
+
+\bibitem{networking:abilene}
+``Abilene Core Topology," [Online], Available: https://itservices.
+stanford.edu/service/network/internet2/abilene
+
+\bibitem{networking:geant}
+``Network Topology," [Online], Available: http://geant3.archive.ge
+ant.net/Network/NetworkTopology/pages/home.aspx
+
+\bibitem{networking:cernet2}
+``Cernet2 Topology," [Online], Available: http://www.edu.cn/20060111
+/3170220.shtml
 
@@
 
-\section{}
+\section{Proof of Theorem 3}
 \begin{proof}
-Fig. (5) shows the 6-nodes cycle and clique topologies. We label three links $l_{ab}$, $l_{cd}$ and $l_{ef}$
+Fig. \ref{figure_circle_and_clique} shows the 6-nodes cycle and clique topologies. We label three links $l_{ab}$, $l_{cd}$ and $l_{ef}$
 for our proof, let $cap_{ab}$, $cap_{cd}$ and $cap_{ef}$ be their link capacities. Now a arbitrary traffic
@@
 \caption{Circle and Clique topology of 6 nodes}
+\label{figure_circle_and_clique}
 \vspace*{0.1in}
@@
 \begin{equation}
+\label{equation_A_1_1_1}
 \frac {\frac{dem_{ab} + dem_{cd}}{cap_{ab}}} {\frac{dem_{ab}}{cap_{ab}}} = 1 + \frac{dem_{cd}}{dem_{ab}}
@@
 \begin{equation}
+\label{inequation_A_1_1_2}
 \frac {dem_{cd}} {cap_{cd}} < \frac {dem_{ab}} {cap_{ab}}
@@
 
-From Ineq. (14) we get:
+From Ineq. (\ref{inequation_A_1_1_2}) we get:
 
 \begin{equation}
+\label{inequation_A_1_1_3}
 \frac {dem_{cd}} {dem_{ab}} < \frac {cap_{cd}} {cap_{ab}}
@@
 
-So we have OPRE in Case \Rmnum{1}.\Rmnum{1} combined by Eq. (13) and Ineq. (15):
+So we have OPRE in Case \Rmnum{1}.\Rmnum{1} combined by Eq. (\ref{equation_A_1_1_1}) and Ineq. (\ref{inequation_A_1_1_3}):
 
 \begin{equation}
+\label{inequation_A_1_1_result}
 1 + \frac {dem_{cd}} {dem_{ab}} < 1 + \frac {cap_{cd}} {cap_{ab}}
@@
 \begin{equation}
+\label{equation_A_1_2_1}
 \frac {\frac{dem_{ef} + dem_{cd}}{cap_{ef}}} {\frac{dem_{ab}}{cap_{ab}}} =
@@
 
-Because the old bottleneck is $l_{ab}$, so we have Ineq. (14) and :
+Because the old bottleneck is $l_{ab}$, so we have Ineq. (\ref{inequation_A_1_1_2}) and :
 
 \begin{equation}
+\label{inequation_A_1_2_2}
 \frac {dem_{ef}} {cap_{ef}} < \frac {dem_{ab}} {cap_{ab}}
@@
 
-So we get inequation from Ineq. (18):
+So we get inequation from Ineq. (\ref{inequation_A_1_2_2}):
 
 \begin{equation}
+\label{inequation_A_1_2_3}
 \frac {dem_{ef} * cap_{ab}} {dem_{ab} * cap_{ef}} < 1
@@
 
-Also from Ineq. (14) we have :
+Also from Ineq. (\ref{inequation_A_1_1_2}) we have :
 
 \begin{equation}
+\label{inequation_A_1_2_4}
 \frac {dem_{cd} * cap_{ab}} {dem_{ab}} < cap_{cd}
@@
 
-Combine Eq. (17), Ineq. (19) and Ineq. (20), we have OPRE in Case \Rmnum{1}.\Rmnum{2}:
+Combine Eq. (\ref{equation_A_1_2_1}), Ineq. (\ref{inequation_A_1_2_3}) and Ineq. (\ref{inequation_A_1_2_4}), we have OPRE in Case \Rmnum{1}.\Rmnum{2}:
 
 \begin{equation}
+\label{inequation_A_1_2_result}
 \frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac {dem_{cd} * cap_{ab}}{dem_{ab} * cap_{ef}}
@@
 
-For Case \Rmnum{2}.\Rmnum{1}, the adjusted link may be $l_{ab}$, namely the old bottleneck link, the new bottleneck
+For Case \Rmnum{2}, the adjusted link may be $l_{ab}$, namely the old bottleneck link, the new bottleneck
 maybe $l_{ef}$. Computing the OPRE similar as above:
@@
 \begin{equation}
+\label{equation_A_2_1}
 \frac {\frac{dem_{ef} + dem_{ab}}{cap_{ef}}} {\frac{dem_{ab}}{cap_{ab}}} =
@@
 
-Becuase the old bottleneck has the maximum link utilization, so combine Ineq. (19) and Eq.(22) we obtain OPRE in Case 
-\Rmnum{2}.\Rmnum{1}:
+Becuase the old bottleneck has the maximum link utilization, so combine Ineq. (\ref{inequation_A_1_2_3}) and Eq. (\ref{equation_A_2_1}) we obtain OPRE in Case
+\Rmnum{2}:
 
 \begin{equation}
+\label{inequation_A_2_result}
 \frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac{cap_{ab}}{cap_{ef}} < 1 + \frac{cap_{ab}}{cap_{ef}}
@@
 
-To sum up, we have inequation from Ineq. (16), Ineq. (21) and Ineq. (23):
+To sum up, we have inequation from Ineq. (\ref{inequation_A_1_1_result}), Ineq. (\ref{inequation_A_1_2_result}) and Ineq. (\ref{inequation_A_2_result}):
 
 \begin{equation}
+\label{inequation_A_result}
 1 + \max \{\frac{cap_{cd}}{cap_{ab}}, \frac{cap_{cd}}{cap_{ef}}, \frac{cap_{ab}}{cap_{ef}} \} < 1 + \frac{\max_{l \in E} cap_{l}}{\min_{l \in E} cap_{l}}
@@
 
-\section{}
+\section{Proof of Theorem 4}
 \begin{proof}
@@
 
-\section{}
+\section{Proof of Theorem 5}
 \begin{proof}
@@
 \begin{equation}
+\label{equation_C_1}
     \frac{\frac{\sum_{(i,j) \in E} dem_{ij}}{cap_{ef}}}{\frac{dem_{ab}}{cap_{ab}}} = \frac{cap_{ab}}{cap_{ef}} \sum_{(i,j) \in E} \frac{dem_{ij}}{dem_{ab}}
@@
 \begin{equation}
+\label{ineqaution_C_2}
     \frac{dem_{ij}}{cap_{ij}} < \frac{dem_{ab}}{cap_{ab}}, \forall (i,j) \in E
@@
 \begin{equation}
+\label{ineqaution_C_3}
     \frac{dem_{ij} * cap_{ab}}{dem_{ab}} < cap_{ij}, \forall (i,j) \in E
@@
 \begin{equation}
+\label{ineqaution_C_4}
     \frac{cap_{ab}}{cap_{ef}} \sum_{(i,j) \in E} \frac{dem_{ij}}{dem_{ab}} < \sum_{(i,j) \in E} \frac{cap_{ij}}{cap_{ef}}
@@
 \begin{equation}
+\label{ineqaution_C_result}
     \sum_{(i,j) \in E} \frac{cap_{ij}}{cap_{ef}} < \frac{n^2}{2} \frac{\max_{l \in E} cap_l}{\min_{l \in E} cap_l}

### 2015-02-04 experiment/cplex/len_path.py

@@ -1,17 +1,22 @@
 from matplotlib.backends.backend_pdf import PdfPages
 import matplotlib.pyplot as plt
+from matplotlib import rc
+
+font = {'size':20}
+rc('font', **font)
 
 fig1, ax1 = plt.subplots()
 
+topology_letter = {'abilene':'a', 'geant':'b', 'cernet2':'c'}
 topology_x_range = {'abilene':5, 'geant':16, 'cernet2':4}
 topology_line_type = {'1.5':'o', '2.5':'s', '3.5':'^'}
 color_type = {'base':'r--', 'new':'b-'}
-remove_type = {'base':'DMP', 'new':'ERLU'}
+remove_type = {'base':'DMP', 'new':'REAR'}
 result_file_template = "path_stretch_%s_%s.txt"
 
 line_list = []
 label_list = []
-for t in ['abilene']:
+for t in ['cernet2']:
     for w in ['1.5', '2.5', '3.5']:
         f = open(result_file_template % (t, w))
         line = f.readline()
@@ -46,12 +51,12 @@ for t in ['abilene']:
         line_list.append(l1)
         line_list.append(l2)
 
-    plt.legend(line_list, label_list, loc=1)
-    plt.xlabel('Removing Links', fontsize=22)
+    plt.legend(line_list, label_list, loc=1, fontsize=15)
+    plt.xlabel('Removing Links\n(%s)' % topology_letter[t], fontsize=22)
     plt.ylabel('Path Stretching Ratio', fontsize=22)
     
     pp = PdfPages('exp4_path_%s.pdf' % t)
-    pp.savefig(fig1)
+    pp.savefig(fig1, bbox_inches='tight')
     pp.close()
 
     #plt.show()

### 2015-02-04 experiment/plot/exp1_power.py

@@ -2,14 +2,21 @@ from matplotlib.backends.backend_pdf import PdfPages
 from matplotlib.ticker import FormatStrFormatter
 import matplotlib.pyplot as plt
 import matplotlib.ticker as tic
+from matplotlib import rc
 
+t = 'cernet2'
+
+
+font = {'size':20}
+rc('font', **font)
 fig1, ax1 = plt.subplots()
 
+topology_letter = {'abilene':'a', 'geant':'b', 'cernet2':'c'}
 topology_x_range = {'abilene':5, 'geant':13, 'cernet2':4}
 remove_links = {'abilene':4, 'geant':15, 'cernet2':3}
 w_line_type = {'1.5':'o', '2.5':'s', '3.5':'^'}
 color_type = {'base':'r--', 'new':'b-'}
-remove_type = {'base':'DMP', 'new':'ERLU'}
+remove_type = {'base':'DMP', 'new':'REAR'}
 result_file_template = "result-compare-%s-%s"
 topology_file_template = "../topology/connected/%s-connected-topology"
 remove_file_template = "../topology/remove/%s-remove-%d-links"
@@ -25,7 +32,6 @@ power_model = [60, 100, 140, 174]
 line_list = []
 label_list = []
 #for t in ['abilene', 'geant', 'cernet2']:
-t = 'abilene'
 for w in ['1.5', '2.5', '3.5']:
     # compute the total power of topology
     f = open(topology_file_template % t)
@@ -138,18 +144,19 @@ for w in ['1.5', '2.5', '3.5']:
     line_list.append(l1)
     line_list.append(l2)
 
-plt.xlabel('Power Saving Ratio (%)', fontsize=22)
+plt.xlabel('Power Saving Ratio (%) \n '+'(%s)' % topology_letter[t], fontsize=22)
 plt.ylabel('OPRE', fontsize=22)
 #plt.legend([l1, l2], ['TMP, w=1.5, 2.0, 2.5...', 'ERLU, w=1.5, 2.0, 2.5...'], loc=2)
-plt.legend(line_list, label_list, loc=2)
+plt.legend(line_list, label_list, loc=2, fontsize=16)
 
 ax1.set_yscale('log')
 ax1.set_ylim([1,y_lim[t]])
 ax1.get_yaxis().set_major_formatter(tic.ScalarFormatter())
[…]

### 2015-02-04 experiment/plot/exp2_sort.py

@@ -1,62 +1,90 @@
 from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import rc
 import matplotlib.pyplot as plt
+
+t = 'geant'
+
+font = {'size':20}
+rc('font', **font)
 
 fig1, ax1 = plt.subplots()
 
-t = 'cernet2'
-result_file_template = "middle-compare-%s-1.5" % t
-count = 1000
-remove = 4
+result_file_template = "middle-compare-%s-%s"
+count = 1001
 
-f = open(result_file_template)
-line = f.readline();
+topology_letter = {'abilene':'a', 'geant':'b', 'cernet2':'c'}
+remove_ = {'abilene':4, 'geant':6, 'cernet2':2}
+remove = remove_[t]
 
-base = [([0] * count) for i in range(remove)]
-new = [([0] * count) for i in range(remove)]
+
+label = {'1.5':'o', '2.5':'s', '3.5':'^'}
+base = {'1.5':[0] * count, '2.5':[0] * count, '3.5':[0] * count}
+new = {'1.5':[0] * count, '2.5':[0] * count, '3.5':[0] * count}
 x = [i/10 for i in range(count)]
-while line:
-    tokens = line.strip().split()
-    r = int(tokens[0])
-    n = int(tokens[1])
-    if int(r) == remove:
-        break
-    base[r][n] = float(tokens[2])
-    new[r][n] = float(tokens[3])
+xx = [0, 5, 10, 15] + [i*20 for i in range(1,5)]+[80, 85, 90, 95, 98, 99, 100]
+print xx
 
-    line = f.readline()
+for w in ['1.5', '2.5', '3.5']:
+    f = open(result_file_template % (t, w))
+    line = f.readline();
+    while line:
+        tokens = line.strip().split()
+        r = int(tokens[0])
+        n = int(tokens[1])
+        if int(r) != remove:
+            line = f.readline()
+            continue
+        base[w][n] = float(tokens[2])
+        new[w][n] = float(tokens[3])
 
-f.close()
+        line = f.readline()
 
+    f.close()
+
+line_list = []
+line_label = []
 line1 = None
-for i in range(0, remove):
+for i in ['1.5', '2.5', '3.5']:
+    base[i][1000] = 1000
     for j in range(count):
         for k in range(j, count):
[…]

### 2015-02-06 paper_linheng_7.tex
update proof

--- 2015-02-04 paper_linheng_5.tex
@@
 \begin{abstract}
-Energy conservation has become a major challenge to the Internet. In existing approaches, a part of line cards
-are switched into sleep mode for energy conservation, and the routing is configured carefully to balance energy saving
-and traffic engineering goals, such as the maximum link utilization ratio (MLUR). Typically, traffic demands are
-used as inputs, and routing is computed accordingly. However, accurate traffic matrices are difficult to obtain and
-are changing frequently. This makes the approaches difficult to implement. Further, the routing may shift
-frequently, and is not robust to sudden traffic changes.
+Energy conservation has become a major challenge to the Internet.
+Switching part of components into sleep mode is an effective way for energy conservation.
+Many existing approaches compute routing based on traffic matrices, to balance energy saving and traffic engineering goals, e.g., the maximum link utilization ratio (MLUR).
+However, accurate traffic matrices are difficult to obtain and change frequently, resulting in lack of routing stability and robustness.
 
-In this paper, we propose a different approach that finds one energy-aware routing robust to a set of traffic
-matrices, particularly to arbitrary traffic demands. Such a routing without energy consideration is known as
-the demand-oblivious routing, and is well studied. However, the problem becomes much more challenging when energy
-conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance
-ratio with energy constraint (OPRE), which reflects the MLUR distance from a routing to the optimal routing when
-certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio,
-and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve
-the problem in two phases. REAR select sleeping links based on extended robust link utilization (ERLU)
-and compute the routing based on a classical demand-oblivious routing algorithm.
-We evaluate our algorithms on real and synthetic topologies. The simulation results show that REAR can save
-19\% of line card power while the performance ratio is less than 34\%.
+We propose to find one energy-aware routing robust to a set of traffic matrices.
+Such demand-oblivious routing problem has been studied without energy conservation, but it becomes more challenging when energy is considered.
+To overcome the challenges, we define a metric that reflects the MLUR distance from a routing to the optimal routing under certain energy conservation requirement.
+We model the problem of minimizing the metric, and analyze the upper bounds.
+Then, we propose a robust energy-aware routing scheme to solve the problem by selecting sleeping links and computing the routing, based on a classical demand-oblivious routing algorithm.
+We evaluate our algorithms by simulations on real topologies.
+The results show that REAR is much more robust than existing approaches while more than 35\% line card power can be saved.
 \end{abstract}
@@
 We evaluate our algorithms by simulations on real topologies and synthetic traffic demands with random fluctuations.
-The results show that REAR can achieve an OPRE of 1.34 while 19\% of line card power is saved.
+The results show that REAR can achieve an OPRE of 2.32 while 25\% of line card power is saved.
 
@@
 \label{related_work}
-Green routing is studied because we can not use as much of a resource as we need \cite{networking:designing}, such as line cards always work in full mode even with 
-low traffic fraction. So there are many studies to save energy consumption by put some links in sleep mode, for example GreenTE \cite{networking:greente} is 
-proposed for maximuming the sleeping links while $E^2$-MCRA \cite{networking:active} is proposed for minimizing the active links and nodes by a depth-first search approach.
-Besides these centralized algorithms, EAR \cite{networking:car} and GRiDA \cite{networking:grida} are proposed for distributed deployment, both of them are compatible 
-with OSPF sharing additional information between nodes. For addressing the problem of routing convergence when traffic changes frequently, GreenFRR 
-\cite{networking:greenfrr} is proposed by leveraging the technique of fast rerouting.
+There have been a number of studies on energy conservation in the Internet using energy efficient routing.
+Many approaches take link utilization as a key factor to avoid network congestions.
+GreenTE \cite{networking:greente} is proposed to find a routing that can maximize the power saving by off/sleeping components, while the link utilization must be less than a given threshold.
+$E^2$-MCRA \cite{networking:active} is proposed to find routing for new incoming flows, such that the number of active links and nodes are minimized while the unpredictable traffic increment is considered.
+ROD \cite{ROD2012Networking} computes the link weights using a Lagrange multiplier method, so as to balance the number of sleeping links and the link utilization under an OSPF-like routing.
+These approaches have to obtain the traffic matrix/demands in real-time.
+REsPoNse \cite{Response11Conext} uses MPLS tunnels to aggregate traffic and saves energy by switching under-utilized links into sleep mode; the sleeping links are activated when some link has an utilization ratio larger than a given threshold.
+This method of activating sleeping links is used in some other approaches \cite{networking:car}\cite{networking:dmp}\cite{networking:grida}\cite{networking:greenfrr}\cite{SPEED14TON}.
+Although these approaches do not need a traffic matrix, they still need the traffic volume on each link in the network, and the routing may shift frequently with the traffic change.
+Our study in this paper is different from the above approaches, because we assume the traffic can be uncertain, and we try to find a static routing that minimizes the distance to the optimal routing with respect to link utilization.
 
-Network may suffer from bad performance because of both frequent traffic demand and routing changes. There are studies to estimate traffic matrices in the context
-of Internet traffic, such as LP approach \cite{networking:lp}, Bayesian Infereence techniques \cite{networking:bayesian} and Time-Varying Network Tomography
-\cite{networking:time}. All the estimatation for traffic matrices result in the changes of routing, \cite{networking:minimize} proposed an oblivious routing algorithm with a polylog 
-competitive ratio with respect to congestion and \cite{networking:polynomial} give a polynomial time algorithm based on applying the Ellipsoid algorithm to an exponential-size LP model.
-To be practical for large networks, the oblivious-demand routing based on polynomial-size LP formulation is investigated in \cite{networking:oblivious}.
-
-In this paper, we proposed robust energy-aware routing based on the oblivious-demand \cite{networking:oblivious}, which is both green for the energy consumption by pruning
-some links based on ERLU, and also robust for uncertain traffic demands. It is more practical than existing green routing algorihtm because it almost do not need changes when 
-real traffic varifies.
+Great efforts have been made to optimize the network performance of delivering traffic.
+Generally, there are two types of approaches for such traffic engineering targets.
+The first type assumes the awareness of the traffic matrix/demands, while the other deals with uncertain traffic demands \cite{DynamicVSOblivious11Algorithmica}.
+In this paper, we are interested in the second category, which is called the oblivious routing.
+R\"{a}cke \cite{networking:minimize} proposes an oblivious routing algorithm with a polylog competitive ratio with respect to congestion.
+Azar et al.
+\cite{networking:polynomial} propose a polynomial time algorithm to solve the oblivious routing based on the ellipsoid method.
+Applegate \cite{networking:oblivious} et al.
+further simplify the problem into a polynomial-size linear programming model.
+Li et al.
+\cite{ASimpleMethodBalancing05ICCCN} propose a penalty method to improve the quality of oblivious routing with respect to path dispersion and path variation.
+Kodialam et al.
+\cite{TrafficOblivious07CommuMagazine} study the problem of providing bandwidth guarantee in VPN using oblivious routing.
+They further extend the application to a set of networking scenarios \cite{ObliviousHighVariable08TON}, and to provide resiliency against link failures \cite{ObliviousHoseModel11TON}.
+Our work in this paper applies oblivious routing in the scenario of energy conservation.
+We need a new metric that is suitable for our scenario, and new routing algorithms as well.
 
@@
 To address this issue, we extend the definition of OPR.
-Formally, let $G^*$ be a sub-graph of $G$ that satisfies the energy constraint (We will formally define the energy constraint in Section III.C, i.e., Eq.
+Formally, let $G^*$ be a sub-graph of $G$ that satisfies the energy constraint (We will formally define the energy constraint in Section III.C, i.e., Ineq.
 (\ref{inequation_power_threshold})).
@@
 Here, we use $p(l)$ to denote the power consumption of link $l$, which is mainly drawn by the line cards at the two ends of the link.
-Note that $p(l)$ is independent of the traffic volume, and this assumption is based on the fact that in current stage, the power of a line card changes little with the traffic volume \cite{networking:hopbyhop}.
+Note that $p(l)$ is independent of the traffic volume, and this assumption is based on the fact that in current stage, the power of a line card changes little with the traffic volume \cite{PowerAware08Infocom}.
 
@@
 Now let us see the results for a large $\theta$.
-Since there is not much difference between the power consumptions for links with different capacities \cite{networking:hopbyhop}, we consider the spanning trees of a graph, which can achieve a near-optimal $\theta$.
+Since there is not much difference between the power consumptions for links with different capacities \cite{networking:greenfrr}, we consider the spanning trees of a graph, which can achieve a near-optimal $\theta$.
 We have
@@
 
-Several heuristics have been proposed to select sleeping links without the knowledge of a specific TM, with various considerations \cite{}\cite{}\cite{}.
+Several heuristics have been proposed to select sleeping links without the knowledge of a specific TM, with various considerations \cite{networking:car}\cite{networking:dmp}\cite{networking:grida}\cite{ESACON11InfocomWs}.
 However, we need a algorithm that can potentially minimize the OPRE.
@@
 Note that there may be multiple paths in $r_0$ between a source-destination pair.
-We first decompose the paths by a standard procedure given in \cite{}.
+We first decompose the paths by a standard procedure given in \cite{networkflow93book}.
 Formally, let $p^h_{ab}$ denote the $h$-th path between nodes $a$ and $b$, and $t^h_{ab}$ be the fraction of the traffic that is routed on $p^h_{ab}$.
@@
 In Step 15, the duplicate paths are merges and new routing $r$ that does not traverse link $l$ is obtained.
-The computation complexity of the RRA algorithm is
+The computation complexity of the RRA algorithm is polynomial.
+We omit the detail due to the space limitation.
+\ignore{
 $O((|E|-|V|)|V|^2(|R||E| + K|V|(|E| + |V|\log|V|) + N(|E||V|^2 + K|E|) + |R||E|))$ in the worst case, where $O(|E|-|V|)$ is the maximum number of sleeping links, $O(|V|^2)$ is the maximum
 number of OD pairs, $O(|R||E|)$ is for computing detoured traffic and remove failed paths where $O(|R|)$ is the number of input routings, $O(K|V|(|E| + |V|\log|V|))$ is for solving the
-yens algorithm where $K$ is the number of shortest paths, $O(N(|E||V|^2 + K|E|))$ is for detouring traffic fraction by $N$ times, and $O(|R||E|)$ is for merging routings.
+yens algorithm where $K$ is the number of shortest paths, $O(N(|E||V|^2 + K|E|))$ is for detouring traffic fraction by $N$ times, and $O(|R||E|)$ is for merging routings.}
 
@@
 \centering
-\vspace*{0.1in}
 \subfloat{\includegraphics[width=6cm]{opr_with_power_abilene}}
@@
 \subfloat{\includegraphics[width=6cm]{opr_with_power_cernet2}}
-\caption{OPRE versus TMs: (a). Abilene, (b). Geant, (c). Cernet2}
+\vspace{-0.1in}
+\caption{OPRE in (a) Abilene. (b) Geant. (c) CERNET2.}
 \label{figure_opr_with_power}
-\vspace*{0.1in}
+\vspace{-0.1in}
 \end{figure*}
@@
 \centering
-\vspace*{0.1in}
 \subfloat{\includegraphics[width=6cm]{exp2_sort_abilene}}
@@
 \subfloat{\includegraphics[width=6cm]{exp2_sort_cernet2}}
-\caption{OPRE versus Power Saving: (a). Abilene with 4 links removed (b). Geant with 6 links removed (c). Cernet2 with 2 links removed}
+\vspace{-0.1in}
+\caption{Performance ratio in (a) Abilene with 4 links pruned. (b) Geant with 6 links pruned. (c) CERNET2 with 2 links pruned.}
 \label{figure_exp2_sort}
-\vspace*{0.1in}
+\vspace{-0.1in}
 \end{figure*}
@@
 We evaluate the REAR approach by simulations on three real-world network topologies, including Abilene \cite{networking:abilene}, Geant \cite{networking:geant}, and CERNET2 \cite{networking:cernet2}.
-The numbers of nodes and links of the topologies are listed in Table \ref{table_topology}.
+The numbers of nodes and links of the topologies are listed in Table \ref{three_topologies}.
 The traffic matrices we used in our simulations are generated as follows.
-We first generate a baseline traffic matrix using the gravity model \cite{networking:gravity}, where the baseline traffic demand $d_{ab}$ is proportional to their total capacity.
+We first generate a baseline traffic matrix using the gravity model \cite{networking:gravity}, where the baseline traffic demand $d_{ab}$ is proportional to the total capacity of nodes $a$ and $b$.
 Then, the traffic demand is generated randomly in the range from $d_{ab}/\omega$ to $d_{ab}\omega$, where $\omega \geq 1$ is a margin factor used to control the fluctuation range of the traffic.
@@
 \begin{table}[h]
-\label{table_topology}
 \renewcommand{\arraystretch}{1}
 \caption{Topologies}
-\label{three topologies}
+\label{three_topologies}
 \centering
@@
 \hline
-Cernet2 & 20 & 22 & 3 \\
+CERNET2 & 20 & 22 & 3 \\
 \hline
@@
 DMP always selects the most power-hungry links to switch into off/sleep mode, and can achieve a large power saving ratio, but does not consider routing robustness.
-We evaluate the OPRE and its distribution, the power saving ratio, and the path stretch of the approaches.
+For the approaches, we evaluate the OPRE, the power saving ratio, the distribution of the performance ratio, and the path stretch.
 
 \begin{table}[h]
-\label{table_line_card_power_consumption}
 \renewcommand{\arraystretch}{1}
 \caption{Line Card Power Consumption}
-\label{power model}
+\label{table_line_card_power_consumption}
 \centering
@@
 \centering
-\vspace*{0.1in}
 \subfloat{\includegraphics[width=6cm]{exp4_path_abilene}}
@@
 \subfloat{\includegraphics[width=6cm]{exp4_path_cernet2}}
-\caption{Path Stretching: (a). Abilene, (b). Geant, (c). Cernet2}
+\vspace{-0.1in}
+\caption{Path Stretch in (a) Abilene. (b) Geant. (c) CERNET2.}
 \label{figure_exp4_path}
-\vspace*{0.1in}
+\vspace{-0.1in}
 \end{figure*}
@@
 \subsection{OPRE versus Power Saving}
-Fig. \ref{figure_opr_with_power} (a) shows the OPRE as a function of power saving ratio $\theta$, in the Abilene topology. We see that the OPRE increases when more power is saved.
-This is not surprising because the routing becomes less robust when more links are switched into off/sleep mode. Our REAR has an OPRE ranging from 
-1.06 to 2.32, which is much less than the results of DMP. This is because REAR takes routing robustness into consideration when it prunes 
+Fig.
+\ref{figure_opr_with_power} (a) shows the OPRE (evaluated by the maximum performance ratio under all 1000 TMs), as a function of power saving ratio $\theta$, in the Abilene topology.
+We see that the OPRE increases when more power is saved.
+This is not surprising because the routing becomes less robust when more links are switched into off/sleep mode.
+Our REAR has an OPRE ranging from 1.06 to 2.32, which is much less than the results of DMP.
+This is because REAR takes routing robustness into consideration when it prunes
 links and computes routing. For instance, when $\omega = 3.5$ and 25\% power is saved, the OPRE of REAR is 2.32, while the OPRE of DMP is 5.09.
@@
 
-Similar results are showed in Fig. \ref{figure_opr_with_power} (b) and (c), namely in Geant and Cernet2 topology. In Geant, we see that OPRE sacle with a wider range both
-in DMP and REAR, it is because Geant is much larger than other topologies, when removing too much links, the network will suffer from more 
-serious congestion. In Cernet2, Although REAR is better than DMP, the difference is marginal when achieved a large $\theta$. It can be explained
-by the density of links, REAR obtains a better performance in dense topology because it will have more choices.
+Fig.
+\ref{figure_opr_with_power} (b) shows the OPRE as a function of power saving ratio $\theta$ in Geant.
+We find that the results are similar to that in Abilene.
+However, the OPRE is larger in Geant than in Abilene for both REAR and DMP.
+One reason for this result is that Geant has a larger link density ($\frac{37}{23} = 1.61$) than Abilene ($\frac{15}{12} = 1.25$).
+Another reason is that the link capacity difference is large in Geant.
+The maximum link capacity is 9920 Mbps while the minimum link capacity is 155 Mbps.
+Such results are consistent with our analysis in Section IV.
 
-\subsection{OPRE versus Margin}
-Fig. \ref{figure_exp2_sort} (a) shows the amount of TMs as a cumulative distribution function (CDF) of OPRE, when remove 4 links in Abilene topology. We see that the curves of
-DMP are right of REAR, means REAR always have lower OPRE whatever TMs is. It is consistent with Fig. \ref{figure_opr_with_power} (a). We also observe that our REAR has
-more concentrated curves, means REAR have the almost same performance when TM changes, it is because REAR remove the less `important' link from 
-topology and the left topology is more robust for TMs than DMP. For instance, REAR ranges from 1.74 to 2.32 while DMP range from 2.97 to 5.09 
-when $\omega = 3.5$. Also we can see that curve become smooth when $\omega$ increases, it is because the TMs range from wider scope, and the OPRE
-may achieved wider scope too. However we see that whatever $\omega$ is, the center of the curve are almost the same postion. It is because 
-we only change the margin $\omega$ rather than the base TM, so the medial value will not changes apparently.
+Fig.
+\ref{figure_opr_with_power} (c) shows the results in CERNET2.
+We observe that the difference between REAR and DMP is small.
+This is because the CERNET2 topology has a small link density, and only a small number of links can be pruned.
 
-Fig. \ref{figure_exp2_sort} (b) shows the amount of TMs as a CDF of OPRE when remove 6 links in Geant, and Fig. \ref{figure_exp2_sort} (c) shows the situation when remove 2 links in Cernet2.
-Similar results are showed in them, however both the centers of REAR curve in Fig. \ref{figure_exp2_sort} (b) and DMP in Fig. \ref{figure_exp2_sort} (c) are not at the same postion 
-when $\omega$ changes. The reasons are two-folds, firstly the curves is drawn by sampling from origin data so the center of curve may not the real 
-center. On the other hand, we calculate the distance of centers over the scope of OPRE, respectively 0.9\% for REAR in Geant and 0.1\% for DMP in Cernet2,
-so it is obvious that from sight of the scope of OPRE, the center of curves are the same `postion'.
+\subsection{Performance Ratio Distribution}
+Fig.
+\ref{figure_exp2_sort} (a) shows the CDF of random TMs as a function of the performance ratio, in Abilene with 4 links pruned.
+The curves of REAR are on the left of DMP, which means that REAR has a lower performance ratio under all TMs.
+We observe that the performance ratio has a larger range with a larger $\omega$, but the performance ratio of REAR has a small range in total (e.g., from 1.74 to 2.32 when $\omega = 3.5$), unlike DMP (e.g., from 2.97 to 5.09 when $\omega = 3.5$).
+This implies that REAR is more robust.
 
-\subsection{Path Stretching}
-Fig. \ref{figure_exp4_path} (a) shows the path stretching ratio (PSR) as a function of the number of removed links in Abilene topology. We see that PSR will 
-equal to 1 when maximum number of links are removed. It is because when the topology reduces to a spanning tree, the routing between two 
-vertices become unique, namely each path is the shortest path. Our REAR has an worst PSR value of 1.30, better than 1.36 in DMP, when 
-remove 1 link and $\omega = 3.5$. We observe that when remove more than 1 link, the DMP is even better than REAR sometimes. This is 
-because both REAR and DMP implement our RRP algorihtm for adjusting routing, and in RRP we always choose the routing path from k-shortest 
-paths for the traffic on the removed link, which make the PSR little as possible. We also see that a larger $\omega$ results in a 
-larger PSR, and reduces to 1 as explained above, because the demand-oblivious routing is computed based on $\omega$, when $\omega$ increases
-the routing will find much more paths for avoiding sudden traffic demand, which makes the PSR increases. For example, when $\omega$ increases
-from 1.5 to 3.5, the PSR of REAR increases about 0.08, while the PSR of DMP increasess about 0.14.
+Fig.
+\ref{figure_exp2_sort} (b) shows the results in Geant with 6 links pruned, and Fig.
+\ref{figure_exp2_sort} (c) shows the results in CERNET2 with 2 links pruned.
+The results are similar to that in Abilene.
 
-Fig. \ref{figure_exp4_path} (b) and Fig. \ref{figure_exp4_path} (c) show the similar results in Geant and Cernet2, while our REAR is always better than DMP. For instance, REAR
-have the worst PSR of 1.35 and DMP is 1.54 when $\omega = 1.5$ in Geant, REAR have the worst PSR of 1.20 and DMP is 1.27 when $\omega = 3.5$
+\subsection{Path Stretch}
 
-\section{Conclusion}
+Now we evaluate the path stretch of the approaches, which reflects the end-to-end delay increment due to link pruning and robust routing.
+Here, path stretch is the ratio of the path length of a routing to the shortest path length, in the topology after pruning links.
+Note that there may be multiple paths in the robust routing for a source-destination pair.
+In such a case, we compute the weighted path stretch of these paths according to the traffic fraction they carry.
+
+Fig.
+\ref{figure_exp4_path} (a) shows the path stretch as a function of pruned link number in Abilene.
+Generally, the path stretch decreases when more links are pruned, and equals 1 when 4 links are pruned.
+This is because the topology becomes less connected when more links are pruned, and reduces to a spanning tree when 4 links are pruned.
+The path stretch of REAR is less than 1.32, because we use YEN's algorithm to find the $k$-th shortest path when searching for paths to detour the traffic.
+We think this path stretch is small and will not induce large end-to-end delay increment.
+The path stretch of REAR is a little larger than that of DMP in some cases.
+This is because most links in Abilene has the same capacity and consumes the same power, and in such a case, DMP randomly selects sleeping links, which may result in less path stretch.
+We also observe that the path stretch increases with $\omega$, because the demand-oblivious routing is computed based on $\omega$, and when $\omega$ increases, the routing will use more paths to increase the robustness.
+
+Fig.
+\ref{figure_exp4_path} (b) and (c) show the path stretch in Geant and CERNET2, respectively.
+We see that our REAR has a less path stretch than DMP.
+For instance, REAR has the largest path stretch of 1.35 in Geant when $\omega = 1.5$, while the result of DMP is 1.54.
+
+\section{Conclusion and Future Work}
 \label{conclusion}
-The conclusion goes here.
+
+In this paper, we studied energy efficient routing under uncertain traffic demands.
+We proposed metric OPRE, which defines the distance between a routing and the optimal routing with respect to the maximum link utilization ratio under energy conservation requirements.
+We modeled the problem of minimizing the OPRE and analyzed the upper bounds of the solution.
+Then, we developed the REAR scheme to solve the problem.
+We did simulations using real network topologies and showed that REAR can saving energy without knowing traffic matrices, and can achieve a smaller OPRE than existing approaches.
+
+In the future, we plan to improve our algorithms, because solving the linear programming does not scale well to large networks.
+We are also interested in realizing the robust energy-aware routing in a hop-by-hop fashion, without fractional traffic and MPLS tunnels.
 
 \begin{thebibliography}{1}
-
-\bibitem{networking:designing}
-J. Carter and K. Rajamani, ``Designing Energy-Efficient Servers and Data Centers," Computer, 2010.
-
-\bibitem{networking:active}
-S. Avallone, G. Ventre. ``Energy efficient online routing of flows with additive constraints." Computer Networks, 2012.
 
@@
 
+\bibitem{networking:active}
+S. Avallone, G. Ventre. ``Energy efficient online routing of flows with additive constraints." Computer Networks, vol. 56, 2368--2382, 2012.
+
+\bibitem{ROD2012Networking}
+M. Shen, H. Liu, K. Xu, et al. ``Routing On Demand: Toward the Energy-Aware Traffic Engineering with OSPF." in Proc. of IFIP Networking, 2012, 232--246.
+
+\bibitem{Response11Conext} N.~Vasic, P.~Bhurat, D.~Novakovic,
+    M.~Canini, S.~Shekhar, and D.~Kostic,
+  ``{I}dentifying and using energy-critical paths,'' in Proc. of CoNext'11, 2011.
+
 \bibitem{networking:car}
@@
 
+\bibitem{networking:dmp}
+A.P. Bianzino, L. Chiaraviglio, M. Mellia, ``Distributed algorithms for green IP networks," in: IEEE INFOCOM Workshop on Green Networking and Smart Grid, 2012
+
 \bibitem{networking:grida}
-A. P. Bianzino, L. Chiaraviglio, M. Mellia, et al. ``GRiDA: GReen Distributed Algorithm for energy-efficient IP backbone networks," Computer Networks, 2012.
+A. P. Bianzino, L. Chiaraviglio, M. Mellia, et al. ``GRiDA: GReen Distributed Algorithm for energy-efficient IP backbone networks," Computer Networks, vol.~56, 3219-–3232, 2012.
 
 \bibitem{networking:greenfrr}
-Y. Yang, M. Xu, Q. Li. ``Towards fast rerouting-based energy efficient routing," Computer Networks, 2014.
+Y. Yang, M. Xu, Q. Li. ``Towards fast rerouting-based energy efficient routing," Computer Networks, vol.~70(9), 1--15, 2014.
+
+\bibitem{SPEED14TON}
+Q. Li, M. Xu, Y. Yang, L. Gao, Y. Cui, and J. Wu. ``Safe and Practical Energy-Efficient Detour Routing in IP Networks,'' IEEE/ACM Transactions on Networking, vol.~22(6), 1925--1937, 2014.
+
+\bibitem{ESACON11InfocomWs} F.~Cuomo, A.~Abbagnale,
+    A.~Cianfrani, and M.~Polverini, ``{K}eeping the
+  {C}onnectivity and {S}aving the {E}nergy in the {I}nternet,'' in \emph{IEEE INFOCOM Workshop on GCN}, April 2011.
+
+\bibitem{DynamicVSOblivious11Algorithmica}
+N. Goyal, N. Olver, F. B. Shepherd. ``Dynamic vs. Oblivious Routing in Network Design,'' Algorithmica, vol. 61(1), 161--173, 2011.
+
+\bibitem{networking:minimize}
+Harald R\"{a}cke. ``Minimizing congestion in general networks," In Proceedings of the 43rd IEEE Symposium on Foundations of Computer Science (FOCS), 2002. Co-Winner of Best Paper Award.
+
+\bibitem{networking:polynomial}
+Y. Azar, E. Cohen, A. Fiat, H. Kaplan, and H. R acke. ``Optimal oblivious routing in polynomial time," In Proceedings of the 35th ACM Symposium on the Theory of Computing, 2003.
 
@@
 
-\bibitem{networking:lp}
-O. Goldschmidt. ``ISP Backbone Traffic Inference Methods to Support Traffic Engineering," In Internet Statistics and Metrics Analysis (ISMA) Workshop, San Diego, CA, December 2000.
+\bibitem{ASimpleMethodBalancing05ICCCN}
+Y. Li, J. Harms, R. Holte. ``A simple method for balancing network utilization and quality of routing,'' in Proc. of ICCCN, 2005.
 
-\bibitem{networking:bayesian}
-C. Tebaldi and M. West. ``Bayesian Inference of Network Traffic Using Link Count Data," J. of the American Statistical Association, June 1998.
+\bibitem{TrafficOblivious07CommuMagazine}
+M. Kodialam, T. V. Lakshman, S. Sengupta. ``Traffic-Oblivious Routing for Guaranteed Bandwidth Performance,'' IEEE Communications Magazine, vol. 45(4), 46--51, 2007.
 
-\bibitem{networking:time}
-J. Cao, D. Davis, S. Vander Weil, and B. Yu. ``Time-Varying Network Tomography," J. of the American Statistical Association, 2000.
+\bibitem{ObliviousHighVariable08TON}
+M. Kodialam, T. V. Lakshman, J. B. Orlin, S. Sengupta. ``Oblivious Routing of Highly Variable Traffic in Service Overlays and IP Backbones,'' IEEE/ACM Trans. on Netw., vol. 17(2), 459--472, 2008.
 
-\bibitem{networking:minimize}
-Harald R\"{a}cke. ``Minimizing congestion in general networks," In Proceedings of the 43rd IEEE Symposium on Foundations of Computer Science (FOCS), 2002. Co-Winner of Best Paper Award.
-
-\bibitem{networking:polynomial}
-Y. Azar, E. Cohen, A. Fiat, H. Kaplan, and H. R ̈acke. ``Optimal oblivious routing in polynomial time," In Proceedings of the 35th ACM Symposium on the Theory of Computing, 2003.
+\bibitem{ObliviousHoseModel11TON}
+M. Kodialam, T. V. Lakshman, J. B. Orlin, S. Sengupta. ``End-to-End Restorable Oblivious Routing of Hose Model Traffic," IEEE/ACM Trans. on Netw., vol. 19(4), 1223--1236, 2011.
 
 \bibitem{networking:gravity}
-M.Roughan, A.Greenberg, C.Kalmanek, M.Rumsewicz, J.Yates, and Y.Zhang.
+M.
+Roughan, A.
+Greenberg, C.
+Kalmanek, M.
+Rumsewicz, J.
+Yates, and Y.
+Zhang.
 ``Experience in measuring backbone traffic variability: models, metrics, measurements, and meaning," InProceedings of the 2nd Internet Measurement Workshop.
-ACM, 2002
+ACM, 2002.
 
-\bibitem{networking:dmp}
-A.P. Bianzino, L. Chiaraviglio, M. Mellia, ``Distributed algorithms for green IP networks," in: IEEE INFOCOM Workshop on Green Networking and Smart Grid, 2012
+\bibitem{PowerAware08Infocom} J.~Chabarek, J.~Sommers,
+    P.~Barford, C.~Estan, D.~Tsiang, and S.~Wright,
+  ``{P}ower {A}wareness in {N}etwork {D}esign and {R}outing,'' in \emph{Proc.
+  of IEEE INFOCOM}, 2008, pp. 457--465.
 
-\bibitem{networking:hopbyhop}
-C. Hou, F. Zhang, A. F. Anta, L. Wang, and Z. Liu. ``A Hopby-hop Energy Efficient Distributed Routing Scheme," in Proc. of Greenmetrics Workshop, 2013.
+\bibitem{networkflow93book}
+R. K. Ahuja, T. L. Magnanti, J. B. Orlin. Network flows: theory, algorithms, and applications. Prentice Hall, Feb., 1993.
 
 \bibitem{networking:yens}
-Yen, Jin Y. ``Finding the k Shortest Loopless Paths in a Network," Management Science 17 (11), 1971
+Yen, Jin Y. ``Finding the k Shortest Loopless Paths in a Network," Management Science 17 (11), 1971.
 
 \bibitem{networking:abilene}
-``Abilene Core Topology," [Online], Available: https://itservices.
-stanford.edu/service/network/internet2/abilene
+``Abilene Core Topology," [Online], Available:\\ https://itservices.stanford.edu/service/network/internet2/abilene
 
 \bibitem{networking:geant}
-``Network Topology," [Online], Available: http://geant3.archive.ge
-ant.net/Network/NetworkTopology/pages/home.aspx
+``Geant Topology," [Online], Available:\\ http://geant3.archive.geant.net/Network/NetworkTopology/pages/home.aspx
 
 \bibitem{networking:cernet2}
-``Cernet2 Topology," [Online], Available: http://www.edu.cn/20060111
-/3170220.shtml
+``CERNET2 Topology," [Online], Available:\\ http://www.edu.cn/20060111/3170220.shtml
 
@@
 \begin{proof}
-Fig. \ref{figure_circle_and_clique} shows the 6-nodes cycle and clique topologies. We label three links $l_{ab}$, $l_{cd}$ and $l_{ef}$
-for our proof, let $cap_{ab}$, $cap_{cd}$ and $cap_{ef}$ be their link capacities. Now a arbitrary traffic
-comes, we compute the optimal routing and forward the demand on the topologies, let $dem_{ab}$, $dem_{cd}$
-and $dem_{ef}$ be the traffic on each link. Without loss of generality, we say the link $l_{ab}$ is the
-bottleneck, namely the link with MLUR.
+We compute the optimal routing for some arbitrary TM and forward the demands on the topologies. Let $d_l$ be the 
+traffic on link $l$, and $cap_l$ be the capacity of link $l$. For circles and cliques are highly homomorphic,
+without loss of generality we say the link $l_1$ is the bottleneck, i.e. the link with MLUR.
 
-Now let's consider the robust routing. When the routing changes, the traffic on each link also changes.
-We image a simple situation, just forward the traffic from one link to another path base on the optimal
-routing, and the link utilization of links on the path will increase, and accordingly the link
-utilization of former link will reduce to 0. Obviously, the routing must have a worse performance than
-the optimal robust routing, so its upper bound also is the bound of minimum OPRE.
+Routing can be adjusted. We image a simple situation that forward the traffic from one link to another path base
+on the routing computed above. The link utilization of links on the path will increase, while accordingly the 
+link utilization of adjusted link will reduce to 0. Obliviously, the adjusted routing must not be better than
+the optimal robust routing, so its upper bound also is the bound of minimum OPRE. Following proof is according 
+to which the adjusted link is, and which the bottleneck is after adjusting routing.
 
-\begin{figure}[!t]
-\centering
-\vspace*{0.1in}
-\subfloat[Circle]{\includegraphics[width=4cm]{circle}
-\label{subfiga}}
-\hfill
-\subfloat[Clique]{\includegraphics[width=4cm]{clique}
-\label{subfigb}}
-\caption{Circle and Clique topology of 6 nodes}
-\label{figure_circle_and_clique}
-\vspace*{0.1in}
-\end{figure}
-
-For Case \Rmnum{1}.\Rmnum{1}, the adjusted link may be $l_{cd}$, the new bottleneck still be $l_{ab}$.
-The traffic on $l_{ab}$ is increased by the origin traffic on link $l_{cd}$, So we compute OPRE by:
+For Case \Rmnum{1}.\Rmnum{1}, the adjusted link is $l_2$, the new bottleneck still be $l_1$. Because $l_1$ is the 
+bottleneck before adjusting, so we have inequation:
 
 \begin{equation}
-\label{equation_A_1_1_1}
-\frac {\frac{dem_{ab} + dem_{cd}}{cap_{ab}}} {\frac{dem_{ab}}{cap_{ab}}} = 1 + \frac{dem_{cd}}{dem_{ab}}
+\label{inequation_A_1_1_1}
+\frac {d_2} {cap_2} \leq \frac {d_1} {cap_1} \Longleftrightarrow \frac {d_2}{d_1} \leq \frac{cap_2}{cap_1}
 \end{equation}
 
-Because the old bottleneck is $l_{ab}$, so we have inequation:
-
-\begin{equation}
-\label{inequation_A_1_1_2}
-\frac {dem_{cd}} {cap_{cd}} < \frac {dem_{ab}} {cap_{ab}}
-\end{equation}
-
-From Ineq. (\ref{inequation_A_1_1_2}) we get:
-
-\begin{equation}
-\label{inequation_A_1_1_3}
-\frac {dem_{cd}} {dem_{ab}} < \frac {cap_{cd}} {cap_{ab}}
-\end{equation}
-
-So we have OPRE in Case \Rmnum{1}.\Rmnum{1} combined by Eq. (\ref{equation_A_1_1_1}) and Ineq. (\ref{inequation_A_1_1_3}):
+we compute OPRE for Case \Rmnum{1}.\Rmnum{1} combined with Ineq. (\ref{inequation_A_1_1_1}):
 
@@
 \label{inequation_A_1_1_result}
-1 + \frac {dem_{cd}} {dem_{ab}} < 1 + \frac {cap_{cd}} {cap_{ab}}
+\frac {\frac{d_1 + d_2}{cap_1}} {\frac{d_1}{cap_1}} = 1 + \frac{d_2}{d_1} \leq 1 + \frac{cap_2}{cap_1}
 \end{equation}
 
-For Case \Rmnum{1}.\Rmnum{2}, the adjusted link also be $l_{cd}$, but the new bottleneck may be $l_{ef}$.
-Computing the OPRE similar as above:
+For Case \Rmnum{1}.\Rmnum{2}, the adjusted link also be $l_2$, but the new bottleneck may be $l_3$.
+Because $l_1$ is the bottleneck before adjusting, so we have inequations:
 
 \begin{equation}
-\label{equation_A_1_2_1}
-\frac {\frac{dem_{ef} + dem_{cd}}{cap_{ef}}} {\frac{dem_{ab}}{cap_{ab}}} =
-\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac {dem_{cd} * cap_{ab}}{dem_{ab} * cap_{ef}}
+\label{inequation_A_1_2_1}
+\frac {d_3} {cap_3} \leq \frac {d_1} {cap_1} \Longleftrightarrow \frac {d_3 * cap_1}{d_1 * cap_3} \leq 1
 \end{equation}
-
-Because the old bottleneck is $l_{ab}$, so we have Ineq. (\ref{inequation_A_1_1_2}) and :
 
@@
 \label{inequation_A_1_2_2}
-\frac {dem_{ef}} {cap_{ef}} < \frac {dem_{ab}} {cap_{ab}}
+\frac {d_2} {cap_2} \leq \frac {d_1} {cap_1} \Longleftrightarrow \frac {d_2 * cap_1}{d_1} \leq cap_2
 \end{equation}
 
-So we get inequation from Ineq. (\ref{inequation_A_1_2_2}):
-
-\begin{equation}
-\label{inequation_A_1_2_3}
-\frac {dem_{ef} * cap_{ab}} {dem_{ab} * cap_{ef}} < 1
-\end{equation}
-
-Also from Ineq. (\ref{inequation_A_1_1_2}) we have :
-
-\begin{equation}
-\label{inequation_A_1_2_4}
-\frac {dem_{cd} * cap_{ab}} {dem_{ab}} < cap_{cd}
-\end{equation}
-
-Combine Eq. (\ref{equation_A_1_2_1}), Ineq. (\ref{inequation_A_1_2_3}) and Ineq. (\ref{inequation_A_1_2_4}), we have OPRE in Case \Rmnum{1}.\Rmnum{2}:
+We compute OPRE for Case \Rmnum{1}.\Rmnum{2} combined with Ineq. (\ref{inequation_A_1_2_1}) and Ineq. (\ref{inequation_A_1_2_2}):
 
@@
 \label{inequation_A_1_2_result}
-\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac {dem_{cd} * cap_{ab}}{dem_{ab} * cap_{ef}}
-< 1 + \frac {cap_{cd}}{cap_{ef}}
+\frac {\frac{d_3 + d_2}{cap_3}} {\frac{d_1}{cap_1}} =
+\frac {d_3 * cap_1}{d_1 * cap_3} + \frac {d_2 * cap_1}{d_1 * cap_3} \leq 1 + \frac{cap_2}{cap_3}
 \end{equation}
 
-For Case \Rmnum{2}, the adjusted link may be $l_{ab}$, namely the old bottleneck link, the new bottleneck
-maybe $l_{ef}$. Computing the OPRE similar as above:
-
-\begin{equation}
-\label{equation_A_2_1}
-\frac {\frac{dem_{ef} + dem_{ab}}{cap_{ef}}} {\frac{dem_{ab}}{cap_{ab}}} =
-\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac{cap_{ab}}{cap_{ef}}
-\end{equation}
-
-Becuase the old bottleneck has the maximum link utilization, so combine Ineq. (\ref{inequation_A_1_2_3}) and Eq. (\ref{equation_A_2_1}) we obtain OPRE in Case
-\Rmnum{2}:
+For Case \Rmnum{2}, the adjusted link is $l_1$, namely the old bottleneck link, the new bottleneck
+maybe $l_3$. Computing the OPRE combined with Ineq. (\ref{inequation_A_1_2_1}):
 
@@
 \label{inequation_A_2_result}
-\frac {dem_{ef} * cap_{ab}}{dem_{ab} * cap_{ef}} + \frac{cap_{ab}}{cap_{ef}} < 1 + \frac{cap_{ab}}{cap_{ef}}
+\frac {\frac{d_3 + d_1}{cap_3}} {\frac{d_1}{cap_1a}} =
+\frac {d_3 * cap_1}{d_1 * cap_3} + \frac{cap_1}{cap_3} \leq 1 + \frac{cap_1}{cap_3}
 \end{equation}
@@
 \label{inequation_A_result}
-1 + \max \{\frac{cap_{cd}}{cap_{ab}}, \frac{cap_{cd}}{cap_{ef}}, \frac{cap_{ab}}{cap_{ef}} \} < 1 + \frac{\max_{l \in E} cap_{l}}{\min_{l \in E} cap_{l}}
+1 + \max \{\frac{cap_2}{cap_1}, \frac{cap_2}{cap_3}, \frac{cap_1}{cap_3} \} \leq 1 + \frac{\max_{l \in E} cap_{l}}{\min_{l \in E} cap_{l}}
 \end{equation}
@@
 \begin{proof}
-The spanning tree of circle is the topology which lose one link. In Appendix. A, when we consider the robust routing, we adjust the traffic
-on one link to another path, it is similar that we switch off the link and forward the traffic to some other path. The complete proof is
-almost the same with Appendix. A.
+The spanning tree of circle is the topology which lose one link. 
+We regard this link as the adjusted link mentioned in Appendix. A. The complete proof is almost the same with Appendix. A.
 \end{proof}
@@
 \begin{proof}
-Every link in the spanning tree will split the graph to two components, the flow between them must need trace this link.
-we say the bottleneck link is $l_{ab}$ for optimal routing on the origin topology, and let $l_{ef}$ be the bottleneck link for
-the robust routing on the spanning tree. Other symbols are consistent with Appendix. A. So we have OPRE:
+Suppose clique has $n$ nodes, every link in the spanning tree will split the tree to two components. 
+Let $l_3$ be the bottleneck in the spanning tree, Let $S$, $D$ be the node sets of two components, and every flow 
+between $S$ and $D$ always trace on $l_3$. Without loss of generality, we say $l_1$ is the bottleneck link for the 
+optimal routing on the original clique.
+
+Because the $l_1$ is the bottleneck link, we have:
 
 \begin{equation}
-\label{equation_C_1}
-    \frac{\frac{\sum_{(i,j) \in E} dem_{ij}}{cap_{ef}}}{\frac{dem_{ab}}{cap_{ab}}} = \frac{cap_{ab}}{cap_{ef}} \sum_{(i,j) \in E} \frac{dem_{ij}}{dem_{ab}}
+\label{ineqaution_C_1}
+    \frac{d_l}{cap_l} \leq \frac{dem_1}{cap_1} \Longleftrightarrow \frac{d_l * cap_1}{d_1} \leq cap_l,  \forall l \in (S,D)
 \end{equation}
 
-Because the $l_{ab}$ is the bottleneck link, we have:
+The $l_3$ is the bottleneck finally, we have OPRE combined with Ineq. (\ref{ineqaution_C_1}):
 
@@
 \label{ineqaution_C_2}
-    \frac{dem_{ij}}{cap_{ij}} < \frac{dem_{ab}}{cap_{ab}}, \forall (i,j) \in E
+    \frac{\frac{\sum_{l \in (S,D)} d_l}{cap_3}}{\frac{d_1}{cap_1}} = \frac{cap_1}{cap_3} \sum_{l \in (S,D)} \frac{d_l}{d_1}
+     \leq \sum_{l \in (S,D)} \frac{cap_l}{cap_3}
 \end{equation}
 
-\begin{equation}
-\label{ineqaution_C_3}
-    \frac{dem_{ij} * cap_{ab}}{dem_{ab}} < cap_{ij}, \forall (i,j) \in E
-\end{equation}
-
-So we have OPRE:
-
-\begin{equation}
-\label{ineqaution_C_4}
-    \frac{cap_{ab}}{cap_{ef}} \sum_{(i,j) \in E} \frac{dem_{ij}}{dem_{ab}} < \sum_{(i,j) \in E} \frac{cap_{ij}}{cap_{ef}}
-\end{equation}
-
-And we know that, the amount of $l_{ij}$ between two parts must less than $\frac{n^2}{2}$, so OPRE must lower than:
+And we know that, the amount of $l$ must less than $\frac{n^2}{2}$ (equal to $\frac{n^2}{2}$ if $|S| == |D| == \frac{n}{2}$), 
+so OPRE must lower than:
 
@@
 \label{ineqaution_C_result}
-    \sum_{(i,j) \in E} \frac{cap_{ij}}{cap_{ef}} < \frac{n^2}{2} \frac{\max_{l \in E} cap_l}{\min_{l \in E} cap_l}
+    \sum_{l \in (S,D)} \frac{cap_l}{cap_3} \leq \frac{n^2}{2} \frac{\max_{l \in (S,D)} cap_l}{\min_{l \in (S,D)} cap_l}
 \end{equation}

### 2015-02-06 experiment/cplex/len_path.py

@@ -14,9 +14,11 @@ color_type = {'base':'r--', 'new':'b-'}
 remove_type = {'base':'DMP', 'new':'REAR'}
 result_file_template = "path_stretch_%s_%s.txt"
 
-line_list = []
-label_list = []
-for t in ['cernet2']:
+line_list_1 = []
+line_list_2 = []
+label_list_1 = []
+label_list_2 = []
+for t in ['geant']:
     for w in ['1.5', '2.5', '3.5']:
         f = open(result_file_template % (t, w))
         line = f.readline()
@@ -45,13 +47,13 @@ for t in ['cernet2']:
         l1, = plt.plot(x[:topology_x_range[t]], a_mine[:topology_x_range[t]], color_type['new']+topology_line_type[w], ms=10)
         l2, = plt.plot(x[:topology_x_range[t]], a_base[:topology_x_range[t]], color_type['base']+topology_line_type[w], ms=10)
 
-        label_list.append(w + '-' + remove_type['base'])
-        label_list.append(w + '-' + remove_type['new'])
+        label_list_1.append(r'$%s\ \omega=%s$' % (remove_type['new'], w))
+        label_list_2.append(r'$%s\ \omega=%s$' % (remove_type['base'], w))
         
-        line_list.append(l1)
-        line_list.append(l2)
+        line_list_1.append(l1)
+        line_list_2.append(l2)
 
-    plt.legend(line_list, label_list, loc=1, fontsize=15)
+    plt.legend(line_list_2+line_list_1, label_list_2+label_list_1, loc=1, fontsize=13)
     plt.xlabel('Removing Links\n(%s)' % topology_letter[t], fontsize=22)
     plt.ylabel('Path Stretching Ratio', fontsize=22)
     
@@ -59,6 +61,6 @@ for t in ['cernet2']:
     pp.savefig(fig1, bbox_inches='tight')
     pp.close()
 
-    #plt.show()
+    plt.show()
 
 

### 2015-02-06 experiment/plot/exp1_power.py

@@ -4,7 +4,7 @@ import matplotlib.pyplot as plt
 import matplotlib.ticker as tic
 from matplotlib import rc
 
-t = 'cernet2'
+t = 'geant'
 
 
 font = {'size':20}
@@ -29,8 +29,10 @@ power_models = {155.0:60, 1240.0:100, 2480.0:140, 9920:174}
 power_model = [60, 100, 140, 174]
 
 
-line_list = []
-label_list = []
+line_list_1 = []
+line_list_2 = []
+label_list_1 = []
+label_list_2 = []
 #for t in ['abilene', 'geant', 'cernet2']:
 for w in ['1.5', '2.5', '3.5']:
     # compute the total power of topology
@@ -138,21 +140,21 @@ for w in ['1.5', '2.5', '3.5']:
     l1, = ax1.plot(power_base_saving_ratio[:topology_x_range[t]], base[:topology_x_range[t]], color_type['base']+w_line_type[w], ms=10)
     l2, = ax1.plot(power_saving_ratio[:topology_x_range[t]], new[:topology_x_range[t]], color_type['new']+w_line_type[w], ms=10)
 
-    label_list.append(remove_type['base'] + '-' + w)
-    label_list.append(remove_type['new'] + '-' + w)
+    label_list_1.append(r'$%s\ \omega=%s$' % (remove_type['base'], w))
+    label_list_2.append(r'$%s\ \omega=%s$' % (remove_type['new'], w))
     
-    line_list.append(l1)
-    line_list.append(l2)
+    line_list_1.append(l1)
+    line_list_2.append(l2)
 
 plt.xlabel('Power Saving Ratio (%) \n '+'(%s)' % topology_letter[t], fontsize=22)
 plt.ylabel('OPRE', fontsize=22)
 #plt.legend([l1, l2], ['TMP, w=1.5, 2.0, 2.5...', 'ERLU, w=1.5, 2.0, 2.5...'], loc=2)
-plt.legend(line_list, label_list, loc=2, fontsize=16)
+plt.legend(line_list_1+line_list_2, label_list_1+label_list_2, loc=2, fontsize=15)
 
 ax1.set_yscale('log')
 ax1.set_ylim([1,y_lim[t]])
 ax1.get_yaxis().set_major_formatter(tic.ScalarFormatter())
-ax1.yaxis.set_minor_formatter(FormatStrFormatter("%0.1f"))
[…]

### 2015-02-06 experiment/plot/exp2_sort.py

@@ -2,7 +2,7 @@ from matplotlib.backends.backend_pdf import PdfPages
 from matplotlib import rc
 import matplotlib.pyplot as plt
 
-t = 'geant'
+t = 'cernet2'
 
 font = {'size':20}
 rc('font', **font)
@@ -56,7 +56,7 @@ for i in ['1.5', '2.5', '3.5']:
     l1, = plt.plot([base[i][ii*10] for ii in xx], xx, 'r--'+label[i], ms=10)
 
     line_list.append(l1)
-    line_label.append('DMP-%s' % i)
+    line_label.append(r'$DMP\ \omega=%s$' % i)
 
 line2 = None
 for i in ['1.5', '2.5', '3.5']:
@@ -71,20 +71,20 @@ for i in ['1.5', '2.5', '3.5']:
     l1, = plt.plot([new[i][ii*10] for ii in xx], xx, 'b-'+label[i], ms=10)
 
     line_list.append(l1)
-    line_label.append('REAR-%s' % i)
+    line_label.append(r'$REAR\ \omega=%s$' % i)
 
 #plt.axis([0, 6, 0, 20])
 
 print (base['3.5'][500] - base['2.5'][500]) / (new['3.5'][1000] - new['2.5'][0])
 
 plt.ylabel('CDF (%)', fontsize=22)
-plt.xlabel("OPRE\n(%s)" % topology_letter[t], fontsize=22)
-plt.legend(line_list, line_label, loc=4, fontsize=16)
+plt.xlabel("Performance Ratio\n(%s)" % topology_letter[t], fontsize=22)
+plt.legend(line_list, line_label, loc=4, fontsize=15)
 
 pp = PdfPages('exp2_sort_%s.pdf' % t)
 pp.savefig(fig1, bbox_inches='tight')
 pp.close()
 
-#plt.show()
+plt.show()
 #plt.savefig('exp2_sort_cernet2.png', bbox_inches='tight')
 
